% \section{Annotation Chapter Thirty-Seven}
\section*{Annotations}

\subsection*{Vivenna Wanders, Then Is Confronted by a Thief Who Takes Her Dress}

The next few Vivenna chapters are short. I wanted to convey that she’s on the streets for a time, but didn’t want us to have to wallow in her problems. I’ve seen books do that quite well, and I don’t want this novel to focus on it. (If you’re interested in one that does it well, Paula Volsky’s \textit{Illusion} has a nice section about what it’s like to be a noblewoman who is forced to live on the streets.)

Instead, these chapters are the transition chapters for Vivenna’s character. The representation of her going as low as she can go, so that later she can begin to rebuild. The dress was a problem—it was way too distinctive, and it could sell for enough that she wouldn’t have to live on the streets. She could buy something cheap and modest, then put herself up in an inn. So, naturally, it had to get stolen.

I didn’t want to strip her all the way, though. We’ve been through enough of that with Siri, and I really didn’t want to go there in this situation. Vivenna can be brought down to the lows she needs to reach without having to be raped by a random man in an alley. (Personally, I think that rape is overused in a lot of fiction.)

\subsection*{Vivenna Hides Her Breath in a Shawl}

This has been possible from the beginning, and if Denth had truly been on her side, he would have admitted that there’s a way she could get rid of her Breaths. What she would need to do is Awaken something with a one-Breath Command. There are some. They don’t \textit{do} much, but you can Awaken a very tiny scrap of cloth tied into the shape of a person with a very simple Command. That takes one Breath.

Next, you put the rest of your Breath into another object. Then you get that one Breath back and go hunting for a Drab to give it to. Then you take the rest of your Breath back from the object. From there, you can repeat the process if you want to. Vivenna could get rid of the Breaths one by one.

Of course, Denth didn’t want \textit{that} to happen. He was coveting those Breaths. What he said was intended to sound like an innocent mistake. Many people unfamiliar with Awakening would make that mistake, so if Vivenna learned the truth later, he wouldn’t look suspicious.



