% \section{Annotation Chapter Fifty}
\section*{Annotations}

\subsection*{Lightsong and Blushweaver Banter One Last Time}

Lightsong wonders if maybe he was a prude in his former life. I can answer this—he was indeed. That’s why he’s always so critical of Blushweaver’s clothing choices. That and the fact that he’s in love with her and feels a little jealous at how flagrantly she shows her body and attracts the attention of so many men. These are little things; he wouldn’t even mention them to others. But he does feel them.

We get some final verbal sparring from the two of them. I wanted to do this to give a nod to the earlier portions of the book; we haven’t gotten this from them in quite a long time. However, I also wanted it to feel forced. I was tempted to rewrite this scene a couple of times until the most amusing lines in the book came here, in this chapter, but in the end I chose to go for something with a little more tension in it. Something that felt contrived, like they were trying too hard—which, indeed, they are.

Beyond that, outside of the banter, they both make some very astute comments—and I think their wisdom in the moment undermines any random joking. Lightsong mentions how ridiculous everything is, and can finally point out and prove what he’s been saying all along—that the rest of the pantheon is more useless than he is. Blushweaver, however, probably makes her most astute comment in the book by explaining to Lightsong just why everyone looks up to him so much.

You set yourself above them, Lightsong, and through your mockery—which they know to be true, deep down—you earn their grudging respect. That puts you apart from them. In a way, he’s become the greatest leader of the pantheon in its current incarnation, all by avoiding contact with most of them and by being bitingly sarcastic when he does meet them.

\textcolor{red}{
\subsection*{Siri Gets Taken by the Priests}
}

\textcolor{red}{
What’s going on here behind the scenes is that the priests know what is likely to happen at the Court Assembly. The declaration of war is going to come, and they’re truly worried for Siri’s safety. They take her into custody because they anticipate riots and maybe even an attack on the Court of Gods. They want her taken and kept safe.
}

\textcolor{red}{
Bluefingers is, of course, aware of this. But he thinks that their taking her captive is because they’re suspicious and might know of his plans. That forces his hand, and when Lightsong decides to forestall the vote, Bluefingers gets really worried. So he puts things into motion and grabs Blushweaver from her palace, then seizes the God King’s palace and Siri.
}

\subsection*{Vivenna and Vasher Watch the Vote}

With this chapter, I wanted to bring together another focus chapter, a bookend—so to speak—with the one earlier in the book where everyone came to the court when Siri was first shown off. If you recall, that was the first time Vivenna saw Vasher, and also the first time we had all of the viewpoint characters together in one location.

Now we’re back, kind of. Siri is here in this chapter, but she’s pulled away before she can make it all the way to the arena. It’s the best I could do, under the circumstances, as I knew I needed to launch us into the “Brandon Avalanche” after this chapter. That meant Siri getting taken captive.

\subsection*{Lightsong Refuses to Vote}

I think this is appropriate for him. He doesn’t do what they want to do, or even what they fear he will do. He just walks away to think some more.

He’s frustrating like that.



