\section*{Annotations}

\subsection*{Vasher Watches Siri}

We get back to Vasher. Showing his viewpoints in the book was tricky. I wanted him to remain an enigma—I didn’t want you to know if you were rooting for him or not. But I did want you to think he was interesting.

\subsection*{Nightblood Origins}

I’ve been wanting to do a book with a talking sword for some time. Sentient objects are a favorite theme of mine from fantasy books I’ve read, and I think you’ll probably see more of them in future books from me.

The magic sword is its own archetype in fantasy, even if there haven’t been any good magic sword books among the big fantasy novels of recent years. Perhaps that’s because Saberhagen and Moorcock did such a good job with their books in the past. I’m not sure. (I don’t count appearances of magic swords like Callandor in the \textit{Wheel of Time}. I mean books with major parts played by swords.)

Anyway, that’s a tangent, and I’m certain that half the people reading this can think of examples and exceptions to what I just said. Either way, this is a theme I wanted to tackle, and the magic system of this world lent me the opportunity.

Nightblood is another favorite character of the readers. I think his personality works the best out of any non-viewpoint character I’ve ever written. He doesn’t get that much dialogue in the book, but it is so distinctive that it just works.

\subsection*{Vasher Meets Bebid the Priest for Food}

Restaurants. They didn’t really exist in a lot of medieval cultures. Now, most of my books don’t take place in medieval times—they’re more preindustrial uchronias, late renaissance if you will. \textit{Warbreaker} is no exception.

T’Telir seems the kind of place that would have restaurants. Places to sit idly, eating and chatting. It is a successful port city with a lot of trade and a great deal of wealth. There’s even something of a middle class, another concept that didn’t exist during a lot of periods in time.

Originally, I had Vasher make an oblique comment about Bebid’s daughter as a way to get him to talk. However, I shied away from this in later drafts, moving to more nebulous indiscretions instead. I felt that a comment about a daughter might sound too much like kidnapping on Vasher’s part, even though I was thinking that his daughter had done something embarrassing that, if revealed, would get the priest into trouble.

\subsection*{Lightsong’s Dream}

The Lightsong sections received two major upgrades during the last few drafts of the novel. The first was the enhancement of his memories of his dreams. We don’t get to see the dreams, just their effect on him.

In the original draft, these dreams were far less ominous, particularly at the beginning of the book. My agent complained that the book felt like it lacked direction, particularly in the Lightsong sequences, and asked me to find a way to make it more tense. He didn’t care if Lightsong joked; he just wanted to feel a tension underneath. A sense that all was not right.

The dreams came from this. Originally, Lightsong just dreamed about the ship leaving the port. In the later drafts, I added him remembering more in this chapter—the city on fire, the flames causing a red reflection on the ocean.

This actually wasn’t a change to the dream. That’s what I’d intended him to have dreamed; I just originally had him forgetting. I didn’t start getting into the violent dreams until much later in the book, one chapter in particular. But because of Joshua’s requests, I moved the sense of danger up from those later chapters to here to begin foreshadowing earlier.

\subsection*{Lightsong’s Wisecracks}

The other major Lightsong revision happened in the form of a humor upgrade. My editor didn’t complain about the same thing as my agent—instead, my editor wanted to laugh more. He wanted more witty lines from Lightsong. I resisted this at first, as I worried that making him too snappy would undermine his internal conflicts. I wanted him to be droll, but not necessarily brilliant.

Eventually, however, my editor prevailed upon me. He was always of the opinion that a few extra witty lines wouldn’t undermine anything. I have to say, I like the lines, and I’m mostly glad to have them. But I do worry about overloading the humor in Lightsong’s chapters, and therefore diluting his internal conflict.


