% \section*{Annotation Chapter Eight}
\section*{Annotations}

\subsection*{Siri Wakes Up Untouched, Then Explores the Palace}

These Siri chapters presented a little bit of a problem to me in that I generally focus my writing around conversations. A given chapter will have some action and description, but usually the series of scenes revolves around important discussions between characters.

But in the palace during the Jubilation, Siri has almost nobody to talk to. She just doesn’t have anything to do. A note to aspiring writers: A character not having anything to do is \textit{bad}. You want action, motion, and conflict in your stories. That’s what keeps them moving and interesting.

But in this case, Siri’s lack of direction was necessary to make the plot work. In these chapters, Siri is just reacting—trying to stay afloat in a world very different from her own. So I had to focus on other ways to make the scenes interesting.

A lot of times, in writing, needs like this end up defining aspects of the books. I hadn’t intended the palace to work as it did—with each room being modular, any of them able to transform into any type of room. I intended to give Siri her own set of chambers, as might be expected in a situation like this.

But when I reached this point in the book, the chapter was looking dull, and I knew I needed some little twist to the palace to make it original enough to hold Siri’s—and the reader’s—attention here. It’s a very small thing, but I think that one change added a lot to the chapter, and therefore the book.



