% \section{Annotation Chapter Forty-Eight}
\section*{Annotations}

\subsection*{Siri and Susebron Decide to Reveal What Has Been Done to Him}

Another short chapter here. You probably have guessed that we’re beginning the push toward the ending. Now that Siri and Susebron have gone about as far as they can (both in their relationship and in their personal growth) without being free, it’s time for them to begin pushing against their boundaries.

As I said before, I think their relationship is one of the most pure and romantic that I’ve ever written. For some reason, they just \textit{fit} together. I tried to explain it in the narrative in the beginning of this chapter, and I think I did a good job. However, it’s more than that—it’s just a feeling that these two belong with each other. Kind of like when one of your friends shows off the person they’ve been dating, and you just feel that it’s a good match.

I don’t think I ever got this far in their relationship when I wrote the original book, \textit{Mythwalker}. One of the reasons I decided to go back to the story was because I’d always missed writing an ending for Siri and Susebron. (Though I think he had a different name back then.) [\textit{Editor’s note: In the }Mythwalker\textit{ draft, he was just called the Emperor.}] I did a much, much better job of the story this time as well; I’ve increased in skill as a writer. I was finally able to tell this story and bring it to a conclusion, something I’d been waiting for years to do. I’m glad I finally found the time, even if writing standalone novels isn’t the fastest way to bestsellerdom in fantasy.



