\section*{Annotations}

\subsection*{Siri Sees the God King}

I think this is my favorite plotline of the book. The Siri/God King one, I mean. It’s hard to choose, but this is the one that I felt most interested in. (Though Lightsong’s ending chapters are powerful too.)

I wanted the God King to be an enigma, much like Vasher is, at the beginning of the book. Well . . . that’s not quite true. Right at the beginning, I wanted him to be scary and dangerous. I wanted the reader to perceive him as Siri did.

By now, however, you should be wondering more. Who is he? What are his motives? Is he angry with her or not?

The driving force behind this, actually, is the Lord Ruler. In \textit{Mistborn}, a part of me always felt that he was just a little too stereotypical an evil emperor. True, I worked hard to round him out, particularly through the later books. But writing him made me want to take an evil emperor archetype in a very different direction.

I’ve spoken on the reversals in this book. Well, one thing I realized after the fact is that the novel is—in a lot of ways—about reversals of my own writing. Things I’ve done before, but taken the opposite direction. Almost like I need to react against myself and explore things in new ways, particularly in cases where (like the Lord Ruler) I did things that were more conventional to the genre.

I think that’s why this book has so much resonance with my previous books. Or maybe it doesn’t really, and I’m just seeing something that doesn’t exist. A lot of my ideas in writing, however, come from seeing something done in a movie or a book (or even in one of my own books) and wondering if I could take it a new and different direction. I hope that doesn’t make me feel like I’m repeating myself.

\subsection*{Lightsong Kneels before the God King}

My vote for most thoughtful line of the first chunk of the book? Lightsong’s comment that he’d found that make-believe things were often the only things of substance in people’s lives. (Not quoted directly.)

It’s a little bit cynical, yet somewhat hopeful as well. As Lightsong perceives it, it’s true.

\subsection*{Kalad’s Phantoms}

Kalad used to be Khlad, by the way. I didn’t want his name to sound so Pahn Kahlish, which I signify with the extra \textit{h} sounds to give them an airy feel to their words. I added the mythology of Kalad’s Phantoms to the book late in the process, wishing to give some more depth to the superstitions of the world. And perhaps do some other things too. . . .

\subsection*{Vivenna Sees Vasher}

I’m sorry that we don’t get to see Vasher as much as you all want. I considered adding more chapters in. I considered it several times during several rewrites. In the end, I just decided that his viewpoints had to remain as they were in the early part of the book. If you see too much of what he’s doing, it will give away things I don’t want to give away.

I don’t like having viewpoints that fail to reveal things about the characters and their emotions and plans. It feels like I’m lying to the reader when I hide things the viewpoint character knows. I avoid it when I can (though I can’t always—reference Kelsier in \textit{Mistborn}).

Either way, I just decided to keep Vasher as he was, with only occasional appearances.

\subsection*{Life Sense as Part of the Magic}

The ability of the Heightenings and Breath to give people an added dose of life sense was part of my attempts to make Awakening, as a magic system, feel more visceral and real. Allomancy is a great magic system, but I wanted a different feel here. In Allomancy, the powers granted are more like superpowers; with Awakening, I wanted something that felt . . . well, closer to what people already do.

Perfect pitch and perfect color recognition are two things that I think resonate this way; the ability to bring inanimate objects to life may seem wildly superpowerish, but I think it’s a part of our own superstition and mythology—or at least the superstition and mythology of our past. Life from things inanimate, like spontaneous generation, was long assumed as something real. Witches were often thought to be able to bring sticks or bundles of cloth to life.

I think that there’s still a lot of superstition in our modern world regarding how it feels to have someone watching you. We are more aware of our surroundings, sometimes, than we realize. I think we attribute a supernatural connection to some of these things. Who knows? Maybe there is one. I don’t know, perhaps I’ve got a bit of it myself.

Enhancing this and making it part of the magic was a way to get the visceral feel I was looking for. It also plays off the idea that by giving up your Breath, you give up part of your life. The fact that Drabs can’t be noticed by life sense allows me to show that they have taken one more step toward being objects themselves.

BioChroma. It turns objects into living things, but turns living things into objects as well.




