\section{Annotation Chapter Nineteen}

\subsection*{Clod Arrives with Jewels}

Early on in the development process, I knew that I wanted to have a Lifeless as a side character. They’re such an interesting part of the world—in fact, they’re a big part of the foundation of the setting, or at least what made me want to write it.

That meant having a Lifeless on Denth’s team, and Clod as a character fit into place quite easily. I had worried about how to make Jewels distinctive in the team, after having Denth and Tonk Fah establish themselves for some twenty chapters before Jewels even makes an appearance. Working with that, I realized that by making her the Lifeless handler, I could add something unique to her—and to the team.

Denth knew that Vivenna wouldn’t react well to there being a Lifeless on the team. That’s part of why he kept Jewels away for so long. (In fact, when Jewels says, “Who’s that woman?” in regards to Vivenna, it should have been slightly suspicious to you. She knew they had a new employer, and she should have made the connection. Indeed, she did. Denth had specifically ordered her to stay away until this moment, as he didn’t want to scare Vivenna off.)

\subsection*{Denth Tells Vivenna to Use Her Breaths}

Don’t forget that Vivenna has a huge wealth of Breath. To most people, anything over one or two Breaths is a huge wealth—and Vivenna has enough to reach the Third Heightening. She’s fully capable of Awakening objects, and while she’s not as powerful as Vasher in Breath right now, she could learn quite quickly. (The more Breath you hold, the easier it is for you to learn how to use it.)



<p></p>
<p>\subsection*{Denth’s Plans}</p>
<p>When I was posting chapters online as I wrote them, I remember one person in my forums noting (upon reading this chapter) that Denth’s plans were a terrible way to help Idris. By attacking supply caravans and creating a crisis in the city, chances are very good that the war factions would be \textit{more} likely to get the others to strike. Desperate times generally give more power to those who are willing to act, even if those actions might lead to even more problems.</p>
<p>This person on the forums is, of course, exactly right. I’m impressed that they caught it, since most everyone else seemed completely taken in by Denth. However, what Denth is doing here is using Vivenna to help continue plots he has long had in motion. He’s lying when he says that he doesn’t know what Lemex was involved in and has only seen pieces. In truth, Lemex was doing what Denth wanted him to—they were Denth’s plans all along.</p>
<p>However, Lemex was beginning to grow more reticent, and Denth was having more trouble manipulating him. Another good reason for the poisoning. (And it took a \textit{lot} of poison to off someone with that much Breath.)</p>
<p>If you’re reading it through again, I hope that Tonk Fah’s line about being able to stow a lot of bodies in the storage space is a creepy line. It’s supposed to be.</p>
<p></p>



