\section{Annotation Chapter Thirty}

\subsection*{Lightsong Tries Pottery}

It’s been a while since one of the gods tried something like this. Lightsong isn’t the first, of course, to wonder at his old life and realize that some of his skills and abilities came with him to his new one. But he’s the first of this generation of gods who has taken any interest in it.

His father was actually a potter, if you’re interested in knowing. As for why he knows nautical terms and mathematics, I’m afraid you’ll have to wait on that. They come up eventually.

The juggling, though . . . well, that’ll just have to remain a mystery.

\subsection*{Lightsong and Blushweaver Visit Hopefinder}

I wanted to show some Returned of different ages; I think it’s important for people to realize that you can be any age when you Return. There are children, babies, grandmothers, and people in their middle years who Return.

Hopefinder is the youngest person at court currently, though there are a couple of other gods who Returned when they were in their teens. It’s hard to tell them from the other gods now, however. (And often, when a god Returns in their middle years, their body transforms to be much more youthful. Not always; it depends on the god.)

Some of Blushweaver’s sparring here should give you a hint that she’s far from the shallow egotist she pretends to be. In a lot of ways, she and Lightsong are perfectly matched, and I imagine this being the reason they ended up spending so much time together. They both have an extreme persona that is almost a parody of the other gods, and for both of them, that persona is but a sliver of who they really are. Blushweaver is more conniving, Lightsong more noble, when you strip everything else away. But they understand each other in a way that I think few people do.



