% \section{Annotation Epilogue}
\section*{Annotations}

\subsection*{The Phantoms Charge Away}

Did they succeed? Yes, they did. The Lifeless were destroyed, and only a couple of the phantoms were lost. That still leaves Hallandren with a very powerful army. Fortunately, Siri and Susebron are the ones in charge of it, so things will be all right for a little while at least.

\subsection*{Vivenna Goes with Vasher}

I was always planning this ending for her. She’s still got a lot of growing she can do as a character, and I think she’ll make for a very interesting heroine in a sequel. She could never return to Idris and face her father; doing so would be returning to a lot of people who expect her to be like she was. But she can’t stay with Siri either. She still hates Hallandren and just wants to be free of it—free where she can calm her fury and really explore who she is now that her life is no longer dominated by the need to go marry the God King.

Life has been very unfair to Vivenna. It’s time for her to live for herself. Here we finally have the last reversal of the book. Siri has become the queen; Vivenna is running away from responsibility, out into the wilds. And it (hopefully) feels very natural for them to be in these roles.

\subsection*{Vasher Explains Some Things, but Leaves Some Things Hidden}

I’m worried about leaving Vivenna’s two questions unanswered. One is pretty obvious—how Vasher can hide how he looks—but the other is unintuitive. I wish I could explain better in the book, as I said above, but I decided in the end to just leave it hanging. It’s a bit of a violation of Sanderson’s First Law, but not a big one. The reason I feel I can get away with it is because Vasher didn’t use his nature as a Returned to solve any problems. It is more a flavoring for his character than it is important to him getting out of danger or fixing things. He could have done everything he needed to in this book without being Returned. So I feel it’s okay not to explain why he can be Returned and not die when he gives away his Breaths.

Can Vivenna change her appearance more? She can indeed. She could actually stoke that fragment of a divine Breath inside of her and start glowing like a Returned. She can’t change her physical features to look like someone else, but she can change her age, her height (within reason), and her body shape (to an extent). It takes practice.

And yes, the scraggly miscreant~\textit{is}~how Vasher sees himself. Not noble and Returned, which is part of how he suppresses his divine Breath.

Events in the second book may change that.

