% \section{Annotation Chapter Forty-Five}
\section*{Annotations}

\subsection*{Lightsong’s Very Short, Two-Paragraph Chapter}

I was tempted to make this annotation the longest in the pile, just for irony’s sake. But I thought that might get boring. So you’ll just have to settle for the only annotation in the batch that’s longer than the chapter it annotates.

I’ve long wanted to do a chapter like this, one that’s just a few sentences in length. (Or even one sentence.) I toyed with it in \textit{Mistborn}, but never found a good place for it. When I was writing this book, it seemed very appropriate here. Something about the rising tension, the need to include a scene from Lightsong, and the poignancy of having a chapter like this right here—following the previous Siri chapter—worked perfectly in the book.

The reason I’m most sad for making Lightsong’s dreams of earlier chapters more violent is that I lose some of the punch of this chapter. Originally, this was the first place he dreamed explicitly of T’Telir burning. Before, there were hints, but he never remembered the actual scene of fire. Then we got here, and it hit with a \textit{pow}.

But the need to keep the tension up earlier outweighed the need to make this scene unique. I have had troubles in the past with my endings being \textit{too} overwhelming, particularly when compared to earlier points in the book. So Joshua’s constant pushing on this point here was very appropriate. I think the book is stronger, even if this chapter is slightly weaker.

And yes, he dreams this while Siri and the God King have sex for the first time. That’s not a coincidence.

\textcolor{red}{
Why does Siri having sex with the God King make Lightsong’s dreams turn more violent? Well, it means that the impending disaster is far more dangerous. If she is with child, then the tragedy of her death is that much greater. Beyond that, her having a child (or being thought to be going to have one) is part of what makes Bluefingers do what he feels he needs to in executing her.
}
\textcolor{red}{
He might have done that anyway, but the actual event of the consummation of the marriage is a powerful turning point in the karma of the city and the future of the world. And Lightsong, who is extra sensitive to these things because of being a Returned, is affected by that change in what is coming in the future.
}



