% \section{Annotation Chapter Twenty-Four}
\section*{Annotations}

\subsection*{Siri Visits the Palace Library}

The Priests here think that Siri is making a play for power, asserting her will in the palace. They wouldn’t have stopped her from reading in the library, if she’d wanted to. Treledees just wants to enforce his will over her and show that she can’t bully the priests. They’re worried about her trying to assert her independence. They assume she already knows the things in the histories that Bluefingers mentions, and so they aren’t concerned about her studying them.

Siri mentions sounding out words as she reads. This was actually a very common thing in most cultures, even literate ones, up until the modern era. People would speak to themselves as they read. Even someone who could read, like Siri, wouldn’t be particularly accustomed to reading. Their society didn’t demand it the same way that ours does.

In her scenes with the God King, I didn’t have her sound out the words for reasons of brevity and clarity. However, if you were there watching, you’d hear her reading out loud each word that the God King wrote on his board.

\subsection*{Susebron and Siri Chat}

This first scene with the two of them chatting is one I’d been looking forward to writing since the beginning. Siri’s scenes become much more interesting to me now that she has someone to talk to. Plus, their relationship is—in my opinion—the most natural romantic relationship I’ve ever written. I’m not sure why that is. They just seem to naturally fall for one another in a way that seems smoother to me than Sarene/Raoden or Vin/Elend.

The priests know about Susebron’s book of stories from his mother, but they haven’t had the heart to take it away from him. They know how much he cherishes it, and they don’t see any real danger in him having it. They think it’s just a memento of his mother.

I worry that Susebron is too innocent in his regard for sex. Some readers like this; others think it’s unrealistic. He’d have had sexual urges, after all. It comes down to the question, how natural is it? If someone had never had sex before, and had never had it explained to them or had friends to talk with about it, would they know what to do? I’ll bet they could figure it out, but I’m not sure it would be something one could simply reason out ahead of time.

Perhaps Susebron’s innocence is a bit of a stretch, but I believe it’s a possible reaction—if not the average one—to his seclusion.



