\section*{Annotations}

A \textit{lot} of people helped me with this book. As you may or may not realize, I posted drafts of the novel online as I was writing it. It was a rather nerve-racking experience in many ways. My goal was to show the process of writing a novel as it happened. As such, I would finish a chapter, spellcheck it, then post it. (Though sometimes I held it for a while, as I eventually wanted to get to posting one chapter a week, and I'd often write two or three a week.)

Why did I do this? Well, for a number of reasons. First off, I'd never seen anyone do it before. I'd seen serialized novels, of course, and I'd seen people post their complete novels once the book was out in stores. I'd never seen anyone post, chapter by chapter, the rough draft of a book that they already had a contract for. This was less serializing a novel and more showing the process. As I finished a new draft, I would post that so that people could compare and see how I tweaked my manuscripts.

I also wanted a free novel on my website so that people could give my work a chance without having to pay for it. I figured that if they liked it, they'd try out my other books (and probably even buy \textit{Warbreaker} when it came out). And if they didn't like it, then at least they hadn't spent any money on it.

The third reason I posted it this way was that I wanted to see what kind of community and feedback I could get for a book while it was being posted, then use that kind of like a writing group. Now, I tend to write fairly clean rough drafts. They're far from perfect, but since I like to outline a lot, I generally know where I'm going with a book when I write it. However, a great deal still changes in drafting, and many of the people who posted comments on my blog had an influence on the novel. Not really in changing the plot or the characters---it's more that their questions and concerns would inspire me to explain something better or develop an aspect of the story more.

I tried to get everyone on the list who helped out in a moderate or significant way. However, I'm sure I missed some people. If you're one of those who gave me a lot of comments during the early months when I was posting the rough draft, and I forgot you in the acknowledgments, drop me an e-mail so I can at least get you added to the electronic version.
