\section{Chapter Twenty-Seven}

\textit{Something happened to those previous God Kings,}~Siri thought, striding through the endless rooms of the God King’s palace, her servants scurrying behind.~\textit{Something that Bluefingers fears will happen to Susebron. It will be dangerous to both the God King and myself.}

She continued to walk, trailing a train made from countless tassels of translucent green silk behind her. The day’s gown was nearly gossamer thin—she’d chosen it, then had asked her servants to fetch an opaque slip for her. It was funny how quickly she’d stopped worrying about what was “ostentatious” and what was not.

There were many much more important problems to worry about.

\textit{The priests}~do~\textit{fear that something will happen to Susebron,}~she thought firmly.~\textit{They are so eager for me to produce an heir. They claim it’s about the succession, but they went fifty years without bothering. They were willing to wait twenty years to get their bride from Idris. Whatever the danger is, it’s not urgent.}

\textit{And yet the priests act like it is.}

Perhaps they’d wanted a bride of the royal line so badly that they’d been willing to risk the danger. Surely they needn’t have waited twenty years, though. Vivenna could have borne children years ago.

Though perhaps the treaty specified a time and not an age. Maybe it just said that the king of Idris had twenty years to provide a bride for the God King. That would explain why her father had been able to send Siri instead. Siri cursed herself for ignoring her lessons about the treaty. She didn’t really know~\textit{what}~it said. For all she knew, the danger could be spelled out in the document itself.

She needed more information. Unfortunately, the priests were obstructive, the servants silent, and Bluefingers, well~.~.~.

She finally caught sight of him moving through one of the rooms, writing on his ledger. Siri hurried up, train rustling. He turned, glimpsing her. His eyes opened wide, and he increased his speed, ducking through the open doorway into another room. Siri called after him, moving as quickly as the dress would allow, but when she arrived, the room was empty.

“Colors!” she swore, feeling her hair grow a deep red in annoyance. “You still think he isn’t avoiding me?” she demanded, turning to the most se nior of her servants.

The woman lowered her gaze. “It would be improper for a servant of the palace to avoid his queen, Vessel. He must not have seen you.”

\textit{Right,}~Siri thought,~\textit{just like every other time.}~When she sent for him, he always arrived after she’d given up and left. When she had a letter scribed to him, he responded so vaguely that it only frustrated her even further.

She couldn’t take books from the palace library, and the priests were disruptively distracting if she tried to read inside the library chamber itself. She’d requested books from the city, but the priests had insisted that they be brought by a priest, then read to her, so as to not “strain her eyes.” She was pretty sure that if there was anything in the book that the priests didn’t want her to know, the reader would simply skip it.

She depended so much upon the priests and scribes for everything, including information.

\textit{Except~.~.~.}~she thought, still standing in the bright red room. There~\textit{was}~another source of information. She turned to her head servant. “What activities are going on today in the courtyard?”

“Many, Vessel,” the woman said. “Some artists have come and are doing paintings and sketches. There are some animal handlers showing exotic creatures from the South—I believe they have both elephants and zebras on display. There are also several dye merchants showing off their newest color combinations. And—of course—there are minstrels.”

“What about at that building we went to before?”

“The arena, Vessel? I believe there will be games there later in the evening. Contests of physical prowess.”

Siri nodded. “Prepare a box. I want to attend.”

\bigskip \hrule \bigskip

Back in her homeland, Siri had occasionally watched running contests. They were usually spontaneous, as the monks did not approve of men showing off. Austre gave all men talents. Flaunting them was seen as arrogance.

Boys cannot be so easily contained. She had seen them run, had even encouraged them. Those contests, however, had been~\textit{nothing}~like what the Hallandren men now put on.

There were a half-dozen different events going on at once. Some men threw large stones, competing for distance. Others raced in a wide circle around the interior of the arena floor, kicking up sand, sweating heavily in the muggy Hallandren heat. Others tossed javelins, shot arrows, or engaged in leaping contests.

Siri watched with a deepening blush—one that ran all the way to the ends of her hair. The men wore only loincloths. During her weeks in the grand city, she had never seen anything quite so~.~.~. interesting.

\textit{A lady shouldn’t stare at young men,}~her mother had taught.~\textit{It’s unseemly.}

Yet what was the point, if not to stare? Siri couldn’t help herself, and it wasn’t just because of the naked skin. These were men who had trained extensively—who had mastered their physical abilities to wondrous effect. As Siri watched, she saw that relatively little regard was given to the winners of each particular event. The contests weren’t really about victory, but about the skill required to compete.

In that respect, these contests were almost in line with Idrian sensibilities—yet, at the same time, they were ironically opposite.

The beauty of the games kept her distracted for much longer than she’d intended, her hair permanently locked into a deep maroon blush, even after she got used to the idea of men competing in so little clothing. Eventually, she forced herself to stand and turn away from the perfor mance. She had work to do.

Her servants perked up. They had brought all kinds of luxuries. Full couches and cushions, fruits and wines, even a few men with fans to keep her cool. After only a few weeks in the palace, such comfort was beginning to seem commonplace to her.

“There was a god who came and spoke to me before,” Siri said, scanning the amphitheater, where many of the stone boxes were decorated with colorful canopies. “Which one was it?”

“Lightsong the Bold, Vessel,” one of the serving women said. “God of bravery.”

Siri nodded. “And his colors are?”

“Gold and red, Vessel.”

Siri smiled. His canopy showed that he was there. He wasn’t the only god to have introduced himself to her during her weeks in the palace, but he~\textit{was}~the only one who had spent any amount of time chatting with her. He’d been confusing, but at least he’d been willing to talk. She left her box, beautiful dress trailing on the stone. She’d had to force herself to stop feeling guilty for ruining them, since apparently each dress was burned the day after she wore it.

Her servants burst into frantic motion, gathering up furniture and foods, following behind Siri. As before, there were people on the benches below—merchants rich enough to buy entrance to the court or peasants who had won a special lottery. Many turned and looked up as she passed, whispering among themselves.

\textit{It’s the only way they get to see me,}~she realized.~\textit{Their queen.}

That was one thing that Idris certainly handled better than Hallandren. The Idrians had easy access to their king and their government, while in Hallandren the leaders were kept aloof—and therefore made remote, even mysterious.

She approached the red and gold pavilion. The god she had seen before lounged inside, relaxing on a couch, sipping from a large, beautifully engraved glass cup filled with an icy red liquid. He looked much as he had before—the chiseled masculine features that she was already coming to associate with godhood, perfectly styled black hair, golden tan skin, and a distinctly blasé attitude.

\textit{That’s something else Idris was right about,}~she thought.~\textit{My people may be too stern, but it also isn’t good to become as self-indulgent as some of these Returned.}

The god, Lightsong, eyed her and nodded in deference. “My queen.”

“Lightsong the Bold,” she said as one of her servants brought her chair. “I trust your day has been pleasant?”

“So far this day I have discovered several disturbing and redefining elements of my soul which are slowly restructuring the very nature of my existence.” He took a sip from his drink. “Other than that, it was uneventful. You?”

“Fewer revelations,” Siri said, sitting. “More confusion. I’m still inexperienced in the way things work here. I was hoping you could answer some of my questions, give me some information, perhaps~.~.~.”

“Afraid not,” Lightsong said.

Siri paused, then flushed, embarrassed. “I’m sorry. Did I do something wrong. I—”

“No, nothing wrong, child,” Lightsong said, his smile deepening. “The reason I cannot help you is because I, unfortunately, know nothing. I’m useless. Haven’t you heard?”

“Um~.~.~. I’m afraid I haven’t.”

“You should pay better attention,” he said, raising his cup toward her. “Shame on you,” he said, smilingly.

Siri frowned, growing more embarrassed. Lightsong’s high priest—distinguished by his oversized headgear—looked on disapprovingly, and that only caused her to be more self-conscious.~\textit{Why should I be the ashamed one?}~she thought, growing annoyed.~\textit{Lightsong is the one who is making veiled insults against me—and making overt ones against himself! It’s like he}~enjoys~\textit{self-deprecation.}

“Actually,” Siri said, looking over at him, lifting her chin, “I~\textit{have}~heard of your reputation, Lightsong the Bold. ‘Useless’ wasn’t the word I heard used, however.”

“Oh?” he said.

“No. I was told you were harmless, though I can see that is not true—for in speaking to you, my sense of reason has certainly been harmed. Not to mention my head, which is beginning to ache.”

“Both common symptoms of dealing with me, I’m afraid,” he said with an exaggerated sigh.

“That could be solved,” Siri said. “Perhaps it would help if you refrained from speaking when others are present. I think I should find you quite amiable in those circumstances.”

Lightsong laughed. Not a belly laugh, like her father or some of the men back in Idris, but a more refined laugh. Still, it seemed genuine.

“I~\textit{knew}~I liked you, girl,” he said.

“I’m not sure if I should feel complimented or not.”

“Depends upon how seriously you take yourself,” Lightsong said. “Come, abandon that silly chair and recline on one of these couches. Enjoy the evening.”

“I’m not sure that would be proper,” Siri said.

“I’m a god,” Lightsong said with a wave of his hand. “I define propriety.”

“I think I’ll sit anyway,” Siri said, smiling, though she did stand and have her servants bring the chair farther under the canopy so that she didn’t have to speak so loudly. She also tried not to pay too much attention to the contests, lest she be drawn in by them again.

Lightsong smiled. He seemed to enjoy making others uncomfortable. But, then, he also seemed to have no concern for how he himself appeared.

“I meant what I said before, Lightsong,” she said. “I need information.”

“And I, my dear, was quite honest as well. I~\textit{am}~useless, mostly. However, I’ll try my best to answer your questions—assuming, of course, you will provide answers to mine.”

“And if I don’t know the answers to your questions?”

“Then make something up,” he said. “I’ll never know the difference. Unknowing ignorance is preferable to informed stupidity.”

“I’ll try to remember that.”

“Do so and you defeat the point. Now, your questions?”

“What happened to the previous God Kings?”

“Died,” Lightsong said. “Oh, don’t look so surprised. It happens to people sometimes, even gods. We make, if you haven’t noticed, laughable immortals. We keep forgetting about that ‘live forever’ part and instead find ourselves unexpectedly dead. And for the~\textit{second time}~at that. You might say that we’re twice as bad at staying alive as regular folk.”

“How do the God Kings die?”

“Gave away their Breath,” Lightsong said. “Isn’t that right, Scoot?”

Lightsong’s high priest nodded. “It is, Your Grace. His Divine Majesty Susebron the Fourth died to cure the plague of distrentia that struck T’Telir fifty years ago.”

“Wait,” Lightsong said. “Isn’t distrentia a disease of the bowels?”

“Indeed,” the high priest said.

Lightsong frowned. “You mean to tell me that our God King—the most holy and divine personage in our pantheon—died to cure a few tummy aches?”

“I wouldn’t exactly put it that way, Your Grace.”

Lightsong leaned over to Siri. “I’m expected to do that someday, you know. Kill myself so that some old lady will be able to stop messing herself in public. No wonder I’m such an embarrassing god. Must have to do with subconscious self-worth issues.”

The high priest looked apologetically at Siri. For the first time, she realized that the overweight priest’s disapproval wasn’t directed at her, but at his god. To her, he smiled.

\textit{Maybe they’re not all like Treledees,}~she thought, smiling back.

“The God King’s sacrifice was not an empty gesture, Vessel,” the priest said. “True, diarrhea may not be a great danger to most, but to the elderly and the young it can be quite deadly. Plus, the epidemic conditions were spreading other diseases, and the city’s commerce—and therefore the kingdom’s—had slowed to a crawl. People in outlying villages went months without necessary supplies.”

“I wonder how those who were cured felt,” Lightsong said musingly, “waking to find their God King dead.”

“One would think they’d be honored, Your Grace.”

“I think they’d be annoyed. The king came all that way, and they were too sick to notice. Anyway, my queen, there you go. That was actually helpful information. You now have me worried that I’ve broken my promise to you about being useless.”

“If it’s any consolation,” she said, “you weren’t all that helpful yourself. It’s your priest who actually seems useful.”

“Yes, I know. I’ve tried for years to corrupt him. Never seems to work. I can’t even get him to acknowledge the theological paradox it causes when I try to tempt him to do evil.”

Siri paused, then found herself smiling even more broadly.

“What?” Lightsong asked, then finished off the last of his drink. It was immediately replaced by another, this one blue.

“Talking to you is like swimming in a river,” she said. “I keep getting pulled along with the current and I’m never sure when I’ll be able to take another breath.”

“Watch out for the rocks, Vessel,” the high priest noted. “They look rather insignificant, but have sharp edges under the surface.”

“Bah,” Lightsong said. “It’s the~\textit{crocodiles}~you have to watch for. They can bite. And~.~.~. what exactly were we talking about, anyway?”

“The God Kings,” Siri said. “When the last one died, an heir had already been produced?”

“Indeed,” the high priest said. “In fact, he had just been married the year before. The child was born only weeks before he died.”

Siri sat back in her chair, thoughtful. “And the God King before him?”

“Died to heal the children of a village which had been attacked by bandits,” Lightsong said. “The commoners love the story. The king was so moved by their suffering that he gave himself up for the simple people.”

“And had he been married the year before?”

“No, Vessel,” the high priest said. “It was several years after his marriage. Though, he~\textit{did}die only a month after his second child was born.”

Siri looked up. “Was the first child a daughter?”

“Yes,” the priest said. “A woman of no divine powers. How did you know?”

\textit{Colors!}~Siri thought.~\textit{Both times, right after the heir was born.}~Did having a child somehow make the God Kings wish to give their lives away? Or was it something more sinister? A cured plague or healed village were both things that, with a little creative propaganda, could be invented to cover up some other cause of death.

“I’m not truly an expert on these things, I’m afraid, Vessel,” the high priest continued. “And I’m afraid that Lord Lightsong is not either. If you press him, he~\textit{could}~very well just start making things up.”

“Scoot!” Lightsong said indignantly. “That’s slanderous. Oh, and by the way, your hat is on fire.”

“Thank you,” Siri said. “Both of you. This has actually been rather helpful.”

“If I might suggest~.~.~.” the high priest said.

“Please,” she replied.

“Try a professional storyteller, Vessel,” the priest said. “You can order one in from the city, and he can recite both histories and tales of imagination to you. They will provide much better information than we can.”

Siri nodded.~\textit{Why can’t the priests in our palace be this helpful?}~Of course, if they really\textit{were}~covering up the true reason their God Kings died, they had good reason to avoid helping her. In fact, it was likely that if she asked for a storyteller, they would just provide one who would tell her what~\textit{they}~wanted her to hear.

She frowned. “Could~.~.~. you do that for me, Lightsong?”

“What?”

“Order in a storyteller,” she said. “I should like you to be there, in case I have any questions.”

Lightsong shrugged. “I guess I could. Haven’t heard a storyteller in some time. Just let me know when.”

It wasn’t a perfect plan. Her servants were listening and they might report to the priests. However, if the storyteller came to Lightsong’s palace, there was at least some chance of Siri hearing the truth.

“Thank you,” she said, rising.

“Ah, ah, ah! Not so fast,” Lightsong said, raising a finger.

She stopped.

He drank from his cup.

“Well?” she finally asked.

He held up the finger again as he continued to drink, tipping his head back, getting the last bits of slushy ice from the bottom of the cup. He set it aside, mouth blue. “How refreshing. Idris. Wonderful place. Lots of ice. Costs quite a bit to bring it here, so I’ve heard. Good thing I don’t ever have to pay for anything, eh?”

Siri raised an eyebrow. “And I’m standing here waiting because~.~.~.”

“You promised to answer some of~\textit{my}~questions.”

“Oh,” she said, sitting back down. “Of course.”

“Now, then,” he said. “Did you know any city guards back in your home?”

She cocked her head. “City guards?”

“You know, fellows who enforce the law. Police. Sheriffs. The men who catch crooks and guard dungeons. That sort.”

“I knew a couple, I guess,” she said. “My home city wasn’t large but it was the capital. It did attract people who could be difficult sometimes.”

“Ah, good,” Lightsong said. “Kindly describe them for me. Not the difficult fellows. The city watch.”

Siri shrugged. “I don’t know. They tended to be careful. They’d interview newcomers to the village, walk the streets looking for wrongdoing, that sort of thing.”

“Would you call them inquisitive types?”

“Yes,” Siri said. “I guess. I mean, as much as anybody. Maybe more.”

“Were there ever any murders in your village?”

“A couple,” Siri said, glancing down. “There shouldn’t have been—my father always said things like that shouldn’t happen in Idris. Said murder was a thing of~.~.~. well, Hallandren.”

Lightsong chuckled. “Yes, we do it all the time. Quite the party trick. Now, did these policemen investigate the murders?”

“Of course.”

“Without having to be asked to do so?”

Siri nodded.

“How’d they go about it?”

“I don’t know,” Siri said. “They asked questions, talked to witnesses, looked for clues. I wasn’t involved.”

“No, no,” Lightsong said. “Of course you weren’t. Why, if you’d been a murderer, they would have done something terrible to you, yes? Like exile you to another country?”

Siri felt herself pale, hair growing lighter.

Lightsong just laughed. “Don’t go taking me so seriously, Your Majesty. Honestly, I gave up wondering if you were an assassin~\textit{days}~ago. Now, if your servants and mine will stay behind for a second, I think I may have something important to tell you.”

Siri started as Lightsong stood up. He began to walk from the pavilion, and his servants remained where they were. Confused but excited, Siri rose from her own seat and hurried after him. She caught up with him a short distance away, on the stone walkway that ran between the various boxes in the arena. Down below, the athletes continued their display.

Lightsong looked down at her, smiling.

\textit{They really are tall,}~she thought, craning a bit. A single foot of extra height made such a difference. Standing next to a man like Lightsong—and not really being that tall herself—she felt dwarfed.~\textit{Maybe he’ll tell me the thing I’ve been looking for,}~Siri thought.~\textit{The secret!}

“You are playing a dangerous game, my queen,” Lightsong said, leaning against the stone railing. It was built for Returned proportions, so it was too high for her to rest against comfortably.

“Game?” she asked.

“Politics,” he said, watching the athletes.

“I don’t want to play politics.”

“If you don’t, it will play you, I’m afraid. I always get sucked in, regardless of what I do. Complaining doesn’t stop that—though it does annoy people, which is satisfying in its own right.”

Siri frowned. “So you pulled me aside to give me a warning?”

“Colors, no,” Lightsong said, chuckling. “If you haven’t already figured out that this is dangerous, then you’re far too dense to appreciate a warning. I just wanted to give some advice. The first is about your persona.”

“My persona?”

“Yes,” he said. “It needs work. Choosing the persona of an innocent newcomer was a good instinct. It suits you. But you need to refine it. Work on it.”

“It’s not a persona,” she said sincerely. “I~\textit{am}~confused and new to all this.”

Lightsong raised a finger. “That’s the trick to politics, child. Sometimes, although you can’t disguise who you are and how you really feel, you~\textit{can}~make use of who you are. People distrust that which they can’t understand and predict. As long as you feel like an unpredictable element in court, you will appear to be a threat. If you can skillfully—and honestly—portray yourself as someone they understand, then you’ll begin to fit in.”

Siri frowned.

“Take me as an example,” Lightsong said. “I’m a useless fool. I always have been, as long as I can remember—which actually isn’t all that long. Anyway, I know how people regard me. I enhance it. Play with it.”

“So it’s a lie?”

“Of course not. This is who I am. However, I make certain that people never forget it. You can’t control everything. But if you can control how people regard you, then you can find a place in this mess. And once you have that, you can begin to influence factions. Should you want to. I rarely do because it’s such a bother.”

Siri cocked her head. Then she smiled. “You’re a good man, Lightsong,” she said. “I knew it, even when you were insulting me. You mean no harm. Is that part of your persona?”

“Of course,” he said, smiling. “But I’m not sure~\textit{what}~it is that convinces people to trust me. I’d get rid of it if I could. It only serves to make people expect too much. Just give what I said some practice. The best thing about being locked in this beautiful prison is that you~\textit{can}~do some good, you~\textit{can}~change things. I’ve seen others do it. People I respected. Even if there haven’t been many of those around the court lately.”

“All right,” she said. “I will.”

“You’re digging for something—I can sense it. And it has to do with the priests. Don’t make too many waves until you’re ready to strike. Sudden and surprising, that’s how you want to be. You don’t want to appear~\textit{too}~nonthreatening—people are always suspicious of the innocent. The trick is to appear~\textit{average}. Just as crafty as everyone else. That way, everyone else will assume that they can beat you with just a little advantage.”

Siri nodded. “Kind of an Idrian philosophy.”

“You came from us,” Lightsong said. “Or, perhaps, we came from you. Either way, we’re more similar than our outward trappings make us seem. What is that Idrian philosophy of extreme plainness except a means of contrasting with Hallandren? All those whites you people use? That makes you stand out on a national scale. You act like us, we act like you, we just do the same things in opposite ways.”

She nodded slowly.

He smiled. “Oh, and one thing. Please,~\textit{please}~don’t depend on me too much. I mean that. I’m not going to be of much help. If your plots come to a head—if things go wrong at the last moment and you’re in danger or distress—don’t think of me. I will fail you.~\textit{That}~I promise from my heart with absolute sincerity.”

“You’re a very strange man.”

“Product of my society,” he said. “And since most of the time, my society consists pretty much only of myself, I blame god. Good day, my queen.”

With that, he sauntered off back to his box and waved for her servants—who had been watching with concern—to finally rejoin her.

