\section{Chapter Fifty-Five}

“There is fighting at the front gates, Your Excellency,” the bloodied soldier said. “The insurgents are fighting each other there. We~.~.~. we might be able to get out.”

Siri felt a stab of relief. Finally, something going right.

Treledees turned toward her. “If we can get into the city, the people will rally around their God King. We should be safe there.”

“Where did they get so many Lifeless?” Siri asked. Treledees shook his head. They had paused in a room near the front of the palace, desperate, yet unsure. Breaking through the Pahn Kahl fortification of the Court of Gods was bound to be difficult.

She looked up at Susebron. His priests treated him like a child—they gave him respect, but they obviously gave no thought to ask his opinion. For his part, he stood, hand on her shoulder. She saw thoughts and ideas working behind those eyes of his, but there was nothing for him to write on to tell her.

“Vessel,” Treledees said, drawing her attention. “You need to know something.”

She looked at him.

“I hesitate to mention this,” Treledees said, “as you are not a priest. But~.~.~. if you survive and we do not~.~.~.”

“Speak it,” she commanded.

“You cannot bear the God King a child,” he said. “Like all Returned, he is unable to sire children. We have not yet learned how the First Returned managed to have a child all those years ago. In fact~.~.~.”

“You don’t even think he did,” she said. “You think the royal line is a fabrication.”~\textit{Of course the priests dispute the record of the royal line coming from the First Returned,}~she thought.~\textit{They wouldn’t want to give credibility to Idris’s claim to the throne.}

He flushed. “It’s what people believe that matters. Regardless, we~.~.~. have a child~.~.~.”

“Yes,” Siri said. “A Returned child you are going to make the next God King.”

He looked at her, shocked. “You~\textit{know}?”

“You’re planning to kill him, aren’t you?” she hissed. “Take Susebron’s Breath and leave him dead!”

“Colors, no!” Treledees said, shocked. “How—how could you think? No, we’d never do such a thing! Vessel, the God King needs only give away the treasure of Breaths he holds, investing them into the next God King, and then he can live the rest of his life—so long as he should desire—in peace. We change God Kings whenever an infant Returns. It is our sign that the previous God King has done his duty, and should be allowed to live the rest of his life without bearing his terrible burdens.”

Siri looked at him skeptically. “That’s foolish, Treledees. If the God King gives away his Breath, he will die.”

“No, there is a way,” the priest said.

“That is supposed to be impossible.”

“Not at all. Think about it. The God King has~\textit{two}~sources of Breath. One is his innate, divine Breath—that which makes him Returned. The other is the Breath given to him as the Treasure of Peacegiver, fifty thousand Breaths strong.~\textit{That}~he could use as any Awakener could, as long as he is careful about the Commands he uses. He could also survive quite easily as a Returned without it. Any of the other gods could do the same, should they gain Breath beyond the one a week which sustains them. They’d consume them at a rate of one a week, of course, but they could stockpile them and use the extras in the meantime.”

“You keep them from realizing that, though,” Siri said.

“Not~\textit{keep}~specifically,” the priest said, looking away. “It does not arise. Why would the Returned care about Awakening? They have everything they need.”

“Except knowledge,” Siri said. “You keep them in ignorance. I’m surprised you didn’t cut out all their tongues to hide your precious secrets.”

Treledees looked back at her, expression hardening. “You judge us still. We do what we do because it is what we~\textit{must,}~Vessel. The power he holds in that Treasure—fifty thousand Breaths—could destroy kingdoms. It is too great a weapon; we were charged as our sole, divine mission to keep it safe and~\textit{not}~let it be used. If Kalad’s army ever returns from where it was exiled, we—”

A sound came from a nearby room. Treledees looked, concerned, and Susebron’s grip on Siri’s shoulder tightened.

She looked up, concerned. “Treledees,” she said. “I need to know. How? How can Susebron give away his Breath? He can speak no Command!”

“I—”

Treledees was interrupted by a group of Lifeless bursting through the doorway to their left. Treledees yelled for her to flee, but another group of the creatures came through the other way. Siri cursed, grabbing Susebron’s hand, pulling him toward yet another doorway. She pulled it open.

Bluefingers stood on the other side. He looked into her eyes, face grim. Lifeless stood behind him.

Siri felt a stab of terror, backing away. Sounds of fighting came from behind her, but she was too focused on the Lifeless stepping around Bluefingers toward her and Susebron. The God King cried out, a tongueless, wordless groan of anger.

And then the priests were there. They threw themselves in front of the Lifeless, trying to beat them back, trying desperately to protect their God King. Siri clung to her husband in the ruddy room, watching as the priests were slaughtered by emotionless warriors with grey faces. Priest after priest jumped in the way, some with weapons, others simply waving their arms in a hopeless attack.

She saw Treledees grit his teeth, terror showing in his eyes as he ran forward, trying to attack a Lifeless. He died like the others. His secrets died with him.

The Lifeless stepped over the corpses. Susebron pushed Siri behind him, arms shaking as he backed them toward a wall, facing down the bloodied monsters. The Lifeless finally stopped, and Bluefingers walked around them, looking past Susebron toward her.

“And now, Vessel, I believe we were going somewhere.”

\bigskip \hrule \bigskip

“I’m sorry, miss,” the guard said, holding up a hand. “All access to the Court of Gods is forbidden.”

Vivenna ground her teeth. “This is unacceptable,” she said. “I’m to report to the goddess Allmother at once! Can’t you see how many Breaths I hold? I’m not someone you can just turn away!”

The guards remained firm. There were a good two dozen of them at the gates, stopping anyone who tried to enter. Vivenna turned away. Whatever Vasher had done inside the night before, he’d apparently caused quite a stir. People clustered around the gateway to the court, demanding answers, asking if something was wrong. Vivenna made her way back through them, leaving the gates behind.

\textit{Go to the side,}~Nightblood said.~\textit{Vasher never asks if he can enter. He just goes in.}

Vivenna glanced at the side of the plateau. There was a short rocky ledge running around the outside of the wall. With the guards so distracted by the people wanting in~.~.~.

She slipped to the side. It was early in the morning yet, the sun not having crested the eastern mountains. There were guards on the wall above—she could feel them with her life sense—but she was below their angle of view as long as they looked outward. She might be able to sneak by them.

She waited until one patrol had passed, then Awakened one of the tapestries. “Lift me,” she said, dropping a drained handkerchief. The tapestry twisted into the air, wrapping around her, the top end still attached to the wall. Like a muscular arm, it lifted her up, twisting and depositing her atop the wall. She glanced around, recovering her breath. To the side, some distance away, a group of guards was pointing at her.

\textit{You’re not any better at this than Vasher is,}~Nightblood noted.~\textit{You people can’t sneak at all! Yesteel would be so disappointed in you.}

She cursed, Awakened the tapestry again and had it lower her into the court. She recovered her breath, then took off running across the grassy lawn. Few people were about, but that only made her stand out even more.

\textit{The palace,}~Nightblood said.~\textit{Go there.}

That was where she~\textit{was}~going. However, the longer she held the sword, the more she understood that it said whatever came to its steely mind, whether or not its comments were relevant. It was like a child, speaking or asking questions without inhibition.

The front of the palace was very well guarded by a group of men who weren’t wearing uniforms.~\textit{He’s in there,}~Nightblood said.~\textit{I can feel him. Third floor. Where he and I were before.}

Vivenna got an image of the room shoved into her head. She frowned.~\textit{Remarkably useful,}~she thought,~\textit{for an evil weapon of destruction.}

\textit{I’m not evil,}~Nightblood said, voice not defensive, simply informative. As if reminding her of something she’d forgotten.~\textit{I destroy evil. I think maybe we should destroy those men up ahead. They look evil. You should pull me out.}

For some reason, she doubted that would be a good idea.

\textit{Come on,}~Nightblood said.

The soldiers were pointing at her. She glanced behind, and saw others rushing across the lawn.~\textit{Austre, forgive me,}~she thought. Then, gritting her teeth, she threw Nightblood—blanket and all—toward the guards in front of the building.

They halted. To a man, they looked down at the sword as it rolled free of the blanket, silver sheath glistening on the lawn.~\textit{Well, I guess this works too,}~Nightblood noted, voice feeling distant now.

One of the soldiers picked up the sword. Vivenna dashed past them, ignored by the soldiers. They started to fight.

\textit{Can’t go that way,}~she thought, eyeing the front entrance, not wanting to risk pushing her way through fighting men. So instead she ran to the side of the massive palace. The lower levels were made of the steplike black blocks that gave the palace its pyramidlike quality. Above these, it grew into a more traditional fortress, with steep walls. There were windows, if she could reach them.

She twitched her fingers, making the tassels on her sleeves clench and unclench. Then she jumped, her Awakened leggings tossing her up a few extra feet. She reached up and made the tassels grab the edge of the large, black block. The tassels just barely held, gripping the stone like footlong fingers. With difficulty, Vivenna pulled herself up onto the block.

Men yelled and screamed below, and she spared them a glance. The guard who had grabbed Nightblood was fighting off the others, a small trail of black smoke swirling around him. As she watched, he backed into the palace itself, the other men following him.

\textit{So much evil,}~Nightblood said, like a woman tisking as she cleaned cobwebs from her ceiling.

Vivenna turned away, feeling slightly guilty for giving the sword to the men. She jumped up and pulled herself onto the next block, continuing as the soldiers who had seen her from the walls arrived. They wore the colors of the city guard, and while a couple of them got caught up in the Nightblood fight, most of them ignored it.

Vivenna continued up.

\textit{To the right,}~Nightblood said distantly.~\textit{That window on the third floor. Two over. He’s in there~.~.~.}

As his voice faded, Vivenna looked up at the window indicated. She still had to climb up a number of blocks, then somehow reach a window that was an entire story up a sheer wall. There did appear to be some decorative stonework that could serve as handholds, but she grew dizzy even thinking about climbing them.

An arrow snapped against the stone beside her, making her jump. Several guards below had bows.

\textit{Colors!}~she thought, pulling herself up to the next block. She heard a whoosh behind her, and cringed, feeling as if she should have been struck, but nothing happened. She pulled herself up onto the block, then twisted around.

She could just barely see a corner of her cloak holding an arrow. She started, grateful that she had Awakened it. It dropped the arrow, then returned to normal.

\textit{Handy, that,}~she thought, climbing up the last block. By the time she got on top of it, her arms were sore. Fortunately, her Awakened fingers were still gripping as well as ever. She took a deep breath, then began to climb straight up the upper wall of the black fortress, using the carvings as handholds.

And decided, for her own sanity, that she’d better avoid looking down.

\bigskip \hrule \bigskip

Lightsong stared ahead. Too much information. Too much was happening. Blushweaver’s murder, then Llarimar’s revelation, the betrayal of the God King’s priests all in such quick succession.

He sat in his cell, arms wrapped around himself, gold and red robes dirtied from crawling through the tunnel, then sitting in his cage. His thigh ached from where it had been struck with the sword, though the wound had not been bad, and it was barely bleeding anymore. He ignored the pain. It was insignificant compared to the pain inside.

The priests talked quietly on the far side of the room. Oddly, as he glanced at them, something caught his eye. He let his mind be diverted by the realization—he finally grasped what was bothering him about them. He should have seen it earlier. It had to do with color—not the color of their clothing, but the color of their faces. It was just slightly off. The deviation in one man would have been easy to ignore. But all of them together was a pattern.

No regular person could have noticed it. To a man with his Heightenings, it was obvious, once he knew what to look for.

These men were not from Hallandren.

\textit{Anyone can wear a set of robes,}~he realized.~\textit{That doesn’t mean that they’re priests.}~In fact, judging by the faces, he realized the men must be from Pahn Kahl.

And then it all made sense to him, that quickly. They’d all been played for fools.

\bigskip \hrule \bigskip

“Bluefingers,” Siri demanded. “Talk to me. What are you going to do with us?”

The labyrinth of the God King’s palace was complex, and it was sometimes difficult even now for her to find her way around. They’d traveled down a stairwell but now were going up another one.

Bluefingers didn’t answer. He walked with his customary nervousness, wringing his hands. The fighting in the hallways seemed to be decreasing. In fact, once they left the stairwell, this newest hallway was dreadfully quiet.

Siri walked with Susebron’s nervous arm around her waist. She didn’t know what he was thinking—they hadn’t been able to pause long enough for him to write anything. He gave her a comforting smile, but she knew that this all must be just as terrifying for him as it was for her. Probably more so.

“You can’t do this, Bluefingers,” Siri said, snapping at the little balding man.

“It is the only way we’d ever be able to break free,” Bluefingers said, not turning, but finally responding to her.

“But you can’t!” Siri said. “The Idrians are innocent!”

Bluefingers shook his head. “How many of my people would you sacrifice, if it would mean freedom for yours?”

“None!” she said.

“I should like to see you say that if our positions were reversed,” he said, still not meeting her eyes. “I’m~.~.~. sorry for your pain. But your people are~\textit{not}~innocent. They’re just like the Hallandren. In the Manywar, you rolled over us, made us your workers and slaves. Only at the end, when the royal family fled, did Idris and Hallandren split.”

“Please,” Siri said.

Susebron suddenly punched a Lifeless.

The God King growled, struggling as he kicked at another. There were dozens of them. He looked at her, waving a hand, motioning for her to flee. She didn’t intend to leave him. Instead, she tried to grab Bluefingers, but a Lifeless was too quick. It took her arm, holding her firm, even when she batted at it. A couple of men wearing the robes of Susebron’s priesthood came out of a stairwell ahead of them, carrying lanterns. Siri, looking closely, immediately recognized them as being from Pahn Kahl. They were too short and their skin color was just slightly off.

\textit{I’ve been a fool,}~she thought.

Bluefingers had played the game so well. He’d driven a wedge between her and the priests from the start. Most of her fears and worries, she’d gotten from him—and it had been reinforced by the priests’ arrogance. All part of the scribe’s plan to someday use her to gain freedom for his people.

“We have Lightsong’s security phrase,” one of the new men said to Bluefingers. “We have checked it, and it works. We changed it to the new one. The rest of the Lifeless are ours.”

Siri glanced to the side. The Lifeless had pulled Susebron to the ground. He yelled—though it came out as more a moan. Siri yanked, trying to escape her Lifeless and help him. She began to cry.

To the side, Bluefingers nodded to his accomplices, looking fatigued. “Very well. Give the Command. Order the Lifeless to march on Idris.”

“It will be done,” the man said, laying a hand on Bluefingers’s shoulder.

Bluefingers nodded, looking morose as the others withdrew.

“What do you have to be sad about?” she spat.

Bluefingers turned toward her. “My friends now are the only ones who know the Command phrases for Hallandren’s Lifeless army. Once those Lifeless leave for Idris—with orders to destroy everything they find there—my friends will kill themselves with poison. There won’t be anyone who can stop the creatures.”

\textit{Austre~.~.~.}~Siri thought, feeling numb.~\textit{Lord of Colors~.~.~.}

“Take the God King below,” Bluefingers said, waving to several Lifeless. “Hold him until it is time.” They were joined by a Pahn Kahl scribe wearing fake priest’s robes as they towed Susebron toward the stairwell. Siri reached for him. He continued to struggle, reaching back, but the Lifeless were too strong. She listened to his inarticulate yells echoing down the stairwell.

“What will you do with him?” Siri asked, tears cold on her cheeks.

Bluefingers glanced at her, but once again, would not meet her eyes. “There will be many in the Hallandren government who see the Lifeless attack as a political mistake, and they may seek to stop the war. Unless Hallandren actually commits itself to this fight, our sacrifice will be useless.”

“I don’t understand.”

“We will take the bodies of Lightsong and Blushweaver—the two gods with the Command phrases—and leave them in the Lifeless barracks, surrounded by dead Idrians we took from the city. Then we will leave the corpse of the God King to be discovered in the palace dungeons. Those who investigate will assume that Idrian assassins attacked and killed him—we’ve hired enough mercenaries from the Idrian slums that it shouldn’t be too difficult to believe. Those of my scribes who survive the night will confirm the story.”

Siri blinked out tears.~\textit{Everyone will assume that Blushweaver and Lightsong sent the armies as retribution for the death of the God King.}

\textit{And with the king dead, the people will be furious.}

“I wish you hadn’t gotten involved in all of this,” Bluefingers said, motioning for her Lifeless captors to pull her along. “It would have been easier for me if you’d been able to keep yourself from getting pregnant.”

“I’m not!” she said.

“The people think you are,” he said with a sigh as they walked toward the stairwell. “And that’s enough. We have to break this government~\textit{and}~we have to make the Idrians angry enough to want to destroy the Hallandren. I think your people will do better in this war than everyone says, especially if the Lifeless march without leadership. Your people will ambush them, making sure this is not an easy war for either side.”

He glanced at her. “But for this war to work right, the Idrians have to~\textit{want}~to fight. Otherwise, they’ll flee and vanish into those highlands. No, both sides have to hate each other, pull as many allies into the battle as possible so that everyone is too distracted~.~.~.”

\textit{And what better way to make Idris willing to fight,}~she thought with horror,~\textit{than to kill me? Both sides will see the death of my supposed child as an act of war. This won’t simply be a fight for domination. It will be a drawn-out war of hatred. The fighting could last for decades.}

\textit{And nobody will ever realize that our real enemy—the one who started it all—is the peaceful, quiet province to the south of Hallandren.}

