% \section{Chapter Thirty-Six}
\chapter{}

\textit{I will not leave you,}~Susebron wrote, sitting on the floor beside the bed, his back propped up by pillows.~\textit{I promise.}

“How can you be sure?” Siri asked from her place on the bed. “Maybe once you have an heir, you’ll grow tired of life, then give away your Breath.”

\textit{First of all,}~he wrote,~\textit{I’m still not even sure how I would get an heir. You refuse to explain it to me, nor will you answer my questions.}

“They’re embarrassing!” Siri said, feeling her short hair grow red. She turned it back to yellow in an instant.

\textit{Secondly,}~he wrote,~\textit{I cannot give away my Breath, not if what I understand about BioChroma is true. Do you think I’ve been lied to about how Breath works?}

\textit{He’s getting much more articulate in his writing,}~Siri thought as she watched him erase.\textit{It’s such a shame that he’s been locked up his entire life.}

“I really don’t know that much about it,” she said. “BioChroma isn’t exactly something we focus on in Idris. I suspect that half of the things I know are rumors and exaggerations. For instance, back in Idris, they think you sacrifice people on altars in the court here—I heard that a dozen times from different people.”

He paused, then continued writing.~\textit{Regardless, we argue something that is absurd. I will not change. I am not going to suddenly decide to kill myself. You do not need to worry.}

She sighed.

\textit{Siri,}~he wrote,~\textit{I lived for fifty years with no information, no knowledge, barely able to communicate. Can you really think that I would kill myself now? Now, when I’ve discovered how to write? When I’ve discovered someone to talk to? When I’ve discovered you?}

She smiled. “All right. I believe you. But I still think we have to worry about your priests.”

He didn’t respond, looking away.

\textit{Why is he so cursedly loyal to them?}~she thought.

Finally, he looked back at her.~\textit{Would you grow your hair?}

She raised an eyebrow. “And what color am I to make it?”

\textit{Red,}~he wrote.

“You Hallandren and your bright colors,” she said, shaking her head. “Do you realize that my people considered red the most flagrant of all colors?”

He paused.~\textit{I’m sorry,}~he wrote.~\textit{I did not mean to offend you. I—}

He broke off as she reached down and touched his arm. “No,” she said. “Look, I wasn’t arguing. I was just being flirtatious. I’m sorry.”

\textit{Flirtatious?}~he wrote.~\textit{My storybook doesn’t use this term.}

“I know,” Siri said. “That book is too full of stories about children getting eaten by trees and things.”

\textit{The stories are meta phors meant to teach—}

“Yes, I know,” she said, interrupting him again.

\textit{So, what is flirtatious?}

“It’s~.~.~.”~\textit{Colors! How do I get myself into these situations?}~“It’s when a girl acts hesitant—or sometimes silly—in order to make a man pay more attention to her.”

\textit{Why would that make a man pay attention to her?}

“Well, like this.” She looked at him, leaning forward a bit. “Do you want me to grow my hair?”

\textit{Yes.}

“Do you~\textit{really}~want me to?”

\textit{Of course.}

“Well then, if I must,” she said, tossing her head and commanding her hair become a deep auburn red. It flushed midtoss, flaring from yellow to red like ink bleeding into a pool of clear water. Then she made it grow. The ability was more instinctive than conscious—like flexing a muscle. In this case, it was a “muscle” she’d been using a lot lately, since she tended to cut her hair off in the eve nings rather than spending the time combing it.

Even as the hair whipped past her face, it grew in length. She tossed her head, one final time—the hair making it feel more heavy, her neck warm from the locks that now tumbled down around her shoulders and down her back, twisting in loose curls.

Susebron looked at her with wide eyes. She met them, then tried a seductive glance. The result seemed so ridiculous to her, however, that she just found herself laughing. She fell back on the bed, newly grown hair flaring around her.

Susebron tapped her leg. She looked over at him, and he stood up, sitting on the side of the bed so that she could see his tablet as he wrote.

\textit{You are very strange,}~he said.

She smiled. “I know. I’m not meant to be a seductress. I can’t keep a straight face.”

\textit{Seductress,}~he wrote.~\textit{I know that word. It is used in a story when the evil queen tries to tempt the young prince with something, though I don’t know what.}

She smiled.

\textit{I think she must have been planning to offer him food.}

“Yeah,” Siri said. “Good interpretation, there, Seb. Completely right.”

He hesitated.~\textit{She wasn’t offering food, was she?}

Siri smiled again.

He flushed.~\textit{I feel like such an idiot. There is so much that everyone else understands intrinsically. Yet I have only the stories of a children’s book to guide me. I’ve read them so often that it’s hard to separate myself—and the way I view them—from the child I was when I first read them.}

He began to erase furiously. She sat up, then laid a hand on his arm.

\textit{I know that there are things I’m missing,}~he wrote.~\textit{Things that embarrass you, and I have guesses. I am not a fool. And yet, I get frustrated. With your flirtation and sarcasm—both behaviors where you apparently act opposite to what you want—I fear that I will never understand you.}

He stared with frustration at his board, wiping cloth held in one hand, charcoal in the other. The fire cracked quietly in the fireplace, throwing waves of overbright yellow against his clean-shaven face.

“I’m sorry,” she said, scooting closer to him. She wrapped her arms around his elbow, laying her head against his upper arm. He actually didn’t seem that much bigger than she, now that she was used to it. There had been men back in Idris who had stood as much as six and a half feet tall, and Susebron was only a few inches taller than that. Plus, because his body was so perfectly proportioned, he didn’t seem spindly or unnatural. He was normal, just bigger.

He glanced at her as she rested her head on his arm and closed her eyes. “I think you are doing better than you think. Most people back in my homeland didn’t understand me half as well as you do.”

He began to write, and she opened her eyes.

\textit{I find that hard to believe.}

“It’s true,” she said. “They kept telling me to become someone else.”

\textit{Who?}

“My sister,” she said with a sigh. “The woman you were supposed to marry. She was everything the daughter of a king should be. Controlled, soft-spoken, obedient, learned.”

\textit{She sounds boring,}~he wrote, smiling.

“Vivenna is a wonderful person,” Siri said. “She was always very kind to me. It’s just that~.~.~. well, I think even she felt that I should have been more reserved.”

\textit{I can’t understand that,}~he wrote.~\textit{You’re wonderful. So full of life and excitement. The priests and servants of the palace, they wear colors, but there’s no color inside of them. They just go about their duties, eyes down, solemn. You’ve got color on the inside, so much of it that it bursts out and colors everything around you.}

She smiled. “That sounds like BioChroma.”

\textit{You are more honest than BioChroma,}~he wrote.~\textit{My Breath, it makes things more bright, but it isn’t mine. It was given to me. Yours is your own.}

She felt her hair shift from the deep red into a golden tone, and she sighed softly with contentment, pulling herself a little closer to him.

\textit{How do you do that?}~he wrote.

“Do what?”

\textit{Change your hair.}

“That one was unconscious,” she said. “It goes blond if I feel happy or content.”

\textit{You’re happy, then?}~he wrote.~\textit{With me?}

“Of course.”

\textit{But when you speak of the mountains, there is such longing in your voice.}

“I miss them,” she said. “But if I left here, I’d miss you too. Sometimes, you can’t have everything you want, since the wants contradict each other.”

They fell silent for a time, and he set aside his board, hesitantly wrapping his arm around her and leaning back against the headboard. A blushful tinge of red crept into her hair as she realized that they were still sitting on the bed, and she was snuggling up beside him wearing only her shift.

\textit{But, well,}~she thought,~\textit{we}~are~\textit{married, after all.}

The only thing that spoiled the moment was the occasional rumbling of her stomach. After a few minutes, Susebron reached for his board.

\textit{You are hungry?}~he wrote.

“No,” she said. “My stomach is an anarchist; it likes to growl when it’s full.”

He paused.~\textit{Sarcasm?}

“A poor attempt,” she said. “It’s all right—I’ll survive.”

\textit{Didn’t you eat before you came to my chambers?}

“I did,” she said. “But growing that much hair is draining. It always leaves me hungry.”

\textit{It makes you hungry every night?}~he asked, writing quickly.~\textit{And you didn’t say anything?}

She shrugged.

\textit{I will get you food.}

“No, we can’t afford to expose ourselves.”

\textit{Expose what?}~he wrote.~\textit{I am God King—I have food whenever I wish it. I have sent for it at night before. This will not be odd.}~He stood, walking toward the doorway.

“Wait!” she said.

He turned, glancing back at him.

“You can’t go to the door like that, Susebron,” she said, keeping her voice quiet, in case someone was listening. “You’re still fully dressed.”

He looked down, then frowned.

“Make your clothing look disheveled at least,” she said, quickly hiding his writing board.

He undid his neck buttons, then threw off his deep black overrobe, revealing an undergown. Like everything white near him, it gave off a halo of rainbow colors. He reached up, mussing his dark hair. He turned back to her, eyes questioning.

“Good enough,” she said, pulling the bedsheets up to her neck, covering herself. She watched curiously as Susebron rapped on the door with his knuckles.

It immediately opened.~\textit{He’s too important to open his own door,}~Siri thought.

He commanded food by putting a hand to his stomach, then pointing away. The servants—barely visible to Siri through the doorway—scuttled away at his order. He turned as the door closed, walking back to sit beside her on the bed.

A few minutes later, servants arrived at the room with a dining table and a chair. They set the table with large amounts of food—everything from roasted fish to pickled vegetables and simmering shellfish.

Siri watched with amazement.~\textit{There’s no way they fixed it that quickly. They simply had it waiting in the kitchens, should their god happen to grow hungry.}

It was wasteful to the point of extravagance, but it was also wondrous. It bespoke a lifestyle that her people back in Idris couldn’t even imagine, one representative of an uncomfortable imbalance in the world. Some people starved; others were so wealthy that they never even~\textit{saw}most meals that were made for them.

The servants set only one chair at the table. Siri watched as they brought in plate after plate. They couldn’t know what the God King wanted, so they apparently brought him some of everything. They filled the table, then retreated as Susebron pointed for them to go.

The scents were almost too much for Siri in her hungered state. She waited, tense, until the door closed. Then she threw off the sheets and rushed over. She had thought the meals prepared for her were extravagant, but they were nothing compared with this feast. Susebron gestured toward the chair.

“Aren’t you going to eat?” she asked.

He shrugged.

She walked over and took one of the blankets from the bed, then spread it on the stone floor. “What looks good to you?” she said, approaching the table.

He pointed at the plate of simmering mussels and several of the breads. She moved these, along with a dish that didn’t appear to have any fish in it—a bowl of exotic fruits tossed in some kind of creamy sauce—to the cloth. She then sat down and began eating.

Susebron carefully situated himself on the floor. He managed to look dig nified even when wearing only his undergown. Siri reached over and handed him his board.

\textit{This is very odd,}~he said.

“What?” she asked. “Eating on the floor?”

He nodded.~\textit{Dining is such a production for me. I eat some of what is on a plate, then servants pull it away, wipe my face, and bring me another one. I never finish an entire dish, even if I like it.}

Siri snorted. “I’m surprised they don’t hold the spoon for you.”

\textit{They did when I was younger,}~Susebron wrote, flushing.~\textit{I eventually got them to let me do it myself. It’s hard, when you can’t speak with anyone.}

“I can imagine,” Siri said between mouthfuls. She eyed Susebron, who ate with small, reserved bites. She felt a slight stab of shame at how fast she was eating, then decided she didn’t care. She put aside the fruit dish and fetched several pastries from the table.

Susebron eyed her as she began to eat one after another.~\textit{Those are Pahn Kahl tinkfans,}he wrote.~\textit{One takes only small bites, making sure to eat a piece of bread between to clear away the taste. They are a delicacy and—}

He broke off as Siri picked up an entire pastry and shoved it into her mouth. She smiled at him, then continued chewing.

After a moment of looking stunned, he wrote on his board again.~\textit{You realize that children in the stories who gorged themselves usually ended up being thrown off of cliffs?}

Siri stuffed another crispbread into her mouth beside the first, dusting her fingers and face with powdered sugar in the process, her cheeks bulging.

Susebron watched her, then reached over and took a whole one himself. He inspected it, then shoved it into his mouth.

Siri laughed, nearly spitting out bits of pastry onto the blanket. “And so my corruption of the God King continues,” she said once she could speak.

He smiled.~\textit{This is very curious,}~he wrote, eating another crispbread. Then another. Then another.

Siri watched him, raising an eyebrow. “One would think that as God King, you would~\textit{at least}~be able to eat sweets whenever you want.”

\textit{I have many rules that others need not follow,}~he wrote as he chewed.~\textit{The stories explained this. Much is required of a prince or a king. I would rather have been born a peasant.}

Siri raised an eyebrow. She had a feeling that he’d be surprised if he actually had to experience things like hunger, poverty, or even discomfort. However, she left him his illusions. Who was she to chastise?

\textit{You are the one who was hungry,}~he wrote.~\textit{But I am the one doing all the eating!}

“They obviously don’t feed you enough,” Siri said, trying a slice of bread.

He shrugged, continuing to eat. She watched him, wondering if eating was different for him, with no tongue. Did that affect his ability to taste? He certainly still seemed to like the sweets. Thinking of her tongue made her mind turn to darker topics.~\textit{We can’t just keep going on like this,}~she thought.~\textit{Playing around at night, pretending like the world isn’t going on without us. We’re going to get crushed.}

“Susebron,” she said. “I think we need to find a way to expose what your priests have been doing to you.”

He looked up, then wrote,~\textit{What do you mean?}

“I mean that we should have you try to talk to the common people,” she said. “Or maybe some of the other gods. The priests gain all of their power by associating with you. If you choose to communicate through someone else, it would overthrow them.”

\textit{Do we need to do that?}

“Pretend with me for a moment that we do,” she said.

\textit{Very well,}~he wrote.~\textit{But how, exactly, would I communicate with someone else? I can’t exactly stand up and begin shouting.}

“I don’t know. Notes, perhaps?”

He smiled.~\textit{There is a story about that in my book. A princess trapped in a tower who throws notes out into the ocean waters. The king of the fishes finds them.}

“I doubt the king of fishes cares about our predicament,” Siri said flatly.

\textit{Such a creature is only slightly less fantastic than the possibility of my notes being found and interpreted correctly. If I threw them out the window, nobody would believe that the God King had written them.}

“And if you passed them to servants?”

He frowned.~\textit{Assuming that you are right, and that my priests are working against me, then wouldn’t it be foolhardy to trust the servants they employ?}

“Perhaps. We could try a Pahn Kahl servant.”

\textit{None of them attend me, for I am the God King,}~he wrote.~\textit{Besides, what if we did get a servant or two on our side? How would that expose the priests? Nobody would believe a Pahn Kahl servant who contradicted the priests.}

She shook her head. “I suppose you could try making a scene, running away or causing a distraction.”

\textit{When outside of the palace, I am constantly attended by a troop of hundreds. Awakeners, soldiers, guards, priests, and Lifeless warriors. Do you honestly think I could make any kind of a scene without being rushed away before I could communicate with anyone?}

“No,” she admitted. “But we have to do something! There has to be a way out of this.”

\textit{I do not see one. We need to work with the priests, not against them. Perhaps they know more about why the God Kings die. They could tell us—I can speak to them, using the artisans’ script.}

“No,” Siri said. “Not yet. Let me think first.”

\textit{Very well,}~he wrote, then tried another pastry.

“Susebron~.~.~.” she finally said. “Would you consider running away with me? Back to Idris?”

He frowned.~\textit{Perhaps,}~he finally wrote.~\textit{That seems extreme.}

“What if I could prove that the priests are trying to kill you? And what if I could provide a way out—someone to smuggle us from the palace and out of the city?”

The concept obviously bothered him.~\textit{If it is the only way,}~he wrote,~\textit{then I will go with you. But I do not believe that we will get to that point.}

“I hope you’re right,” she said.~\textit{But if you’re not,}~she thought,~\textit{then we’re escaping. We’ll take our chances back with my family, war or no war.}

