% \section{Chapter Thirty-Eight}
\chapter{}

Lightsong sat on the edge of his bed, sweat thick on his brow as he stared down at the floor in front of him. He was breathing heavily.

Llarimar eyed a lesser scribe, who lowered his pen. Servants clustered around the edges of the bedchamber. They had, at his request, woken him up unusually early in the morning.

“Your Grace?” Llarimar asked.

\textit{It’s nothing,}~Lightsong thought.~\textit{I dream of war because I’m thinking about it. Not because of prophecy. Not because I’m a god.}

It felt so real. In the dream he had been a man, on the battlefield, with no weapon. Soldiers had died around him. Friend after friend. He had known them, each one close to him.

\textit{A war against Idris wouldn’t be like that,}~he thought.~\textit{It would be fought by our Lifeless.}

He didn’t want to acknowledge that his friends during the dream hadn’t been wearing bright colors. He hadn’t been seeing through the eyes of a Hallandren soldier, but an Idrian. Perhaps that was why it had been such a slaughter.

\textit{The Idrians are the ones threatening us. They’re the rebels who broke off, maintaining a second throne inside of Hallandren borders. They need to be quelled.}

\textit{They deserve it.}

“What did you see, Your Grace?” Llarimar asked again.

Lightsong closed his eyes. There were other images. The recurring ones. The glowing red panther. The tempest. A young woman’s face, being absorbed by darkness. Eaten alive.

“I saw Blushweaver,” he said, speaking only of the very last part of the dreams. “Her face red and flushed. I saw you, and you were sleeping. And I saw the God King.”

“The God King?” Llarimar asked, sounding excited.

Lightsong nodded. “He was crying.”

The scribe wrote the images down. Llarimar, for once, didn’t prompt further. Lightsong stood, forcing the images out of his mind. Yet he couldn’t ignore that his body felt weak. It was his feast day, and he would have to take in a Breath or he would die.

“I’m going to need some urns,” Lightsong said. “Two dozen of them, one for each of the gods, painted after their colors.”

Llarimar gave the order without even asking why.

“I’ll also need some pebbles,” Lightsong said as the servants dressed him. “Lots of them.”

Llarimar nodded. Once Lightsong was dressed, he turned to leave the room. Off once again to feed on the soul of a child.

\orn

Lightsong threw a pebble into one of the urns in front of him. It made a slight ringing sound.

“Well done, Your Grace,” Llarimar complimented him, standing beside Lightsong’s chair.

“Nothing to it,” Lightsong said, tossing another pebble. It fell short of the intended urn, and a servant rushed forward, plucking it off the ground and depositing it in the proper container.

“I appear to be a natural,” Lightsong noted. “I get it in every time.” He felt much better, having been given fresh Breath.

“Indeed, Your Grace,” Llarimar said. “I believe that Her Grace the goddess Blushweaver is approaching.”

“Good,” Lightsong said, throwing another pebble. He hit the target this time. Of course, the urns were only a few feet from his seat. “I can show off my pebble-throwing skills.”

He sat on the green of the courtyard, a cool breeze blowing, his pavilion set up just inside the court’s gates. He could see the blocking wall, the one that kept him from looking out at the city proper. With the wall in the way, it was a rather depressing sight.

\textit{If they’re going to lock us in here,}~he thought,~\textit{they could at least give us the courtesy of a decent view out.}

“What in the name of the Iridescent Tones are you doing?”

Lightsong didn’t need to look to know that Blushweaver was standing with hands on hips beside him. He threw another pebble.

“You know,” he said, “it’s always struck me as strange. When we say oaths like that, we use the colors. Why not use our own names? We are, allegedly, gods.”

“Most gods don’t like their names being used as an oath,” Blushweaver said, sitting beside him.

“Then they are far too pompous for my taste,” Lightsong said, tossing a pebble. It missed, and a servant deposited it. “I, personally, should find it very flattering to have my name used as an oath. Lightsong the Brave! Or, by Lightsong the Bold! I suppose that’s a bit of a mouthful. Perhaps we could shorten it to a simple Lightsong!”

“I swear,” she said. “You are getting stranger by the day.”

“No, actually,” he said. “You~\textit{didn’t}~swear in that particular statement. Unless you’re proposing we should swear using the personal pronoun.~\textit{You!}~So, your line at this point is ‘What in the name of You are you doing?’~”

She grumbled at him under her breath.

He eyed her. “I certainly don’t deserve that yet. I’ve barely gotten started. Something else must be bothering you.”

“Allmother,” she said.

“Still won’t give you the Commands?”

“Refuses to even speak with me now.”

Lightsong threw a pebble into one of the urns. “Ah, if only she knew the refreshing sense of frustration she was missing out on knowing by refusing your acquaintance.”

“I’m not that frustrating!” Blushweaver said. “I’ve actually been rather charming with her.”

“Then that is your problem, I surmise,” Lightsong said. “We’re gods, my dear, and we quickly grow tired of our immortal existences. Surely we seek for extreme ranges in emotion—good or bad, it doesn’t matter. In a way, it’s the~\textit{absolute value}~of emotion that is important, rather than the positive or negative nature of that emotion.”

Blushweaver paused. So did Lightsong.

“Lightsong, dear,” she said. “What in the name of You did that mean?”

“I’m not exactly sure,” he said. “It just kind of came out. I can visualize what it means in my head, though. With numbers.”

“Are you all right?” she asked, sounding genuinely concerned.

Images of warfare flashed in his mind. His best friend, a man he didn’t know, dying with a sword through the chest. “I’m not sure,” he said. “Things have been rather strange for me lately.”

She sat quietly for a moment. “You want to go back to my palace and frolic? That always makes me feel better.”

He tossed a pebble, smiling. “You, my dear, are incorrigible.”

“I’m the goddess of lust, for Your sake,” she said. “I’ve got to fill the role.”

“Last I checked,” he said, “you were goddess of honesty.”

“Honesty and honest emotions, my dear,” she said sweetly. “And let me tell you, lust is one of the most honest of all emotions. Now, what~\textit{are}~you doing with those silly pebbles?”

“Counting,” he said.

“Counting your inanities?”

“That,” Lightsong said, tossing another pebble, “and counting the number of priests who come through the gates wearing the colors of each god or goddess.”

Blushweaver frowned. It was midday, and the gates were fairly busy with the comings and goings of servants and performers. There were only occasionally priests or priestesses, however, since they would have been required to come in early to attend their gods.

“Each time a priest of a particular god enters,” Lightsong said, “I toss a pebble into the urn representing that god.”

Blushweaver watched him toss—and miss—with another pebble. As he’d instructed, the servants picked the pebble up and put it in the proper urn. Violet and silver. To the side, one of Hopefinder’s priestesses rushed across the green toward her god’s palace.

“I’m baffled,” Blushweaver finally said.

“It’s easy,” Lightsong said. “You see someone wearing purple, you throw a pebble in the urn of the same color.”

“Yes, dear,” she said. “But~\textit{why}?”

“To keep track of how many priests of each god enter the court, of course,” Lightsong said. “They’ve slowed to nearly a trickle. Scoot, would you mind counting?”

Llarimar bowed and then gathered several servants and scribes, ordering them to empty the urns and count the contents of each one.

“My dear Lightsong,” Blushweaver said. “I~\textit{do}~apologize if I’ve been ignoring you lately. Allmother has been rudely unresponsive to my suggestions. If my lack of attention has caused your fragile mind to snap~.~.~.”

“My mind is quite unsnapped, thank you,” Lightsong said, sitting up, watching the servants count.

“Then, you must be so very bored,” Blushweaver continued. “Perhaps we can come up with something to entertain you.”

“I’m well entertained.” He smiled even before the counting results were in. Mercystar had one of the smallest piles.

“Lightsong?” Blushweaver asked. Nearly all of her playful attitude was gone.

“I ordered my priests in early today,” Lightsong said, glancing at her. “And to set up position here, in front of the gates, before the sun even rose. We’ve been counting priests for some six hours now.”

Llarimar walked over, handing Lightsong a list of the gods and the number of priests who had entered wearing their colors. Lightsong scanned it, nodding to himself.

“Some of the gods have had over a hundred priests report for ser vice, yet a couple of them have had barely a dozen. Mercystar is one of those.”

“So?” Blushweaver asked.

“So,” Lightsong said. “I’m going to send my servants to watch and count at Mercystar’s palace, keeping track of the number of priests who are there. I already suspect that I know what they’ll find. Mercystar doesn’t have fewer priests than the rest of us. They’re just getting into the court by a different route.”

Blushweaver looked at him blankly, but then cocked her head. “The tunnels?”

Lightsong nodded.

Blushweaver leaned back, sighing. “Well at least you’re not insane or bored. You’re just obsessed.”

“Something’s going on with those tunnels, Blushweaver. And it relates to the servant who was murdered.”

“Lightsong, we have~\textit{much}~bigger problems to worry about!” Blushweaver shook her head, holding her forehead as if she could have a headache. “I can’t believe that you’re still bothering with this. Honestly! The kingdom is about to go to war—for the first time, your position in the assembly is important—and you’re worrying about how priests are getting into the court?”

Lightsong didn’t respond immediately. “Here,” he finally said, “let me prove my point to you.”

He reached over to the side of his couch and picked a small box up off the ground. He held it up, showing it to Blushweaver.

“A box,” she said flatly. “What a convincing argument you make.”

He pulled the top off of the box, leaving a small grey squirrel sitting in his hand. It stood perfectly still, staring forward, fur blowing in the breeze.

“A Lifeless rodent,” Blushweaver said. “That’s~\textit{much}~better. I feel myself being swayed already.”

“The person who broke into Mercystar’s palace used this as a distraction,” Lightsong said. “Do you know anything about breaking Lifeless, my dear?”

She shrugged.

“I didn’t either,” Lightsong said. “Not until I required my priests to break this one. Apparently, it requires~\textit{weeks}~to take control of a Lifeless for which you do not have the right security phrases. I’m not even sure how the process goes—has something to do with Breath and torture, apparently.”

“Torture?” she said. “Lifeless can’t feel.”

Lightsong shrugged. “Anyway, my servants broke this one for me. The stronger and more skilled the Awakener who created the Lifeless, the more difficult it is to break it.”

“That’s why we need to get the Commands from Allmother,” Blushweaver said. “If something were to happen to her, her ten thousand would become useless to us. It would take years to break that many Lifeless!”

“The God King and some of Allmother’s priestesses have the codes as well,” Lightsong said.

“Oh,” Blushweaver said, “and you think~\textit{he}~is going to just give them over to us? Assuming we’re even allowed to talk to him?”

“I’m just pointing out that a single assassination couldn’t ruin our entire army,” Lightsong said, holding up the squirrel. “That’s not the point. The point is that whoever made this squirrel held quite a bit of Breath and knew what he was doing. The creature’s blood has been replaced with ichor-alcohol. The sutures are perfect. The Commands controlling the rodent were extremely strong. It’s a marvelous piece of BioChromatic art.”

“And?” she asked.

“And he released it in Mercystar’s palace,” Lightsong said. “Creating a distraction so that he could sneak into those tunnels. Someone else followed the intruder, and this second person killed a man to keep him from revealing what he’d seen. Whatever is in those tunnels—wherever they lead—it’s important enough to waste Breath on. Important enough to kill for.”

Blushweaver shook her head. “I still can’t believe you are even worrying about this.”

“You said you knew about the tunnels,” Lightsong said. “I had Llarimar ask around, and others know of them too. They’re used for storage beneath the palaces, as said. Different gods have ordered them constructed at various times during the history of the court.

“But,” he continued, excited, “they would also be the perfect place to set up a clandestine operation! The court is outside the jurisdiction of the regular city guards. Each palace is like a little autonomous country! Expand a few of those cellars so that their tunnels connect with others, dig them out past the walls so that you can come and go secretly~.~.~.”

“Lightsong,” Blushweaver said. “If something~\textit{that}~secret were going on, then why would the priests use those tunnels to come into the court? Wouldn’t that be a little suspicious? I mean, if you noticed it, how hard could it be to discover?”

Lightsong paused, then flushed slightly. “Of course,” he said. “I got so wrapped up in pretending to be useful that I forgot myself! Thank you so much for reminding me that I am an idiot.”

“Lightsong, I didn’t mean—”

“No, it’s quite all right,” he said, standing. “Why bother? I need to remember who I am. Lightsong, self-hating god. The most useless person ever granted immortality. Just answer one question for me.”

Blushweaver paused. “What question?”

“Why?” he asked, looking at her. “\textit{Why}~do I hate being a god? Why do I act so frivolous? Why do I undermine my own authority. Why?”

“I always assumed it was because you were amused by the contrast.”

“No,” he said. “Blushweaver, I was~\textit{like this from the first day.}~When I awoke, I refused to believe I was a god. Refused to accept my place in this pantheon and this court. I’ve acted accordingly ever since. And, if I might say, I’ve gotten quite a bit more clever about it as the years have passed. Which is beside the point. The thing I must focus on—the important point here—is~\textit{why.}”

“I don’t know,” she confessed.

“I don’t either,” he said. “But whoever I was before, he’s trying to get out. He keeps whispering for me to dig at this mystery. Keeps warning me that I’m no god. Keeps prompting me to deal with all this in a frivolous way.” He shook his head. “I don’t know who I was—nobody will tell me. But I’m beginning to have suspicions. I was a person who couldn’t simply sit and let something unexplained slide away into the fog of memory. I was a man who hated secrets. And I’m only just beginning to understand how many secrets there are in this court.”

Blushweaver looked taken aback.

“Now,” he said, walking away from the pavilion, his servants hurrying to catch up, “if you will excuse me, I have some business to attend to.”

“What business?” Blushweaver demanded, rising.

He glanced back. “To see Allmother. There are some Lifeless Commands that need to be dealt with.”

