\section{Chapter Thirty}

Lightsong!” Blushweaver said, hands on hips. “What in the name of the Iridescent Tones are you doing?”

Lightsong ignored her, instead applying his hands to the clump of muddy clay in front of him. His servants and priests stood in a large ring, looking nearly as confused as Blushweaver—who had arrived at his pavilion just a few moments before.

The pottery wheel spun. He held the clay, trying to get it to stay in place. Sunlight shone in through the sides of the pavilion, and the neatly manicured grass under his table was flecked with clay. As the wheel sped up, the clay twirled round, flipping out clods and clumps. Lightsong’s hands became soaked with grimy, slick clay, and it didn’t take long for the entire mess to flip off the wheel and squish to the ground.

“Hum,” he said, regarding it.

“Have you taken leave of your senses?” Blushweaver asked. She wore one of her customary dresses—which meant nothing on the sides, very little at the top, and only slightly more through the front and back. She had her hair up in an intricately twisting woven pattern of braids and ribbon. Likely the work of a master stylist, who had been invited into the court to perform for one of the gods.

Lightsong hopped to his feet, holding his hands out to either side as servants rushed to wash them off. Others came and wiped the bits of clay from his fine robes. He stood thoughtfully as other servants removed the pottery wheel.

“Well?” Blushweaver asked. “What~\textit{was}~that?”

“I just discovered that I am no good at pottery,” Lightsong said. “Actually, I am worse than ‘no good.’ I am pathetic. Ridiculously bad. Can’t even get the blasted clay to stay on the wheel.”

“Well what did you expect?”

“I’m not sure,” Lightsong said, walking across the pavilion toward a long table. Blushweaver—obviously annoyed at being led along—followed. Lightsong suddenly grabbed five lemons off of the table and threw them into the air. He proceeded to juggle them.

Blushweaver watched. And, for just a moment, she looked honestly concerned. “Lightsong?” she asked. “Dear. Is~.~.~. everything all right?”

“I have never practiced juggling,” he said, watching the lemons. “Now, please grab that guava fruit.”

She hesitated, then carefully picked up the guava.

“Throw it,” Lightsong said.

She tossed it at him. He deftly plucked it from the air, then threw it into the pattern with the lemons. “I didn’t know I could do this,” he said. “Not before today. What do you make of it?”

“I~.~.~.” she cocked her head.

He laughed. “I don’t think I’ve ever seen you at a loss for words, my dear.”

“I don’t know that I’ve ever seen another god throwing fruit into the air.”

“It’s more than this,” Lightsong said, dipping down as he nearly lost one of the lemons. “Today I have discovered that I know a surprising number of sailing terms, that I am fantastic at mathematics, and that I have a fairly good eye for sketching. On the other hand, I know nothing about the dyeing industry, horses, or gardening. I have no talent for sculpting, I can’t speak any foreign languages, and—as you’ve seen—I’m terrible at pottery.”

Blushweaver watched him for a second.

He looked at her, letting the lemons drop but snatching the guava out of the air. He tossed it to a servant, who began peeling it for him. “My previous life, Blushweaver. These are skills that I—Lightsong—have no right to know. Whoever I was before I died,~\textit{he}~could juggle. He knew about sailing. And he could sketch.”

“We’re not supposed to worry about the people we were before,” Blushweaver said.

“I’m a god,” Lightsong said, taking back a plate containing the peeled and sliced guava, then offering a piece to Blushweaver. “And, by Kalad’s Phantoms, I’ll worry about whatever I please.”

She paused, then smiled and took a slice. “Just when I thought I had you figured out~.~.~.”

“You didn’t have me figured out,” he said lightly. “And neither did I. That’s the point. Shall we go?”

She nodded, joining him as they began to cross the lawn, their servants bringing parasols to shade them. “You can’t tell me that you’ve never wondered,” Lightsong said.

“My dear,” she replied, sucking on a guava piece, “I was~\textit{boring}~before.”

“How do you know?”

“Because I was an ordinary person! I would have been~.~.~. Well, have you~\textit{seen}~regular women?”

“Their proportions aren’t quite up to your standards, I know,” he said. “But many are quite attractive.”

Blushweaver shivered. “Please. Why would you want to know about your normal life? What if you were a murderer or a rapist? Worse, what if you had bad fashion sense?”

He snorted at the twinkle in her eye. “You act so shallow. But I see the curiosity. You should try some of these things, let them tell you a little of who you were. There must have been something special about you for you to have Returned.”

“Hum,” she said, smiling and sidling up to him. He stopped as she ran her finger down the front of his chest. “Well, if you’re trying new things today, maybe there’s something else you ought to think about.~.~.~.”

“Don’t try to change the subject.”

“I’m not,” she said. “But, how will you know who you were if you don’t try? It would be an~.~.~. experiment.”

Lightsong laughed, pushing her hand away. “My dear, I fear you would find me less than satisfactory.”

“I think you overestimate me.”

“That’s impossible.”

She paused, flushing slightly.

“Uh~.~.~.” Lightsong said. “Hum. I didn’t exactly mean~.~.~.”

“Oh, bother,” she said. “Now you’ve spoiled the moment. I was about to say something very clever, I just know it.”

He smiled. “Both of us, at a loss for words in one afternoon. I do believe we’re losing our touch.”

“\textit{My}~touch is perfectly fine, which you’d discover if you’d just let me show you.”

He rolled his eyes and continued to walk. “You’re hopeless.”

“When all else fails, use sexual innuendo,” she said lightly, joining him. “It always brings the focus back to where it belongs. On me.”

“Hopeless,” he said again. “But, I doubt we have time for me to chastise you again. We’ve arrived.”

Indeed, Hopefinder’s palace was before them. Lavender and silver, it had a pavilion out front prepared with three tables and food. Naturally, Blushweaver and Lightsong had arranged for the meeting ahead of time.

Hopefinder the Just, god of innocence and beauty, stood up as they approached. He appeared to be about thirteen years old. By apparent physical age, he was the youngest of the gods in the court. But they weren’t supposed to acknowledge such discrepancies. After all, he’d Returned when his body had been two, which made him—in god years—Lightsong’s se nior by six years. In a place where most gods didn’t last twenty years, and the average age was probably closer to ten, six years difference was very significant.

“Lightsong, Blushweaver,” Hopefinder said, stiff and formal. “Welcome.”

“Thank you, dear,” Blushweaver said, smiling at him.

Hopefinder nodded, then gestured toward the tables. The three small tables were separate, but set close enough together for the meal to remain intimate while giving each god his or her own space.

“How have you been, Hopefinder?” Lightsong asked, sitting.

“Very well,” Hopefinder said. His voice always seemed a little too mature for his body. Like a boy trying to imitate his father. “There was a particularly difficult case during petitions this morning. A mother with a child who was dying of the fevers. She’d already lost her other three, as well as her husband. All in the space of a year. Tragic.”

“My dear,” Blushweaver said with concern. “You’re not actually considering~.~.~. passing your Breath, are you?”

Hopefinder sat. “I don’t know, Blushweaver. I am old. I feel old. Perhaps it is time for me to go. I’m fifth most aged, you know.”

“Yes, but with the times growing so exciting!”

“Exciting?” he asked. “Why, they’re calming down. The new queen is here, and my sources in the palace say that she’s pursuing her duties to produce an heir with great vigor. Stability will soon arrive.”

“Stability?” Blushweaver asked as the servants bought them each a chilled soup. “Hopefinder, I find it hard to believe that you’re~\textit{so}~uninformed.”

“You think the Idrians plan to use the new queen in a play for the throne,” Hopefinder said. “I know what you’ve been doing, Blushweaver. I disagree.”

“And the rumors out in the city?” Blushweaver said. “The Idrian agents who are causing such a ruckus? This so-called second princess somewhere in the city?”

Lightsong paused, spoon halfway to his lips.~\textit{What was that?}

“The city’s Idrians are~\textit{always}~creating one crisis or another,” Hopefinder said, waving his fingers dismissively. “What was that disturbance six months ago, the rebel on the outer dye plantations? He died in prison, I recall. Foreign workers rarely provide a stable societal underclass, but I don’t fear them.”

“They’ve never claimed to have a royal agent working with them,” Blushweaver said. “Things could get out of hand~\textit{very}~quickly.”

“My interests in the city are quite secure,” Hopefinder said, lacing his fingers in front of him. The servants took away his soup. He’d taken only three sips. “How about yours?”

“That’s what this meeting is for,” Blushweaver said.

“Excuse me,” Lightsong said, raising a finger. “But what in the~\textit{Colors}~are we talking about?”

“Unrest in the city, Lightsong,” Hopefinder said. “Some of the locals are unsettled by the prospect of war.”

“They could turn dangerous very easily,” Blushweaver said, stirring her soup with a lazy motion. “I think that we should be prepared.”

“I am,” Hopefinder said, watching Blushweaver with his too-young face. Like all younger Returned—the God King included—Hopefinder would continue to age until his body reached maturity. Then, he would stop aging—just over the brink into the prime adulthood—until he gave up his Breath.

He acted so much like an adult. Lightsong hadn’t interacted much with children, but some of his attendants—when training—were youths. Hopefinder was not like those. All accounts said that Hopefinder, like other young Returned, had matured very quickly during his first year of life, coming to think and speak as an adult while his body was still that of a young child.

Hopefinder and Blushweaver continued to talk about the stability of the city, mentioning various acts of vandalism that had occurred. War plans stolen, city supply stations poisoned. Lightsong let them talk.~\textit{He doesn’t seem to find Blushweaver’s beauty distracting,}~he thought as he watched. She turned to the fruit course, acting characteristically lascivious as she sucked on pieces of pineapple. Hopefinder either didn’t care, or didn’t notice, as she leaned forward, showing an impressive amount of cleavage.

\textit{Something}~is~\textit{different about him,}~Lightsong thought.~\textit{He Returned when he was a child and acted like one for a very short time. Now, he’s an adult in some ways, but a child in others.}

The transformation had made Hopefinder more mature. He was also taller and more physically impressive than ordinary boys his age, even if he didn’t have the chiseled, majestic features of a fully grown god.

\textit{And yet,}~Lightsong thought, eating a piece of pineapple,~\textit{different Gods have different body styles. Blushweaver is inhumanly well endowed, particularly for how thin she is. Yet Mercystar is plump and curvaceous all around. Others, like Allmother, look physically old.}

Lightsong knew he didn’t deserve his powerful physique. Like the knowledge of how to juggle, he somehow understood that a person usually had to work hard at manual labor to have such a muscular body. Lounging about, eating and drinking, should have made him plump and flabby.

\textit{But there have been gods who were fat,}~he thought, remembering some of the pictures he had seen of Returned who had come before him.~\textit{There was a time in our culture’s history when that was seen as the ideal.~.~.~.}~Did Returned looks have something to do with the way society saw them? Perhaps their opinion of ideal beauty? That would certainly explain Blushweaver.

Some things survived the transformation. Language. Skills. And, as he thought about it, social competence. Considering the fact that the gods spent their lives locked up atop a plateau, they probably should have been far less well adjusted than they were. At the very least, they should have been ignorant and naive. Yet most of them were consummate schemers, sophisticates with a surprisingly good grasp of what happened in the outside world.

Memory itself didn’t survive. Why? Why could Lightsong juggle and understand the meaning of the word “bowsprit,” yet at the same time be unable to remember who his parents had been? And who was that face he saw in his dreams? Why had storms and tempests dominated his dreams lately? What was the red panther that had appeared, yet again, in his nightmares the night before?

“Blushweaver,” Hopefinder said, holding up a hand. “Enough. Before we go any further, I must point out that your obvious attempts to seduce me will gain you nothing.”

Blushweaver glanced away, looking embarrassed.

Lightsong shook himself out of his contemplations. “My dear Hopefinder,” he said. “She was\textit{not}~trying to seduce you. You must understand; Blushweaver’s aura of allure is simply a part of who she is; it’s part of what makes her so charming.”

“Regardless,” he said. “I will not be swayed by it or by her paranoid arguments and fears.”

“My contacts do not think that these things are simple ‘paranoia,’~” Blushweaver said as the fruit dishes were removed. A small chilled fish fillet arrived next.

“Contacts?” Hopefinder asked. “And just who are these ‘contacts’ you keep mentioning?”

“People within the God King’s palace itself.”

“We all have people in the God King’s palace,” Hopefinder said.

“I don’t,” Lightsong said. “Can I have one of yours?”

Blushweaver rolled her eyes. “My contact is~\textit{quite}~important. He hears things, knows things. War~\textit{is}~coming.”

“I don’t believe you,” he said, picking at his food, “but that doesn’t really matter now, does it? You’re not here to get me to believe you. You just want my army.”

“Your codes,” Blushweaver said. “Lifeless security phrases. What will it cost us to get them?”

Hopefinder picked at his fish some more. “Do you know, Blushweaver, why I find my existence so boring?”

She shook her head. “Honestly, I~\textit{still}~think you’re bluffing on that count.”

“I’m not,” he said. “Eleven years. Eleven years of peace. Eleven years to grow to sincerely loathe this system of government we have. We all attend the assembly court of judgment. We listen to the arguments. But most of us don’t matter. In any given vote, only those with sway in that field have any real say over anything. During war times, those of us with Lifeless Commands are important. The rest of the time, our opinion rarely matters.

“You want my Lifeless? Be welcome to them! I have had no opportunity to use them in eleven years, and I venture that another eleven will pass without incident. I will give you those Commands, Blushweaver—but only in exchange for~\textit{your}~vote. You sit on the council of social ills. You have an important vote practically every week. In exchange for my security phrases, you must promise to vote in social matters as I say, from now until one of us dies.”

The pavilion fell silent.

“Ah, so now you reconsider,” Hopefinder said, smiling. “I’ve heard you complain about your duties in court—that you find your votes trivial. Well, it’s not so easy to let go of them, is it? Your vote is all the influence you have. It isn’t flashy, but it is potent. It—”

“Done,” Blushweaver said sharply.

Hopefinder cut off.

“My vote is yours,” Blushweaver said, meeting his eyes. “The terms are acceptable. I swear it in front of your priests and mine, before another god even.”

\textit{By the Colors,}~Lightsong thought.~\textit{She really}~is~\textit{serious.}~Part of him had presumed, all along, that her posturing about the war was just another game. Yet the woman who stared Hopefinder in the eyes was not playing. She sincerely believed that Hallandren was in danger, and she wanted to make certain that the armies were unified and prepared. She cared.

And that left him worried. What had he gotten himself into? What if there really was a war? As he watched the interaction of the two gods, he was left chilled by how easily and quickly they dealt with the fate of the Hallandren people. To Hopefinder, his control of a quarter of the Hallandren armies should have been a sacred obligation. He was ready to toss that aside simply because he had grown bored.

\textit{Who am I to chastise another’s lack of piety?}~Lightsong thought.~\textit{I, who don’t even believe in my own divinity.}

And yet~.~.~. at that moment, as Hopefinder prepared to release his Commands to Blushweaver, Lightsong thought he saw something. Like a remembered fragment of a memory. A dream that he might never have dreamed.

A shining room, glowing, reflecting light. A room of steel.

A prison.

“Servants and priests, withdraw,” Hopefinder commanded.

They retreated, leaving the three gods alone beside their half-eaten meals, pavilion silk flapping slightly in the wind.

“The security phrase,” Hopefinder said, looking at Blushweaver, “is ‘A candle by which to see.’~”

It was the title of a famous poem; even Lightsong knew it. Blushweaver smiled. Speaking those words to any of Hopefinder’s ten thousand Lifeless in the barracks would allow her to override their current orders and take complete control of them. Lightsong suspected that by the end of the day, she’d make the trip down to the barracks—which lay at the base of the court, and were considered part of it—and begin imprinting Hopefinder’s soldiers with a new security phrase, known only to her and perhaps a few of her most trusted priests.

“And now, I withdraw,” Hopefinder said, standing. “There is a vote this evening at the court. You will attend, Blushweaver, and you will cast your vote in favor of the reformist arguments.”

With that, he left.

“Why do I feel like we’ve just been manipulated?” Lightsong asked.

“We only got manipulated, my dear, if there~\textit{isn’t}~war. If there is, then we may have just set ourselves up to save the entire court—perhaps the kingdom itself.”

“How very altruistic of us,” Lightsong said.

“We’re like that,” Blushweaver said as the servants returned. “So selfless at times it’s painful. Either way, that means we control two gods’ worth of Lifeless.”

“Mine and Hopefinder’s?”

“Actually,” she said, “I was speaking of Hopefinder’s and Mercystar’s. She confided hers to me yesterday, all the while talking about how comforting she found it that you’d taken a personal interest in the incident at her palace. That was very well done, by the way.”

She seemed to be fishing for something. Lightsong smiled. “No, I didn’t know that would encourage her to release her Commands to you. I was just curious.”

“Curious about a murdered servant?”

“Actually, yes,” Lightsong said. “The death of a servant of the Returned is quite disconcerting to me, particularly in its proximity to our own palaces.”

Blushweaver raised an eyebrow.

“Would I lie to you?” Lightsong asked.

“Only every time you claim you don’t want to sleep with me. Lies, brazen lies.”

“Innuendo again, my dear?”

“Of course not,” she said. “That was quite blatant. Regardless, I know that you are lying about that investigation. What was the~\textit{real}~purpose of it?”

Lightsong paused, then sighed, shaking his head, waving for a servant to bring back the fruit—he liked that better. “I don’t know, Blushweaver. In all honesty, I’m beginning to wonder if I might have been a kind of officer of the law in my previous life.”

She frowned.

“You know, like city watch. I was~\textit{extremely}~good at interrogating those servants. At least, that’s my own humble opinion.”

“Which we’ve already established is quite altruistic.”

“Quite,” he agreed. “I think this might explain how I ended up dying in a ‘bold’ way, giving me my name.”

Blushweaver raised an eyebrow. “I just always assumed you were found in bed with a much younger woman and her father killed you. Seems far more bold than dying from stab wounds while trying to catch some petty thief.”

“Your mockery slides right off of my altruistic humility.”

“Ah, indeed.”

“Either way,” Lightsong said, eating another chunk of pineapple. “I was a sheriff or investigator of some kind. I’ll bet that if I ever got my hands on a sword, I’d prove one of the best duelists this city has ever seen.”

She regarded him for a moment. “You’re serious.”

“Dead serious. Dead as a squirrel serious.”

She paused, looking puzzled.

“Personal joke,” he said, sighing. “But yes, I believe it. Though, there’s one thing I can’t figure out.”

“And that is?”

“How juggling lemons fits into it all.”

