% \section{Chapter Sixteen}
\chapter{}

“. . . still say that we cannot~\textit{possibly}~justify military action against Idris!” a priest shouted. The man wore blue and gold. It was Stillmark’s high priest—Lightsong couldn’t quite remember the man’s name. Nanrovah?

The argument was not unexpected. Lightsong leaned forward. Nanrovah and his master, Stillmark, were both staunch traditionalists. They tended to argue against pretty much every proposal, but were well respected. Stillmark was nearly as old as Blushweaver, and was considered wise. Lightsong rubbed his chin.

Opposing Nanrovah was Blushweaver’s own high priestess, Inhanna. “Oh, come now,” the woman said from the sands down below. “Do we really need to have~\textit{this}~argument again? Idris is nothing more than a rebel enclave set up inside the borders of our own kingdom!”

“They keep to themselves,” Nanrovah said. “Holding lands we don’t want anyway.”

“Lands we don’t want?” Blushweaver’s priestess said, sputtering. “They hold every single pass to the northern kingdoms! Every workable copper mine! They have military garrisons within striking distance of T’Telir! And they~\textit{still}~claim to be ruled by the rightful kings of Hallandren!”

Nanrovah fell silent, and there was a surprisingly large rumble of assent from the watching priests. Lightsong eyed them. “You’ve seeded the group with people sympathetic to your cause?” he asked.

“Of course,” Blushweaver said. “So did the others. I just did a better job.”

The debate continued, other priests stepping up to argue for and against an assault on Idris. The priests spoke the concerns of the people of the nation; part of their duty was to listen to the people and study issues of national import, then discuss them here so that the gods—who didn’t have the opportunity to go out among the people—could be kept informed. If an issue came to a head, the gods would make their judgments. They were divided into subgroups, each having responsibility for a certain area. Some gods were in charge of civic issues; others governed agreements and treaties.

Idris was not a new topic for the assembly. However, Lightsong had never seen the discussion become so explicit and extreme. Sanctions had been discussed. Blockades. Even some military pressure. But war? Nobody had said the word yet, but they all knew what the priests were discussing.

He could not dispel the images from his dreams—visions of death and pain. He did not accept them as prophetic, but he did acknowledge that they must have something to do with the worries inside his subconscious. He feared what war would do to them. Perhaps he was just a coward. It did seem that suppressing Idris would solve so much.

“You’re behind this debate, aren’t you,” he said, turning to Blushweaver.

“Behind it?” Blushweaver said sweetly. “Dear Lightsong, the priests decide the issues to be discussed. Gods don’t bother with such mundanity.”

“I’m sure,” Lightsong said, reclining. “You want my Lifeless Commands.”

“I wouldn’t say that,” Blushweaver said, “I just want you to be informed should you~.~.~.”

She trailed off as Lightsong gave her a flat look.

“Aw, Colors,” she swore. “Of~\textit{course}~I need your Commands, Lightsong. Why else would I go to all the trouble to get you up here? You’re a very difficult person to manipulate, you know.”

“Nonsense,” he said. “You just have to promise me that I won’t have to do a thing, and then I’ll do anything you want.”

“Anything?”

“Anything that doesn’t require doing anything.”

“That’s nothing, then.”

“Is it?”

“Yes.”

“Well, that’s something!”

Blushweaver rolled her eyes.

Lightsong was more troubled than he let on. The arguments for attack had never been so strong. There was proof of a military buildup in Idris and the highlanders had been particularly stingy with the northern passes lately. Beyond that, there was a growing belief that the Returned were weaker than they’d been in previous generations. Not less powerful in BioChroma, just less~.~.~. divine. Less benevolent, less wise. Lightsong happened to agree.

It had been three years since a Returned had given up his or her life to heal someone. The people were growing impatient with their gods. “There’s more, isn’t there?” he said, glancing at Blushweaver, who was still lounging back, delicately eating cherries. “What aren’t they saying?”

“Lightsong, dear,” she said. “You were right. Bring you to government proceedings, and it absolutely corrupts you.”

“I just don’t like secrets,” he said. “They make my brain itch, keep me awake at nights. Engaging in politics is like pulling off a bandage—best to get the pain over with quickly.”

Blushweaver pursed her lips. “Forced simile, dear.”

“Best I can do at the moment, I’m afraid. Nothing dulls the wit more quickly than politics. Now, you were saying~.~.~.”

She snorted. “I’ve told you already. The focus of all this is that woman.”

“The queen,” he said, glancing at the God King’s box.

“They sent the wrong one,” Blushweaver said. “The younger instead of the elder.”

“I know,” Lightsong said. “Clever of them.”

“Clever?” Blushweaver said. “It’s downright brilliant. Do you know what a fortune we paid these last twenty years to spy upon, study, and learn about the eldest daughter? Those of us who thought to be careful even studied the second daughter, the one they’ve made a monk. But the youngest? Nobody gave her half a thought.”

\textit{And so the Idrians send a random element into court,}~Lightsong thought.~\textit{One that upsets plans and conniving that our politicians have been working on for decades.}

It~\textit{was}~brilliant.

“Nobody knows~\textit{anything}~about her,” Blushweaver said, frowning deeply. She obviously did not like being taken by surprise. “My spies in Idris insist the girl is of little consequence—which makes me worry that she is even more dangerous than I’d feared.”

Lightsong raised an eyebrow. “And you don’t think, maybe, that you might be overreacting a tad?”

“Oh?” Blushweaver asked. “And tell me, what would~\textit{you}~do if you wanted to inject an agent into the court? Would you, perhaps, set up a decoy that you could display, drawing attention away from the~\textit{real}~agent, whom you could train secretly with a clandestine agenda?”

Lightsong rubbed his chin.~\textit{She has a point.}~Maybe. Living among so many scheming people tended to make one see plots everywhere. However, the plot that Blushweaver suggested had a very serious chance of being dangerous. What better way to get an assassin close to the God King than to send someone to marry him?

No, that wouldn’t be it. Killing the God King would just cause Hallandren to go on the rampage. But if they’d sent a woman skilled in the art of manipulation—a woman who could secretly poison the mind of the God King~.~.~.

“We need to be ready to act,” Blushweaver said. “I won’t sit and let my kingdom be pulled out from under me—I won’t idly be cast out as the royals once were. You control a fourth of our Lifeless. That’s ten thousand soldiers who don’t need to eat, who can march tirelessly. If we convince the other three with Commands to join us~.~.~.”

Lightsong thought for a moment, then nodded and stood.

“What are you doing?” Blushweaver asked, sitting up.

“I think I’ll go for a stroll,” Lightsong said.

“Where?”

Lightsong glanced over at the queen.

“Oh, blessed Colors,” Blushweaver said with a sigh. “Lightsong, do~\textit{not}~ruin this. We walk a very delicate line, here.”

“I’ll do my best.”

“I don’t suppose I can talk you out of interacting with her?”

“My dear,” Lightsong said, glancing backward. “I at least have to chat with her. Nothing would be more intolerable than being overthrown by a person with whom I’d never even had a nice conversation.”

\orn

Bluefingers wandered off sometime during the court proceedings. Siri didn’t notice—she was too busy watching the priests debate.

She had to be misunderstanding. Surely they couldn’t be thinking about attacking Idris. What would be the point? What would Hallandren gain? As the priests finished their discussion on that topic, Siri turned to one of her serving women. “What was that about?”

The woman glanced down, not answering.

“They sounded like they were discussing war,” Siri said. “They wouldn’t really invade, would they?”

The woman shuffled uncomfortably, then glanced at one of her companions. That woman rushed away. A few moments later, the servant returned with Treledees. Siri frowned slightly. She did~\textit{not}~like speaking with the man.

“Yes, Vessel?” the tall man said, eyeing her with his usual air of disdain.

She swallowed, refusing to be intimidated. “The priests,” she said. “What were they just discussing?”

“Your homeland of Idris, Vessel.”

“I know that much,” Siri said. “What do they want with Idris?”

“It seemed to me, Vessel, that they were arguing about whether or not to attack the rebel province and bring it back under proper royal control.”

“Rebel province?”

“Yes, Vessel. Your people are in a state of rebellion against the rest of the kingdom.”

“But you rebelled against us!”

Treledees raised an eyebrow.

\textit{Different viewpoints on history indeed,}~Siri thought. “I can see how somebody might think as you do,” she said. “But~.~.~. you wouldn’t really attack us, would you? We sent you a queen, just as you demanded. Because of that, the next God King will have royal blood.”

\textit{Assuming the current God King ever decides to consummate our marriage.~.~.~.}

Treledees simply shrugged. “It is likely nothing, Vessel. The gods simply needed to be apprised of the current political climate of T’Telir.”

His words didn’t offer Siri much comfort. She shivered. Should she be doing something? Trying to politic in Idris’s defense?

“Vessel,” Treledees said.

She glanced at him. His peaked hat was so tall it brushed the top of the canopy. In a city full of colors and beauty, for some reason Treledees’s long face seemed even bleaker for the contrast. “Yes?” she asked.

“There is a matter of some delicacy I fear that I must discuss with you.”

“What is that?”

“You are familiar with monarchies,” he said. “Indeed, you are the daughter of a king. I assume that you know how important it is to a government that there be a secure, stable plan for succession.”

“I guess.”

“Therefore,” Treledees said, “you realize that it is of no small importance that an heir be provided as~\textit{quickly}~as possible.”

Siri blushed. “We’re working on that.”

“With all due respect, Vessel,” Treledees said. “There is some degree of disagreement upon whether or not you actually are.”

Siri blushed further, hair reddening as she glanced away from those callous eyes.

“Such arguments, of course, are limited to those inside the palace,” Treledees said. “You can trust in the discretion of our staff and priests.”

“How do you know?” Siri said, looking up. “I mean, about us. Maybe we~\textit{are}~.~.~. working on it. Maybe you’ll have your heir before you know it.”

Treledees blinked once, slowly, regarding her as if she were a ledger to be added up and accounted. “Vessel,” he said. “Do you honestly think that we would take an unfamiliar, foreign woman and place her in close proximity to our most holy of gods without keeping watch?”

Siri felt her breath catch, and she had a moment of horror.~\textit{Of course!}~she thought.~\textit{Of course they were watching. To make sure I didn’t hurt the God King, to make certain things went according to plan.}

Being naked before her husband was bad enough. To be so exposed before men like Treledees—men who saw her not as a woman, but as an annoyance—felt even worse, somehow. She found herself slouching, arms wrapping around her chest and its revealing neckline.

“Now,” Treledees said, leaning in. “We understand that the God King may not be what you expected. He may even be~.~.~. difficult to work with. You are a woman, however, and should know how to use your charms to motivate.”

“How can I ‘motivate’ if I can’t talk to him or look at him?” she snapped.

“I’m sure you’ll find a way,” Treledees said. “You only have one task in this palace. You want to make certain Idris is protected? Well, give the God King’s priesthood what we desire, and your rebels will earn our appreciation. My colleagues and I have no small influence in the court, and we can do much to safeguard your homeland. All we ask is that you perform this single duty. Give us an heir. Give the kingdom stability. Not everything in Hallandren is as~.~.~. cohesive as it may appear to you at first.”

Siri remained slouched down, not looking at Treledees.

“I see that you understand,” he said. “I feel that~.~.~.” He trailed off, turning to the side. A procession was approaching Siri’s box. Its members wore gold and red, and a tall figure at the front caused them to shine with vibrant color.

Treledees frowned, then glanced at her. “We will speak further, if it becomes necessary. Do your duty, Vessel. Or there will be consequences.”

With that, the priest withdrew.

\orn

She didn’t~\textit{look}~dangerous. That, more than anything else, made Lightsong inclined to believe Blushweaver’s concerns.~\textit{I’ve been in the court for far too long,}~he thought to himself as he smiled pleasantly at the queen.~\textit{All my life, actually.}

She was a small thing, much younger than he had expected. Barely a woman. She looked intimidated as he nodded to her, waiting while his priests arranged furniture for him. Then he sat, accepting some grapes from the queen’s serving women, even though he wasn’t hungry.

“Your Majesty,” he said. “It is a pleasure to meet you, I’m sure.”

The girl hesitated. “You’re sure?”

“Figure of speech, my dear,” Lightsong said. “A rather redundant one—which is quite appropriate, since~\textit{I}~am a rather redundant person.”

The girl cocked her head.~\textit{Colors,}~Lightsong thought, remembering that she’d just finished with her period of isolation.~\textit{I’m probably the only Returned that she’s met besides the God King. What a bad first impression.}~Still, there was nothing to be done about it. Lightsong was who he was. Whoever that was.

“I’m pleased to make your acquaintance, Your Grace,” the queen said slowly. She turned as a serving woman whispered his name to her. “Lightsong the Brave, Lord of Heroes,” she said, smiling at him.

There was a hesitancy about her. Either she had not been trained for formal situations—which Lightsong found difficult to believe, since she’d been raised in a palace—or she was a quite a good actress. He frowned inwardly.

The woman’s arrival should have put an end to the discussions of war, but instead she had only exacerbated them. He kept his eyes open, for he feared the images of destruction he would see flashing inside his mind’s eye if he so much as blinked. They waited like Kalad’s Phantoms, hovering just beyond his vision.

He couldn’t accept those dreams as foretellings. If he did, it meant that he~\textit{was}~a god. And if that were the case, then he feared greatly for them all.

On the outside, he simply gave the queen his third most charming smile and popped a grape into his mouth. “No need to be so formal, Your Majesty. You will soon realize that among Returned, I am by far the least. If cows could Return, they’d undoubtedly be ranked higher than I.”

She wavered again, obviously uncertain how to deal with him. It was a common reaction. “Might I inquire as to the nature of your visitation?” she asked.

Too formal. Not at ease. Uncomfortable around those of high rank. Could it be possible that she~\textit{was}~genuine? No. It was likely an act to put him at ease. To make him underestimate her. Or was he just thinking too much?

\textit{Colors take you, Blushweaver!}~he thought.~\textit{I really don’t want to be part of this.}

He almost withdrew. But, then, that wouldn’t be very pleasant of him—and contrary to some of the things he said, Lightsong~\textit{did}~like being pleasant.~\textit{Best to be kind,}~he thought, smiling idly to himself.~\textit{That way, if she ever does take over the kingdom, perhaps she’ll behead me last.}~“You ask after the nature of my visitation?” he said. “I believe it has no nature, Your Majesty, other than to appear natural—at which I have already failed by staring at you for far too long while thinking to myself about your place in this mess.”

The queen frowned again.

Lightsong popped a grape in his mouth. “Wonderful things,” he said, holding up another one. “Delightfully sweet, wrapped in their own little package. Deceptive, really. So hard and dry on the outside, but so delectable on the inside. Don’t you think?”

“We~.~.~. don’t have many grapes in Idris, Your Grace.”

“I’m rather the opposite, you know,” he said. “Fluffy and pretty on the outside, without much of import on the inside. But I guess that is beside the point. You, my dear, are a very welcome sight. Much more so than a grape.”

“I~.~.~. How is that, Your Grace?”

“We haven’t had a queen in such a long time,” Lightsong said. “Since before my Return, in fact. And old Susebron up there really~\textit{has}~been moping about the palace lately. Looking forlorn. It’s good he has a woman in his life.”

“Thank you for the compliment, Your Grace,” the queen said.

“You’re welcome. I’ll make up a few more, if you like.”

She fell silent.

\textit{Well, then, that’s it,}~he thought, sighing.~\textit{Blushweaver was right. I probably shouldn’t have come.}

“All right,” the queen said, hair suddenly turning red as she threw her hands up in the air. “\textit{What}~is going on here?”

He hesitated. “Your Majesty?”

“Are you making fun of me?”

“Probably.”

“But you’re supposed to be a god!” she said, leaning back, staring up at the canopy. “Just when I thought things in this city were starting to make sense, the priests start yelling at me, then you come along! What am I supposed to do with you? You seem more like a schoolboy than a god!”

Lightsong paused, then settled back into his seat, smiling. “You have me found out,” he said, opening his hands. “I killed the real god and took his place. I’ve come to hold you ransom for your sweets.”

“There,” the queen said, pointing. “Aren’t you supposed to be~.~.~. I don’t know, distinguished or something?”

He spread his hands out. “My dear, this~\textit{is}~what passes for being distinguished in Hallandren.”

She didn’t seem convinced.

“I am, of course, lying through my teeth,” he said, eating another grape. “You shouldn’t base your opinion of the others upon what you think of me. They’re all much more deific than I am.”

The queen sat back. “I thought you were the god of bravery.”

“Technically.”

“You seem more like the god of jesters to me.”

“I’ve applied for the position and been turned down,” he said. “You should see the person they have doing the job. Dull as a rock and twice as ugly.”

Siri hesitated.

“I wasn’t lying that time,” Lightsong said. “Mirthgiver, god of laughter. If ever there was a god more poorly suited to his position than I, it’s he.”

“I don’t understand you,” she said. “It appears there’s a~\textit{lot}~I don’t understand in this city.”

\textit{This woman is no fake,}~Lightsong thought, staring into her youthful, confused eyes.~\textit{Or, if she is, then she’s the best actress I’ve ever met.}

That meant something. Something important. It was possible there were mundane reasons this girl had been sent instead of her sister. Sickness on the part of the elder daughter, perhaps. But Lightsong didn’t buy that. She was part of something. A plot, or perhaps several. And whatever those plots were,~\textit{she}~didn’t know about them.

\textit{Kalad’s Phantoms!}~Lightsong cursed mentally.~\textit{This child is going to get ripped apart and fed to the wolves!}

But what could he really do about it? He sighed, standing, causing his priests to begin packing his things. The girl watched with confusion as he nodded to her, giving her a wan smile of farewell. She stood and curtsied slightly, though she probably didn’t need to. She was his queen, even if she wasn’t herself Returned.

Lightsong turned to go, then stopped, recalling his own first few months in the court, and the confusion he’d known. He reached over, laying a gentle hand on her shoulder. “Don’t let them get to you, child,” he whispered.

And with that, he withdrew.

