\section{Chapter Eighteen}

Siri stood before the door to her husband’s bedchamber, shuffling nervously. As usual, Bluefingers stood beside her, and he was the only other one in the hallway. He scribbled on his pad, giving no indication of how he always knew when it was time for her to enter.

For once, she didn’t mind the delay, nervous though she was. It gave her more time to think about what she was going to do. The day’s events still buzzed about in her head: Treledees, telling her that she needed to provide an heir. Lightsong the Bold, talking in circles, then leaving her with what had seemed like a heartfelt farewell. Her king and husband, sitting on his tower above, bending light around him. The priests below, arguing about whether or not to invade her homeland.

A lot of people wanted to push her in different directions, yet none of them were really willing to tell her how to do what they wanted—and some didn’t even bother to tell her~\textit{what}they wanted. The only thing they were accomplishing was annoying her. She was not a seductress. She had no idea how to make the God King desire her—particularly since she was terrified of him doing just that.

High Priest Treledees had given her a command. Therefore, she intended to show him how she responded to commands, particularly when they had threats attached to them. Tonight, she would go into the king’s bedchamber, sit down on the floor, and refuse to strip. She’d confront the God King. He didn’t want her. Well, she was tired of being ogled every night.

She intended to explain all this to him in no uncertain terms. If he wanted to see her naked again, he’d have to order servants to strip her. She doubted that he’d do that. He’d made no move toward her, and when he presided over the arena debates, he’d actually done no more than sit and watch. She was getting a new impression of this God King. He was a man with so much power, he had grown lazy. He was a man who had everything, and so he bothered with nothing. He was a man who expected others to do everything for him. People like him annoyed her. She was reminded of a guard captain in Idris who had insisted on making his men work hard, while he spent his afternoons playing cards.

It was time the God King was defied. More than that, it was time that his priests learned that they couldn’t bully her. She was tired of being used. To night, she would react. That was her decision. And it made her nervous as all Colors.

She glanced at Bluefingers. Eventually, she caught his eye. “Do they really watch me each night?” she asked, leaning in and whispering.

He paused, paling slightly. He glanced to either side, then shook his head.

She frowned.~\textit{But Treledees knew that I hadn’t been bedded by the God King.}

Bluefingers raised a finger, pointing to his eyes, then shook his head. Then he pointed to his ears and nodded. He pointed to a doorway down the hall.

\textit{They listen,}~Siri thought.

Bluefingers leaned in closer. “They would never watch, Vessel,” he whispered. “Remember, the God King is their holiest of deities. Seeing him nude, watching him with his wife~.~.~. no, they wouldn’t dare. However, they aren’t above~\textit{listening.}”

She nodded. “They are very concerned about an heir.”

Bluefingers glanced about nervously.

“Am I really in danger from them?” she asked.

He met her eyes, then nodded sharply. “More danger than you know, Vessel.” Then he backed away, gesturing at the doorway.

\textit{You have to help me!}~she mouthed at him.

He shook his head, holding up his hands.~\textit{I cannot. Not now.}~With that, he pushed open the door, bowed, and scuttled away, glancing nervously over his shoulder.

Siri glared at him. The time was swiftly approaching when she’d need to corner him and find out what he really knew. Until then, she had other people to annoy. She turned and glanced into the dark room. Her nervousness returned.

\textit{Is this wise?}~Being belligerent had never bothered her before. And yet~.~.~. her life wasn’t like it had been before. Bluefingers’s fear had left her even more on edge.

Defiance. It had always been her way to get attention. She hadn’t been obstinate out of spite. She’d simply been unable to measure up to Vivenna, so she’d just done the opposite of what was expected of her. Her defiance had worked in the past. Or had it? Her father had been perpetually angry at her, and Vivenna had always treated her like a child. The city’s people had loved her, but sufferingly.

\textit{No,}~Siri thought suddenly.~\textit{No, I can’t go back to that. The people in this palace—this court—they aren’t the types you can defy just because you’re annoyed.}~Spurn the palace priests, and they wouldn’t grumble at her like her father had. They’d show her what it really meant to be in their power.

But what to do then? She couldn’t keep throwing off her clothing and kneeling on the floor, naked, could she?

Feeling confused, and a little angry at herself, she stepped into the dark room and pulled the door closed. The God King waited in his corner, shadowed as always. Siri looked at him, staring at that too-calm face. She knew that she should disrobe and kneel, but she didn’t.

Not because she felt defiant. Not even because she felt angry or petulant. Because she was tired of wondering. Who was this man who could rule gods and bend light with the force of his BioChroma? Was he really just spoiled and indolent?

He stared back at her. As before, he didn’t grow angry at her insolence. Watching him, Siri pulled at the strings on her dress, dropping the bulky garment to the floor. She reached for the shoulders of her shift, but hesitated.

\textit{No,}~she thought.~\textit{This isn’t right either.}

She glanced down at the shift; the edges of the white garment fuzzed, the white bending into color. She looked up at the God King’s impassive face.

Then—gritting her teeth against her nervousness—Siri took a step forward.

He tensed. She could see it in the edges of his eyes and around his lips. She took another step forward, the white of her garment bending further into prismatic colors. The God King didn’t do anything. He just watched as she drew closer and closer.

She stopped right in front of him. Then she turned from him and climbed up onto the bed, feeling the deep softness beneath her as she crawled to the middle of its mattress. She sat up on her knees, regarding the black marble wall with its obsidian sheen. The God King’s priests waited just beyond, listening carefully to hear things that were really none of their business.

\textit{This,}~she thought, taking a deep breath,~\textit{is going to be exceptionally embarrassing.}~But she’d been forced to lie prostrate, naked, before the God King for over a week. Was now really the time to start feeling self-conscious?

She began to bounce up and down on the bed, making its springs creak. Then, cringing slightly, she started to moan.

She hoped it was convincing. She didn’t really know what it was supposed to sound like. And how long did it usually continue? She tried to make her moans get louder and louder, her bouncing more furious, for what she assumed was a proper amount of time. Then she stopped sharply, let out a final moan, and fell back onto the bed.

All was still. She glanced up, eyeing the God King. Some of his emotional mask had softened, and he displayed a very human look of confusion. She almost laughed out loud at how perplexed he seemed. She just met his eyes and shook her head. Then—her heart beating, her skin a bit sweaty—she lay back on the bed to rest.

Tired from the day’s events and intrigues, it wasn’t long after that she found herself rolled up in the luxurious comforter and relaxing. The God King left her alone. In fact, he’d grown tense at her approach, almost as if he were worried. Even frightened of her.

That couldn’t be. He was the God and King of Hallandren, and she was just a silly girl, swimming in waters that were far over her head. No, he wasn’t frightened. The concept was enough to again make her feel like laughing. She restrained herself, maintaining the illusion for the listening priests as she drifted off in the luxurious comfort of the bed.

\bigskip \hrule \bigskip

The next morning, Lightsong did not get out of bed. His servants stood around the perimeter of his room like a flock of birds waiting for seed. As noon approached, they began to shuffle uncomfortably, shooting glances at one another.

He remained in bed, staring up at the ornate red canopy. Some servants approached tentatively, placing a tray of food atop a small table beside him. Lightsong did not reach for it.

He had dreamed of war again.

Finally, a figure walked up to the bed. Large of girth and draped in his priestly robes, Llarimar looked down at his god, betraying none of the annoyance that Lightsong was sure that he felt. “Leave us, please,” Llarimar said to the servants.

They hesitated, uncertain. When was a god without his servants?

“Please,” Llarimar repeated, though somehow his tone indicated that it was not a request. Slowly, the servants filed from the room. Llarimar moved the tray of food, then sat down on the edge of the low table. He studied Lightsong, expression thoughtful.

\textit{What did I ever do to earn a priest like him?}~Lightsong thought. He knew many of the high priests of other Returned, and most of them were various levels of insufferable. Some were quick to anger, others quick to point out fault, and still others were so fulsomely effusive toward their gods that it was downright maddening. Treledees, the God King’s own high priest, was so stuck-up that he made even~\textit{gods}~feel inferior.

And then there was Llarimar. Patient, understanding. He deserved a better god.

“All right, Your Grace,” Llarimar said. “What is it this time?”

“I’m sick,” Lightsong said.

“You can’t get sick, Your Grace.”

Lightsong gave a few weak coughs, to which Llarimar just rolled his eyes.

“Oh come on, Scoot,” Lightsong said. “Can’t you just play along a little?”

“Play along that you are sick?” Llarimar asked, showing a hint of amusement. “Your Grace, to do that would be to pretend that you’re not a god. I do not believe that’s a good pre cedent for your high priest to set.”

“It’s the truth,” Lightsong whispered. “I’m no god.”

Again, there was no sign of annoyance or anger from Llarimar. He just leaned down. “Please don’t say such things, Your Grace. Even if you yourself do not believe, you should not say so.”

“Why not?”

“For the sake of the many who~\textit{do}~believe.”

“And I should continue to deceive them?”

Llarimar shook his head. “It is no deception. It’s not so uncommon for others to have more faith in someone than he has in himself.”

“And that doesn’t strike you as a little odd in my case?”

Llarimar smiled. “Not knowing your temperament, it doesn’t. Now, what brought this on?”

Lightsong turned, looking up at the ceiling again. “Blushweaver wants my Commands for the Lifeless.”

“Yes.”

“She’ll destroy that new queen of ours,” Lightsong said. “Blushweaver worries that the Idrian royals are making a play for the Hallandren throne.”

“Do you disagree?”

Lightsong shook his head. “No. They probably are. But the thing is, I don’t think the girl—the queen—knows that she’s part of anything. I’m worried that Blushweaver will crush the child out of fear. I’m worried that she’ll be too aggressive and get us all into a war, when I don’t know yet if that’s the right thing to do.”

“It seems that you already have a good handle on all this, Your Grace,” Llarimar said.

“I don’t want to be part of it, Scoot,” Lightsong said. “I feel myself getting sucked in.”

“It is your duty to be involved so that you can lead your kingdom. You can’t avoid politics.”

“I can if I don’t get out of bed.”

Llarimar raised an eyebrow. “You don’t honestly believe that, do you, Your Grace?”

Lightsong sighed. “You’re not going to give me a lecture about how even my inaction has political effects, are you?”

Llarimar hesitated. “Perhaps. Like it or not, you are a part of the workings of this kingdom—and you produce effects even if you stay in bed. If you do nothing, then the problems are as much your fault as if you had instigated them.”

“No,” Lightsong said. “No, I think you’re wrong. If I don’t do anything, then at least I can’t ruin things. Sure, I can~\textit{let}~them go wrong, but that’s not the same thing. It really isn’t, no matter what people say.”

“And if, by acting, you could make things better?”

Lightsong shook his head. “Not going to happen. You know me better than that.”

“I do, Your Grace,” Llarimar said. “I know you better, perhaps, than you think I do. You’ve always been one of the best men I have known.”

Lightsong rolled his eyes, but then stopped, noting the expression on Llarimar’s face.

\textit{Best men I have known~.~.~.}

Lightsong sat up. “You knew me!” he accused. “\textit{That’s}~why you chose to be my priest. You did know me before! Before I died!”

Llarimar said nothing.

“Who was I?” Lightsong asked. “A good man, you claim. What was it about me that made me a good man?”

“I can say nothing, Your Grace.”

“You’ve already said something,” Lightsong said, raising a finger. “You might as well go on. No turning back.”

“I’ve said too much already.”

“Come on,” Lightsong said. “Just a little bit. Was I from T’Telir, then? How did I die?”~\textit{Who is she, the woman I see in my dreams?}

Llarimar said nothing further.

“I could command you to speak~.~.~.”

“No you couldn’t,” Llarimar said, smiling as he stood up. “It’s like the rain, Your Grace. You can~\textit{say}~you want to command the weather to change, but you don’t believe it, deep down. It doesn’t obey, and neither would I.”

\textit{Convenient bit of theology, that,}~Lightsong thought.~\textit{Particularly when you want to hide things from your gods.}

Llarimar turned to go. “You have paintings waiting to be judged, Your Grace. I suggest that you let your servants bathe and dress you so that you can get through the day’s work.”

Lightsong sighed, stretching.~\textit{How exactly did he just do that to me?}~he thought. Llarimar hadn’t even really revealed anything, yet Lightsong had overcome his bout of melancholy. He eyed Llarimar as the priest reached the door and waved for the servants to return. Perhaps dealing with sullen deities was part of his job description.

\textit{But~.~.~. he knew me before,}~Lightsong thought.~\textit{And now he’s my priest. How did that happen?}~“Scoot,” Lightsong said, drawing the priest’s attention. Llarimar turned, guarded, obviously expecting Lightsong to pry further into his past.

“What should I do?” Lightsong asked. “About Blushweaver and the queen?”

“I cannot tell you, Your Grace,” Llarimar said. “You see, it is from what~\textit{you}~do that we learn. If I guide you, then we gain nothing.”

“Except perhaps the life of a young girl who is being used as a pawn.”

Llarimar paused. “Do your best, Your Grace,” he said. “That is all I can suggest.”

\textit{Great,}~Lightsong thought as he stood. He didn’t know what his “best” was.

The truth was, he’d never bothered to find out.

