% \section{Chapter Forty}
\chapter{}

Siri was enjoying a meal on the court green when Treledees found her. She ignored him, content to pick at the dishes in front of her.

The sea, she had decided, was quite strange. What else could be said of a place that could spawn creatures with such wiggly tentacles and boneless bodies, and yet others with such needly skins? She poked at something the locals called a cucumber, but which—in actuality—tasted nothing like one.

She tried each dish, testing them with her eyes closed, focusing on the flavor. Some hadn’t been as bad as the others. She hadn’t really liked any of them. Seafood just wasn’t appetizing to her.

\textit{I would have trouble becoming a true Hallandren,}~she decided, sipping her fruit juice.

Fortunately, the juice was delicious. The variety, and flavor, of the numerous Hallandren fruits was almost as remarkable as the oddity of its sea life.

Treledees cleared his throat. The God King’s high priest was not one accustomed to waiting.

Siri nodded to her serving women, motioning for them to prepare another series of plates. Susebron had been coaching Siri on how to eat with etiquette, and she wanted to practice. Coincidentally, his way of eating—taking small bites, never really finishing anything—was a good one for testing out new dishes. She wanted to become familiar with Hallandren, its ways, its people, its tastes. She’d forced her servants to begin talking to her more, and she planned to meet with more of the gods. In the distance, she saw Lightsong wandering by, and she waved to him fondly. He seemed uncharacteristically preoccupied; he waved back, but didn’t come over to visit her.

\textit{Pity,}~she thought.~\textit{I would have liked a good excuse to keep Treledees waiting even longer.}

The high priest cleared his throat again, this time more demandingly. Finally, Siri stood, gesturing for her servants to stay behind.

“Would you mind walking with me for a bit, Your Excellency?” she asked lightly. She passed him, moving languidly in a gorgeous violet dress with a gossamer train that trailed through the grass behind her.

He hurried to catch up. “I need to speak to you about something.”

“Yes,” she said. “I deduced that by the way that you summoned me several times today.”

“You didn’t come,” he said.

“It seems to me that the consort of the God King should not make a habit of responding to demands and hopping to attend upon others whenever she is requested.”

Treledees frowned.

“However,” she continued, “I will of course make time for the high priest himself, should he come to speak to me.”

He eyed her, standing tall and straight-backed, wearing the God King’s colors of the day—blue and copper. “You should not antagonize me, Your Highness.”

Siri felt a brief flush of anxiety, but caught her hair before it bleached white. “I am not antagonizing you,” she said. “I am simply establishing some rules that should have been understood from the beginning.”

Treledees got a hint of a smile on his face.

\textit{What?}~Siri thought with surprise.~\textit{Why that reaction?}

As they walked, he drew himself up. “Is that so?” he said, his voice turning condescending. “You know very little of what you presume, Your Highness.”

\textit{Blast!}~she thought.~\textit{How did this conversation get away from me so quickly?}

“I might say the same to you, Your Excellency.” The massive black temple of a palace loomed above them, sheer ebony blocks stacked like the playthings of gigantic child.

“Oh?” he said, glancing at her. “Somehow I doubt that.”

She had to force back another spear of anxiety. Treledees smiled again.

\textit{Wait,}~she thought.~\textit{It’s like he can read my emotions. Like he can see~.~.~.}

Her hair hadn’t changed colors, at least not discernibly. She glanced at Treledees, trying to figure out what was wrong. She noticed something interesting. In a circle around Treledees, the grass seemed just a shade more colorful.

\textit{Breath,}~she thought.~\textit{Of course he’d have it! He’s one of the most powerful men in the kingdom.}

People with lots of Breath were supposed to be able to see very minute changes in color. Could he really be reading her from such faint reactions in her hair? Was that why he had always been so dismissive? Could he see her fear?

She gritted her teeth. In her youth, Siri had ignored the exercises that Vivenna had done to make sure she had complete control over her hair. Siri was an emotional person, and people had been able to read her regardless of her hair, so she’d figured that there was no point in learning to manipulate the Royal Locks.

She hadn’t imagined a Court of Gods and men with the power of BioChroma. Those tutors had been a~\textit{whole}~lot more intelligent than Siri had credited. As were the priests. Now that she thought about it, it was obvious that Treledees and the others would have studied the meanings of all the shades of hair changes.

She needed to get the conversation back on course. “Do not forget, Treledees,” she said. “You are the one who came to see me. Obviously, I have~\textit{some}~power here, if I could force even the high priest to do as I wish.”

He glanced at her, eyes cold. Focusing, she kept her hair the deepest black. Black, for confidence. She met his eyes, and let not even a slight tinge color her locks.

He finally turned away. “I have heard disturbing rumors.”

“Oh?”

“Yes. It appears that you are no longer fulfilling your wifely duties. Are you pregnant?”

“No,” she said. “I had my women’s issue just a couple of days ago. You can ask my servants.”

“Then why have you stopped trying?”

“What?” she asked lightly. “Are your spies disappointed to be missing their nightly show?”

Treledees flushed just slightly. He glanced at her, and she still managed to keep her hair perfectly black. Not even a glimmer of white or red. He seemed more uncertain.

“You Idrians,” the priest spat. “Living up in your lofty mountains, dirty and uncultured, but still assuming that you’re better than us. Don’t judge me. Don’t judge us. You know nothing.”

“I know that you’ve been listening in on the God King’s chamber.”

“Not just listening,” Treledees said. “The first few nights, there was a spy in the chambers itself.”

Siri couldn’t mask this blush. Her hair remained mostly black, but if Treledees really did have enough BioChroma to distinguish subtle changes, he would have seen a hint of red.

“I am well aware of the poisonous things your monks teach,” Treledees said, turning away. “The hatred into which you’re indoctrinated. Do you really think that we’d let a woman from Idris confront the God King himself, alone, unwatched? We had to make certain you weren’t intending to kill him. We’re still not convinced.”

“You speak with remarkable frankness,” she noted.

“Merely saying some things that~\textit{I}~should have established from the beginning.” They stopped in the shadow of the massive palace. “You are not important here. Not compared to our God King. He is everything, and you are~\textit{nothing.}~Just like the rest of us.”

\textit{If Susebron is so important,}~Siri thought, meeting Treledees’s eyes,~\textit{then why are you planning to kill him?}~She held his eyes. The woman she’d been a few months ago would have looked away. But when she felt weak, she remembered Susebron. Treledees was orchestrating the plot to subdue, control, and eventually kill his own God King.

And Siri wanted to know why.

“I stopped having sex with the God King on purpose,” she said, keeping her hair dark with some effort. “I knew it would get your attention.”

In truth, she had simply stopped her little perfor mances each night. Treledees’s reaction, fortunately, proved that the priests believed her acting. For that she blessed her luck. They might still be unaware that she could communicate with Susebron. She was extra careful to whisper at night, and had even taken to writing things herself, to keep up the charade.

“You must produce an heir,” Treledees said.

“Or what? Why are you so eager, Treledees?”

“It is none of your concern,” he said. “Suffice it to say that I have obligations that you cannot comprehend. I am subject to the gods, and I do their will,~\textit{not}~yours.”

“Well you’re going to have to bend on that last part if you want your heir,” Siri said.

Treledees obviously did not like how the conversation was going. He glanced at her hair. And, somehow, she kept it from showing even a slight bit of uncertainty. He looked back at her eyes.

“You can’t kill me, Treledees,” she said. “Not if you want a royal heir. You can’t bully me or force me. Only the God King could do that. And, we know how~\textit{he}~is.”

“I don’t know what you mean,” Treledees said flatly.

“Oh, come now,” Siri said. “Did you honestly expect me to sleep with the man and not find out he has no tongue? That he’s virtually a child? I doubt he can even go to the privy without help from some servants.”

Treledees flushed with anger.

\textit{He really does care,}~Siri noted abstractly.~\textit{Or, at least, insulting his God King insults him. He’s more devoted than I would have expected.}

So it probably wasn’t about money. She couldn’t be sure, but she suspected that this was not the type of man to sell out his religion. Whatever the reasons for what was happening inside the palace, it probably had to do with true conviction.

Revealing what she knew about Susebron was a gamble. She figured that Treledees would guess anyway, and so it would be better to indicate that she thought Susebron a fool with the mind of a child. Give away one bit of information, but also mislead with another. If they assumed that she thought Susebron a fool, they wouldn’t suspect a conspiracy between her and her husband.

Siri wasn’t certain if she was doing the right thing. But she needed to learn, or Susebron would die. And the only way to learn was to do. She didn’t have much, but she~\textit{did}~have one thing that the priests wanted: her womb.

It seemed that she could hold it for ransom effectively, for Treledees suppressed his anger and maintained a semblance of calm. Turning from her, he glanced up at the palace. “Do you know much about the history of this kingdom? After your family departed, of course.”

Siri frowned, surprised at the question.~\textit{More than you probably think,}~she thought. “Not really,” she said out loud.

“Lord Peacegiver left us with a challenge,” Treledees said. “He gave us the treasure our God King now holds, a wealth of BioChromatic Breath such as nobody had ever seen. Over fifty thousand Breaths. He told us to keep them safe.” Treledees turned back to her. “And he warned us not to use it.”

Siri felt a slight shiver.

“I do not expect you to understand what we have done,” Treledees said. “But it was necessary.”

“Necessary to keep a man in bondage?” Siri said. “To deprive him of the ability to speak, to make a permanent child out of a grown man? He didn’t even understand what he was supposed to do with a woman!”

“It was necessary,” Treledees said, jaw set. “You Idrians. You don’t even try to understand. I’ve had dealings with your father for years, and I sense the same ignorant prejudice in him.”

\textit{He’s baiting me,}~Siri thought, keeping her emotions in check. It was harder than she’d expected. “Believing in Austre instead of your living gods is not ignorance. After all, you’re the ones who abandoned our faith and took an easier path.”

“We follow the god who came to protect us when your Austre—an unseen, unknown thing—abandoned us to the destroyer Kalad. Peacegiver returned to life with a specific purpose—to stop the conflict between men, to bring peace again to Hallandren.”

He glanced at her. “His name is holy.~\textit{He}~is the one who gave us life, Vessel. And he only asked one thing of us: to care for his power. He died to give it to us, but demanded that it be held in case he should Return again and need it. We couldn’t let it be used. We couldn’t let it be profaned. Not even by our God King.”

He fell silent.

\textit{So how do you get that trea sure away from him to pass on?}~she thought. She was tempted to ask. Would that be giving away too much?

Finally, Treledees continued. “I see now why your father sent you instead of the other one. We should have studied all of the daughters, not just the first. You are far more capable than we had been led to believe.” The statement surprised her, but she kept her hair in check. Treledees sighed, looking away. “What are your demands? What will it take to make you return to your~.~.~. duties each night?”

“My servants,” she said. “I want to replace my main serving women with the women from Pahn Kahl.”

“You are displeased with your serving women?”

“Not particularly,” Siri said. “I simply feel that I have more in common with the women of Pahn Kahl. They, like me, are living in exile from their own people. Besides, I like the browns they wear.”

“Of course,” Treledees said, obviously thinking her Idrian prejudices were behind the request.

“The Hallandren girls can continue to serve in the roles that the Pahn Kahl women did,” Siri said. “They don’t have to leave me completely—in fact, I still want to talk to some of them. However, the main women who are with me always, they are to be from Pahn Kahl.”

“As I said,” Treledees said. “It shall be done. You’ll return to your efforts, then?”

“For now,” Siri said. “That will earn you a few more weeks.”

Treledees frowned, but what could he really do? Siri smiled at him, then turned and walked away. However, she found herself dissatisfied with the way the conversation had gone. She’d achieved a victory—but at the cost of antagonizing Treledees even further.

\textit{I doubt he would have taken a liking to me, no matter how hard I tried,}~she decided, sitting down in her pavilion.~\textit{This is probably the better way.}

She still didn’t know what was going to happen to Susebron; at least she had confirmed that manipulating the priests was possible. That meant something, though she knew she was treading dangerous ground. She turned back to her meal, ready to try another round of seafood. She did her best to learn about Hallandren, but if it came down to Susebron’s life, she was going to get him out. She hoped that giving Bluefingers’s Pahn Kahl a more prominent role in her ser vice would facilitate that escape. She hoped.

With a sigh, she raised the first bit of food to her lips and continued with her tasting.

