% \section{Chapter Forty-Eight}
\chapter{}

Susebron didn’t leave in the mornings anymore.

Siri lay in the bed beside him, curled slightly, her skin against his. He slept peacefully, chest going up and down, the white bed sheets throwing out prismatic colors around him as they inevitably reacted to his presence. A few months back, who could have understood where she’d find herself? Not only married to the God King of Hallandren, but in love with him as well.

She still thought it amazing. He was the most important religious and secular figure in the whole of the Inner Sea area. He was the basis for worship of the Hallandren Iridescent Tones. He was a creature feared and hated by most people in Idris.

And he was dozing quietly at her side. A god of color and beauty, his body as perfectly sculpted as a statue. And what was Siri? Not perfect, of that she was sure. And yet, somehow, she’d brought to him something that he needed. A hint of spontaneity. A breath from the outside, untamed by his priests or his reputation.

She sighed, head resting on his chest. There would be a price to be paid for their enjoyment these last few nights.~\textit{We really are fools,}~she thought idly.~\textit{We only have to avoid one thing: giving the priests a child. We’re aiming ourselves straight toward disaster.}

She found it hard to berate herself too firmly. She suspected that her act wouldn’t have fooled the priests for much longer. They would grow suspicious, or at least frustrated, if she continued it without producing an heir. She could imagine them interfering if faced with more stalling.

Whatever she and Susebron did to change events, they would have to do it quickly.

He stirred beside her, and she twisted, looking at his face as he opened his eyes. He regarded her for a few minutes, stroking her hair. It was amazing how quickly they had become comfortable in their intimacy.

He reached for his writing board.~\textit{I love you.}

She smiled. It was always the first thing he wrote in the mornings. “And I love you,” she said.

\textit{However,}~he continued,~\textit{we are probably in trouble, aren’t we?}

“Yes.”

\textit{How long?}~he asked.~\textit{Until it’s obvious that you will bear a child, I mean?}

“I’m not sure,” she said, frowning. “I don’t have much experience with this, obviously. I know that some of the women back in Idris complained of not being able to have children as quickly as they wanted, so maybe it doesn’t always happen immediately. I know other women who bore children almost exactly nine months after their wedding night.”

Susebron looked thoughtful.

\textit{A year from now, I could be a mother,}~Siri thought. She found the concept daunting. Up until a short time ago, she hadn’t really thought of herself as an adult.~\textit{Of course,}~she thought, feeling a bit sick,~\textit{according to what we’ve been told, any children I bear the God King would be stillborn anyway.}~Even if that was a lie, her child would be in danger. She still suspected that the priests would spirit it away, then replace it with a Returned. In all likelihood, Siri would then be made to disappear as well.

\textit{Bluefingers tried to warn me,}~she thought.~\textit{He spoke of danger, not only to Susebron, but to me.}

Susebron was writing.~\textit{I’ve made a decision,}~he wrote.

Siri raised an eyebrow.

\textit{I want to try making myself known to the people,}~he wrote,~\textit{and the other gods. I want to take control of my kingdom for myself.}

“I thought we decided that would be too dangerous.”

\textit{It will be,}~he wrote.~\textit{But I’m beginning to think that it is a risk we must take.}

“And your objections from before?” she asked. “You can’t shout out the truth, and your guards are likely to rush you away if you try something like escaping.”

\textit{Yes,}~Susebron wrote,~\textit{but you have far fewer guards, and you}~can~\textit{yell.}

Siri paused. “Yes,” she said. “But would anyone believe me? What would they think if I just started screaming about how the God King is being held prisoner by his own priests?”

Susebron cocked his head.

“Trust me,” she said. “They’d think that I was crazy.”

\textit{What if you gained the confidence of the Returned you often speak about?}~he wrote.~\textit{Lightsong the Bold.}

Siri gave that some thought.

\textit{You could go to him,}~Susebron wrote.~\textit{Tell him the truth. Perhaps he will lead you to other Returned he thinks might listen. The priests will not be able to silence us all.}

Siri lay beside him for a moment, head still resting on his chest. “It sounds possible, Seb, but why not just run? My serving women are from Pahn Kahl now. Bluefingers has said that he will try to get us out, if I ask. We can flee to Idris.”

\textit{If we flee, Hallandren troops will follow, Siri. We would not be safe in Idris.}

“We could go somewhere else, then.”

He shook his head.~\textit{Siri, I have been listening to the arguments in the court of judgment. There will soon be war between our kingdoms. If we run, we will be abandoning Idris to invasion.}

“The invasion will happen if we stay, too.”

\textit{Not if I take control of my throne,}~Susebron wrote.~\textit{The people of Hallandren, even the gods, are obligated to obey me. There will be no war if they know I disapprove.}~He erased, then continued, writing faster.~\textit{I have told the priests that I don’t wish to go to war, and they appeared sympathetic. However, they have done nothing.}

“They are probably worried,” Siri said. “If they let you start making policy, then you may begin to think that you don’t need them.”

\textit{They’d be right,}~he wrote, smiling.~\textit{I need to become the leader of my people, Siri. That is the only way to protect your beautiful hills and the family you love so much.}

Siri fell silent, offering no further objections. To do as he was saying would be to play their hand. Make a gamble for everything. If they failed, the priests would undoubtedly figure out that Siri and Susebron were in communication. That would spell the end of their time alone together.

Susebron obviously noticed her concern.~\textit{It is dangerous, but it is the best option. Fleeing would be just as risky, and it would leave us in far worse circumstances. In Idris, we would be seen as the reason the Hallandren armies had come. Other countries would be even more dangerous.}

Siri slowly nodded. In another country, they’d have no money and would make perfect subjects for ransom. They’d escape the priests only to find themselves being held captive to be used against Hallandren. The Kingdom of Iridescence was still widely disliked because of the Manywar.

“We’d be taken captive, as you say,” she acknowledged. “Plus, if we were in another country, I doubt we’d be able to get you a Breath every week. Without them, you’d die.”

He looked hesitant.

“What?” she asked.

\textit{I would not die without Breath,}~he wrote.~\textit{But that is not an argument in favor of flight.}

“You mean the stories of Returned needing Breath to live are lies?” Siri asked incredulously.

\textit{Not at all,}~he wrote quickly.~\textit{We do need Breath—but you forget that I hold the wealth of Breath passed down for generations in my family. I heard my priests speak of this once. If it were necessary to move me, I could survive on the extra Breaths I hold. Those over and above the Breath that makes me Returned. My body would simply feed off those extra Breaths, absorbing one a week.}

Siri sat back thoughtfully. That seemed to imply something about Breath that she couldn’t quite figure out. Unfortunately, she just didn’t have the experience to sort through it.

“All right,” she said. “So we~\textit{could}~go into hiding if we needed to.”

\textit{I said this was not an argument for fleeing,}~Susebron wrote.~\textit{My treasure of Breaths might keep me alive, but it would also make me a very valuable target. Everyone will want those Breaths—even if I weren’t the God King, I would be in danger.}

That was very true. Siri nodded. “All right,” she said. “If we’re really going to try exposing what the priests have done, I think we make our move soon. If I display any signs of being pregnant, I bet it will take the priests all of two heartbeats to sequester me.”

Susebron nodded.~\textit{There will be a general assembly of the court in a couple of days. I have heard my priests say that this will be an important meeting—it is rare that the gods are all called together to vote. That meeting will decide whether or not we march on Idris.}

Siri nodded nervously. “I could sit with Lightsong,” she said, “and plead for his help. If we go to several of the other gods, perhaps they—in front of the crowds—can demand to know whether or not I am lying.”

\textit{And I will open my mouth and reveal that I have no tongue,}~he wrote.~\textit{Then let us see what the priests do. They will be forced to bow to the will of their own pantheon.}

Siri nodded. “All right,” she said. “Let’s try it.”

