% \section{Chapter Forty-Three}
\chapter{}

Vivenna awoke, sick, tired, thirsty, starving. But alive.

She opened her eyes, feeling a strange sensation. Comfort. She was in a comfortable soft bed. She sat up immediately; her head spun. “I’d be careful,” a voice said. “Your body is weak.”

She blinked fuzzy eyes, focusing on a figure sitting at a table a short distance away, his back to her. He appeared to be eating. A black sword in a silver sheath rested against the table. “You,” she whispered. “Me,” he said between bites. She looked down at herself. She wasn’t wearing her shift anymore, but instead had on a set of soft cotton sleeping garments. Her body was clean. She raised a hand to her hair, feeling that the tangles and mats were gone. It was still white. She felt so strange to be clean. “Did you rape me?” she asked quietly.

He snorted. “A woman who’s been to Denth’s bed holds no temptation for me.”

“I never slept with him,” she said, though she didn’t know why she cared to tell him. Vasher turned, face still framed by the patchy, ragged beard. His clothing was far less fine than her own. He studied her eyes. “He had you fooled, didn’t he?”

She nodded.

“Idiot.”

She nodded again.

He turned back to his meal. “The woman who runs this building,” he said. “I paid her to bathe you, dress you, and change your bedpan. I never touched you.”

She frowned. “What~.~.~. happened?”

“Do you remember the fight on the street?”

“With your sword?”

He nodded.

“Vaguely. You saved me.”

“I kept a tool out of Denth’s hands,” he said. “That’s all that really matters.”

“Thank you anyway.”

He was silent for a few moments. “You’re welcome,” he finally said.

“Why do I feel so ill?”

“Tramaria,” the man said. “It’s a disease you don’t have in the highlands. Insect bites spread it. You probably got it a few weeks before I found you. It stays with you, if you’re weak.”

She put a hand to her head.

“You probably had a pretty bad time lately,” Vasher noted. “What with the dizziness, the dementia, and the hunger.”

“Yes,” she said.

“You deserved it.” He continued to eat.

She didn’t move for a long moment. His food smelled so good, but she’d apparently been fed during the fevers, for she wasn’t as famished as she might have expected. Just mildly hungry. “How long was I unconscious?” she asked.

“A week,” he said. “You should sleep some more.”

“What are you going to do with me?”

He didn’t reply. “The BioChromatic Breaths you had,” he said. “You gave them to Denth?”

She paused, thinking. “Yes.”

He glanced at her, raising an eyebrow.

“No,” she admitted, looking away. “I put them in the shawl I was wearing.”

He stood, leaving the room. She considered running. Instead, she got out of the bed and began to eat his food—a fish, whole and fried. Seafood didn’t bother her anymore.

He returned, then stopped in the doorway, watching her ravage the fish bones. He didn’t force her out of the seat; he simply took the other chair at the table. Finally, he held up the shawl, washed and clean.

“This?” he asked.

She froze, a bit of fish on her cheek.

He set the shawl on the table beside her.

“You’re giving it back to me?” she asked.

He shrugged. “If there really is Breath stored in it, I can’t get to it. Only you can.”

She picked it up. “I don’t know the Command.”

He raised an eyebrow. “You escaped those ropes of mine without Awakening them?”

She shook her head. “I guessed that one.”

“I should have gagged you better. What do you mean you ‘guessed’ it?”

“It was the first time I’d ever used Breath.”

“That’s right, you’re of the royal line.”

“What does that mean?”

He just shook his head, pointing toward the shawl. “Your Breath to mine,” he said. “That’s the Command you want.”

She laid her hand on the shawl and said the words. Immediately, everything changed.

Her dizziness went away. Her deadness to the world vanished. She gasped, shaking with the pleasure of Breath restored. It was so strong that she actually fell from the chair, quivering like a person having a fit with the wonder of it. It was amazing. She could sense life. Could sense Vasher making a pocket of color around him that was bright and beautiful. She was~\textit{alive}~again.

She basked in that for a long moment.

“It’s shocking, when you first get it,” Vasher said. “It’s usually not too bad if you take the Breath back after only an hour or so. Wait weeks, or even a few days, and it’s like taking it in for the first time.”

Smiling, feeling amazing, she climbed back into the seat and wiped the fish from her face. “My sickness is gone!”

“Of course,” he said. “You’ve got enough Breath for at least the Third Heightening, if I’m reading you right. You’ll never know sickness. You’ll barely even age. Assuming you manage to hang on to the Breath, of course.”

She looked up at him in a panic.

“No,” he said. “I’m not going to force you to give it to me. Though I probably should. You’re far more trouble than you’re worth, Princess.”

She turned back to the food, feeling more confident. It seemed now as if the last few weeks had been a nightmare. A bubble, surreal, disconnected from her life. Had it really been she who had sat on the street, begging? Had she really slept in the rain, lived in the mud? Had she really considered turning to prostitution?

She had. She couldn’t forget that just because she now had Breath again. But had becoming a Drab had a hand in her actions? Had the sickness had a part in it too? Either way, the greatest part had been simple desperation.

“All right,” he said, standing, picking up the black sword. “Time to go.”

“Go where?” she asked, suspicious. The last time she had met this man, he’d bound her, forced her to touch that sword of his, and left her gagged.

He ignored her concern, tossing a pile of clothing onto the table. “Put this on.”

She picked through it. Thick trousers, a tunic that tucked into them, a vest to go over the tunic. All of various shades of blue. There were undergarments of a less bright color.

“That’s a man’s clothing,” she said.

“It’s utilitarian,” Vasher said, walking toward the doorway. “I’m not going to waste money buying you fancy dresses, Princess. You’ll just have to get used to those.”

She opened her mouth, but then shut it, discarding her complaint. She’d just spent~.~.~. she didn’t know how long running around in a thin, nearly translucent shift that had only covered her to midthigh. She took the trousers and shirts gratefully.

“Please,” she said, turning toward him. “I appreciate this clothing. But can I at least know what you intend to do with me?”

Vasher hesitated in the doorway. “I have work for you to do.”

She shivered, thinking of the bodies Denth had shown her, and of the men Vasher had killed. “You’re going to kill again, aren’t you?”

He turned back toward her, frowning. “Denth is working toward something. I’m going to block him.”

“Denth was working for me,” she said. “Or, at least, he was pretending to. All of those things he did, they were at my command. He was just playing along to keep me complacent.”

Vasher gave a barking laugh, and Vivenna flushed. Her hair—responding to her mood for the first time since her shock at seeing Parlin dead—turned red.

It felt so surreal. Two weeks on the street? It felt so much longer. But now, suddenly, she was cleaned and fed, and somehow she felt like her old self again. Part of it was the Breath. The beautiful, wonderful Breath. She never wanted to be parted from it again.

Not her old self at all. Who was she, then? Did it matter?

“You laugh at me,” she said, turning to Vasher. “But I was just doing the best I could. I wanted to help my people in the upcoming war. Fight against Hallandren.”

“Hallandren isn’t your enemy.”

“It is,” she said sharply. “And it is planning to march on my people.”

“The priests have good reasons for acting as they do.”

Vivenna snorted. “Denth said that every man thinks he’s doing the right thing.”

“Denth is too smart for his own good. He was playing with you, Princess.”

“What do you mean?”

“Didn’t it ever occur to you?” Vasher asked. “Attacking supply caravans? Rousing the Idrian poor to rebel? Reminding them of Vahr and his promises of freedom, which were so fresh in their minds? Showing yourself to thug lords, making them think that Idris was working to undermine the Hallandren government? Princess, you say every man thinks he’s on the right side, that every man who opposed you was deluding himself.” He met her eyes. “Didn’t you ever once stop to think that maybe~\textit{you}~were the one on the wrong side?”

Vivenna froze.

“Denth wasn’t working for you,” Vasher said. “He wasn’t even pretending to. Someone in this city hired him to start a war between Idris and Hallandren, and he’s spent these last few months using you to make it happen. I’m trying to figure out why. Who’s behind it, and why would a war serve them?”

Vivenna sat back, eyes wide. It couldn’t be. He had to be wrong.

“You were the perfect pawn,” Vasher said. “You reminded the people in the slums of their true heritage, giving Denth someone to rally them behind. The Court of Gods is a hair’s breadth away from marching on your homeland. Not because they hate Idrians, but because they feel like Idrian insurgents have~\textit{already}~been attacking them.”

He shook his head. “I couldn’t believe that you didn’t realize what you were doing. I assumed you had to be working with him intentionally to start the war.” He eyed her. “I underestimated your stupidity. Get dressed. I don’t know if we have enough time to undo what you’ve done, but I intend to try.”

\orn

The clothing felt strange. The trousers pulled at her thighs, making her feel like she was exposed. It was odd not to have the swishing of skirts at her ankles.

She walked beside Vasher without comment, head bowed, hair too short to even put into a braid. She didn’t try to regrow it yet. That would draw needed nourishment from her body.

They passed through the Idrian slum, and Vivenna had to fight to keep herself from jumping at every sound, looking over her shoulder to see if someone was following her. Was that an urchin wanting to steal the money she’d begged? Was that a group of thugs, wishing to sell her to Denth? Were those shadows grey-eyed Lifeless, come to attack and slaughter? They passed a waif beside the road, a young woman of indeterminable age but with a soot-covered face and bright eyes that watched them. Vivenna could read the hunger in those eyes. The woman was trying to decide whether or not to try stealing from them.

The sword in Vasher’s hand was obviously enough to ward the girl away. Vivenna watched her scurry down an alleyway, feeling an odd sense of connection.

\textit{Colors,}~she thought.~\textit{Was that really me?}

No. She hadn’t even been as capable as that girl. Vivenna had been so naive that she’d been kidnapped without knowing it, then worked to start a war without realizing what she was doing.

\textit{Didn’t you ever stop to think that maybe you were on the wrong side?}

She wasn’t sure what to believe. She’d been taken in so quickly by Denth that she was hesitant to accept anything this Vasher said. However, she~\textit{could}~see signs that some of what he had told her was true.

Denth had always taken her to meet with the less reputable elements in the city. Not only were they the ones a mercenary like him would know, but they would be more likely to prefer the chaos of war. Attacking the Hallandren supplies wouldn’t only make it more difficult to administer the war, it would make the priests more likely to attack while they were still strong. The losses would also serve to make them angrier.

It made chilling sense—sense it was hard for her to ignore. “Denth made me think that the war was inevitable,” Vivenna whispered as they walked through the slums. “My father thinks it’s inevitable. Everyone says it’s going to happen.”

“They’re wrong,” Vasher said. “War between Hallandren and Idris has been close for decades, but never inevitable. Getting this kingdom to attack requires convincing the Returned—and they’re generally too focused on themselves to want something as disruptive as a war. Only an extended effort—first convincing the priests, then getting them to argue until the gods believed them—would be successful.”

Vivenna stared ahead down the dirty streets with their colorful refuse. “I really am useless, aren’t I?” she whispered.

Vasher glanced over at her.

“First, my father sent my sister to marry the God King instead of me. I followed, but I didn’t even know what I was doing—Denth took me on the very first day I was here. When I finally escaped him, I couldn’t make it a month on the street without getting robbed, beaten, and then captured. Now you claim that I’ve single-handedly brought my people to the edge of war.”

Vasher snorted. “Don’t give yourself~\textit{too}~much credit. Denth has been working on this war for a long time. From what I hear, he corrupted the Idrian ambassador himself. Plus there are elements in the Hallandren government—the ones who hired Denth in the first place—who want this conflict to happen.”

It was all so confusing. What he said made sense, but Denth had made sense too. She needed to know more. “Do you have any guesses who they might be? The ones who hired Denth?”

Vasher shook his head. “One of the gods, I think—or perhaps a cabal of them. Maybe a group of priests, working on their own.”

They fell silent again.

“Why?” Vivenna finally asked.

“How should I know?” Vasher asked. “I can’t even figure out~\textit{who’s}~behind it.”

“No,” Vivenna said. “Not that. I mean, why are you involved? Why do you care?”

“Because,” Vasher said.

“Because why?”

Vasher sighed. “Look, Princess. I’m not like Denth; I don’t have his ability with words, and I don’t really like people in the first place. Don’t expect me to chat with you. All right?”

Vivenna shut her mouth in surprise.~\textit{If he’s trying to manipulate me,}~she thought,~\textit{he has a very strange way of doing it.}

Their destination turned out to be a run-down building on the corner of a run-down intersection. As they approached, Vivenna paused to wonder exactly how slums like this one came to exist. Did people build them cramped and shoddy on purpose? Had these streets, like others she’d seen, once been part of a better section of town that had fallen into disrepair?

Vasher grabbed her arm as she stood there, then pulled her up to the door and pounded on it with the hilt of his sword. The door creaked open a second later, and a pair of nervous eyes glanced out.

“Get out of the way,” Vasher said, testily shoving the door open the rest of the way and pulling Vivenna inside. A young man stumbled back, pressing up against the wall of the hallway and letting Vasher and Vivenna pass. He closed the door behind them.

Vivenna felt as if she should be frightened, or at least angry, at the treatment. However, after what she had been through, it just didn’t seem like much. Vasher let go of her and thumped his way down a set of stairs. Vivenna followed more carefully, the dark stairwell reminding her of the cellar in Denth’s hideout. She shivered. At the bottom, fortunately, the similarities between cellars ended. This one had a wooden floor and walls. A rug sat in the middle of the room with a group of men sitting on it. A couple of them rose as Vasher rounded the stairs.

“Vasher!” one said. “Welcome. Do you want something to drink?”

“No.”

The men glanced uncomfortably at each other as Vasher tossed his sword toward the side of the room. It hit with a clank, skidding on the wood. Then he reached back and pulled Vivenna forward.

“Hair,” he said.

She hesitated. He was using her just as Denth had. But rather than make him angry, she obliged, changing the color of her hair. The men watched with awe; then several of them bowed their heads. “Princess,” one whispered.

“Tell them you don’t want them to go to war,” Vasher said.

“I don’t,” she said honestly. “I have never wanted my people to fight Hallandren. They would lose, almost certainly.”

The men turned to Vasher. “But she was working with the slumlords. Why did she change her mind?”

Vasher looked at her. “Well?”

Why did she change her mind?~\textit{Had}~she changed her mind? It was all too quick.

“I~.~.~.” she said. “I’m sorry. I~.~.~. didn’t realize. I’ve~\textit{never}~wanted war. I thought it was inevitable, and so I tried to plan for it. I might have been manipulated, though.”

Vasher nodded, then pushed her aside. He left her and joined the men as they sat back on the rug. Vivenna remained where she was. She wrapped her hands around herself, feeling the unfamiliar cloth of the tunic and coat.

\textit{These men are Idrians,}~she realized, listening to their accents.~\textit{And now they’ve seen me, their princess, wearing a man’s clothing. How is it that I can still care about such things, considering everything else that is happening?}

“All right,” Vasher said, squatting. “What are you doing to stop this?”

“Wait,” one of the men said. “You expect that to change our minds? A few words from the princess, and we’re supposed to believe everything you’ve been telling us?”

“If Hallandren goes to war, you’re dead,” Vasher snapped. “Can’t you see that? What do you think will happen to the Idrians in these slums? You think things are bad now, wait until you’re seen as enemy sympathizers.”

“We know that, Vasher,” another said. “But what do you expect us to do? Submit to Hallandren treatment of us? Cave in and worship their indolent gods?”

“I don’t really care what you do,” Vasher said, “as long as it doesn’t involve threatening the security of the Hallandren government.”

“Maybe we~\textit{should}~just admit that war is coming and fight,” another said. “Maybe the slumlords are right. Maybe the best thing to do is hope that Idris wins.”

“They hate us,” another of them said, a man in his twenties with anger in his eyes. “They treat us worse than they do the statues in their streets! We’re less than Lifeless, to them.”

\textit{I know that anger,}~Vivenna realized.~\textit{I felt it. Feel it still. Anger at Hallandren.}

The man’s words rang hollow to her now. The truth was, she hadn’t really felt any ire from the Hallandren people. If anything, she’d felt indifference. She was just another body on the street to them.

Perhaps that’s why she hated them. She’d worked all of her life to become something important for them—in her mind, she’d been dominated by the monster that was Hallandren and its God King. And then, in the end, the city and its people had simply ignored her. She didn’t matter to them. And that was infuriating.

One of the Idrian men, an older man wearing a dark tan cap, shook his head in thought. “The people are restless, Vasher. Half the men talk of storming the Court of Gods in anger. The women store up food, waiting for the inevitable. Our youths go out in secret groups, searching the jungles for Kalad’s legendary army.”

“They believe that old myth?” Vasher asked.

The man shrugged. “It offers hope. A hidden army, powerful enough that it nearly ended the Manywar itself.”

“Believing myths isn’t what frightens me,” another man said. “It’s that our youths would even~\textit{think}~of using Lifeless as soldiers. Kalad’s Phantoms. Bah!” He spat to the side.

“What it means is that we’re desperate,” one of the older men said. “The people are angry. We can’t stop the riots, Vasher. Not after that slaughter a few weeks back.”

Vasher pounded the floor with a fist. “That’s what they want! Can’t you fools see that you’re giving your enemies perfect scapegoats? Those Lifeless that attacked the slum weren’t given their orders by the government. Someone slipped a few broken Lifeless into the group with orders to kill so that things would turn ugly!”

\textit{What?}~Vivenna thought.

“The Hallandren theocracy is a top-heavy structure laden with bureaucratic foolishness and inertia,” Vasher said. “It never moves unless someone pushes it! If we have riots in the street, that will be just what the war faction needs.”

\textit{I could help him,}~Vivenna thought, watching the reactions of the Idrians. She knew them instinctively in a way Vasher obviously didn’t. He made good arguments, but he approached them in the wrong way. He needed credibility.

She could help. But should she?

Vivenna didn’t know what to think anymore. If Vasher was right, she’d been played like a puppet by Denth. She believed that was true, but how could she know that Vasher wasn’t doing the same thing?

Did she want war? No, of course she didn’t. Particularly not a war Idris would have a very hard time surviving, let alone winning. Vivenna had worked so hard to undermine Hallandren’s ability to wage war. Why hadn’t she ever considered trying to head it off?

\textit{I did,}~she realized.~\textit{That was my original plan when I was back in Idris. I’d intended to talk the God King out of war when I became his bride.}

She’d given up on that plan. No, she’d been manipulated into giving up on it. Either by her father’s sense of inevitability or by Denth’s subtlety—or by both—it didn’t really matter. Her initial instinct had been to prevent the conflict. That was the best way to protect Idris; and it was—she now realized—also the best way to protect Siri. She’d practically given up on saving her sister, focusing on her own hate and arrogance instead.

Stopping the war wouldn’t protect Siri from being abused by the God King. But it would probably keep her from being used as a pawn or a hostage. It could save her life.

That was enough for Vivenna.

“It’s too late,” one of the men said.

“No,” Vivenna said. “Please.”

The men in the circle paused, looking over at her. She walked back to the circle and then knelt before them. “Please do not say such things.”

“But Princess,” one of the men said, “what can we do? The slumlords rile the people to anger. We have no power compared to them.”

“You must have some influence,” she said. “You seem like men of wisdom.”

“We’re family men and workers,” another said. “We have no riches.”

“But people listen to you?” she asked.

“Some do.”

“Then tell them that there~\textit{are}~more options,” Vivenna said, bowing her head. “Tell them to be stronger than I was. The Idrians here in the slums—I’ve seen their strength. If you tell them that they’ve been used, maybe they can avoid being manipulated further.”

The men fell silent.

“I don’t know if everything this man says is true,” she said, nodding to Vasher. “But I do know that Idris will not win this war. We should be doing everything we can to prevent a conflict, not to encourage one.” She felt a tear on her cheek, and her hair had grown a pale white. “You can see. I~.~.~. no longer have the control a princess and follower of Austre should show. I am a disgrace to you, but please don’t let my failure doom you. The Hallandren don’t hate us. They barely even notice us. I know this is frustrating, but if you~\textit{make}~them notice you by rioting and destroying, they will only be shaken into anger against our homeland.”

“So we should just roll over?” the younger man asked. “Let them step on us? What does it matter if they do it unintentionally? We still get crushed.”

“No,” Vivenna said. “There must be a better way. An Idrian is their queen, now. Perhaps, if we give them time, they will get over their prejudice. We~\textit{must}~focus our energies now on keeping them from attacking!”

“Your words make sense, Princess,” said the older man wearing the cap. “But—and forgive me for my ostentation—those of us here in Hallandren find it difficult to care about Idris much anymore. It failed us before we even left, and now we can’t really go back.”

“We~\textit{are}~Idrians,” one of the others said. “But~.~.~. well, our families here are more important.”

A month ago, Vivenna would have been offended. Her sojourn on the streets, though, had taught her a little of what desperation could do to a person. What was Idris to them if their families starved? She could not blame them for their attitude.

“You think you will fare better if Idris is conquered?” Vasher asked. “If there’s war, you’ll be treated even worse than you are now.”

“There~\textit{are}~other options,” Vivenna said. “I know of your plight. If I return to my father and explain it, perhaps we can find a way to return you to Idris.”

“Return us to Idris?” one of the men said. “My family has been here in Hallandren for fifty years now!”

“Yes, but as long as the king of Idris lives,” Vivenna said, “you have an ally. We can work with diplomacy to make things better for you.”

“The king doesn’t care about us,” another said sadly.

“I care,” Vivenna said.

And she did. She found it strange, but a part of her felt more of a kinship with the Idrians in the city than with those she had left behind. She understood.

“We must find a way to bring attention to your suffering without bringing hatred as well,” she said. “We will find a way. As I said, my sister is married to the God King himself. Perhaps through her, he can be persuaded to improve the slums. Not because he’s afraid of the violence our people might cause, but because of the pity he feels for their situation.”

She continued to kneel, ashamed before these men. Ashamed to be crying, to be seen in the immodest clothing and with ragged, short hair. Ashamed to have failed them so completely.

\textit{How could I fail so easily?}~she thought.~\textit{I, who was supposed to be so prepared, so in control. How could I be so angry that I ignored my people’s needs just because I wanted to see Hallandren pay?}

“She is sincere,” one of the men finally said. “I will give her that.”

“I don’t know,” said another. “I still feel it’s too late.”

“If that’s the case,” Vivenna said, still looking at the floor, “what do you have to lose? Think of the lives you could save. I promise. Idris will not forget you any longer. If you make peace with Hallandren, I will ensure that you are seen as heroes back in our homeland.”

“Heroes, eh?” one of them said. “It would be nice to be known as a hero, rather than the ones who left the highlands to live in brazen Hallandren.”

“Please,” Vivenna whispered.

“I’ll see what I can do,” one of the men said, standing.

Several of the others voiced agreement. They stood as well, shaking hands with Vasher. Vivenna remained kneeling as they left.

Eventually, the room was empty save for her and Vasher. He sat down across from her.

“Thanks,” he said.

“I didn’t do it for you,” she whispered.

“Get up,” he said. “Let’s go. I want to meet with someone else.”

“I~.~.~.” She sat up on the rug, trying to make sense of her feelings. “Why should I do as you tell me? How do I know that you’re not just using me? Lying to me. Like Denth did.”

“You don’t know,” Vasher said, recovering his sword from the corner. “You’ll just have to do what I say.”

“Am I a prisoner then?”

He glanced at her. Then he walked over and squatted. “Look,” he said. “We both agree that war is bad for Idris. I’m not going to take you on raids or make you meet with slumlords. All you have to do is tell people you don’t want a war.”

“And if I’m not willing to do that?” she said. “Will you force me?”

He watched her for a moment, then swore under his breath, standing. He pulled out a bag of something and tossed it at her. It clinked as it hit her chest and then fell to the floor.

“Go,” he said. “Get back to Idris. I’ll do it without you.”

She just continued to sit, staring. He began to walk away.

“Denth used me,” she found herself whispering. “And the worst part is, I still feel like this must all be just a misunderstanding. I feel that he’s really my friend, and that I should go to him and find out why he did what he did. Maybe we are all just confused.”

She closed her eyes, resting her head on her knees. “But then I remember the things I saw him do. My friend Parlin is dead. Other soldiers sent by my father, stuffed in sacks. I’m so confused.”

The room fell silent. “You’re not the first one he’s taken in, Princess,” Vasher finally said. “Denth~.~.~. he’s a subtle one. A man like him can be evil to the core, but if he is charismatic and amusing, people will listen to him. They’ll even like him.”

She looked up, blinking teary eyes.

Vasher turned away. “Me,” he said. “I’m not like that. I have trouble talking. I get frustrated. I snap at people. Doesn’t make me very popular. But I promise you that I won’t lie to you.” He met her eyes. “I want to stop this war. That’s all that really matters to me right now. I promise you.”

She wasn’t sure if she believed him. Yet she found herself wanting to.~\textit{Idiot,}~she thought.~\textit{You’re just going to get taken in again.}

She hadn’t proven herself a very good judge of character. Still, she didn’t pick up the bag of coins. “I am willing to help. Assuming it doesn’t involve anything more than telling others that I wish to keep Idris from harm.”

“Good enough.”

She hesitated. “Do you really think we can do it. Stop the war?”

He shrugged. “Maybe. Assuming I can keep myself from beating the Colors out of all these Idrians for acting like idiots.”

\textit{A pacifist with temper-control issues,}~she thought ruefully.~\textit{What a combination. A little like a devout Idrian princess who holds enough BioChromatic Breath to populate a small village.}

“There are more places like this,” Vasher said. “I would show you to the people there.”

“All right,” she said, trying not to look at the blade as she stood. Even now, it had a strange ability to make her feel sick.

Vasher nodded. “There won’t be many people at each meeting. I don’t have Denth’s connections, and I’m not friendly with important people. The ones I know are workers. We’ll have to go visit the dye vats, perhaps even some of the fields.”

“I understand,” she said.

Without further comment, Vasher picked up his bag of coins, then led her out onto the street.~\textit{And so,}~she thought,~\textit{I begin again.}

\textit{I can only hope that this time, I’m on the right side.}

