% \section{Chapter Eleven}
\chapter{}

But surely we can bend the rules a little bit,” Siri said, walking quickly beside Treledees.

Treledees eyed her. The priest—high priest of the God King—would have been tall even without the elaborate miter on his head. With it, he seemed to tower over her almost like one of the Returned.

Well, a spindly, obnoxious, disdainful Returned. “An exception?” he asked with his leisurely Hallandren accent. “No, I do not think that will be possible, Vessel.”

“I don’t see why not,” Siri said as a servant pulled open the door in front of them, allowing them to leave a green-colored room and pass into a blue one. Treledees respectfully let her pass through the doorway first, though she sensed that he was displeased he had to do so.

Siri ground her teeth, trying to think of another avenue of attack.~\textit{Vivenna would be calm and logical,}~she thought.~\textit{She’d explain why she should be allowed to leave the palace in a way that made sense so that the priest listened to her.}~Siri took a deep breath, trying to ease the red from her hair and the frustration from her attitude.

“Look. Couldn’t I, maybe, go on~\textit{one}~trip outside? Just into the court itself?”

“Impossible,” Treledees said. “If you lack for entertainment, why not have your servants send for minstrels or jugglers? I’m sure they could keep you occupied.”~\textit{And out of my hair,}~his tone seemed to imply.

Couldn’t he understand? It wasn’t lack of something to do that frustrated her. It was that she couldn’t see the sky. Couldn’t run away from walls and locks and rules. Barring that, she would have settled for someone to talk to. “At least let me meet with one of the gods. I mean, really—what is accomplished by keeping me locked up like this?”

“You’re not ‘locked up,’ Vessel,” Treledees said. “You are observing a period of isolation in which you can dedicate yourself to contemplating your new place in life. It is an ancient and worthy practice, one that shows respect for the God King and his divine monarchy.”

“Yes, but this is Hallandren,” Siri said. “It’s the land of laxness and frivolity! Surely you can see your way to making an exception.”

Treledees stopped short. “We do~\textit{not}~make exceptions in matters of religion, Vessel. I must assume that you are testing me in some way, for I find it hard to believe that anyone worthy of touching our God King could harbor such vulgar thoughts.”

Siri cringed.~\textit{Less than a week in the city,}~she thought,~\textit{and I’ve already started letting my tongue get me into trouble.}~Siri didn’t dislike people—she loved to talk to them, spend time with them, laugh with them. However, she couldn’t make them do what she wanted, not in the way that a politician was supposed to be able to do. That was something she should have learned from Vivenna.

She and Treledees continued walking. Siri wore a long, flowing brown skirt that covered her feet and had a train that trailed behind her. The priest was wearing golds and maroons—colors matched by the servants. It still amazed her that everyone in the palace had so many costumes, even if they were identical save for color.

She knew that she shouldn’t let herself get annoyed with the priests. They already didn’t seem to like her, and getting snappish wouldn’t help. It was just that the last few days had been so~\textit{dull.}~Trapped in the palace, unable to leave, unable to find anyone to talk to, she felt herself nearly going mad.

But there would be no exceptions. Apparently.

“Will that be all, Vessel?” Treledees asked, pausing beside a door. It almost seemed like he found it a chore to remain civil toward her.

Siri sighed, but nodded. The priest bowed, then opened the door and quickly rushed away. Siri watched him go, tapping her foot, arms folded. Her servants stood arrayed behind her, silent as always. She considered finding Bluefingers, but~.~.~. no. He always had so much to do, and she felt bad distracting him.

Sighing again, she motioned for her servants to prepare the evening meal. Two fetched a chair from the side of the room. Siri sat, resting as food was gathered. The chair was plush, but it was still difficult to sit in a way that didn’t aggravate one of her aches or cramps. Each of the last six nights, she had been forced to kneel, naked, until she finally grew so drowsy that she drifted off. Sleeping on the hard stone had left a dull, persistent pain in her back and neck.

Each morning, once the God King was gone, she moved to the bed. When she awoke the second time, she burned the sheets. After that, she chose her clothing. There was a new array each time, with no repeated outfits. She wasn’t sure where the servants got such a steady supply of clothing in Siri’s size, but it made her hesitant about choosing her daily costume. She knew that she’d likely never see any of the options again.

After dressing, she was free to do as she wished, assuming she didn’t leave the palace. When night came, she was bathed, then given a choice of luxurious gowns to wear into the bedchamber. As a matter of comfort, she had started requesting more and more ornate gowns, with more fabric to use in sleeping. She often wondered what the dressmakers would think if they knew that their gowns were only worn for a few brief moments before being discarded to the floor, then eventually used as blankets.

She didn’t own anything, yet could have whatever she wanted. Exotic foods, furniture, entertainers, books, art~.~.~. she only needed ask. And yet, when she was finished, it was removed. She had everything and nothing at the same time.

She yawned. The interrupted sleep schedule left her bleary-eyed and tired. The completely empty days didn’t help either.~\textit{If only there were someone to talk to.}~But servants, priests, and scribes were all locked into their formal roles. That accounted for everyone she interacted with.

Well, except~\textit{him.}

Could she even call that interacting? The God King appeared to enjoy looking at her body, but he’d never given her any indication that he wanted more. He simply let her kneel, those eyes of his watching and dissecting her. That was the sum total of their marriage.

The servants finished putting out her dinner, then lined up by the wall. It was getting late—almost time for her nightly bathing.~\textit{I’ll have to eat quickly,}~she thought, sitting at the table.\textit{After all, I wouldn’t want to be late for the evening’s ogling.}

\orn

A few hours later, Siri stood bathed, perfumed, and dressed before the massive golden door that led into the God King’s bedchamber. She breathed deeply, calming herself, anxiety bringing her hair to a pale brown. She still hadn’t gotten used to this part.

It was silly. She knew what would happen. And yet, the anticipation—the fear—was still there. The God King’s actions proved the power he had over her. One day he would take her, and it could come at any time. Part of her wished he’d just be done with it. The extended dread was even worse than that first single evening of terror.

She shivered. Bluefingers eyed her. Perhaps eventually he’d trust her to arrive at the bedchamber on time. Each night so far, he’d come to escort her.

\textit{At least he hasn’t shown up while I’m bathing again.}~The warm water and pleasant scents should have made her relax—unfortunately, she tended to spend each bath worrying about either her impending visit to the God King or some male servant walking in on her.

She glanced at Bluefingers.

“A few more minutes, Vessel,” he said.

\textit{How does he know?}~she thought. The man seemed to have a supernatural sense of time. She hadn’t seen any form of timepiece in the palace—neither sundial, metered candle, nor water clock. In Hallandren, apparently, gods and queens didn’t worry about such things. They had servants to remind them of appointments.

Bluefingers glanced at the door, then at her. When he saw that she was watching him, he immediately turned away. As he stood, he started shuffling his weight from foot to foot.

\textit{What does}~he~\textit{have to be nervous about?}~she thought with annoyance, turning to stare at the door’s intricate gold designs.~\textit{He’s not the one who has to go through this every night.}

“Do~.~.~. things go well with the God King, then?” Bluefingers asked suddenly.

Siri frowned.

“I can see that you’re tired a lot of the time,” Bluefingers said. “I~.~.~. guess that means you are very~.~.~. active at night.”

“That’s good, right? Everyone wants an heir as soon as possible.”

“Yes, of course,” Bluefingers said, wringing his hands. “It’s just that~.~.~.” He trailed off, then glanced at her, meeting her eyes. “You just might want to be careful, Vessel. Keep your wits about you. Try to stay alert.”

Her hair bleached the rest of the way white. “You make it sound as if I’m in danger,” she said softly.

“What? Danger?” Bluefingers said, glancing to the side. “Nonsense. What would you have to fear? I was simply suggesting that you remain alert, should the God King have needs you should fulfill. Ah, see, now it’s time. Enjoy your evening, Vessel.”

With that, he pushed open the door, placed a hand on her back, and guided her into the room. At the last moment, he moved his head up next to hers. “You should watch yourself, child,” he whispered. “Not all here in the palace is as it seems.”

Siri frowned, turning, but Bluefingers plastered on a false smile and pushed the door shut.

\textit{What in Austre’s name was that?}~she thought, pausing for what was probably too long a time as she stared at the door. Finally, she sighed, turning away. The usual fire crackled in the hearth, but it was smaller than previously.

He was there. Siri didn’t need to look to see him. As her eyes grew more accustomed to the darkness, she could notice that the fire’s colors—blue, orange, even black—were far too true, far too~\textit{vibrant.}~Her gown, a brilliant golden satin, seemed to burn with its own inner color. Anything that was white—some of the lace on her dress, for instance—bent slightly, giving off a rainbow of colors as if seen through a prism. Part of her wished for a well-lit room, where she could experience the full beauty of BioChroma.

But, of course, that was not right. The God King’s Breath was a perversion. He was fed on the souls of his people, and the colors he evoked came at their expense.

Shivering, Siri undid the side of her dress, then let the garment fall to pieces around her—the long sleeves slipping free, bodice falling forward, skirt and gown rustling as they dropped to the floor. She completed the ritual, sliding the straps of her shift off her shoulders, then dropping the garment to the floor beside the gown. She stepped free of both, then bowed herself down into her customary posture.

Her back complained, and she ruefully contemplated another uncomfortable night.~\textit{The least they could do,}~she thought,~\textit{is make certain the fire is large enough.}~At night in the large stone palace, it got chilly despite the Hallandren tropical climate. Particularly if one were naked.

\textit{Focus on Bluefingers,}~she thought, trying to distract herself.~\textit{What did he mean? Things are not what they seem in the palace?}

Was he referring to the God King and his ability to have her killed? She was well aware of the God King’s power. How could she forget it, with him sitting not fifteen feet away, watching from the shadows? No, that wasn’t it. He’d felt he’d needed to give this warning quietly, without others hearing.~\textit{Watch yourself.~.~.~.}

It smelled of politics. She gritted her teeth. If she’d paid more attention to her tutors, might she have been able to pick out a more subtle meaning in Bluefingers’s warning?

\textit{As if I needed something else to be confused about,}~she thought. If Bluefingers had something to tell her, why hadn’t he just said it? As the minutes passed, his words turned over and over in her mind like a restless sleeper, but she was too uncomfortable and cold to come to any conclusions. That only left her feeling~\textit{more}~annoyed.

Vivenna would have figured it out. Vivenna probably would have known instinctively why the God King hadn’t chosen to sleep with her. She would have fixed it the first night.

But Siri was incompetent. She tried so~\textit{hard}~to do as Vivenna would have—to be the best wife she could, to serve Idris. To be the woman that everyone expected her to be.

But she wasn’t. She~\textit{couldn’t}~just keep doing this. She felt trapped in the palace. She couldn’t get the priests to do more than roll their eyes at her. She couldn’t even tempt the God King to bed her. On top of that, she could very well be in danger, and she couldn’t even understand why or how.

In simpler terms, she was just plain frustrated.

Groaning at her aching limbs, Siri sat up in the dark room and looked at the shadowy form in the corner. “Will you please just get~\textit{on}~with it?” she blurted out.

Silence.

Siri felt her hair bleach a terrible bone white as she realized what she’d just done. She stiffened, casting her eyes down, weariness fleeing in the face of sudden anxiety.

What had she been~\textit{thinking}? The God King could call servants to execute her. In fact, he didn’t even need that. He could bring her own dress to life, Awakening it to strangle her. He could make the rug rise up and smother her. He could probably bring the ceiling down on her, all without moving from his chair.

Siri waited, breathing with shallow anxiety, anticipating the fury and retribution. But~.~.~. nothing happened. Minutes passed.

Finally, Siri glanced up. The God King had moved, sitting up straighter, regarding her from his darkened chair beside the bed. She could see his eyes reflecting the firelight. She couldn’t make out much of his face, but he didn’t~\textit{seem}~angry. He just seemed cold and distant.

She almost cast her eyes down again, but hesitated. If snapping at him wouldn’t provoke a reaction, then looking at him wasn’t likely to either. So she turned her chin up and met his eyes, knowing full well that she was being foolish. Vivenna would never have provoked the man. She would have remained quiet and demure, either solving the problem or—if there was no solution—kneeling every night until her patience impressed even the God King of Hallandren.

But Siri was not Vivenna. She was just going to have to accept that fact.

The God King continued to look at her, and Siri found herself blushing. She’d knelt before him naked six nights in a row, but~\textit{facing}~him unclothed was more embarrassing. Still, she didn’t back down. She continued to kneel, watching him, forcing herself to stay awake.

It was difficult. She was tired, and the position was actually less comfortable than bowing had been. She watched anyway, waiting, the hours passing.

Eventually—at about the same time that he left the room every night—the God King stood up. Siri stiffened, shocked alert. However, he simply walked to the door. He tapped quietly, and it opened for him, servants waiting on the other side. He stepped out and the door closed.

Siri waited tensely. No soldiers came to arrest her; no priests came to chastise her. Eventually, she just walked over to the bed and burrowed into its covers, savoring the warmth.

\textit{The God King’s wrath,}~she thought drowsily,~\textit{is decidedly less wrathful than reported.}

With that, she fell asleep.

