\section{Chapter Five}

\textit{This will complicate things,}~Vasher thought, standing in the shadows atop the wall that enclosed the Court of Gods.

\textit{What’s wrong?}~Nightblood asked.~\textit{So the rebels actually sent a princess. Doesn’t change your plans.}

Vasher waited, watching, as the new queen’s carriage crept up the incline and disappeared into the palace’s maw.

\textit{What?}~Nightblood demanded. Even after all of these years, the sword re acted like a child in many ways.

\textit{She’ll be used,}~Vasher thought.~\textit{I doubt we’ll be able to get through this without dealing with her.}~He hadn’t believed that the Idrians would actually send royal blood back to T’Telir. They’d given up a pawn of terrible value. Vasher turned away from the court, wrapping his sandaled foot around one of the banners that ran down the outside of the wall. Then he released his Breath.

“Lower me,” he Commanded. The large tapestry—woven from wool threads—sucked hundreds of Breaths from him. It hadn’t the form of a man, and it was massive in size, but Vasher now had enough Breath to spend in such extravagant Awakenings. The tapestry twisted, a thing alive, and formed a hand, which picked Vasher up. As always, the Awakening tried to imitate the form of a human—looking closely at the twistings and undulations of the fabric, Vasher could see outlines of muscles and even veins. There was no need for them; the Breath animated the fabric, and no muscles were necessary for it to move.

The tapestry carefully carried Vasher down, pinching him by one shoulder, placing his feet on the street. “Your Breath to mine,” Vasher Commanded. The large banner-tapestry lost its animate form immediately, life vanishing, and it fluttered back against the wall.

Some few people paused in the street, yet they were interested, not awed. This was T’Telir, home of the gods themselves. Men with upward of a thousand Breaths were uncommon, but not unheard of. The people gawked—as peasants in other kingdoms might pause to watch the carriage of a passing lord—but then they moved on with their daily activities.

The attention was unavoidable. Though Vasher still dressed in his usual outfit—ragged trousers, well-worn cloak despite the heat, a rope wrapped several times around his waist for a belt—he now caused colors to brighten dramatically when he was near. The change would be noticeable to normal people and blatantly obvious to those of the First Heightening.

His days of being able to hide and skulk were gone. He’d have to grow accustomed to being noticed again. That was one of the reasons he was glad to be in T’Telir. The city was large enough and filled with enough oddities—from Lifeless soldiers to Awakened objects serving everyday functions—that he probably wouldn’t stand out~\textit{too}~much.

Of course, that didn’t take Nightblood into account. Vasher moved through the crowds, carrying the overly heavy sword in one hand, sheathed point nearly dragging on the ground behind him. Some people shied away from the sword immediately. Others watched it, eyes lingering far too long. Perhaps it was time to stuff Nightblood back in the pack.

\textit{Oh, no you don’t,}~Nightblood said.~\textit{Don’t even start thinking about that. I’ve been locked away for too long.}

\textit{What does it matter to you?}~Vasher thought.

\textit{I need fresh air,}~Nightblood said.~\textit{And sunlight.}

\textit{You’re a sword,}~Vasher thought,~\textit{not a palm tree.}

Nightblood fell silent. He was smart enough to realize that he was not a person, but he didn’t like being confronted with that fact. It tended to put him in a sullen mood. That suited Vasher just fine.

He made his way to a restaurant a few streets down from the Court of Gods. This was one thing he~\textit{had}~missed about T’Telir: restaurants. In most cities, there were few dining options. If you intended to stay for a while, you hired a local woman to give you meals at her table. If you stayed a short time, you ate what your innkeeper gave you.

In T’Telir, however, the population was large enough—and rich enough—to support dedicated food providers. Restaurants still hadn’t caught on in the rest of the world, but in T’Telir, they were commonplace. Vasher already had a booth reserved, and the waiter nodded him to the spot. Vasher settled himself, leaving Nightblood up against the wall.

The sword was stolen within a minute of his letting go of it.

Vasher ignored the thievery, thoughtful as the waiter brought him a warm cup of citrus tea. Vasher sipped at the sweetened liquid, sucking on the bit of rind, wondering why in the world a people who lived in a tropical lowland preferred heated teas. After a few minutes, his life sense warned him that he was being watched. Eventually, that same sense alerted him that someone was approaching. Vasher slipped his dagger from his belt with his free hand as he sipped.

The priest sat down opposite Vasher in the booth. He wore street clothing, rather than religious robes. However—perhaps unconsciously—he had still chosen to wear the white and green of his deity. Vasher slipped his dagger back into its sheath, masking the sound by taking a loud sip.

The priest, Bebid, looked about nervously. He had enough of a Breath aura to indicate that he’d reached the First Heightening. It was where most people—those who could afford to buy Breath—stopped. That much Breath would extend their lifespan by a good decade or so and give them an increased life sense. It would also let them see Breath auras and distinguish other Awakeners, and—in a pinch—let them do a little Awakening themselves. A decent trade for spending enough money to feed a peasant family for fifty years.

“Well?” Vasher asked.

Bebid actually jumped at the sound. Vasher sighed, closing his eyes. The priest was not accustomed to these kinds of clandestine meetings. He wouldn’t have come at all, had Vasher not exerted certain~.~.~. pressures on him.

Vasher opened his eyes, staring at the priest as the waiter arrived with two plates of spiced rice. Tektees food was the restaurant’s specialty—the Hallandren liked foreign spices as much as they liked odd colors. Vasher had placed the order earlier, along with a payment that would keep the sur rounding booths empty.

“Well?” Vasher repeated.

“I~.~.~.” Bebid said. “I don’t know. I haven’t been able to find out much.”

Vasher regarded the man with a stern stare.

“You have to give me more time.”

“Remember your indiscretions, friend,” Vasher said, drinking the last of his tea, feeling a twinge of annoyance. “Wouldn’t want news of those getting out, would we?”~\textit{Do we have to go through this}~again\textit{?}

Bebid was quiet for a time. “You don’t know what you’re asking, Vasher,” he said, leaning in. “I’m a priest of Brightvison the True. I can’t betray my oaths!”

“Good thing I’m not asking you to.”

“We’re not supposed to release information about court politics.”

“Bah,” Vasher snapped. “Those Returned can’t so much as~\textit{look}~at one another without half of the city learning about it within the hour.”

“Surely you’re not implying—” Bebid said.

Vasher gritted his teeth, bending his spoon with his finger in annoyance. “\textit{Enough,}~Bebid! We both know that your oaths are all just part of the game.” He leaned in. “And I~\textit{really}~hate games.”

Bebid paled and didn’t touch his meal. Vasher eyed his spoon with annoyance, then bent it back, calming himself. He shoveled in a spoonful of rice, mouth burning from the spices. He’d didn’t believe in letting food sit around uneaten—you never knew when you’d have to leave in a hurry.

“There have been~.~.~. rumors,” Bebid finally said. “This goes beyond simple court politics, Vasher—beyond games played between gods. This is something very real, and~\textit{very}~quiet. Quiet enough that even observant priests only hear hints of it.”

Vasher continued to eat.

“There is a faction of the court pushing to attack Idris,” Bebid said. “Though I can’t fathom why.”

“Don’t be an idiot,” Vasher said, wishing he had more tea to wash down the rice. “We both know Hallandren has sound reasons to slaughter every person up in those highlands.”

“Royals,” Bebid said.

Vasher nodded. They were called rebels, but those “rebels” were the true Hallandren royal family. Mortal men though they might be, their bloodline was a challenge to the Court of Gods. Any good monarch knew that the first thing you did to stabilize your throne was execute anyone who had a better claim to it than you did. After that, it was usually a good idea to execute everyone who~\textit{thought}~they might have claim.

“So,” Vasher said. “You fight, Hallandren wins. What’s the problem?”

“It’s a bad idea, that’s the problem,” Bebid said. “A~\textit{terrible}~idea. Kalad’s Phantoms, man! Idris won’t go easily, no matter what people in the court say. This won’t be like squashing that fool Vahr. The Idrians have allies from across the mountains and the sympathies of dozens of kingdoms. What some are calling a ‘simple quelling of rebel factions’ could easily spin into another Manywar. Do you want that? Thousands upon thousands dead? Kingdoms falling to never rise again? All so we can grab a little bit of frozen land nobody really wants.”

“The trade passes are valuable,” Vasher noted.

Bebid snorted. “The Idrians aren’t foolish enough to raise their tariffs~\textit{too}~high. This isn’t about money. It’s about fear. People in the court talk about what~\textit{might}~happen if the Idrians cut off the passes or what~\textit{may}~happen if the Idrians let enemies slip through and besiege T’Telir. If this were about money, we’d never go to war. Hallandren thrives on its dye and textiles trade. You think that business would boom in war? We’d be lucky not to suffer a full economic collapse.”

“And you assume that I care about Hallandren’s economic well-being?” Vasher asked.

“Ah, yes,” Bebid said dryly. “I forgot who I was talking to. What~\textit{do}~you want, then? Tell me so we can get this over with.”

“Tell me about the rebels,” Vasher said, chewing on rice.

“The Idrians? We just talked—”

“Not them,” Vasher said. “The ones in the city.”

“They’re unimportant now that Vahr is dead,” the priest said with a wave of his hand. “Nobody knows who killed him, by the way. Probably the rebels themselves. Guess they didn’t appreciate his getting himself captured, eh?”

Vasher said nothing.

“Is that all you want?” Bebid said impatiently.

“I need to contact the factions you mentioned,” Vasher said. “The ones who are pushing for war against Idris.”

“I won’t help you enrage the—”

“Do~\textit{not}~presume to tell me what to do, Bebid. Just give me the information you promised, and you can be free of all this.”

“Vasher,” Bebid said, leaning in even further. “I~\textit{can’t}~help. My lady isn’t interested in these kinds of politics, and I move in the wrong circles.”

Vasher ate some more, judging the man’s sincerity. “All right. Who, then?”

Bebid relaxed, using his napkin to wipe his brow. “I don’t know,” he said. “Maybe one of Mercystar’s priests? You could also try Bluefingers, I suppose.”

“Bluefingers? That’s an odd name for a god.”

“Bluefingers isn’t a god,” Bebid said, chuckling. “That’s just a nickname. He’s the High Place steward, head of the scribes. He pretty much keeps the court running; if anyone knows anything about this faction, it will be him. Of course, he’s so stiff and straight, you’ll have a hard time breaking him.”

“You’d be surprised,” Vasher said, shoveling the last bit of rice into his mouth. “I got you, didn’t I?”

“I suppose.”

Vasher stood. “Pay the waiter when you leave,” he said, grabbing his cloak off its peg and wandering out. He could feel a~.~.~. darkness to his right. He walked down the street, then turned down an alley, where he found Nightblood—still sheathed—sticking from the chest of the thief who had stolen him. Another cutpurse lay dead on the alley floor.

Vasher pulled the sword free, then snapped the sheath closed—it had only been opened a fraction of an inch—and did up the clasp.

\textit{You lost your temper in there for a bit,}~Nightblood said with a chastising tone.~\textit{I thought you were going to work on that.}

\textit{Guess I’m relapsing,}~Vasher thought.

Nightblood paused.~\textit{I don’t think you ever really unlapsed in the first place.}

\textit{That’s not a word,}~Vasher said, leaving the alley.

\textit{So?}~Nightblood said.~\textit{You’re too worried about words. That priest—you spent all those words on him, then you just let him go. It’s not really how I would have handled the situation.}

\textit{Yes, I know,}~Vasher said.~\textit{Your way would have involved making several more corpses.}

\textit{Well, I}~am~\textit{a sword,}~Nightblood said with a mental huff.~\textit{Might as well stick to what you’re good at.~.~.~.}

\bigskip \hrule \bigskip

Lightsong sat on his patio, watching his new queen’s carriage pull up to the palace. “Well, this has been a pleasant day,” he remarked to his high priest. A few cups of wine—along with some time to get past thinking about children deprived of their Breath—and he was beginning to feel more like his usual self.

“You’re that happy to have a queen?” Llarimar asked.

“I’m that happy to have avoided petitions for the day thanks to her arrival. What do we know about her?”

“Not much, Your Grace,” Llarimar said, standing beside Lightsong’s chair and looking toward the God King’s palace. “The Idrians surprised us by not sending the eldest daughter as planned. They sent the youngest in her stead.”

“Interesting,” Lightsong said, accepting another cup of wine from one of his servants.

“She’s only seventeen years old,” Llarimar said. “I can’t imagine being married to the God King at her age.”

“I can’t imagine you being married to the God King at~\textit{any}~age, Scoot,” Lightsong said. Then he pointedly cringed. “Actually, yes I~\textit{can}~imagine it, and the dress looks painfully inelegant on you. Make a note to have my imagination flogged for its insolence in showing me that particular sight.”

“I’ll put it in line right behind your sense of decorum, Your Grace,” Llarimar said dryly.

“Don’t be silly,” Lightsong said, taking a sip of wine. “I haven’t had one of~\textit{those}~in years.”

He leaned back, trying to decide what the Idrians were signaling by sending the wrong princess. Two potted palms waved in the wind, and Lightsong was distracted by the scent of salt on the incoming sea breeze.~\textit{I wonder if I sailed that sea once,}~he thought.~\textit{A man of the ocean? Is that how I died? Is that why I dreamed of a ship?}

He could only vaguely remember that dream now. A red sea~.~.~.

Fire. Death, killing, and battle. He was shocked as he suddenly remembered his dream in starker, more vivid detail. The sea had been red as it reflected the magnificent city of T’Telir, engulfed in flames. He could almost hear people crying out in pain, he could nearly hear~.~.~. what? Soldiers marching and fighting in the streets?

Lightsong shook his head, trying to dispel the phantom memories. The ship he’d seen in his dream had been burning too, he now remembered. It didn’t have to mean anything; everyone had nightmares. But it made him uncomfortable to know that~\textit{his}~nightmares were seen as prophetic omens.

Llarimar was still standing beside Lightsong’s chair, watching the God King’s palace.

“Oh, sit down and stop looming over me,” Lightsong said. “You’re making the buzzards jealous.”

Llarimar raised an eyebrow. “And which buzzards would that be, Your Grace?”

“The ones who keep pushing for us to go to war,” Lightsong said waving a hand.

The priest sat down on one of the patio’s wooden recliners and relaxed as he sat, removing the bulky miter from his head. Underneath, Llarimar’s dark hair was plastered to his head with sweat. He ran his hand through it. During the first few years, Llarimar had remained stiff and formal at all times. Eventually, however, Lightsong had worn him down. After all, Lightsong was the god. In his opinion, if he could lounge on the job, then so could his priests.

“I don’t know, Your Grace,” Llarimar said slowly, rubbing his chin. “I don’t like this.”

“The queen’s arrival?” Lightsong asked.

Llarimar nodded. “We haven’t had a queen in the court for some thirty years. I don’t know how the factions will deal with her.”

Lightsong rubbed his forehead. “Politics, Llarimar? You know I frown on such things.”

Llarimar eyed him. “Your Grace, you are—by default—a politician.”

“Don’t remind me, please. I should very well like to extract myself from the situation. Do you think, perhaps, I could bribe one of the other gods to take control of my Lifeless Commands?”

“I doubt that would be wise,” Llarimar said.

“It’s all part of my master plan to ensure that I become totally and redundantly useless to this city by the time I die. Again.”

Llarimar cocked his head. “Redundantly useless?”

“Of course. Regular uselessness wouldn’t be enough—I am, after all, a god.” He took a handful of grapes from a servant’s tray, still trying to dismiss his dream’s disturbing images. They didn’t mean anything. Just dreams.

Even so, he decided he would tell Llarimar about them the next morning. Perhaps Llarimar could use the dreams to help push for peace with Idris. Since old Dedelin hadn’t sent his firstborn daughter, it would mean more debates in the court. More talk of war. This princess’s arrival should have settled it, but he knew that the war hawks among the gods would not let the issue die.

“Still,” Llarimar said, as if talking to himself. “They did send~\textit{someone.}~That is a good sign, surely. An outright refusal would have meant war for certain.”

“And whoever Certain is, I doubt we should have a war for him,” Lightsong said idly, inspecting a grape. “War is, in my divine opinion, even worse than politics.”

“Some say the two are the same, Your Grace.”

“Nonsense. War is far worse. At least where politics is going on, there are usually nice hors d’oeuvres.”

As usual, Llarimar ignored Lightsong’s witty remarks. Lightsong would have been offended if he hadn’t known there were three separate lesser priests standing at the back of the patio, recording his words, searching for wisdom and meaning within them.

“What will the Idrian rebels do now, do you think?” Llarimar asked.

“Here’s the thing, Scoot,” Lightsong said, leaning back, closing his eyes and feeling the sun on his face. “The Idrians don’t consider themselves to be rebels. They’re not sitting up in their hills, waiting for the day when they can return in triumph to Hallandren. This isn’t their home anymore.”

“Those peaks are hardly a kingdom.”

“They’re enough of a kingdom to control the area’s best mineral deposits, four vital passes to the north, and the original royal line of the original Hallandren dynasty. They don’t need us, my friend.”

“And the talk of Idrian dissidents in the city, ones rousing the people against the Court of Gods?”

“Rumors only,” Lightsong said. “Though, when I’m proven wrong and the underprivileged masses storm my palace and burn me at the stake, I’ll be sure to inform them that you were right all along. You’ll get the last laugh. Or~.~.~. well, the last scream, since you’ll probably be tied up beside me.”

Llarimar sighed, and Lightsong opened his eyes to find the priest regarding him with a contemplative expression. The priest didn’t chastise Lightsong for his levity. Llarimar just reached down, putting his headdress back on. He was the priest; Lightsong was the god. There would be no questioning of motives, no rebukes. If Lightsong gave an order, they would all do exactly as he said.

Sometimes, that terrified him.

But not this day. He was, instead, annoyed. The queen’s arrival had somehow gotten him talking about politics—and the day had been going so well until then.

“More wine,” Lightsong said, raising his cup.

“You can’t get drunk, Your Grace,” Llarimar noted. “Your body is immune to all toxins.”

“I know,” Lightsong said as a lesser servant filled his cup. “But trust me—I’m~\textit{quite}~good at pretending.”

