\section{Chapter Fifty-Three}

Vivenna waited up for Vasher. He did not return.

She paced in the small, one-room hideout—the sixth in a series. They never spent more than a few days in each location. Unadorned, it held only their bedrolls, Vasher’s pack, and a single flickering candle.

Vasher would have chastised her for wasting the candle. For a man who held a king’s fortune in Breaths, he was surprisingly frugal.

She continued pacing. She knew that she should probably just go to sleep. Vasher could take care of himself. It seemed that the only one in the city who couldn’t do~\textit{that}~was Vivenna.

And yet he’d told her he was only going on a quick scouting mission. Though he was a solitary person himself, he apparently understood her desire to be a part of things, so he usually let her know where he was going and when to expect him back.

She’d never waited up for Denth to come back from a night mission, and she’d been working with Vasher for a fraction of the time she’d spent with the mercenaries. Why did she worry so much now?

Though she had felt like she was Denth’s friend, she hadn’t really cared about him. He’d been amusing and charming, but distant. Vasher was~.~.~. well, who he was. There was no guile in him. He wore no false mask. She’d only met one other person like that: her sister, the one who would bear the God King’s child.

\textit{Lord of Colors!}~Vivenna thought, still pacing.~\textit{How did things turn into such a mess?}

\bigskip \hrule \bigskip

Siri awoke with a start. There was shouting coming from outside her room. She roused herself quickly, moving over to the door and putting her ear to it. She could hear fighting. If she were going to run, perhaps now would be the time. She rattled the door, hoping for some reason that it was unlocked. It wasn’t.

She cursed. She’d heard fighting earlier—screaming, and men dying. And now again.~\textit{Someone trying to rescue me, perhaps?}~she thought hopefully.~\textit{But who?}

The door shook suddenly, and she jumped back as it opened. Treledees, high priest of the God King, stood in the doorway. “Quickly, child,” he said, waving to her. “You must come with me.”

Siri looked desperately for a way to run. She backed away from the priest, and he cursed quietly, waving for a couple of soldiers in city guard uniforms to rush in and grab her. She screamed for help.

“Quiet, you fool!” Treledees said. “We’re trying to help you.”

His lies rang hollow in her ears, and she struggled as the soldiers pulled her from the room. Outside, bodies were lying on the ground, some in guard uniforms, others in nondescript armor, still others with grey skin.

She heard fighting down the hallway, and she screamed toward it as the soldiers roughly pulled her away.

\bigskip \hrule \bigskip

Old Chapps, they called him. Those who called him anything, that is.

He sat in his little boat, moving slowly across the dark water of the bay. Night fishing. During the day, one had to pay a fee to fish in T’Telir waters. Well, technically, during the night you were supposed to pay too.

But the thing about night was, nobody could see you. Old Chapps chuckled to himself, lowering his net over the side of the boat. The waters made their characteristic lap, lap, lap against the side of the boat. Dark. He liked it dark. Lap, lap, lap.

Occasionally, he was given better work. Taking bodies from one of the city’s slumlords, weighting them down with rocks tied in a sack to the foot, then tossing them into the bay. There were probably hundreds of them down there, floating in the current with their feet weighed to the floor. A party of skeletons, having a dance. Dance, dance, dance.

No bodies tonight, though. Too bad. That meant fish. Free fish he didn’t have to pay tariffs on. And free fish were good fish.

\textit{No~.~.~.}~a voice said to him.~\textit{A little bit more to your right.}

The sea talked to him sometimes. Coaxed him this way or that. He happily made his way in the direction indicated. He was out on the waters almost every night. They should know him pretty well by now.

\textit{Good. Drop the net.}

He did so. It wasn’t too deep in this part of the bay. He could drag the net behind his boat, pulling the weighted edges along the bottom, catching the smaller fish that came up into the shallows to feed. Not the best fish, but the sky was looking too dangerous to be out far from the shore. A storm brewing?

His net struck something. He grumbled, yanking it. Sometimes it got caught on debris or coral. It was heavy. Too heavy. He pulled the net back up over the side, then opened the shield on his lantern, risking a bit of light.

Tangled in the net, a sword lay in the bottom of his boat. Silvery, with a black handle.

Lap, lap, lap.

\textit{Ah, very nice,}~the voice said, much clearer now.~\textit{I hate the water. So wet and icky down there.}

Transfixed, Old Chapps reached out, picking up the weapon. It felt heavy in his hand.

\textit{I don’t suppose you’d want to go destroy some evil, would you?}~the voice said.~\textit{I’m not really sure what that means, to be honest. I’ll just trust you to decide.}

Old Chapps smiled.

\textit{Oh, all right,}~the sword said.~\textit{You can admire me a little bit longer, if you must. After that, though, we really need to get back to shore.}

\bigskip \hrule \bigskip

Vasher awoke groggily.

He was tied by his wrists to a hook in the ceiling of a stone room. The rope that had been used to tie him, he noticed, was the same one he’d used to tie up the maid. It had been completely drained of color.

In fact, everything around him was a uniform grey. He had been stripped save for his short, white underbreeches. He groaned, his arms feeling numb from the awkward angle of being hung by his wrists.

He wasn’t gagged, but he had no Breath left—he’d used the last of it in the fight, to Awaken the cloak of the fallen man. He groaned.

A lantern burned in the corner. A figure stood next to it. “And so we both return,” Denth said quietly.

Vasher didn’t reply.

“I still owe you for Arsteel’s death, too,” Denth said quietly. “I want to know how you killed him.”

“In a duel,” Vasher said in a croaking voice.

“You didn’t beat him in a duel, Vasher,” Denth said, stepping forward. “I know it.”

“Then maybe I snuck up and stabbed him from behind,” Vasher said. “It’s what he deserved.”

Denth backhanded him across the face, causing him to swing from the hook. “Arsteel was a good man!”

“Once,” Vasher said, tasting blood. “Once, we were all good men, Denth. Once.”

Denth was quiet. “You think your little quest here will undo what you’ve done?”

“Better than becoming a mercenary,” Vasher said. “Working for whoever will pay.”

“I am what you made me,” Denth said quietly.

“That girl trusted you. Vivenna.”

Denth turned, eyes darkened, the lanternlight not quite reaching his face. “She was supposed to.”

“She liked you. Then you killed her friend.”

“Things got a little out of hand.”

“They always do, with you,” Vasher said.

Denth raised an eyebrow, his face growing amused in the wan light. “\textit{I}~get out of hand, Vasher? Me? When’s the last time~\textit{I}~started a war? Slaughtered tens of thousands? You’re the one who betrayed his closest friend and killed the woman who loved him.”

Vasher didn’t respond. What argument could he offer? That Shashara had needed to die? It had been bad enough when she’d revealed the Commands to make Lifeless from a single breath. What if the way of making Awakened steel, like Nightblood, had entered the Manywar? Undead monsters slaughtering people with Awakened swords thirsting for blood?

None of that mattered to a man who’d seen his sister murdered by Vasher’s hand. Besides, Vasher knew he had little credibility to stand on. He’d created his own monsters to fight in that war. Not Awakened steel like Nightblood, but deadly enough in their own right.

“I was going to let Tonk Fah have you,” Denth said, turning away again. “He likes hurting things. It’s a weakness he has. We all have weaknesses. With my direction, he’s been able to restrict it to animals.”

Denth turned to him, holding up a knife. “I’ve always wondered what he finds so enjoyable about causing pain.”

\bigskip \hrule \bigskip

Dawn was approaching. Vivenna threw off her blanket, unable to sleep. She dressed, frustrated, but not sure why. Vasher was probably just fine. He was likely out carousing somewhere.

\textit{Of course,}~she thought wryly,~\textit{carousing. That sounds}~just~\textit{like him.}

He’d never stayed out an entire night before. Something had gone wrong. She slowed as she pulled on her belt, glancing over at Vasher’s pack and the change of clothing he had inside of it.~\textit{Every single thing I’ve tried since I left Idris has failed miserably,}~she thought, continuing to dress.~\textit{I failed as a revolutionary, I failed as a beggar, and I failed as a sister. What am I supposed to do? Find him? I don’t even know where to start.}

She looked away from the pack. Failure. It wasn’t something she’d been accustomed to, back in Idris. Everything she’d done there had turned out well.

\textit{Maybe that’s what this is all about,}~she thought, sitting.~\textit{My hatred of Hallandren. My insistence on saving Siri, on taking her place.}~When their father had chosen Siri over her, it had been the first time in her life she’d felt that she wasn’t good enough. So she’d come to T’Telir, determined to prove the problem wasn’t with her. It’d been with someone else. Anyone else. As long as Vivenna wasn’t flawed.

But Hallandren had repeatedly proved that she~\textit{was}~flawed. And now that she’d tried and failed so often, she found it hard to act. By choosing to act, she might fail—and that was so daunting that doing nothing seemed preferable.

It was the crowning arrogance in Vivenna’s life. She bowed her head. One last bit of feathered hypocrisy to adorn her royal hair.

\textit{You want to be competent?}~she thought.~\textit{You want to learn to be in control of what goes on around you, rather than just being pushed around? Then you’ll have to learn to deal with failure.}

It was frightening, but she knew it was true. She stood up and walked over to Vasher’s pack. She pulled out a wrinkled overshirt and a pair of leggings. Both had tassels hanging from the cuffs.

Vivenna put them on. Vasher’s spare cloak followed. It smelled like him, and was cut—like his other one—into the vague shape of a man. She understood, at least, one of the reasons his clothing looked so tattered.

She pulled out a couple of colorful handkerchiefs. “Protect me,” she Commanded the cloak, imagining it grabbing people who tried to attack her. She placed a hand on the sleeve of the shirt.

“Upon call,” she Commanded, “become my fingers and grip that which I must.” She’d only heard Vasher give the Command a couple of times, and she still wasn’t quite sure how to visualize what she wanted the shirt to do. She imagined the tassels closing around her hands as she had seen them do for Vasher.

She Awakened the leggings, commanding them to strengthen her legs. The leg tassels began to twist, and she raised each foot in turn, letting the tassels wrap around the bottoms. Her stance felt firmer, the leggings pulled tight against her skin.

Finally, she tied on the sword Vasher had given her. She still didn’t know how to use it, though she could hold it properly. It felt right to bring it.

Then she left.

\bigskip \hrule \bigskip

Lightsong had rarely seen a goddess cry.

“It wasn’t supposed to go this way,” Blushweaver said, heedless of the tears streaming down her cheeks. “I had things under control.”

The dungeon beneath the God King’s palace was a cramped room. Cages—like the kind that might be used for animals—lined both walls. They were large enough to hold a god. Lightsong couldn’t decide if that was just a coincidence.

Blushweaver sniffled. “I thought I had the God King’s priesthood on my side. We were working together.”

\textit{Something’s wrong about this,}~Lightsong thought, glancing at the group of priests chatting anxiously at the side of the room. Llarimar sat in his own cage—the one next to Lightsong’s—head bowed.

Lightsong looked back at Blushweaver. “How long?” he asked. “How long were you working with them?”

“From the beginning,” Blushweaver said. “I was supposed to get the Command phrases. We came up with the plan together!”

“Why did they turn on you?”

She shook her head, glancing down. “They claimed I didn’t do my part. That I was withholding things from them.”

“Were you?”

She looked away, eyes tearstained. She looked very odd, sitting in her cell. A beautiful woman of deific proportions, wearing a delicate silk gown, sitting on the ground, surrounded by bars. Crying.

\textit{We have to get out of here,}~Lightsong thought. He crawled over to the bars separating his cage from Llarimar’s, ignoring the pain of his thigh. “Scoot,” he hissed. “Scoot!”

Llarimar glanced up. He looked haggard.

“What does one use to pick a lock?” Lightsong asked.

Llarimar blinked. “What?”

“Pick a lock,” Lightsong said, pointing. “Maybe I’ll discover that I know how to do it, if I get my hands into the right position. I still haven’t figured out why my swordsmanship skills were so poor. But surely I can do this. If I can only remember what to use.”

Llarimar stared at him.

“Maybe I—” Lightsong began.

“What is wrong with you?” Llarimar whispered.

Lightsong paused.

“What is wrong with you!” Llarimar bellowed, standing. “You were a~\textit{scribe,}~Lightsong. A Colors-cursed~\textit{scribe}. Not a soldier. Not a detective. Not a thief. You were an accountant for a local moneylender!”

\textit{What?}~Lightsong thought.

“You were as much an idiot then as you are now!” Llarimar shouted. “Don’t you ever~\textit{think}~about what you’re going to do before you just saunter off and do it! Why can’t you just stop, occasionally, and ask yourself if you’re being a complete fool or not? I’ll give you a hint! The answer is~\textit{usually}~yes!”

Lightsong stumbled back from the bars, shocked. Llarimar.~\textit{Llarimar}~was yelling.

“And every time,” Llarimar said, turning away, “\textit{I}~get in trouble with you. Nothing has changed. You become a god, and I~\textit{still}~end up in prison!”

The heavy priest slumped down, breathing in deep gasps, shaking his head in obvious frustration. Blushweaver was staring at them. And so were the priests.

\textit{What is it I find odd about them?}~Lightsong thought, trying to sort out his thoughts and emotions as the group of priests approached. “Lightsong,” one of them said, stooping down beside his cage. “We need your Command phrases.”

He snorted. “I’m sorry to say that I’ve forgotten them. You probably know my reputation for being weak-minded. I mean, what kind of fool would come charging in here and get himself captured so easily?”

He smiled at them.

The priest by his cage sighed, then waved a hand at the others. They unlocked Blushweaver’s cage and pulled her out. She yelled and fought, and Lightsong smiled at the trouble she gave them. Yet there were six priests, and they finally managed to get her out.

Then one got out a knife and slit her throat.

The shock of the moment hit Lightsong like a physical force. He froze, eyes wide, watching in horror as the red blood spilled out the front of Blushweaver’s throat, staining her beautiful nightgown.

Far more disturbing was the look of panicked terror in her eyes. Such beautiful eyes.

“\textit{No!}” Lightsong screamed, slamming against the bars, reaching helplessly toward her. He strained his godly muscles, pressing himself against the steel as he felt his body begin to shake. It was useless. Even a perfect body couldn’t push its way through steel.

“You bastards!” he yelled. “You Colors-cursed bastards!” He struggled, pounding the bars with one hand as Blushweaver’s eyes began to dim.

And then her BioChroma faded. Like a blazing bonfire dimming down to a single candle. It puffed out.

“No~.~.~.” Lightsong said, sliding down to his knees, numb.

The priest regarded him. “So you~\textit{did}~care for her,” he said. “I’m sorry that we had to do that.” He knelt down, solemn. “However, Lightsong, we decided that we had to kill her so that you would understand that we’re serious. I do know your reputation, and I know that you usually take things lightheartedly. That is a fine attribute to have in many situations. Right now, you must realize how dangerous things are. We have shown you that we will kill. If you don’t do as we ask, others will die.”

“Bastard~.~.~.” Lightsong whispered.

“I need your Command phrases,” the priest said. “This is important. More important than you can understand.”

“You can beat them out of me,” Lightsong growled, feeling rage slowly overwhelm his shock.

“No,” the priest said, shaking his head. “We’re actually new to all of this. We don’t know how to torture very well, and it would take too much time to force you to talk that way. Those who~\textit{are}~skilled at torture aren’t being very cooperative right now. Never pay a mercenary before the job is done.”

The priest waved, and the others left Blushweaver’s corpse on the ground. Then they moved to Llarimar’s cage.

“No!” Lightsong screamed.

“We are serious, Lightsong,” the man said. “Very, very, serious. We know how much you care for your high priest. You now know that we will kill him if you don’t do as we say.”

“Why?” Lightsong said. “What is this even about? The God King you serve could order us to move the armies if he wanted to! We’d listen to him. Why do you care so much about those Command phrases?”

The priests forced Llarimar from his cage, then pushed him to his knees. One put a knife to his throat.

“Red panther!” Lightsong yelled, weeping. “That’s the Command phrase. Please. Leave him be.”

The priest nodded to the others, and they put Llarimar back in his cell. They left Blushweaver’s corpse on the ground, facedown in the blood.

“I hope that you haven’t lied to us, Lightsong,” the main priest said. “We’re not playing games. It would be unfortunate if we discovered that you still are.” He shook his head. “We are not cruel men. But we are working for something very important. Do not test us.”

With that, he left. Lightsong barely noticed. He was still staring at Blushweaver, trying to convince himself that he was hallucinating, or that she was faking, or that~\textit{something}~would change to make him realize that it was all just an elaborate scam.

“Please,” he whispered. “Please, no.~.~.~.”

