\section{Chapter Twenty-Two}

Weatherlove, god of storms, selected one of the wooden spheres from the rack, then hefted it in his hand. It had been built to fill the palm of a god, and was weighted in the middle with lead. Carved with rings across the surface, it was painted a deep blue.

“A doubling sphere?” asked Lifeblesser. “A bold move.”

Weatherlove eyed the small group of gods behind him. Lightsong was among them, sipping on a sweet orange fruited drink with some kind of alco hol enhancement. It had been several days since he’d allowed Llarimar to talk him out of bed, but he still had come to no conclusion on how to proceed.

“A bold move indeed,” Weatherlove said, tossing the sphere up into the air, then catching it. “Tell me, Lightsong the Bold. Do you favor this throw?”

The other gods chuckled. There were four of them playing. As usual,

Weatherlove wore a green and gold robe that hung from only one shoulder with a wrap around his waist that came down to mid-thigh. The outfit—patterned after the ancient dress of the Returned from paintings centuries past—revealed his sculpted muscles and divine figure. He stood at the edge of the balcony, as it was his turn to throw.

Seated behind him were the three others. Lightsong on the left and

Lifeblesser—god of healing—in the middle. Truthcall, god of nature, sat on the far right, wearing his ornate cloak and uniform of maroon and white.

The three gods were variations on a theme. If Lightsong hadn’t known them well, he would have had trouble telling them apart. Each stood almost exactly seven feet tall, with bulging muscles that any mortal would have envied. True, Lifeblesser had brown hair, while Weatherlove had blond and Truthcall had black. But all three had that same set of square-jawed features, perfect coiffure, and innate seamless grace that marked them as Returned divinities. Only their costumes really offered any variety.

Lightsong sipped his drink. “Do I bless your throw, Weatherlove?” he asked. “Are we not in competition against one another?”

“I suppose,” the god said, tossing the wooden ball up and down.

“Then why would I bless you when you throw against me?”

Weatherlove just smirked, then pulled back his arm and launched the ball out across the pitch. It bounced, then rolled over the grass, eventually coming to rest. This section of the courtyard had been divided into an expansive game board with ropes and stakes. Priests and servants scurried about on the sides, making notations and keeping track of the score so that the gods wouldn’t have to. Tarachin was a complex game, played only by the wealthy. Lightsong had never bothered to learn the rules.

He found it more amusing to play when he had no idea what he was doing.

It was his throw next. He stood up, selecting one of the wooden spheres from the rack because it matched the color of his drink. He tossed the orange sphere up and down; then—not paying attention to where he was throwing—he tossed it out onto the field. The sphere flew much farther than it probably should have; he had the strength of a perfect body. That was part of the reason the field was so vast; it had to be built to the scale of gods, and so when they played, they required the elevated perspective of a balcony to view their game.

Tarachin was supposed to be one of the most difficult games in the world; it required strength to throw the spheres correctly, keen wit to understand where to place them, coordination to do so with the necessary precision, and a great understanding of strategy to pick the proper sphere and dominate the game field.

“Four hundred and thirteen points,” a servant announced after being fed the number by scribes working below.

“Another magnificent throw,” Truthcall said, perking up in his wooden lounging chair. “How do you do it? I’d~\textit{never}~have thought to use a reversal sphere for that throw.”

\textit{Is that what the orange ones are called?}~Lightsong thought, returning to his seat. “You just have to understand the playing field,” he said, “and learn to get inside the mind of the sphere. Think like it does, reason as it might.”

“Reason like a sphere?” Lifeblesser said, standing up. He wore flowing robes of his colors, blue and silver. He selected a green sphere off the rack, then stared at it. “What type of reasoning does a wooden sphere do?”

“The circular type, I should think,” Lightsong said lightly. “And, by coincidence, it is my favorite type as well. Perhaps that’s why I’m so good at the game.”

Lifeblesser frowned, opening his mouth to reply. He finally shut it, looking confused by Lightsong’s comment. Becoming a god did not, unfortunately, increase one’s mental capacity along with one’s physical attributes. Lightsong didn’t mind. For him, the real sport of a game of Tarachin never involved where the spheres landed.

Lifeblesser made his throw, then sat down. “I do say, Lightsong,” he said, smiling. “I mean this as a compliment, but having you around can be draining!”

“Yes,” Lightsong said, sipping his drink, “I’m remarkably like a mosquito in that regard. Truthcall, isn’t it your throw?”

“Actually, it’s yours again,” Weatherlove said. “You achieved the crown pairing during your last toss, remember?”

“Ah yes, how could I forget,” Lightsong said, rising. He took another sphere, tossed it over his shoulder out onto the green, then sat down.

“Five hundred and seven points,” the priest announced.

“Now you’re just showing off,” Truthcall said.

Lightsong said nothing. In his opinion, it revealed an inherent flaw in the game that the one who knew least about it tended to do the best. He doubted, however, that the others would take it that way. All three were very dedicated to their sport, and they played every week. There was blessed little else for them to do with their time.

Lightsong suspected that they kept inviting him only because they wanted to prove, at last, that they could defeat him. If he’d fathomed the rules, he’d have tried to lose on purpose to keep them from insisting that he come play with them. Still, he liked the way his victories annoyed them—though, of course, they never showed him anything other than perfect decorum. Either way, under the circumstances, he suspected that he couldn’t lose if he wanted to. It was rather difficult to throw a game when you had no idea what you were doing to win it in the first place.

Truthcall finally stepped up to throw. He always wore clothing of a martial style, and the colors maroon and white were very handsome on him. Lightsong suspected that he’d always been jealous that instead of being given Lifeless Commands as his duty to the court, he’d been given a vote over issues of trade with other kingdoms.

“I hear that you spoke with the queen a few days back, Lightsong,” Truthcall said as he threw.

“Yes, indeed,” Lightsong said, sipping his drink. “She was extraordinarily pleasant, I must say.”

Weatherlove gave a quiet laugh, obviously thinking that last comment to be sarcasm—which was a little annoying, since Lightsong had meant it sincerely.

“The entire court is abuzz,” Truthcall said, turning and flipping back his cape, then leaning against the balcony railing as he waited for the points from his throw to be tabulated. “The Idrians betrayed the treaty, one could say.”

“The wrong princess,” Weatherlove agreed. “It gives us an opening.”

“Yes,” Truthcall said musingly, “but an opening for what?”

“To attack!” Lifeblesser said in his usual, dense way. The other two regarded him wincingly.

“There is so much more to be gained than that, Lifeblesser.”

“Yes,” Weatherlove said, idly spinning the last bit of wine in his cup. “My plans are already in motion, of course.”

“And what plans would those be, divine brother?” Truthcall said.

Weatherlove smiled. “I wouldn’t want to spoil the surprise, now, would I?”

“That depends,” Truthcall said evenly. “Will it keep me from demanding the Idrians give us more access to the passes? I’m willing to bet that some~.~.~. pressures could be placed on the new queen to gain her favor for such a proposal. She’s said to be rather naive.”

Lightsong felt a slight nausea as they spoke. He knew how they plotted, always scheming. They played their game with spheres, but just as much of their reason for seeing one another at these events was to posture and make deals.

“Her ignorance must be an act,” Lifeblesser said in a rare moment of thoughtfulness. “They wouldn’t have sent her if she was really that inexperienced.”

“She’s Idrian,” Truthcall said dismissively. “Their most important city has fewer people than a small T’Telir neighborhood. They barely understand the concept of politics, I’ll warrant. They are more used to talking to sheep than humans.”

Weatherlove nodded. “Even if she’s ‘well trained’ by their standards, she’ll be easy to manipulate here. The real trick is going to be to make certain others don’t get to her first. Lightsong, what was your impression? Will she be quick to do as the gods tell her?”

“I really wouldn’t know,” he said, waving for more juice. “As you know, I’m not much interested in political games.”

Weatherlove and Truthcall shared a smirking look; like most in the court, they considered Lightsong hopeless when it came to practical matters. And by their definition, “practical” meant “taking advantage of others.”

“Lightsong,” Lifeblesser said with his tactlessly honest voice. “You really need to take more of an interest in politics. It can be very diverting. Why, if you only knew the secrets to which I’m privy!”

“My dear Lifeblesser,” Lightsong replied, “please trust me when I say that I have~\textit{no}~desire to know any secrets which involve you and a privy.”

Lifeblesser frowned, obviously trying to work through that one.

The other two began to discuss the queen again as the priests reported the score from the last throw. Oddly, Lightsong found himself increasingly troubled. As Lifeblesser stood up to take his next toss, Lightsong found himself rising as well.

“My divine brothers,” he said, “I suddenly feel quite weary. Perhaps it was something I ingested.”

“Not something I served, I hope?” Truthcall said. It was his palace.

“Food, no,” Lightsong said. “The other things you’re serving today, perhaps. I really must be on my way.”

“But you’re in the lead!” Truthcall said. “If you leave now, we’ll have to play again next week!”

“Your threats roll off of me like water, my divine brother,” Lightsong said, nodding respectfully to each in turn. “I bid you farewell until such time as you drag me up here again to play this tragic game of yours.”

They laughed. He wasn’t sure whether to be amused or insulted that they so often confused his jokes for serious statements and the other way around.

He collected his priests—Llarimar included—from the room just inside the balcony, but didn’t feel like speaking with any of them. He just made his way through the palace of deep reds and whites, still troubled. The men on the balcony were rank amateurs compared to the~\textit{real}political masters, like Blushweaver. They were so blunt and obvious with their plans.

But even men who were blunt and obvious could be dangerous, particularly to a woman like the queen, who obviously had little experience with such things.

\textit{I’ve already determined that I can’t help her,}~Lightsong thought, leaving the palace and entering the green outside. To the right, a complex network of rope squares and patterns marked the Tarachin pitch. A sphere bounced with a distant thud in the grass. Lightsong walked the other direction on the springy lawn, not even waiting for his priests to erect a canopy to shade him from the afternoon sun.

He still worried that if he tried to help, he’d just make things worse. But then there were the dreams. War and violence. Over and over again, he saw the fall of T’Telir itself, the destruction of his homeland. He couldn’t continue to ignore the dreams, even if he didn’t accept them as prophetic.

Blushweaver thought that war was important. Or, at least, that it was important to prepare for. He trusted her more than any other god or goddess, but he also worried about how aggressive she was. She had come to him, asking him to be a part of her plans. Had she done it, perhaps, because she knew he would be more temperate than she? Was she intentionally balancing herself?

He heard petitions, even though he didn’t intend to ever give up his Breath and die. He interpreted paintings, even though he didn’t think he was seeing anything prophetic in them. Couldn’t he help secure power in the court in order to be prepared when he didn’t believe that his visions meant anything? Particularly if those preparations helped protect a young woman who, undoubtedly, would have no other allies?

Llarimar had told him to do his best. That sounded like an awful lot of work. Unfortunately, doing nothing was beginning to seem like even~\textit{more}~work. Sometimes, when you stepped in something foul, the only thing to do was to stop walking and make the effort to clean it off.

He sighed, shaking his head. “I’m probably going to regret this,” he muttered to himself.

Then he went looking for Blushweaver.

\bigskip \hrule \bigskip

The man was slight, almost skeletal, and each shellfish he slurped made Vivenna cringe for two reasons. Not only did she have trouble believing that anyone would enjoy such slimy, sluglike food, but the mussels were also of a very rare and expensive variety.

And she was paying.

The afternoon restaurant crowd was large—people usually ate out at midday, when it made more sense to buy food than return home for a meal. The entire concept of restaurants still seemed strange to her. Didn’t these men have wives or servants to make them meals? Didn’t they feel uncomfortable eating in such a public place? It was so~.~.~. impersonal.

Denth and Tonk Fah sat on either side of her. And, of course, they helped themselves to the plate of mussels as well. Vivenna wasn’t certain—she’d pointedly not asked—but she thought that the shellfish were raw.

The thin man across from her slurped down another one. He didn’t seem to be enjoying himself much despite the expensive surroundings and free food. He had a sneer on his lips and while he didn’t appear nervous, she did notice that he kept an eye on the restaurant entrance.

“So,” Denth said, setting another empty shell on the table, then wiping his fingers on the tablecloth—a common practice in T’Telir. “Can you help us or not?”

The little man—he called himself Fob—shrugged. “You tell a wild tale, mercenary.”

“You know me, Fob. When have I lied to you?”

“Whenever you’ve been paid to do it,” Fob said with a snort. “I’ve just never been able to catch you.”

Tonk Fah chuckled, reaching for another mussel. It slipped free of the shell as he brought it to his lips; Vivenna had to steel herself to keep from gagging at the slimy plop it made when it hit the table.

“You don’t disagree that war is coming, though,” Denth said.

“Of course not,” Fob said. “But it’s been coming for decades now. What makes you think that it will finally happen this year?”

“Can you afford to ignore the chance that it might?” Denth asked.

Fob squirmed a bit, then began eating mussels again. Tonk Fah began stacking the shells, seeing how many he could get balanced on top of one another. Vivenna said nothing for the moment. Her minor part in the meetings didn’t bother her. She watched, she learned, and she thought.

Fob was a landowner. He cleared forests, then rented the land to growers. He often relied on Lifeless to help with his clearing—workers loaned to him through the government. There was only one stipulation upon the lending. Should war come, all of the food produced on his holdings during wartime immediately became the property of the Returned.

It was a good deal. The government would probably seize his lands during a war anyway, so he didn’t really lose anything save for his right to complain.

He ate another mussel.~\textit{How does he keep packing them down?}~she thought. Fob had managed to slurp away nearly twice as many of the disgusting little creatures as Tonk Fah.

“That harvest won’t come in, Fob,” Denth said. “You will lose quite a bit this year, should we prove right.”

“But,” Tonk Fah said, adding another shell to his stack, “harvest early, sell your stockpiles, and you stand to get ahead of your competitors.”

“And what do you gain?” Fob asked. “How do I know those same competitors haven’t hired you to~\textit{convince}~me a war is coming?”

The table fell silent, making noticeable the other diners clattering at their own meals. Denth finally turned, eyeing Vivenna, and nodded.

She pulled up her shawl—not the matronly one she’d brought from Idris, but a silken, gossamer one that Denth had found for her. She met Fob’s eyes, then changed her hair to a deep red. With the shawl up, only those at the table and watching closely would be able to see the change.

He froze. “Do that again,” he said.

She changed it to blond.

Fob sat back, letting his mussel fall free of its shell. It splatted against the table near the one Tonk Fah had dropped. “The~\textit{queen}?” he asked with shock.

“No,” Vivenna said. “Her sister.”

“What’s going on here?” Fob asked.

Denth smiled. “She’s here to organize a resistance against the Returned gods and to prepare Idrian interests here in T’Telir for the coming war.”

“You don’t think that old royal up in the highlands would send his daughter for nothing?” Tonk Fah said. “War. It’s the only thing that would call for such desperation.”

“Your sister,” Fob said, eyeing Vivenna. “They sent the younger one into the court. Why?”

“The king’s plans are his own, Fob,” Denth said.

Fob looked thoughtful. Finally, he flipped the fallen mussel onto the plate of shells and reached for a fresh one. “I~\textit{knew}~there was more behind that girl’s arrival than simple chance.”

“So you’ll harvest?” Denth asked.

“I’ll think about it,” Fob said.

Denth nodded. “Good enough, I guess.”

He nodded to Vivenna and Tonk Fah, and the three of them left Fob eating his shellfish. Vivenna settled the tab—which was even higher than she’d feared—and then they joined Parlin, Jewels, and Clod the Lifeless waiting outside. The group moved away from the restaurant, pushing through the crowd easily, if only because of the massive Lifeless that walked before them.

“Where now?” Vivenna asked.

Denth eyed her. “Not tired even a little?”

Vivenna didn’t acknowledge her sore feet or her drowsiness. “We’re working for the good of my people, Denth. A little weariness is a small price.”

Denth shot a glance toward Tonk Fah, but the overweight mercenary had split off into the crowd toward a merchant’s stand, Parlin tagging along behind. Parlin, Vivenna noticed, had gone back to wearing his ridiculous green hat despite her disapproval. What was wrong with that man? He wasn’t terribly bright, true, but he had always been levelheaded.

“Jewels,” Denth called up ahead. “Take us to the Raymar place.”

Jewels nodded, giving instructions to Clod that Vivenna couldn’t hear. The group turned in another direction through the crowd.

“It only responds to her?” Vivenna said.

Denth shrugged. “It has basic instructions to do what Tonks and I say and I’ve got a security phrase I can use if I need more control.”

Vivenna frowned. “Security phrase?”

Denth eyed her. “This is a rather heretical discussion we’re getting into. You sure you want to continue?”

Vivenna ignored the amusement in his tone. “I still do~\textit{not}~like the idea of that thing being with us, particularly if I don’t have any way to control it.”

“All Awakening works by way of the Command, Princess,” Denth said. “You infuse something with life, then give it an order. Lifeless are valuable because you can give them Commands~\textit{after}~you create them, unlike regular Awakened objects, which you can only Command once in advance. Plus, Lifeless can remember a long list of complicated orders and are generally good about not misunderstanding them. They retain a bit of their humanity, I guess.”

Vivenna shivered. That made them seem far too sentient for her liking.

“However, that means pretty much anyone can control a Lifeless,” Denth said. “Not just the person who created them. So we give them security phrases. A couple words you can say that will let you imprint the creature with new Commands.”

“So what’s the security phrase for Clod?”

“I’ll have to ask Jewels if you can have it.”

Vivenna opened her mouth to complain, but thought better of it. Denth obviously didn’t like interfering with Jewels or her work. Vivenna would simply have to make a point of it later, once they were in a more private location. Instead, she just eyed Clod. He was dressed in simple clothing. Grey trousers and grey shirt, with a leather jerkin that had been drained of color. He carried a large blade at his waist. Not a dueling sword—a more brutal, broad-bladed weapon.

\textit{All in grey,}~Vivenna thought.~\textit{Is that because they want everyone to recognize Clod for a Lifeless?}~Despite what Denth said about Lifeless being common, many people gave the thing a wide berth.~\textit{Snakes might be common in the jungle,}~she thought,~\textit{but that doesn’t mean that people are pleased to see them.}

Jewels chatted quietly at the Lifeless, though it never responded. It simply walked, face forward, inhuman in the steady rhythm of its steps.

“Does she always~.~.~. talk to it like that?” Vivenna asked, shivering.

“Yeah,” Denth said.

“That doesn’t seem very healthy.”

Denth looked troubled, though he said nothing. A few moments later, Tonk Fah and Parlin returned. Tonk Fah, Vivenna was displeased to see, had a small monkey on his shoulder. It chittered a bit, then ran behind Tonk Fah’s neck, moving to the other shoulder.

“A new pet?” Vivenna asked. “What happened to that parrot of yours, anyway?”

Tonk Fah looked ashamed, and Denth just shook his head. “Tonks isn’t very good with pets.”

“That parrot was boring anyway,” Tonk Fah said. “Monkeys are~\textit{much}~more interesting.”

Vivenna shook her head. It wasn’t long before they arrived at the next restaurant, one far less lavish than the previous one. Jewels, Parlin, and the Lifeless took up places outside, as usual, and Vivenna and the two male mercenaries walked in.

The meetings were becoming routine. During the last couple of weeks, they’d met with at least a dozen people of varying usefulness. Some were underground leaders Denth thought might be capable of making a ruckus. Others were merchants, like Fob. All in all, Vivenna was impressed with the variety of covert ways Denth had come up with to disrupt things in T’Telir.

Most of the schemes did, however, require a display of Vivenna’s Royal Locks as a clincher. Most people instantly grasped the importance of a royal daughter being in the city, and she was left wondering just how Lemex had intended to achieve results without such convincing proof.

Denth led them to a table in the corner, and Vivenna frowned at how dirty the restaurant was. The only light came in the form of slim slatlike windows shining beams of sunlight through the ceiling, but even that was enough to show the grime. Despite her hunger, she quickly determined that she would not be eating anything at~\textit{this}~establishment. “Why do we keep switching restaurants, anyway?” she said, sitting down—but only after wiping off the stool with her handkerchief.

“Harder to spy on us that way,” Denth said. “I keep warning you, Princess. This is more dangerous than it seems. Don’t let the simple meetings over food throw you off. In any other city, we’d be meeting in lairs, gambling parlors, or alleyways. Best to keep moving.”

They settled down, and as if they hadn’t just come from their second lunch of the day, Denth and Tonk Fah ordered food. Vivenna sat quietly in her chair, preparing for the meeting. Gods Feast was something of a holy day in Hallandren—though, from what she’d seen, the people of the pagan city had no real concept of what a “holy day” should be. Instead of helping the monks in their fields or caring for the needy, the people took the evening off and splurged on meals—as if the gods wanted them to be extravagant.

And perhaps they did. From what she’d heard, the Returned were profligate beings. It made sense for their followers to spend their “holy day” being idle and gluttonous.

Their contact arrived before the food did. He walked in with two bodyguards of his own. He wore nice clothing—which meant bright clothing, in T’Telir—but his beard was long and greasy, and he appeared to be short several teeth. He pointed, and his bodyguards pulled a second table over next to Vivenna’s, then arranged three chairs by it. The man took a seat, careful to keep his distance from Denth and Tonk Fah.

“A little paranoid, aren’t we?” Denth said.

The man raised his hands. “Caution never hurt a man.”

“More food for us, then,” Tonk Fah said as the plate arrived. It was covered with bits of~.~.~. something that had been battered and fried. The monkey immediately scrambled down Tonk Fah’s arm and snatched a few pieces.

“So,” the man said, “you’re the infamous Denth.”

“I am. I assume you’re Grable?”

The man nodded.

\textit{One of the city’s less reputable thieving lords,}~Vivenna thought.~\textit{A strong ally of Vahr’s rebellion.}~They had been waiting weeks to set up this meeting.

“Good,” Denth said. “We have some interest in making certain supply carts disappear on the way to the city.” He said it so openly. Vivenna glanced about, making certain no other tables were close.

“Grable owns this restaurant, Princess,” Tonk Fah whispered. “Every second man in this room is probably a bodyguard.”

\textit{Great,}~she thought, annoyed they hadn’t told her before they entered. She glanced around again, feeling far more jumpy this time.

“Is that so?” Grable asked, bringing Vivenna’s attention back to the conversation. “You want to make things disappear? Caravans of food?”

“It’s a difficult job we’re asking for,” Denth said grimly. “These aren’t long-distance caravans. Most of them will simply be coming into the city from the outlying farms.” He nodded to Vivenna, and she pulled out a small pouch of coins. She handed them to him, and he tossed them to a nearby table.

One of the bodyguards investigated.

“For your trouble in coming today,” Denth said.

Vivenna watched the money go with a crimp in her stomach. It felt downright~\textit{wrong}~to be using royal funds to bribe men like Grable. What she had just given away wasn’t even a real bribe—it was simply “grease money,” as Denth put it.

“Now,” Denth said, “the carts we’re talking about—”

“Wait,” Grable said. “Let’s see the hair first.”

Vivenna sighed, moving to put up the shawl.

“No shawl,” Grable said. “No tricks. The men in this room are loyal.”

Vivenna shot a glance at Denth, and he nodded. So she shifted colors a couple of times. Grable watched intently, scratching at his beard.

“Nice,” he finally said. “Nice indeed. Where’d you find her?”

Denth frowned. “What?”

“A person with enough royal blood to imitate one of the princesses.”

“She’s no impostor,” Denth said as Tonk Fah continued to work on the plate of fried somethings.

“Come now,” Grable said, smiling with a wide, uneven smile. “You can tell me.”

“It’s true,” Vivenna said. “Being royal is about more than just blood. It’s about lineage and the holy calling of Austre. My children will not have the Royal Locks unless I become queen of Idris. Only potential heirs have the ability to change their hair color.”

“Superstitious nonsense,” Grable said. He leaned forward, ignoring her and focusing on Denth. “I don’t care about your caravans, Denth. I want to buy the girl from you. How much?”

Denth was silent.

“Word of her is spreading about town,” Grable said. “I see what you’re doing. You could move a lot of people, make a lot of noise, with a person who seemed to be of the royal family. I don’t know where you found her, or how you trained her so well, but I want her.”

Denth stood up slowly. “We’re leaving,” he said. Grable’s bodyguards stood up too.

Denth moved.

There were flashes—reflections of sunlight, and bodies moving too fast for Vivenna’s shocked mind to follow. Then the motion stopped. Grable remained in his chair. Denth stood poised, his dueling blade sticking through the neck of one of the bodyguards.

The bodyguard looked surprised, his hand still on his sword. Vivenna hadn’t even seen Denth draw his weapon. The other bodyguard stumbled, blood staining the front of his jerkin from where—shockingly—Denth seemed to have managed to stab him as well.

He slipped to the ground, bumping Grable’s table in his death throes.

\textit{Lord of Colors~.~.~.}~Vivenna thought.~\textit{So fast!}

“So, you~\textit{are}~as good as they say,” Grable said, still looking unconcerned. Around the room, other men had stood. Some twenty of them. Tonk Fah grabbed another handful of fried things, then nudged Vivenna. “We might want to get up,” he whispered.

Denth pulled his sword free of the bodyguard’s neck, and the man joined his friend, bleeding and dying on the floor. Denth slammed his sword into its sheath without wiping it, never breaking Grable’s gaze.

“People speak of you,” Grable said. “Say you appeared out of nowhere a decade or so back. Gathered yourself a team of the best—stole them from important men. Or important prisons. Nobody knows much about you, other than the fact that you’re fast. Some say inhumanly so.”

Denth nodded toward the doorway. Vivenna stood nervously, then let Tonk Fah pull her through the room. The guards stood with their hands on their swords, but nobody attacked.

“It’s a pity we couldn’t do business,” Grable said, sighing. “I hope you’ll think of me for future dealings.”

Denth finally turned away, joining Vivenna and Tonk Fah as they left the restaurant and moved out onto the sunny street. Parlin and Jewels hurried to catch up.

“He’s letting us go?” Vivenna asked, heart thumping.

“He just wanted to see my blade,” Denth said. He still seemed tense. “It happens sometimes.”

“Barring that, he wanted to steal himself a princess,” Tonk Fah added. “He either got to verify Denth’s skill or he got you.”

“But~.~.~. you could have killed him!” Vivenna said.

Tonk Fah snorted. “And bring down the wrath of half the thieves, assassins, and burglars in the city? No, Grable knew he wasn’t ever in any danger from us.”

Denth looked back at her. “I’m sorry for wasting your time—I thought he’d be more useful.”

She frowned, noting for the first time the careful mask that Denth kept on his emotions. She’d always thought of him as carefree, like Tonk Fah, but now she saw hints of something else. Control. Control that was, for the first time since they’d met, in danger of cracking.

“Well, no harm done,” she said.

“Except for those slobs that Denth poked,” Tonk Fah added, happily feeding another morsel to his monkey.

“We need to—”

“Princess?” a voice asked from the crowd.

Denth and Tonk Fah both spun. Once again, Denth’s sword was out before Vivenna could track. This time, however, he didn’t strike. The man behind them didn’t seem much of a threat. He wore ragged brown clothing, and had a leathery suntanned face. He had the look of a farmer.

“Oh, Princess,” the man said, hurrying forward, ignoring the blades. “It is you. I heard rumors, but~.~.~. oh, you’re here!”

Denth shot a look at Tonk Fah, and the larger mercenary reached out, putting a hand in front of the newcomer before he got too close to Vivenna. She would have thought the caution unnecessary had she just not seen Denth kill two men in an eyeblink. The danger Denth always talked about was slowly seeping into her mind. If this man had a hidden weapon and a little skill, he could kill her before she knew what was happening.

It was a chilling realization.

“Princess,” the man said, falling to his knees. “I am your servant.”

“Please,” she said. “Do not put me above others.”

“Oh,” the man said, looking up. “I’m sorry. It’s been so long since I left Idris! But, it~\textit{is}~you!”

“How did you know I was here?”

“The Idrians in T’Telir,” the man said. “They say you’ve come to take the throne back. We’ve been oppressed here for so long that I thought people were just making up stories. But it’s true! You’re here!”

Denth glanced at her, then at Grable’s restaurant, which was still close behind them. He nodded to Tonk Fah. “Grab him, search him, and we’ll talk somewhere else.”

\bigskip \hrule \bigskip

The “somewhere else” turned out to be a ragged dump of a building in a poor section of town about fifteen minutes from the restaurant.

Vivenna found the slums of T’Telir to be very interesting, on an intellectual level at least. Even here, there was color. People wore faded clothing. Bright strips of cloth hung from windows, stretched across overhangs, and even sat in puddles on the street. Colors, muted or dirty. Like a carnival that had been hit by a mudslide.

Vivenna stood outside the shack with Jewels, Parlin, and the Idrian, waiting as Denth and Tonk Fah made sure the building wasn’t hiding any unseen threats. She wrapped her arms around herself, feeling an odd sense of despair. The faded colors in the alley felt wrong. They were dead things. Like a beautiful bird that had fallen motionless to the ground, its shape intact, but the magic gone.

Ruined reds, stained yellows, broken greens. In T’Telir, even simple things—like chair legs and storage sacks—were dyed bright colors. How much must the people of the city spend on dyes and inks? If it hadn’t been for the Tears of Edgli, the vibrant flowers that grew only in the T’Telir climate, it would have been impossible. Hallandren had made an entire economy out of growing, harvesting, and producing dyes from the special flowers.

Vivenna wrinkled her nose at the smell of refuse. Scents were more vibrant to her now, too, much like colors. It wasn’t that her ability to smell was any better, the things that she smelled just seemed rich. She shivered. Even now, weeks after the infusion of Breath, she didn’t feel normal. She could~\textit{sense}~the teeming people of the city, could sense Parlin beside her, watching the nearby alleys with suspicion. She could sense Denth and Tonk Fah inside—one of them appeared to be inspecting the basement.

She could~.~.~.

She froze. She~\textit{couldn’t}~feel Jewels. She glanced to the side, but the shorter woman was there, hands on hips, muttering to herself about being left with the “kids.” Her Lifeless abomination was beside her; Vivenna hadn’t expected to be able to feel it. Why couldn’t she feel Jewels? Vivenna had a sharp moment of panic, thinking that Jewels might be some twisted Lifeless creation. Then, however, she realized that there was a simple explanation.

Jewels had no Breath. She was a Drab.

Now that Vivenna knew what to look for, it was obvious. Even without her wealth of Breath, Vivenna thought she might have been able to tell. There was less of a sparkle of life in Jewels’s eyes. She seemed more grumpy, less pleasant. She seemed to put others on edge.

Plus Jewels never noticed when Vivenna was watching her. Whatever sense made others glance about if they were watched for too long, Jewels didn’t have it. Vivenna turned away, and found herself blushing. Seeing a person without Breath~.~.~. it felt like spying on someone when they were changing. Seeing them exposed.

\textit{Poor woman,}~she thought.~\textit{I wonder how it happened.}~Had she sold it herself? Or had it been taken from her? Suddenly, Vivenna felt awkward.~\textit{Why should I have so much, when she has nothing?}~It was the worst kind of ostentation.

She felt Denth approach before he actually pushed the door open. It looked ready to fall off its hinges. “Safe,” he said. Then he eyed Vivenna. “You don’t have to be involved with this, if you don’t want to waste your time, Princess. Jewels can take you back to the house. We’ll question the man and bring you word.”

She shook her head. “No. I want to hear what he has to say.”

“I figured as much,” Denth said. “We’ll want to cancel our next appointment, though. Jewels, you—”

“I’ll do it,” Parlin said.

Denth paused, glancing at Vivenna.

“Look, I may not understand everything going on in this city,” Parlin said, “but I can deliver a simple message. I’m not an idiot.”

“Let him go,” Vivenna said. “I trust him.”

Denth shrugged. “All right. Head straight down this alley until you find the square with the broken statue of a horse man, then turn east and follow that road through its curves. That’ll take you out of the slum. The next appointment was to happen at a restaurant called the Armsman’s Way; you’ll find it in the market on the west side.”

Parlin nodded and took off. Denth waved for Vivenna and the others to enter the building. The nervous Idrian man—Thame—went first. Vivenna followed him in, and was surprised to find that the inside of the building looked quite a bit sturdier than the outside had indicated. Tonk Fah found a stool, and he put it down in the center of the room.

“Have a seat, friend,” Denth said, gesturing.

Thame nervously settled on the stool.

“Now,” Denth said, “why don’t you tell us how you found out that the princess was going to be in that particular restaurant today?”

Thame glanced from side to side. “I just happened to be walking in the area and I—”

Tonk Fah cracked his knuckles. Vivenna glanced at him, suddenly noticing that Tonk Fah seemed more~.~.~. dangerous. The idle, overweight man who liked to nap had vanished. In his place was a thug with sleeves rolled up, showing off muscles that bulged impressively.

Thame was sweating. To the side, Clod the Lifeless stepped into the room, his inhuman eyes falling into shadow, his face looking like something molded in wax. A simulacrum of a human.

“I~.~.~. run jobs for one of the bosses in the city,” Thame said. “Little things. Nothing big. When you’re one of us, you take the jobs you can get.”

“One of us?” Denth asked, resting his hand on the pommel of his sword.

“Idrian.”

“I’ve seen Idrians in good positions in the city, friend,” Denth said. “Merchants. Moneylenders.”

“The lucky ones, sir,” Thame said, gulping. “They have their own money. People will work with anyone who has money. If you’re just an ordinary man, things are different. People look at your clothing, listen to your accent, and they find others to do their work. They say we’re not trustworthy. Or that we’re boring. Or that we steal.”

“And do you?” Vivenna found herself asking.

Thame looked at her, then glanced down at the building’s dirt floor. “Sometimes,” he said. “But not at first. I only do it now, when my boss asks me to.”

“That still doesn’t answer how you knew where to find us, friend,” Denth said quietly. His pointed use of the word “friend,” when contrasted with Tonk Fah on one side and the Lifeless on the other, made Vivenna shiver.

“My boss talks too much,” Thame said. “He knew what was happening at that restaurant—he sold the information to a couple of people. I heard for free.”

Denth glanced at Tonk Fah.

“Everyone knows she’s in the city,” Thame said quickly. “We’ve all heard the rumors. It’s no coincidence. Things are bad for us. Worse than they’ve ever been. The princess came to help, right?”

“Friend,” Denth said. “I think it’s best that you forget this entire meeting. I realize that there will be the temptation to sell information. But I promise you, we can find out if you do that. And we can—”

“Denth, that’s enough,” Vivenna said. “Stop scaring the man.”

The mercenary glanced at her, causing Thame to jump.

“Oh, for the Colors’ sake,” she said walking forward, crouching beside Thame’s stool. “No harm will come to you, Thame. You have done well in seeking me out, and I trust you to keep news of our meeting quiet. But, tell me, if things are so bad in T’Telir, why not return to Idris?”

“Travel costs money, Your Highness,” he said. “I can’t afford it—most of us can’t.”

“Are there many of you here?” Vivenna asked.

“Yes, Your Highness.”

Vivenna nodded. “I want to meet with the others.”

“Princess—” Denth said, but she silenced him with a glance.

“I can gather some together,” Thame said, nodding eagerly. “I promise. I’m known to a lot of the Idrians.”

“Good,” Vivenna said. “Because I~\textit{have}~come to help. How shall we contact you?”

“Ask around for Rira,” he said. “That’s my boss.”

Vivenna rose and then gestured toward the doorway. Thame fled without further prompting. Jewels, who stood guarding the doorway, reluctantly stepped aside and let the man scuttle away.

The room was silent for a moment.

“Jewels,” Denth said. “Follow him.”

She nodded and was gone.

Vivenna glanced back at the two mercenaries, expecting to find them angry at her.

“Aw, did you have to let him go so fast?” Tonk Fah said, sitting down on the floor, looking morose. Whatever he’d done to look dangerous was gone, evaporating faster than water on metal in the sun.

“Now you’ve done it,” Denth said. “He’ll be sullen for the rest of the day.”

“I~\textit{never}~get to be the bad guy anymore,” Tonk Fah said, falling back and staring up at the ceiling. His monkey wandered over and sat atop his ample stomach.

“You’ll get over it,” Vivenna said, rolling her eyes. “Why were you so hard on him, anyway?”

Denth shrugged. “You know what I like least about being a mercenary?”

“I suspect that you’re going to tell me,” Vivenna said, folding her arms.

“People are always trying to fool you,” he said, sitting down on the floor beside Tonk Fah. “They all think that because you’re hired muscle, you’re an idiot.”

He paused, as if expecting Tonk Fah to give his usual counterpoint. Instead, however, the bulky mercenary just continued to stare at the ceiling. “Arsteel~\textit{always}~got to be the mean one,” he said.

Denth sighed, giving Vivenna a “This is your fault” look. “Anyway,” he continued. “I couldn’t be sure that our friend there wasn’t a plant arranged by Grable. He could have pretended to be a loyal subject, gotten inside our defenses, then knifed you in the back. Best to be safe.”

She sat down on the stool, and was tempted to say that he was overreacting, but~.~.~. well, she had just seen him kill two men in her defense.~\textit{I’m paying them,}~she thought.~\textit{I should probably just let them do their job.}~“Tonk Fah,” she said. “You can be the mean one next time.”

He looked up. “You promise?”

“Yes,” she said.

“Can I yell at the person we are interrogating?”

“Sure,” she said.

“Can I growl at him?” he asked.

“I guess,” she said.

“Can I break his fingers?”

She frowned. “No!”

“Not even the unimportant ones?” Tonk Fah asked. “I mean, people have~\textit{five}~after all. The little ones don’t even do that much.”

Vivenna paused, then Tonk Fah and Denth started laughing.

“Oh, honestly,” she said, turning away. “I can never tell when you shift from being serious to being ridiculous.”

“That’s what makes it so funny,” Tonk Fah said, still chuckling.

“Are we leaving, then?” Vivenna said, rising.

“Nah,” Denth said. “Let’s wait a bit. I’m still not sure that Grable isn’t looking for us. Best to lay low for a few hours.”

She frowned, glancing at Denth. Tonk Fah, amazingly, was already snoring softly.

“I thought you said that Grable would let us go,” she said. “That he was just testing us—that he wanted to see how good you were.”

“It’s likely,” Denth said. “But I’ve been known to be wrong. He might have let us go because he was worried about my sword being so close to him. He could be having second thoughts. We’ll give it a few hours, then head back and ask my watchers if anyone has been poking around the house.”

“Watchers?” Vivenna asked. “You have people watching our house?”

“Of course,” Denth said. “Kids work cheap in the city. Worth the coin, even when you’re not protecting a princess from a rival kingdom.”

She folded her arms, standing. She didn’t feel like sitting, so she began to pace.

“I wouldn’t worry too much about Grable,” Denth said, eyes closed as he sat back, leaning against the wall. “This is just a precaution.”

She shook her head. “It makes sense that he’d want revenge, Denth,” she said. “You killed two of his men.”

“Men can be cheap in this city too, Princess.”

“You say he was testing you,” Vivenna said. “But what would be the point of that? Provoking you to action just to let you go?”

“To see how much of a threat I was,” Denth said, shrugging, eyes still closed. “Or, more likely, to see if I was worth the pay I usually demand. Again, I wouldn’t worry so much.”

She sighed, then wandered over to the window so she could watch the street.

“You should probably stay away from the window,” Denth said. “Just to be safe.”

\textit{First he tells me not to worry, then he tells me not to let myself be seen,}~she thought with frustration, walking toward the back of the room, moving toward the door down to the cellar.

“I wouldn’t do that, either,” Denth noted. “Stairs are broken in a few places. Not much to see, anyway. Dirt floor. Dirt walls. Dirt ceiling.”

She sighed again, turning away from the door.

“What is with you, anyway?” he asked, still not opening his eyes. “You’re not usually this nervous.”

“I don’t know,” she said. “Being locked in like this makes me anxious.”

“I thought princesses were taught to be patient,” Denth noted.

\textit{He’s right,}~she realized.~\textit{That sounded like something Siri would say. What}~is~\textit{wrong with me lately?}~She forced herself to sit down on the stool, folding her hands in her lap, reasserting control of her hair, which had rebelliously started to lighten to a brown. “Please,” she said, forcing herself to sound patient, “tell me of this place. Why did you select this building?”

Denth cracked an eyelid. “We rent it,” he finally said. “It’s nice to have safe houses around the city. Since we don’t use them very often, we find the cheapest ones we can.”

\textit{I noticed,}~Vivenna thought, but fell silent, recognizing how stilted her attempt at conversation had sounded. She sat quietly, looking down at her hands, trying to figure out just what had set her on edge.

It was more than the fight. The truth was, she was worried about how long things in T’Telir were taking. Her father would have received her letter two weeks before and would know that\textit{two}~of his daughters were in Hallandren. She could only hope that the logic of her letter, mixed with her threats, would keep him from doing anything foolish.

She was glad Denth had made her abandon Lemex’s house. If her father did send agents to retrieve her, they would naturally try to find Lemex first—just as she had. However, a cowardly part of her wished that Denth hadn’t shown such foresight. If they were still living in Lemex’s home, she might have been discovered already. And be on her way back to Idris.

She acted so determined. Indeed, sometimes she~\textit{felt}~quite determined. Those were the times when she thought about Siri or her kingdom’s needs. However, those times—the royal times—were actually rather rare. The rest of the time, she wondered.

What was she doing? She didn’t know about subterfuge or warfare. Denth was really behind everything she was “doing” to help Idris. What she had suspected on that first day had proved true. Her preparation and study amounted to little. She didn’t know how to go about saving Siri. She didn’t know what to do about the Breath she held within her. She didn’t even know, really, if she wanted to stay in this insane, overcrowded, over\textit{colored}~city.

In short, she was useless. And that was the one thing, above all else, that her training had never prepared her to deal with.

“You really want to meet with the Idrians?” Denth asked. Vivenna looked up. Outside, it was growing darker as evening approached.

\textit{Do I?}~she thought.~\textit{If my father has agents in the city, they might be there. But, if there’s something I can do for those people~.~.~.}

“I’d like to,” she said.

He fell silent.

“You don’t like it,” she said.

He shook his head. “It will be hard to arrange, hard to keep quiet, and will make you hard to protect. These meetings we’ve been having—they’ve all been in controlled areas. If you meet with the common folk, that won’t be possible.”

She nodded quietly. “I want to do it anyway. I have to do something, Denth. Something useful. Being paraded before these contacts of yours is helping. But I need to do more. If war is coming, we need to prepare these people. Help them, somehow.”

She looked up, staring out toward the windows. Clod the Lifeless stood in the corner where Jewels had left him. Vivenna shivered, looking away. “I want to help my sister,” she said. “And I want to be useful to my people. But I can’t help feeling that I’m not doing much for Idris by staying in the city.”

“Better than leaving,” Denth said.

“Why?

“Because if you left, there wouldn’t be anyone to pay me.”

She rolled her eyes.

“I wasn’t joking,” Denth noted. “I really do like getting paid. However, there are better reasons to stay.”

“Like what?” she asked.

He shrugged. “Depends, I guess. Look, Princess, I’m not the type to give brilliant advice or deep counsel. I’m a mercenary. You pay me, you point me, and I go stab things. But I figure that if you think about it, you’ll find that running back to Idris is about the~\textit{least}~useful thing you could do. You won’t be able to do anything there other than sit about and knit doilies. Your father has other heirs. Here, you might be largely ineffective—but there you’re completely redundant.”

He fell silent, stretching, leaning back a little more.~\textit{Tough man to have a conversation with, sometimes,}~Vivenna thought to herself, shaking her head. Still, she found his words comforting. She smiled, turning.

And found Clod standing right beside her stool.

She yelped, half-scrambling, half-falling backward. Denth was on his feet in a heartbeat, sword drawn, and Tonk Fah wasn’t far behind.

Vivenna stumbled to her feet, her skirts getting in the way, and placed a hand against her chest, as if to still her heartbeat. The Lifeless stood, watching her.

“He does that sometimes,” Denth said, chuckling, though it sounded false to Vivenna. “Just walks up to people.”

“Like he was curious about them,” Tonk Fah said.

“They~\textit{can’t}~be curious,” Denth said. “No emotion at all. Clod. Go back to your corner.”

The Lifeless turned and began to walk.

“No,” Vivenna said, shivering. “Put it in the basement.”

“But, the stairs—” Denth said.

“\textit{Now!}” Vivenna snapped, hair tingeing red at the tips.

Denth sighed. “Clod, to the cellar.”

The Lifeless turned and walked to the door at the back. As he went down the steps, Vivenna heard one crack slightly, but the creature made it safely, judging by the sound of his footsteps. She sat back down, trying to calm her breathing.

“Sorry about that,” Denth said.

“I can’t feel him,” Vivenna said. “It’s unnerving. I forget that he’s there, and don’t notice when he approaches.”

Denth nodded. “I know.”

“Jewels, too,” she said, glancing at him. “She is a Drab.”

“Yeah,” Denth said, settling back down. “Has been since she was a child. Her parents sold her Breath to one of the gods.”

“They each need a Breath a week to survive,” Tonk Fah added.

“How horrible,” Vivenna said.~\textit{I really need to show her more kindness.}

“It’s really not so bad,” Denth said. “I’ve been without Breath myself.”

“You have?”

He nodded. “Everyone goes through times when they’re short of coin. The nice thing about Breath is that you can always buy one off someone else.”

“Somebody is always selling,” Tonk Fah said.

Vivenna shook her head, shivering. “But you have to live without it for a time. Have no soul.”

Denth laughed—and this time it was definitely genuine. “Oh, that’s just superstition, Princess. Lacking Breath doesn’t change you that much.”

“It makes you less kind,” Vivenna said. “More irritable. Like~.~.~.”

“Jewels?” Denth asked, amused. “Nah, she’d be like that anyway. I’m sure of it. Either way, when I’ve sold my Breath, I didn’t feel much different. You really have to pay attention to even notice it’s missing.”

Vivenna turned away. She didn’t expect him to understand. It was easy to call her beliefs superstition, but she could just as easily turn the words back on Denth. People saw what they wanted to see. If he believed he felt the same without Breath, that was just an easy way to rationalize the selling of it—and then purchase of another Breath from an innocent person. Besides, why even bother buying one back if it didn’t matter?

The conversation died off until Jewels returned. She walked in and, once again, Vivenna barely noticed her.~\textit{I’m starting to rely on that life sense far too much,}~she thought with annoyance, standing as Jewels nodded to Denth.

“He is who he says he is,” Jewels said. “I asked around, got three confirmations from people I kind of trust.”

“All right, then,” Denth said, stretching and climbing to his feet. He kicked Tonk Fah awake. “Let’s~\textit{carefully}~head back to the house.”

