\section{Chapter Eight}

Siri groaned, rolling over. Her back hurt, her arms hurt, and her head hurt. In fact, she was so uncomfortable that she couldn’t stay asleep, despite her fatigue. She sat up, holding her head.

She’d spent the night on the floor of the God King’s bedchamber—sleeping, kind of. Sunlight poured into the room, reflecting off of the marble where the floor wasn’t covered with rugs.

\textit{Black rugs,}~she thought, sitting in the middle of the rumpled blue dress, which she’d used as both blanket and pillow.~\textit{Black rugs on a black floor with black furniture. These Hallandren certainly know how to run with a motif.}

The God King wasn’t in the room. Siri glanced toward the oversized black leather chair where he’d spent much of the night. She hadn’t noticed him leave.

She yawned, then rose, pulling her shift out of the wadded mound of dress and putting it on over her head. She pulled her hair out, flipping it behind her. Keeping it so long was going to take some getting used to. It fell down against her back, a contented blond in color.

She’d somehow survived the night untouched.

She walked on bare feet over to the leather chair, running her fingers along its smooth surface. She’d been less than respectful. She’d dozed off. She’d curled up and pulled her dress close. She’d even glanced over at the chair a few times. Not because of defiance or a disobedient heart; she’d simply been too drowsy to remember that she wasn’t supposed to look at the God King. And he hadn’t ordered her executed. Bluefingers had made her worry that the God King was volatile and quick to anger, yet if that was the case, then he had held his temper with her. What else was he going to do? The Hallandren had waited for decades to get a royal princess to marry into their line of God Kings. She smiled.~\textit{I do have some power.}~He couldn’t kill her—not until he had what he wanted.

It wasn’t much, but it did give her a bit more confidence. She walked around the chair, noting its size. Everything in the room was built to be just a little too large, skewing her perspective, making her feel shorter than she was. She rested her hand on the arm of the chair, and found herself wondering why he hadn’t decided to take her. What was wrong with her? Wasn’t she desirable?

\textit{Foolish girl,}~she told herself, shaking her head and walking over to the still-undisturbed bed.\textit{You spent most of the trip here worrying about what would happen on your wedding night, and then when nothing happens, you complain about that too?}

She knew she wasn’t free. He would take her eventually—that was the point of the entire arrangement. But it hadn’t happened last night. She smiled, yawning, then she climbed up into the bed and curled up under the covers, drifting off.

\bigskip \hrule \bigskip

The next time she woke was a great deal more pleasant than the previous one had been. Siri stretched, and then noticed something.

Her dress, which she’d left sitting in a heap on the floor, was gone. Also, the fire in the hearth had been rebuilt—though why that was necessary was beyond her. The day was warm, and she’d kicked off the covers as she’d slept.

\textit{I’m supposed to burn the sheets,}~she remembered.~\textit{That’s the reason they stoked the fire.}

She sat up in her shift, alone in the black room. The servants and priests wouldn’t know that she’d spent the entire night on the floor unless the God King had told someone. How likely would it be for a man of his power to speak with his priests about intimate details?

Slowly, Siri climbed out of bed and pulled the sheets free. She wadded them up, walked over, and threw them into the large hearth. Then she watched the flames. She still didn’t know why the God King had left her alone. Until she knew, it was surely better to just let everyone assume that the marriage had been consummated.

After the sheets were done burning, Siri scanned the room, looking for something to wear. She found nothing. Sighing, she walked to the door, clothed only in her shift. She pulled it open, and jumped slightly. Two dozen serving women of varying ages knelt outside.

\textit{God of Colors!}~Siri thought.~\textit{How long have they been kneeling out here?}~Suddenly, she didn’t feel quite so indignant at being forced to wait upon the God King’s whims.

The women stood up, heads bowed, and walked into the room. Siri backed up, cocking her head when she noticed that several of the women carried in large chests.~\textit{They’re dressed in different colors from yesterday,}~Siri thought. The cut was the same—divided skirts, like flowing trousers, topped with sleeveless blouses and small caps, their hair coming out the back. Instead of the blue and silver, the outfits were now yellow and copper.

The women opened the trunks, removing various layers of clothing. All were of bright colors, and each was of a different cut. The women spread them out on the floor before Siri, then settled back on their knees, waiting.

Siri hesitated. She’d grown up the daughter of a king, so she’d never lacked. Yet, life in Idris was austere. She’d owned five dresses, which had nearly been an extravagant number. One had been white, and the other four had been the same wan blue.

Being confronted by so many colors and options felt overwhelming. She tried to imagine how each would look on her. Many of them were dangerously low-cut, even more so than the shirts the serving women wore—and those were already scandalous by Idrian standards.

Finally, hesitantly, Siri pointed at one outfit. It was a dress in two pieces, red skirt and matching blouse. As Siri pointed, the serving women stood, some putting away the unchosen outfits, others walking over to carefully remove Siri’s shift.

In a few minutes, Siri was dressed. She was embarrassed to find that—while the clothing fit her perfectly—the blouse was designed to reveal her midriff. Still, it wasn’t as low-cut as the others, and the skirt went all the way down to her calves. The silky red material was far lighter than the thick wools and linen she was accustomed to wearing. The skirt flared and ruffled when she turned, and Siri couldn’t be completely certain it wasn’t sheer. Standing in it, she almost felt as naked as she’d been during the night.

\textit{That appears to be a recurring theme for me here,}~she thought wryly as the serving women backed away. Others approached with a stool, and she sat, waiting as the women cleaned her face and arms with a pleasantly warm cloth. When that was done, they reapplied her makeup, did her hair, then sprayed her with a few puffs of perfume.

When she opened her eyes—perfume misting down around her—Bluefingers was standing in the room. “Ah, excellent,” he said, servant boy standing obediently behind with ink, quill, and paper. “You’re up already.”

\textit{Already?}~Siri thought.~\textit{It has to be well past noon!}

Bluefingers looked her over, nodded to himself, then glanced at the bed, obviously checking to see that the linens had been destroyed. “Well,” he said. “I trust that your servants will see to your needs, Vessel.” With that, he began to walk away with the anxious tread of a man who felt he had far too much to do.

“Wait!” Siri said, standing, jostling several of her serving women.

Bluefingers hesitated. “Vessel?”

Siri floundered, uncertain how to express what she was feeling. “Do you know~.~.~. what I’m supposed to do?”

“Do, Vessel?” the scribe asked. “You mean, in regards to~.~.~.” He glanced at the bed.

Siri flushed. “No, not that. I mean with my time. What are my duties? What is expected of me?”

“To provide an heir.”

“Beyond that.”

Bluefingers frowned. “I~.~.~. well, to be honest, Vessel, I really don’t know. I must say, your arrival has certainly caused a level of disruption in the Court of Gods.”

\textit{In my life, too,}~she thought, flushing slightly, hair turning red.

“Not that you’re to blame, of course,” Bluefingers said quickly. “But then~.~.~. well, I certainly wish I’d had more forewarning.”

“More forewarning?” Siri asked. “This marriage was arranged by treaty over twenty years ago!”

“Yes, well, but nobody thought~.~.~.” He trailed off. “Ahem. Well, either way, we shall do our best to accommodate you here in the king’s palace.”

\textit{What was that?}~Siri thought.~\textit{Nobody thought~.~.~. that the marriage would really happen? Why not? Did they assume that Idris wouldn’t keep its part of the bargain?}

Regardless, he still hadn’t answered her question. “Yes, but what am I supposed to~\textit{do}?” she said, sitting down on the stool again. “Am I to sit here in the palace and stare at the fire all day?”

Bluefingers chuckled. “Oh, Colors no! My lady, this is the Court of Gods! You’ll find plenty to occupy you. Each day, performers are allowed to enter the court and display their talents for their deities. You may have any of these brought to you for a private perfor mance.”

“Ah,” Siri said. “Can I, maybe, go horse back riding?”

Bluefingers rubbed his chin. “I suppose we could bring some horses into the court for you. Of course, we’d have to wait until the Wedding Jubilation is over.”

“Wedding Jubilation?” she asked.

“You~.~.~. don’t know, then? Were you not prepared for any of this?”

Siri flushed.

“No offense intended, Vessel,” Bluefingers said. “The Wedding Jubilation is a weeklong period in which we celebrate the God King’s marriage. During that time, you are not to leave this palace. At the end of it, you will officially be presented to the Court of Gods.”

“Oh,” she said. “And after that, I can go out of the city?”

“Out of the city!” Bluefingers said. “Vessel, you can’t leave the Court of Gods!”

\textit{“What?”}

“You may not be a god yourself,” Bluefingers continued. “But you’re the wife of the God King. It would be far too dangerous to let you out. But do not fret—anything and everything you might request can be provided for you.”

\textit{Except freedom,}~she thought, feeling a bit sick.

“I assure you, once the Wedding Jubilation is over, you will find little to complain about. Everything you could want is here: every type of indulgence, every luxury, every diversion.”

Siri nodded numbly, still feeling trapped.

“Also,” Bluefingers said, holding up an ink-stained finger. “If you wish, the Court Assembly meets to provide decisions to the people. Full assembly meets once a week, though daily there are smaller judgments to be made. You aren’t to sit on the assembly itself, of course, but you will certainly be allowed to attend, once the Jubilation is over. If none of this suits you, you may request an artist of the God King’s priesthood to attend you. His priests include devout and accomplished artists from all genres: music, painting, dance, poetry, sculpture, puppetry, play perfor mance, sandpainting, or any of the lesser genres.”

Siri blinked.~\textit{God of Colors!}~she thought.~\textit{Even being idle is daunting here.}~“But there isn’t any of this that I’m~\textit{required}~to attend?”

“No, I shouldn’t think so,” Bluefingers said. “Vessel, you look displeased.”

“I~.~.~.” How could she explain? Her entire life, she’d been expected to be something—and for most of her life she’d intentionally avoided being it. Now that was gone from her. She couldn’t disobey lest she get herself killed and get Idris into a war. For once, she was willing to serve, to try and be obedient. But, ironically, there didn’t seem to be anything for her to do. Except, of course, bear a child.

“Very well,” she said with a sigh. “Where are my rooms? I’ll go there and situate myself.”

“Your rooms, Vessel?”

“Yes. I assume I’m not to reside in this chamber itself.”

“No,” Bluefingers said, chuckling. “The conception room? Of course not.”

“Then where?” Siri asked.

“Vessel,” Bluefingers said. “In a way, this entire palace is yours. I don’t see why you’d need specific rooms. Ask to eat, and your servants will set up a table. If you wish to rest, they will bring you a couch or a chair. Seek entertainment, and they will fetch performers for you.”

Suddenly, the strange actions of her servants—simply bringing her an array of colors to choose from, then doing her makeup and hair right there—made more sense. “I see,” she said, almost to herself. “And the soldiers I brought with me? Did they do as I commanded?”

“Yes, Vessel,” Bluefingers said. “They left this morning. It was a wise decision; they are not dedicated servants of the Tones, and would not have been allowed to remain here in the court. They could do you no further ser vice.”

Siri nodded.

“Vessel, if I might be excused~.~.~.~?” Bluefingers asked.

Siri nodded distractedly, and Bluefingers bustled away, leaving her to think about how terribly alone she was.~\textit{Can’t focus on that,}~she thought. Instead, she turned to one of her serving women—a younger one, about Siri’s own age. “Well, that really doesn’t tell me what to spend my time on, does it?”

The servant blushed quietly, bowing her head.

“I mean, there seems to be a lot to do, if I want,” Siri said. “Maybe too much.”

The girl bowed again.

\textit{That’s going to get very annoying very quickly,}~Siri thought, gritting her teeth. Part of her wanted to do something shocking to get a reaction out of the servant, but she knew she was just being foolish. In fact, it seemed that many of her natural impulses and reactions wouldn’t work here in Hallandren. So, to keep herself from doing something silly, Siri stood up, determined to examine her new home. She left the overly black room, poking her head out into the hallway. She turned back to her servants, who stood obediently in a line behind her.

“Is there any place I’m forbidden to go?” she asked.

The one she was addressing shook her head.

\textit{Fine, then,}~she thought.~\textit{I’d better not end up stumbling upon the God King in the bath.}She crossed the hallway, opened the door, then stepped into the yellow room she’d been in the day before. The chair and bench she’d used had been removed, replaced by a group of yellow couches. Siri raised an eyebrow, then walked through into the tub room beyond.

The tub was gone. She started. The room was the one she remembered, with the same red colorings. Yet, the sloped tile platforms with their inset tubs were gone. The entire contraption must have been portable, brought in for her bath, then removed.

\textit{They really}~can~\textit{transform any room,}~she thought with amazement.~\textit{They must have chambers full of furniture, tubs, and drapings, each of a different color, waiting upon the whims of their god.}

Curious, she left the tubless room and moved in a random direction. Each room appeared to have four doors, one on each wall. Some rooms were larger than others. Some had windows to the outside, while others were in the middle of the palace. Each was a different color, yet it was still difficult to tell the difference between them. Endless rooms, pristine with their dec orations following a single color’s theme. Soon, she was hopelessly lost—but it didn’t seem to matter. Every room was, in a way, the same as any other.

She turned to her servants. “I would like breakfast.”

It happened far faster than Siri would have thought possible. Several of the women ducked out and returned with a stuffed green chair to match her current room. Siri sat down, waiting as a table, chairs, and finally food were produced as if out of nowhere. In less than fifteen minutes, she had a hot meal waiting for her.

Hesitantly, she picked up a fork and tried a bite. It wasn’t until that moment that she realized how hungry she was. The meal was composed primarily of a group of sausages mixed with vegetables. The flavors were far stronger than she was accustomed to. However, the more she ate the spicy Hallandren food, the more she found herself liking it.

Hungry or not, it was strange to eat in silence. Siri was accustomed to either eating in the kitchens with the servants or at the table with her father, his generals, and whatever local people or monks he had invited to his home that evening. It was never a silent affair, yet here in Hallandren—land of colors, sounds, and ostentation—she found herself eating alone, quietly, in a room that felt dull despite its bright decorations.

Her servants watched. None of them spoke to her. Their silence was supposed to be respectful, she knew, but Siri just found it intimidating. She tried several times to draw them into conversation, but she managed to get only terse replies.

She chewed on a spiced caper.~\textit{Is this what my life is to be from now on?}~she thought.~\textit{A night spent feeling half-used, half-ignored by my husband, then days spent surrounded by people, yet somehow still alone?}

She shivered, her appetite waning. She set down the fork, and her food slowly grew cold on the table before her. She stared at it, a part of her wishing she’d simply remained in the comfortable, oversized black bed.

