% \section{Chapter Seven}
\chapter{}

The door shut behind her.

A large fire growled in a hearth to her left, bringing a shifting orange light to the large room. The black walls seemed to draw in and absorb the illumination, making deep shadows at the edges of the room.

Siri stood quietly in her ornate velvet dress, heart thumping, brow sweating. To her right, she could make out a massive bed, with sheets and covers of black to match the rest of the room. The bed appeared unoccupied. Siri peered into the darkness, eyes adjusting.

The fire crackled, throwing a flicker of light across a large, thronelike chair sitting beside the bed. It was occupied by a figure wearing black, bathed in darkness. He watched her, eyes twinkling, unblinking in the firelight.

Siri gasped, casting her eyes downward, her heartbeat surging as she remembered Bluefingers’s warnings.~\textit{Vivenna should be here instead of me,}~Siri thought desperately.~\textit{I can’t deal with this! Father was wrong to send me!}

She squeezed her eyes shut, her breathing coming more quickly. She worked shaking fingers and pulled nervously at the strings on the side of her dress. Her hands were slick with sweat. Was she taking too long to undress? Would he be angered? Would she be killed before even the first night was out?

Would she, perhaps, prefer that?

\textit{No,}~she thought with determination.~\textit{No. I need to do this. For Idris. For the fields and the children who took flowers from me. For my father and Mab and everyone else in the palace.}

She finally got the strings undone, and the gown fell away with surprising ease—she could now see that it had been constructed with that goal in mind. She dropped the dress to the floor, then paused, looking at her undershift. The white fabric was throwing out a spectrum of colors, like light bent by a prism. She regarded this with shock, wondering what was causing the strange effect.

It didn’t matter. She was too nervous to think about that. Gritting her teeth, she forced herself to pull off her undershift, leaving her naked. She quickly knelt on the cold stone floor, curling up, heart thudding in her ears as she bowed with her forehead touching the floor.

The room fell silent save for the crackling hearth. The fire wasn’t necessary in the Hallandren warmth, but she was glad for it, unclothed as she was.

She waited, hair pure white, arrogance and stubbornness discarded, naked in more than one way. This was where she ended up—this was where all her “inde pendent” sense of freedom came to an end. No matter what she claimed or how she felt, in the end, she had to bow to authority. Just like anyone else.

She gritted her teeth, imagining the God King sitting there, watching her be subservient and naked before him. She hadn’t seen much of him, other than to notice his size—he was a good foot taller than most other men she’d seen, and was wider of shoulders and more powerful of build as well. More significant than other, lesser men.

He was Returned.

In and of itself, being Returned wasn’t a sin. After all, Returned came in Idris, too. The Hallandren people, however, kept the Returned alive, feeding them on the souls of peasants, tearing away the Breath of hundreds of people each year.~.~.~.

\textit{Don’t think of that,}~Siri told herself forcefully. Yet as she tried to clear her thoughts, the God King’s eyes returned to her memory. Those black eyes, which had seemed to glow in the firelight. She could feel them on her still, watching her, as cold as the stones upon which she knelt.

The fire crackled. Bluefingers had said that the king would knock for her. What if she missed it? She didn’t dare glance upward. She’d already met his gaze once, if by accident. She couldn’t risk upsetting him further. She just continued to kneel in place, elbows on the ground, back beginning to ache.

\textit{Why doesn’t he do something?}

Was he displeased with her? Was she not as pretty as he’d desired, or was he angered that she’d met his eyes and then taken too long to undress? It would be particularly ironic if she offended him when trying so hard not to be her usual flippant self. Or was something else wrong? He had been promised the eldest daughter of the Idrian king, but had instead received Siri. Would he know the difference? Would he even care?

The minutes passed, the room growing darker as the fire consumed its logs.

\textit{He’s toying with me}, Siri thought.~\textit{Forcing me to wait on his whims.}~Making her kneel in such an uncomfortable position was probably a message—one that showed who was in power. He would take her when~\textit{he}~willed it, and not before.

Siri gritted her teeth as the time passed. How long had she been kneeling? An hour, maybe longer. And still, there wasn’t a hint of sound—no knock, no cough, not even a shuffle from the God King. Perhaps it was a test to see how long she would remain as she was. Perhaps she was just reading too much into things. Either way, she forced herself to remain in place, shifting only when she absolutely had to.

Vivenna had the training. Vivenna had the poise and the refinement. But Siri, she had the stubbornness. One only had to look back at her history of repeatedly ignoring lessons and duties to appreciate that. With time, she’d even broken down her father. He’d started letting her do as she pleased, if only to save his own sanity.

And so she continued to wait—naked in the light of the coals—as the night wore on.

\orn

Fireworks sprayed sparks upward in a fountain of light. Some fell close to where Lightsong was sitting, and these blazed with an extra, frenzied light until they died away.

He reclined on a couch in the open air, watching the display. Servants waited around him, complete with parasols, a portable bar, steaming and chilled towels to rub his face and hands should he feel the need, and a host of other luxuries that—to Lightsong—were simply commonplace.

He watched the fireworks with mild interest. The firemasters stood in a nervous cluster near his position. Beside them were a troop of minstrels that Lightsong had called for, but hadn’t yet asked to perform. While there were always entertainers in the Court of Gods for the Returned to enjoy, this night—the wedding night of their God King—was even more extravagant.

Susebron wasn’t in attendance himself, of course. Such festivities were beneath him. Lightsong glanced to the side, where the king’s palace rose soberly above the court. Eventually, Lightsong just shook his head and turned his attention back to the courtyard. The palaces of the gods formed a ring, and each building had a patio below and a balcony above, both facing the central area. Lightsong sat a short distance from his patio, out amidst the lush grass of the expansive courtyard.

Another firefountain sprayed into the air, throwing shadows across the courtyard. Lightsong sighed, accepting another fruit drink from a servant. The night was cool and pleasant, fit for a god. Or gods. Lightsong could see others set up in front of their palaces. Different groups of performers cluttered the sides of the courtyard, waiting for their chance to please one of the Returned.

The fountain ran low, and the firemasters looked toward him, smiling hopefully in the torchlight. Lightsong nodded with his best benevolent expression. “More fireworks,” he said. “You have pleased me.” This caused the three men to whisper in excitement and wave for their assistants.

As they set up, a familiar figure wandered into Lightsong’s ring of torches. Llarimar wore his priestly robes, as always. Even when he was out in the city—which was where he should have been this night—he represented Lightsong and his priesthood.

“Scoot?” Lightsong asked, sitting up.

“Your Grace,” Llarimar said, bowing. “Are you enjoying the festivities?”

“Certainly. You might say I’m positively in\textit{fested}. But what are you doing here in the court? You should be out with your family.”

“I just wanted to make certain everything was to your liking.”

Lightsong rubbed his forehead. “You’re giving me a headache, Scoot.”

“You can’t get headaches, Your Grace.”

“So you’re fond of telling me,” Lightsong said. “I assume the revelry outside the Holy Prison is nearly as amazing as what we have here inside?”

Llarimar frowned at Lightsong’s dismissive reference to the divine compound. “The party in the city is fantastic, Your Grace. T’Telir hasn’t seen a festival this grand in decades.”

“Then I repeat that you should be out enjoying it.”

“I just—”

“Scoot,” Lightsong said, giving the man a pointed look, “if there’s~\textit{one}~thing you can trust me to do competently on my own, it’s enjoy myself. I will—I promise in all solemnity—have a ravishingly good time drinking to excess and watching these nice men light things on fire. Now go be with your family.”

Llarimar paused, then stood, bowed, and withdrew.

\textit{That man,}~Lightsong thought, sipping his fruity drink,~\textit{takes his work far too seriously.}

The concept amused Lightsong, and he leaned back, enjoying the fireworks. However, he was soon distracted by the approach of someone else. Or, rather, one very important someone else leading a group of far less important someone elses. Lightsong sipped his drink again.

The newcomer was beautiful. She was a goddess, after all. Glossy black hair, pale skin, lushly curvaceous body. She wore far less clothing than Lightsong did, but that was typical of the court’s goddesses. Her thin gown of green and silver silk was split on both sides, showing hips and thighs, and the neckline was draped so low that very little was left to imagination.

Blushweaver the Beautiful, goddess of honesty.

\textit{This should be interesting,}~Lightsong thought, smiling to himself.

She was trailed by about thirty servants, not to mention her high priestess and six lesser priests. The firemasters grew excited, realizing that they now had not one, but two divine observers. Their apprentices scurried about in a flurry of motion, setting up another series of firefountains. A group of Blushweaver’s servants rushed forward, carrying an ornate couch, which they set on the grass beside Lightsong.

Blushweaver lay down with customary lithe grace, crossing perfect legs and resting on her side in a seductive yet ladylike pose. The orientation left her able to watch the fireworks should she wish, but her attention was obviously focused on Lightsong.

“My dear Lightsong,” she said as a servant approached with a bunch of grapes. “Aren’t you even going to greet me?”

\textit{Here we go,}~Lightsong thought. “My dear Blushweaver,” he said, setting aside his cup and lacing his fingers before him. “Why would I go and do something rude like that?”

“Rude?” she asked, amused.

“Of course. You obviously make quite a determined effort to draw attention to yourself—the details are magnificent, by the way. Is that makeup on your thighs?”

She smiled, biting into a grape. “It’s a kind of paint. The designs were drawn by some of the most talented artists in my priesthood.”

“My compliments to them,” Lightsong said. “Regardless, you ask why I did not greet you. Well, let us assume that I had acted as you suggest I should. Upon your approach, you would have had me gush over you?”

“Naturally.”

“You would have me point out how stunning you appear in that gown?”

“I wouldn’t complain.”

“Mention how your dazzling eyes glisten in the fireworks like burning embers?”

“That would be nice.”

“Expound on how your lips are so perfectly red that they could leave any man breathless with wonder, yet drive him to compose the most brilliant of poetry each time he recalled the moment?”

“I’d be flattered for certain.”

“And you claim you want these reactions from me?”

“I do.”

“Well blast it, woman,” Lightsong said, picking up his cup. “If I’m stunned, dazzled, and breathless, then how the hell am I supposed to~\textit{greet}~you? By definition, won’t I be struck dumb?”

She laughed. “Well, then, you’ve obviously found your tongue now.”

“Surprisingly, it was in my mouth,” he said. “I always forget to check there.”

“But isn’t that where it is expected to be?”

“My dear,” he said, “haven’t you known me long enough to realize that my tongue, of all things, rarely does what it is expected to do?”

Blushweaver smiled as the fireworks went off again. Within the auras of~\textit{two}~gods, the sparks’ colors grew quite powerful indeed. On the far side, some sparks fell to the ground too far from the Breath auras, and these looked dull and weak in comparison—as if their fire were so cool and in significant that they could be picked up and tucked away.

Blushweaver turned from the display. “So you~\textit{do}~find me beautiful?”

“Of course. Why, my dear, you’re positively~\textit{rank}~with beauty. You’re literally part of the definition of the word—it’s in your title somewhere, if I’m not mistaken.”

“My dear Lightsong,~\textit{I}~do believe that you’re making sport of me.”

“I never make fun of ladies, Blushweaver,” Lightsong said, picking up his drink again. “Mocking a woman is like drinking too much wine. It may be fun for a short time, but the hangover is hell.”

Blushweaver paused. “But we don’t get hangovers, for we cannot get drunk.”

“We can’t?” Lightsong asked. “Then why the blazes am I drinking all of this wine?”

Blushweaver raised an eyebrow. “Sometimes, Lightsong,” she finally said, “I’m not certain when you are being silly and when you’re being serious.”

“Well, I can help you with that one easily enough,” he said. “If you~\textit{ever}~conclude that I’m being serious, then you can be sure that you’ve been working too hard on the problem.”

“I see,” she said, twisting on her couch so that she was facedown. She leaned on her elbows with breasts pushed up between them, fireworks playing off her exposed back and throwing colorful shadows between her arched shoulder blades. “So, then. You admit that I’m stunning and beautiful. Would you then care to retire from the festivities this evening? Find~.~.~. other entertainments?”

Lightsong hesitated. Being unable to bear children didn’t stop the gods from seeking intimacy, particularly with other Returned. In fact, from what Lightsong could guess, the impossibility of offspring only increased the laxness of the court in these matters. Many a god took mortal lovers—Blushweaver was known to have a few of her own among her priests. Dalliances with mortals were never seen as infidelity among the gods.

Blushweaver lounged on her couch, supple, inviting. Lightsong opened his mouth, but in his mind, he saw~.~.~. her. The woman of his vision, the one from his dreams, the face he’d mentioned to Llarimar. Who was she?

Probably nothing. A flash from his former life, or perhaps simply an image crafted by his subconscious. Maybe even, as the priests claimed, some kind of prophetic symbol. That face shouldn’t give him pause. Not when confronted with perfection.

“I~.~.~. must decline,” he found himself saying. “I need to watch the fireworks.”

“Are they that much more fascinating than I?”

“Not at all. They simply seem far less likely to burn me.”

She laughed at that. “Well, why don’t we wait until they are through, then retire?”

“Alas,” Lightsong said. “I still must decline. I am far too lazy.”

“Too lazy for sex?” Blushweaver asked, rolling back onto her side and regarding him.

“I’m really quite indolent. A poor example of a god, as I keep telling my high priest. Nobody seems to listen to me, so I fear that I must continue to be diligent in proving my point. Dallying with you would, unfortunately, undermine the entire basis of my argument.”

Blushweaver shook her head. “You confuse me sometimes, Lightsong. If it weren’t for your reputation, I’d simply presume you to be shy. How could you have slept with Calmseer, but consistently ignore me?”

\textit{Calmseer was the last honorable Returned this city has known,}~Lightsong thought, sipping his drink.~\textit{Nobody left has a shred of her decency. Myself included.}

Blushweaver fell silent, watching the latest display from the firemasters. The show had grown progressively more ornate, and Lightsong was considering calling halt, lest they use up all of their fireworks on him and not have any left should another god call upon them.

Blushweaver didn’t make any move to return to her own palace grounds, and Lightsong said nothing further. He suspected that she hadn’t come simply for verbal sparring, or even to try and bed him. Blushweaver always had her plans. In Lightsong’s experience, there was more depth to the woman than her gaudy surface suggested.

Eventually, his hunch paid off. She turned from the fireworks, eyeing the dark palace of the God King. “We have a new queen.”

“I noticed,” Lightsong said. “Though, admittedly, only because I was reminded several times.”

They fell silent.

“Have you no thoughts on the matter?” Blushweaver finally asked.

“I try to avoid having thoughts. They lead to other thoughts, and—if you’re not careful—those lead to actions. Actions make you tired. I have this on rather good authority from someone who once read it in a book.”

Blushweaver sighed. “You avoid thinking, you avoid me, you avoid effort~.~.~. is there anything you~\textit{don’t}~avoid?”

“Breakfast.”

Blushweaver didn’t react to this, which Lightsong found disappointing. She was too focused on the king’s palace. Lightsong usually tried to ignore the large black building; he didn’t like how it seemed to loom over him.

“Perhaps you should make an exception,” Blushweaver said, “and give some thought to~\textit{this}particular situation. This queen means something.”

Lightsong turned his cup around in his fingers. He knew that Blushweaver’s priests were among those who called most strongly for war in the Court Assembly. He hadn’t forgotten his phantom nightmare from earlier, the vision of T’Telir on fire. That image refused to fade from his mind. He never said anything for or against the idea of war. He just didn’t want to be involved.

“We’ve had queens before,” he finally said.

“Never one of the royal line,” Blushweaver replied. “At least, there hasn’t been one since the days of Kalad the Usurper.”

Kalad. The man who had started the Manywar, the one who had used his knowledge of BioChromatic Breath to create a vast army of Lifeless and seize power in Hallandren. He had protected the kingdom with his armies, yet had shattered the kingdom as well by driving the royals into the highlands.

Now they were back. Or, at least, one of them was.

“This is a dangerous day, Lightsong,” Blushweaver said quietly. “What happens if that woman bears a child who isn’t Returned?”

“Impossible,” Lightsong said.

“Oh? You are that confident?”

Lightsong nodded. “Of the Returned, only the God King can engender children, and they’re always stillborn.”

Blushweaver shook her head. “The only word we have for that is from the palace priests themselves. Yet I’ve heard of~.~.~. discrepancies in the records. Even if we don’t worry about those, there are plenty of other considerations. Why do we need a royal to ‘legitimize’ our throne? Isn’t three hundred years of rule by the Court of Gods sufficient to make the kingdom legitimate?”

Lightsong didn’t respond.

“This marriage implies that we still accept royal authority,” Blushweaver said. “What happens if that king up in the highlands decides to take his lands back? What happens if that queen of ours in there has a child by another man? Who is the heir? Who rules?”

“The God King rules. Everyone knows that.”

“He didn’t rule three hundred years ago,” Blushweaver said. “The royals did. Then, after them, Kalad did—and after him, Peacegiver. Change can happen quickly. By inviting that woman into our city, we may have initiated the end of Returned rule in Hallandren.”

She fell silent, pensive. Lightsong studied the beautiful goddess. It had been fifteen years since her Return—which made her old, for a Returned. Old, wise, and incredibly crafty.

Blushweaver glanced at him. “I don’t intend to find myself caught, surprised, like the royals were when Kalad seized their throne. Some of us are planning, Lightsong. You can join us, if you wish.”

“Politics, my dear,” he said with a sigh. “You know how I loathe it.”

“You’re the god of bravery. We could use your confidence.”

“At this point, I’m only confident that I’ll be of no use to you.”

Her face stiffened as she tried not to show her frustration. Eventually, she sighed and stood, stretching, showing off her perfect figure once more. “You’ll have to stand for something eventually, Lightsong,” she said. “You’re a god to these people.”

“Not by choice, my dear.”

She smiled, then bent down and kissed him softly. “Just consider what I said. You’re a better man than you give yourself credit for being. You think I’d offer myself to just anyone?”

He hesitated, then frowned. “Actually~.~.~. yes. I do.”

She laughed, turning as her servants picked up her couch. “Oh, come now! There must be at least~\textit{three}~of the other gods I wouldn’t~\textit{think}~of letting touch me. Enjoy the party, and do try to imagine what our king is doing to our legacy up there in his chambers right now.” She glanced back at him. “Particularly if that imagining reminds you of what you just missed out on.” She winked, then glided away.

Lightsong sat back on his couch, then dismissed the firemasters with words of praise. As the minstrels began to play, he tried to empty his mind of both Blushweaver’s ominous words and the visions of war that had plagued his dreams.

