% \section{Chapter Fifty}
\chapter{}

“And so we each have twenty thousand,” Blushweaver said, walking beside Lightsong on the stone pathway that led in a circle around the arena.

“Yes,” Lightsong said. Their priests, attendants, and servant s followed in a holy herd, though the two gods had refused palanquin or parasol. They walked alone, side by side. Lightsong in gold and red. Blushweaver, for once, wearing a gown that actually covered her.

\textit{Amazing, how good she looks in something like that,}~he found himself thinking,~\textit{when she takes the time to respect herself.}~He wasn’t certain what made him dislike her revealing outfits. Maybe he’d been a prude in his former life.

Or maybe he simply was one now. He smiled ruefully to himself.~\textit{How much can I really blame on my “old” self? That man is dead. He wasn’t the one who got himself involved in the kingdom’s politics.}

The arena was filling, and—in a rare show—all of the gods would be in attendance. Only Weatherlove was late, but he was often unpredictable.

\textit{Important events are imminent,}~Lightsong thought.~\textit{They have been building for years now. Why should I be at the center of them?}

His dreams the night before had been so odd. Finally, no visions of war. Just the moon. And some odd twisting passages. Like~.~.~. tunnels. Many of the gods nodded in respect as he passed their pavilions—though, admittedly, some scowled at him, and a few just ignored him.~\textit{What a strange system of rule}, he thought.~\textit{Immortals who only last a decade or two—and who have never seen the outside world. And yet the people trust us.}

\textit{The people trust us.}

“I think we should share the Command phrases with each other, Lightsong,” Blushweaver said. “So that we each have all four, just in case.”

He didn’t say anything.

She turned away from him, looking at the people in their colorful clothing, clogging the benches and seats. “My, my,” Blushweaver said, “quite the crowd. And so few of them paying attention to me. Quite rude of them, wouldn’t you say?”

Lightsong shrugged.

“Oh, that’s right,” she said. “Perhaps they’re just~.~.~. what was it? Stunned, dazzled, and dumbfounded?”

Lightsong smiled faintly, remembering their conversation a few months back. The day this all had started. Blushweaver looked at him, a longing in her eyes.

“Indeed,” Lightsong said. “Or, perhaps, they’re really just ignoring you. In order to compliment you.”

Blushweaver smiled. “And how, exactly, does ignoring me make a compliment?

“It provokes you to be indignant,” Lightsong said. “And we all know that is when you are in best form.”

“You like my form, then?”

“It has its uses. Unfortunately, I cannot compliment you by ignoring you as the others do. You see, only truly,~\textit{sincerely}~ignoring you would provide the intended compliment. I am, actually, helpless and unable to ignore you. I do apologize.”

“I see,” Blushweaver said. “I’m flattered. I think. Yet you seem very good at ignoring~\textit{some}~things. Your own divinity. General good manners. My feminine wiles.”

“You’re hardly wily, my dear,” Lightsong said. “A wily man is one who fights with a small, carefully hidden dagger in reserve. You are more like a man who crushes his opponent with a stone block. Regardless, I do have another method of dealing with you, one that you shall likely find quite flattering.”

“Somehow I find myself doubting.”

“You should have more faith in me,” he said with a suave wave of the hand. “I am, after all, a god. In my divine wisdom, I have realized that the only way to truly compliment one such as you—Blushweaver—is to be far more attractive, intelligent, and interesting than you.”

She snorted. “Well, then, I feel rather insulted by~\textit{your}~presence.”

“Touché,” Lightsong said.

“And are you going to explain~\textit{why}~you consider competing with me to be the most sincere form of compliment?”

“Of course I am,” Lightsong said. “My dear, have you ever known me to make an inflammatorily ridiculous statement without providing an equally ridiculous explanation to substantiate it?”

“Of course not,” she agreed. “You are nothing if not exhaustive in your self-congratulatory made-up logic.”

“I am rather exceptional in that regard.”

“Undoubtedly.”

“Anyway,” Lightsong said, holding up a finger, “by being far more stunning than you are, I invite people to ignore you and pay attention to me. That, in turn, invites~\textit{you}~to be your usual charming self—throwing little tantrums and being overly seductive—to draw their attention back to you. And that, as I explained, is when you are most majestic. Therefore, the only way to make certain you receive the attention you deserve is to draw it all away from you. It’s really~\textit{quite}~difficult. I hope you appreciate all the work I do to be so wonderful.”

“Let me assure you,” she said, “I do appreciate it. In fact, I appreciate it so very much that I would like to give you a break. You can back off. I will bear the awful burden of being the most wonderful of the gods.”

“I couldn’t possibly let you.”

“But if you are~\textit{too}~wonderful, my dear, you will completely destroy your image.”

“That image is getting tiresome anyway,” Lightsong said. “I’ve long sought to be the most notoriously lazy of the gods, but I’m realizing more and more that the task is beyond me. The others are all naturally so much more delightfully useless than I am. They just pretend not to be aware of it.”

“Lightsong!” she said. “One could say you begin to sound jealous!”

“One could also say that my feet smell like guava fruit,” he said. “Just because one~\textit{could}~say it doesn’t mean it’s relevant.”

She laughed. “You’re incorrigible.”

“Really? I thought I was in T’Telir. When did we move?”

She held up a finger. “That pun was a stretch.”

“Perhaps it was just a feint.”

“A feint?”

“Yes, an intentionally weak joke to distract from the~\textit{real}~one.”

“Which is?”

Lightsong hesitated, glancing at the arena. “The joke that has been played on all of us,” he said, voice growing softer. “The joke the others in the pantheon have played by giving me so much influence over what our kingdom will do.”

Blushweaver frowned at him, obviously sensing the growing bitterness in his voice. They stopped on the walkway, Blushweaver facing him, her back to the arena floor. Lightsong feigned a smile, but the moment was dying. They couldn’t go on as they had. Not amidst the weighty matters in motion all around them.

“Our brothers and sisters aren’t as bad as you imply,” she said quietly.

“Only a matchless group of idiots would give~\textit{me}~control of their armies.”

“They trust you.”

“They’re~\textit{lazy,}” Lightsong said. “They want others to make the difficult decisions. That’s what this system encourages, Blushweaver. We’re all locked in here, expected to spend our time in idleness and pleasure. And then we’re supposed to know what is best for our country?” He shook his head. “We’re more afraid of the outside than we’re willing to admit. All we have are artworks and dreams. That’s why you and I ended up with these armies. Nobody else wants to be the one who actually sends our troops out to kill and die. They all want to be involved, but nobody wants to be~\textit{responsible.}”

He fell silent. She looked up at him, a goddess of perfect form. So much stronger than the others, but she hid it behind her own veil of triviality. “I know one thing that you said is true,” she said quietly.

“And that is?”

“You~\textit{are}~wonderful, Lightsong.”

He stood there, looking into her eyes for a time. Widely set, beautiful green eyes.

“You’re not going to give me your Command Phrases, are you?” she asked.

He shook his head.

“I brought you into this,” she said. “You always talk about being useless, but we all know that you’re one of the few who always goes through every picture, sculpture, and tapestry in his gallery. The one who hears every poem and song. The one who listens most deeply to the pleas of his petitioners.”

“You are all fools,” he said. “There is nothing in me to respect.”

“No,” she said. “You’re the one who makes us laugh, even while you insult us. Can’t you see what~\textit{that}~does? Can’t you see how you’ve inadvertently set yourself above everyone else? You didn’t do it intentionally, Lightsong, and that’s what makes it work so well. In a city of frivolity, you’re the only one who’s shown any measure of wisdom. In my opinion, that’s why you hold the armies.”

He didn’t reply.

“I knew you might resist me,” she said. “But I thought that I’d be able to influence you anyway.”

“You can,” he said. “As you’ve said, it’s your doing that I’m involved in all of this.”

She shook her head, still staring into his eyes. “I can’t decide which feeling for you is stronger, Lightsong. My love or my frustration.”

He took her hand and kissed it. “I accept them both, Blushweaver. With honor.” And with that, he turned from her and went to his box. Weatherlove had arrived; that left only the God King and his bride. Lightsong sat down, wondering where Siri was. She usually got to the arena long before it was time to begin.

He found it difficult to focus his attention on the young queen. Blushweaver still stood on the walkway where he had left her, watching him.

Finally, she turned, and made her way to her own pavilion.

\orn

Siri walked through the palace corridors, surrounded by her brown-uniformed serving women, a dozen worries circling through her brain.

\textit{First, go to Lightsong,}~she told herself, going over the plan.~\textit{It won’t look odd for me to sit with him—we often spend time together at these things.}

\textit{I wait for Susebron to arrive. Then I ask Lightsong if we can talk in private, without our servants or his priests. I explain what I have discovered about the God King. I tell him about the way Susebron is being held captive. Then we see what he does.}

Her biggest fear was that Lightsong would already know. Could he be part of the entire conspiracy? She trusted him as much as she trusted anyone except Susebron, but her nerves had a way of making her question everything and everyone.

She passed through room after room, each one decorated in its own color theme. She didn’t notice how bright those were anymore.

\textit{Assuming Lightsong agrees to help,}~she thought,~\textit{I wait for the break. Once the priests leave the sand, Lightsong goes and speaks with several other gods. They each go to their priests and instruct them to begin a discussion in the arena about why the God King never speaks to them. They force the God King’s priests to let him offer his own defense.}

She didn’t like depending on the priests, even those who weren’t members of Susebron’s priesthood, but this did seem like the best way. Besides, if the priests of the various gods didn’t do as instructed, Lightsong and the others would realize that they were being undermined by their own servants. Either way, Siri realized she was getting into very dangerous territory.

\textit{I}~started~\textit{in dangerous territory,}~she thought, leaving the formal rooms of the palace and entering the dark outer hallway.~\textit{The man I love is threatened with death, and any children I bear will be taken from me.}~She either had to act or let the priests continue to push her around. Susebron and she were in agreement. The best plan was—

Siri slowed. At the end of the hallway, in front of the doors out to the court, a small group of priests stood with several Lifeless soldiers. They were silhouetted by the evening light. The priests turned toward her, and one pointed.

\textit{Colors!}~Siri thought, spinning. Another group of priests was approaching up the back hallway.~\textit{No! Not now!}

The two groups of priests closed on her. Siri considered running, but where? Dashing in her long dress—pushing through servants and Lifeless—was hopeless. She raised her chin—eyeing the priests with a haughty stare—and kept her hair completely under control. “What is the meaning of this?” she demanded.

“We’re terribly sorry, Vessel,” the lead priest said. “But it has been decided that you shouldn’t be exerting yourself while in your condition.”

“My condition?” Siri asked icily. “What foolishness is this?”

“The child, Vessel,” the priest said. “We can’t risk danger to it. There are many who would try to harm you, should they know that you are carrying.”

Siri froze.~\textit{Child?}~she thought with shock.~\textit{How could they know that Susebron and I have actually started~.~.~.}

But no. She would know if she were with child. However, she’d supposedly been sleeping with the God King for months now. That was just enough time for a pregnancy to have begun to show. It would sound plaus ible to the people of the city.

\textit{Fool!}~She thought to herself in a sudden panic.~\textit{Assuming they’ve already found their replacement God King, I don’t actually need to bear them a child. They just have to make everyone}~think~\textit{I was pregnant!}

“There is no child,” she said. “You were just waiting—you just had to stall until you had an excuse to lock me away.”

“Please, Vessel,” one of the priests said, gesturing for a Lifeless to take her arm. She didn’t struggle; she forced herself to remain calm, looking the priest in the eyes.

He looked away. “This will be for the best,” he said. “It’s for your own good.”

“I’m sure it is,” she snapped, but allowed herself to be led back to her rooms.

\orn

Vivenna sat among the crowds, watching and waiting. Part of her found it foolish to come out into the open so flagrantly. However, that part of her—the cautious Idrian princess—was growing more and more quiet.

Denth’s people had found her when she’d been hiding in the slums. She’d probably be safer in the crowds with Vasher than she ever had been in the alleyways, particularly considering how well she now blended in. She hadn’t realized how natural it could feel to sit in trousers and a tunic, brightly colored and completely ignored.

Vasher appeared at the railing above the benches. She carefully slipped out of her seat—someone else took it immediately—and walked toward him. The priests had already begun their arguments down below. Nanrovah, his daughter restored to him, had started by announcing the retraction of his previous position. He currently was leading the discussion against war.

He had very little support.

Vivenna joined Vasher along the railing, and he quite unapologetically elbowed open a space for her. He didn’t carry Nightblood—at her insistence, he had left the sword behind with her own dueling blade. She wasn’t certain how he’d managed to sneak the blade in the last time he’d come to the court, but the last thing they wanted was to draw attention.

“Well?” she asked quietly.

He shook his head. “If Denth is here, I couldn’t find him.”

“No surprise, considering the size of this crowd,” Vivenna said quietly. There were bodies all around them—hundreds lining the railing alone. “Where did they all come from? This is far more jammed than the other assembly sessions.”

He shrugged. “People who are granted a one-time visit to the court can hold their token of entry until they want to use it. A lot of them use those at a general Court Assembly, rather than one of the smaller meetings. It’s their one chance to see all of the gods together.”

Vivenna turned back to look over the throng. She suspected it also had to do with the rumors she’d heard. People thought that this session would be the one where the Pantheon of Returned finally declared war on Idris.

“Nanrovah argues well,” she said, although she was having trouble hearing him because of the crowds—the Returned apparently had messengers relaying transcripts. She wondered why someone just didn’t order all the people to be quiet. That didn’t seem to be the Hallandren way. They liked chaos. Or, at least, they liked the opportunity to sit and chat while important events were in progress.

“Nanrovah is being ignored,” Vasher said. “He’s changed his mind twice now on the same issue. He lacks credibility.”

“He should explain why he changed his mind, then.”

“He might, but I don’t know. If the people knew his child had been kidnapped, it would make some more afraid and they would decide that Idrian instigators had been behind it, no matter what he said. Plus there’s that stubborn Hallandren pride. Priests are particularly bad. Mentioning that his daughter had been taken, and that he had been pressured into changing his politics~.~.~.”

“I thought you liked the priests,” she said.

“Some of them,” he said. “Not others.” When he said that, he eyed the God King’s pedestal. Susebron had yet to arrive, and they had started without him.

Siri wasn’t there either. That annoyed Vivenna, since she’d been anticipating checking in on the girl, if only from a distance.

\textit{I’ll help you, Siri. For real this time. The first step has to be stopping this war.}

Vasher looked back at the floor of the arena, leaning on the railing, looking anxious.

“What?” she asked.

He shrugged.

She rolled her eyes. “Tell me.”

“I just don’t like leaving Nightblood alone for too long,” he said.

“What’s it going to do?” Vivenna asked. “We locked it in the closet.”

He shrugged again.

“Honestly,” she said. “You would think that you’d admit that bringing a five-foot-long black sword out in public would be rather conspicuous. It doesn’t help, mind you, that said sword bleeds smoke and can talk in people’s minds.”

“I don’t mind being conspicuous.”

“I do,” she replied.

Vasher grimaced, and she thought he’d argue some more, but he finally just nodded. “You’re right, of course,” he said. “I’ve just never been good at being unobtrusive. Denth used to make fun of me for that too.”

Vivenna frowned. “You were friends?”

Vasher turned away and fell silent.

\textit{Kalad’s Phantoms!}~she thought in frustration.~\textit{One of these days, someone in this Colors-cursed city is going to tell me the whole truth. I’ll probably die of shock.}

“I’m going to go see if I can find out why the God King is taking so long,” Vasher said, leaving the railing. “I’ll be back.”

She nodded, and he was gone. She leaned down, wishing she hadn’t relinquished her seat. Once, she would have felt stifled by the large mass of people, but she’d grown used to the busy market streets, and so being surrounded by people wasn’t as intimidating as it had been. Besides, there was her Breath. She’d put some of it into her shirt, but she’d held onto a portion—she needed to be of at least the First Heightening to pass through the gates into the court without being questioned.

Her Breath let her feel life as an ordinary person felt the air: always there, cool against the skin. Having so many people in such close proximity left her feeling a little intoxicated. So much life, so many hopes and desires. So much Breath. She closed her eyes, drinking it in, listening to the voices of the priests down below rise over the crowd.

She felt Vasher approach before he arrived. Not only did he have a lot of Breath, but he was watching her, and she could feel the slight familiarity of that gaze. She turned, picking him out of the crowd. He stood out far more than she did, in his darker, ragged clothing.

“Congratulations,” he said as he approached, taking her arm.

“Why?”

“You’ll soon be an aunt.”

“What are you~.~.~.” She trailed off. “\textit{Siri?}”

“Your sister is pregnant,” he said. “The priests are going to make an announcement later this evening. The God King is apparently remaining in his palace to celebrate.”

Vivenna stood, stunned.~\textit{Siri. Pregnant.}~Siri, who was still a little girl in Vivenna’s mind, bearing the child of that~\textit{thing}~in the palace. And yet wasn’t Vivenna now fighting to keep that thing on his throne?

\textit{No,}~she thought.~\textit{I haven’t forgiven Hallandren, even if I am learning not to hate it. I can’t let Idris be attacked and destroyed.}

She felt a panic. Suddenly, all of her plans seemed meaningless. What would the Hallandren do to her once they had their heir? “We have to get her out,” Vivenna found herself saying. “Vasher, we have to rescue her.”

He remained quiet.

“\textit{Please,}~Vasher,” she whispered. “She’s my~\textit{sister.}~I thought to protect her by ending this war, but if your hunch is right, then the God King himself is one of those who wants to invade Idris. Siri won’t be safe with him.”

“All right,” Vasher said. “I will do what I can.”

Vivenna nodded, turning back to the arena. The priests were withdrawing. “Where are they going?”

“To their gods,” Vasher said. “To seek the Will of the Pantheon in formal vote.”

“About the war?” Vivenna asked, feeling a chill.

Vasher nodded. “It is time.”

\orn

Lightsong waited beneath his canopy, a couple of serving men fanning him, a cup of chilled juice in his hand, lavish snacks spread out to his side.

\textit{Blushweaver brought me into this,}~he thought.~\textit{Because she was worried that Hallandren would be taken by surprise.}

The priests were consulting with their gods. He could see several of them kneeling before their Returned, heads bowed. It was the way that government worked in Hallandren. The priests debated their options and then they sought the will of the gods. That would become the Will of the Pantheon. That would become the Will of Hallandren itself. Only the God King could veto a decision of the full Pantheon.

And he had chosen not to attend this meeting.

\textit{So self-congratulatory on spawning a child that he couldn’t even bother with the future of his people?}~Lightsong thought with annoyance.~\textit{I had hoped he was better than that.}

Llarimar approached. Though he had been down below with the other high priests, he had offered no arguments to the court. Llarimar tended to keep his thoughts to himself.

The high priest knelt before him. “Please, favor us with your will, Lightsong my god.”

Lightsong didn’t respond. He looked up, across the open arena to where Blushweaver’s canopy stood, verdant in the dimming evening light.

“Oh, God,” Llarimar said. “Please. Give me the knowledge I seek. Should we go to war with our kinsmen, the Idrians? Are they rebels who need to be quelled?”

Priests were already returning from their supplications. Each held aloft a flag indicating the will of their god or goddess. Green for a favorable response. Red for dissatisfaction with the petition. In this case green meant war. So far, five of the returning seven flew green.

“Your Grace?” Llarimar asked, looking up.

Lightsong stood.~\textit{They vote, but what good are their votes?}~he thought, walking out from beneath his canopy.~\textit{They hold no authority. Only two votes really matter.}

More green. Flags flapped as priests ran down the walkways. The arena was abuzz with people. They could see the inevitable. To the side, Lightsong could see Llarimar following him. The man must be frustrated. Why didn’t he ever show it?

Lightsong approached Blushweaver’s pavilion. Almost all of the priests had gotten their answers, and the vast majority of them carried flags of green. Blushweaver’s high priestess still knelt before her. Blushweaver, of course, waited upon the drama of the moment.

Lightsong stopped outside of her canopy. Blushweaver reclined inside, watching him calmly, though he could sense her true anxiety. He knew her too well.

“Are you going to make your will known?” she asked.

He looked down at the center of the arena. “If I resist,” he said, “this declaration will be for naught. The gods can shout ‘war’ until they are blue, but~\textit{I}~control the armies. If I don’t allow them my Lifeless, then Hallandren will not win any wars.”

“You would defy the Will of the Pantheon?”

“It is my right to do so,” he said. “Just as any of them have the same right.”

“But you have the Lifeless.”

“That doesn’t mean I have to do what I’m told.”

There was a moment of silence before Blushweaver waved to her priestess. The woman stood, then raised a flag of green and ran down to join the others. This brought forth a roar. The people must know that Blushweaver’s political wranglings had left her in a position of power. Not bad, for a person who had started without command of a single soldier.

\textit{With her control of that many troops, she’ll be an integral part of the planning, diplomacy, and execution of the war. Blushweaver could emerge from this as one of the most powerful Returned in the history of the kingdom.}

\textit{And so could I.}

He stared for a long moment. He hadn’t spoken of his dreams the last night to Llarimar. He’d kept them to himself. Those dreams of twisting tunnels and of the rising moon, just barely cresting the horizon. Could it be possible that they actually meant something?

He couldn’t decide. About anything.

“I need to think about this some more,” Lightsong said, turning to go.

“What?” Blushweaver demanded. “What about the vote?”

Lightsong shook his head.

“Lightsong!” she said as he left. “Lightsong, you can’t leave us hanging like this!”

He shrugged, glancing back. “Actually, I can.” He smiled. “I’m frustrating like that.”

And with that, he left the arena, heading back to his palace without giving his vote.

