% \section{Chapter Nineteen}
\chapter{}

“This is nice,” Denth said, looking over the house. “Strong wood paneling. Will break very cleanly.”

“Yeah,” Tonk Fah added, peeking into a closet. “And it has plenty of storage. Bet we could fit a good half-dozen bodies in here alone.”

Vivenna shot the two mercenaries a look, causing them to chuckle to themselves. The house wasn’t as nice as Lemex’s had been; she didn’t want to be ostentatious. It was one of many that were built in a row along a well-maintained street. Deeper than it was wide, the building was bordered on either side with large palm trees, obscuring the view should someone try to spy from the neighboring buildings.

She was pleased. Part of her balked at living in a home that was—despite being modest by Hallandren standards—nearly as large as the king’s palace back in Idris. However, she and Parlin had looked at and rejected cheaper sections of town. She didn’t want to live in a place where she was afraid to go out at night, particularly since she worried that her Breath might make her a target.

She trailed down the stairs, the mercenaries following. The house had three stories—a small upper story with sleeping chambers, the main floor with a kitchen and sitting room, and a cellar for storage. The building was sparsely furnished, and Parlin had gone to the market to shop for more. She hadn’t wanted to spend the money, but Denth had pointed out that they must at least\textit{try}~to keep up appearances, lest they end up drawing even more attention.

“Old Lemex’s house will be taken care of soon,” Denth said. “We left some hints in the underground, mentioning that the old man was dead. Whatever we didn’t ransack, a gang of burglars will take care of tonight. By tomorrow, the city guard will be there, and they’ll assume that the place was burgled. The nurse has been paid off, and she never knew who Lemex really was anyway. When nobody comes to pay for the funeral ser vices, the authorities will take the house in forfeit and have the body burned with other debtors.”

Vivenna stopped at the bottom of the stairs, paling. “That doesn’t sound very respectful.”

Denth shrugged. “What do you want to do? Go claim him at the charnel house yourself? Give him an Idrian ceremony?”

“Good way to get people asking questions, that,” Tonk Fah said.

“Better to just let others deal with it,” Denth said.

“I suppose,” Vivenna said, turning away from the stairs and walking into the sitting room. “It just bothers me, letting his body be cared for by~.~.~.”

“By what?” Denth said, amused. “Pagans?”

Vivenna didn’t look at him.

“The old man didn’t seem to care much about heathen ways,” Tonk Fah noted. “Not with the number of Breaths he held. Of course, didn’t your daddy give him the money to buy them?”

Vivenna closed her eyes.

\textit{You hold those same Breaths,}~she told herself.~\textit{You’re not innocent in all of this.}

She hadn’t been given a choice. She could only hope and assume that her father had felt he was in a similar position—no choice but to do what seemed wrong.

Lacking furniture, Vivenna arranged her dress and knelt on the wooden floor, hands in her lap. Denth and Tonk Fah sat back against the wall, looking just as comfortable sitting on a hardwood floor as they were when lounging in plush chairs. “All right, Princess,” Denth said, unfolding a paper from his pocket. “We’ve got some plans for you.”

“Please continue, then.”

“First,” Denth said, “we can get you a meeting with some of Vahr’s allies.”

“Who exactly was this man?” Vivenna said, frowning. She didn’t like the idea of working with revolutionaries.

“Vahr was a worker in the dye fields,” Denth said. “Things can get bad out in those fields—long hours, little more than food for pay. About five years back, Vahr got the bright idea that if he could convince enough of the other workers to give him their Breath, he might be able to use the power to start a revolt against the overseers. Became enough of a hero to the people in the outer flower plantations that he actually drew the attention of the Court of Gods.”

“Never truly had a chance of starting a real rebellion,” Tonk Fah said.

“So what good are his men to us?” Vivenna asked. “If they never had a chance of succeeding.”

“Well,” Denth said, “you didn’t say anything about a rebellion or anything like that. You just want to make it tough for the Hallandren when they go to war.”

“Revolts in the fields would sure be a pain during war,” Tonk Fah added.

Vivenna nodded. “All right,” she said. “Let’s meet with them.”

“Just so you know, Princess,” Denth said. “These aren’t particularly~.~.~. sophisticated kinds of folks.”

“I am not offended by poverty or people of small means. Austre regards all people equally.”

“I didn’t mean that,” Denth said, rubbing his chin. “It’s not that they’re peasants, it’s that~.~.~. well, when Vahr’s little insurrection went bad, these are the people who were smart enough to get out quickly. That means they weren’t all that committed to him in the first place.”

“In other words,” Tonk Fah said, “they were really just a bunch of thugs and crime lords who thought Vahr might be the source of some easy influence or money.”

\textit{Great,}~Vivenna thought. “And do we want to associate with people like that?”

Denth shrugged. “We have to start somewhere.”

“The other things on the list are a bit more fun,” Tonk Fah said.

“And they are?” Vivenna asked.

“Raid the Lifeless storage warehouse, for one,” Denth said, smiling. “We won’t be able to kill the things—not without drawing the rest of them down on us. But we might be able to muck up the way the creatures work.”

“That sounds dangerous,” Vivenna said.

Denth glanced at Tonk Fah, who opened his eyes. They shared a smile.

“What?” Vivenna asked.

“Hazard pay,” Tonk Fah said. “We may not steal your money, but we have nothing against overcharging you for extremely dangerous stunts!”

Vivenna rolled her eyes.

“Beyond that,” Denth added, “from what I can tell, Lemex wanted to undermine the city’s food supply. It’s a good idea, I suppose. Lifeless don’t need to eat, but the humans who form the support structure of the army~\textit{do}. Disrupt supply, and perhaps people here will begin to worry if they can afford a long term war.”

“That sounds more reasonable,” Vivenna said. “What did you come up with?”

“We raid merchant caravans,” Denth said. “Burn things up, cost them a bunch. We make it look like bandits or maybe even remnants of Vahr’s supporters. That ought to confuse people in T’Telir and maybe make it more difficult for the priests to go to war.”

“Priests run a lot of the trade in the city,” Tonk Fah added. “They have all the money so they tend to own the supplies. Burn away the stuff they intended to use for the war, and they’ll be more hesitant to attack. It’ll buy your people more time.”

Vivenna swallowed. “Your plans are a bit more~.~.~. violent than I had anticipated.”

The mercenaries shared a look.

“You see,” Denth said. “This is where we get our bad reputation. People hire us to do difficult things—like undermine a country’s ability to wage war—then complain that we’re too violent.”

“Very unfair,” Tonk Fah agreed.

“Perhaps she’d rather we buy puppies for all of her enemies, then send them with nice apologetic notes, asking them to stop being so mean.”

“And then,” Tonk Fah said, “when they~\textit{don’t}~stop, we could kill the puppies!”

“All right,” Vivenna said. “I understand that we’ll have to use a firm hand, but~.~.~. really. I don’t want the Hallandren to starve because of what we do.”

“Princess,” Denth said, sounding more serious. “These people want to attack your homeland. They see your family as the greatest existing threat to their power—and they’re going to make certain that nobody of the royal blood lives to challenge them.”

“They get a child by your sister to be the next God King,” Tonk Fah said, “then they kill every other person of royal blood. They never have to worry about you again.”

Denth nodded. “Your father and Lemex were right. The Hallandren have~\textit{everything}~to lose by not attacking you. And, from what I can see, your people are going to need every bit of help you can give them. That means doing everything we can—scaring the priests, breaking their supply reserves, weakening their armies—to help out.”

“We can’t stop the war,” Tonk Fah added. “We can just make the fight a little more fair.”

Vivenna took a deep breath, then nodded. “All right, then, we’ll—”

At that moment, the door to the building flew open, slamming against the other side of the wall. Vivenna looked up. A figure stood in the doorway—a tall, bulky man with unusually large muscles and flat features. It took her a moment to register the other oddity about him.

His skin was grey. His eyes too. There was no color to him at all, and her Heightenings told her that he didn’t have a single Breath. A Lifeless soldier.

Vivenna scrambled to her feet, barely keeping in a cry of distress. She backed away from the large soldier. It just stood there, immobile, not even breathing. Its eyes tracked her—they didn’t just stare ahead like those of a dead man.

For some reason, she found that the most unnerving.

“Denth!” Vivenna said. “What are you doing? Attack!”

The mercenaries remained where they were, lounging on the floor. Tonk Fah barely cracked an eye open. “Ah well,” Denth said. “Looks like we’ve been discovered by the city watch.”

“Pity,” Tonk Fah said. “This was looking like it would be a fun job.”

“Nothing but execution for us now,” Denth said.

“Attack!” Vivenna cried. “You’re my bodyguards, you’re~.~.~.” She trailed off, noticing as the two men began to chuckle.

\textit{Oh, Colors, not again,}~she thought. “What?” she said. “Some kind of joke? Did you paint that man grey? What’s going on?”

“Move it, you rock on legs,” a voice said from behind the Lifeless. The creature walked into the room, carrying a couple of canvas bags over its shoulders. As it entered, it revealed a shorter woman standing behind. Thick through the thighs and through the bust, she had light brown hair that came down to her shoulders. She stood with hands on hips, looking upset.

“Denth,” she snapped, “he’s here. In the city.”

“Good,” Denth said, lounging back. “I owe that man a sword through the gut.”

The woman snorted. “He killed Arsteel. What makes you think you can beat him?”

“I’ve always been the better swordsman,” Denth said calmly.

“Arsteel was good too. Now he’s dead. Who’s the woman?”

“New employer.”

“Hope she lives longer than the last one,” the woman grumbled. “Clod, put those down and go get the other bag.”

The Lifeless responded, setting down its bags and then walking back out. Vivenna watched, by now having figured out that the short woman must be Jewels, the third member of Denth’s team. What was she doing with a Lifeless? And how had she found the new house? Denth must have sent her a message.

“What’s wrong with you?” Jewels said, glancing at Vivenna. “Some Awakener come by and steal your colors?”

Vivenna paused. “What?”

“She means,” Denth said, “why do you look so surprised?”

“That, and her hair is white,” Jewels said, walking over to the canvas bags.

Vivenna flushed, realizing that her shock had gotten the better of her. She returned her hair to its proper dark color. The Lifeless was returning, carrying another bag.

“Where did that creature come from?” Vivenna asked.

“What?” Jewels asked. “Clod? Made him from a dead body, obviously. I didn’t do it myself—I just paid money for someone else to.”

“Too much money,” Tonk Fah added.

The creature clomped back into the room. It wasn’t unnaturally tall—not like a Returned. It could have been a normal, if well-muscled, man. Only the skin coloring, mixed with the emotionless face, was different.

“She bought him?” Vivenna asked. “When? Just now?”

“Nah,” Tonk Fah said, “we’ve had Clod for months.”

“It’s useful to have a Lifeless around,” Denth said.

“And you didn’t tell me about this?” Vivenna asked, trying to keep the hysteria out of her voice. First she’d had to deal with the city and all of its colors and people. Then she was given a dose of unwanted Breath. Now she was confronted by the most unholy of abominations.

“The topic didn’t come up,” Denth said, shrugging. “They’re pretty common in T’Telir.”

“We were just talking about defeating these things,” Vivenna said. “Not embracing them!”

“We talked about defeating~\textit{some}~of them,” Denth said. “Princess, Lifeless are like swords. They’re tools. We can’t destroy~\textit{all}~of them in the city, nor would we want to. Just the ones being used by your enemies.”

Vivenna slid down, sitting on the wooden floor. The Lifeless set down its final bag, then Jewels pointed toward the corner. It walked over and stood there, patiently waiting for further orders.

“Here,” Jewels said to the other two, untying the final large bag. “You wanted these.” She turned it on its side, exposing glittering metal shining within.

Denth smiled, rising. He kicked Tonk Fah back awake—the large man had an uncanny ability to fall asleep at a moment’s notice—and walked over to the bag. He pulled out several swords, shiny and new-looking with long, thin blades. Denth made a few practice swings while Tonk Fah wandered over, pulling out wicked-looking daggers, some shorter swords, and then some leather jerkins.

Vivenna sat, back against the wall, using her breathing to calm herself. She tried not to feel threatened by the Lifeless in the corner. How could they just go about, ignoring it like that? It was so unnatural that it made her itch and squirm. Eventually, Denth noticed her. He told Tonk Fah to oil the blades, then walked over and sat down in front of Vivenna, leaning back with hands against the floor behind him.

“That Lifeless is going to be a problem, Princess?” he asked.

“Yes,” she said curtly.

“Then we’ll need to work it out,” he said, meeting her eyes. “My team can’t function if you tie our hands. Jewels has invested a lot of effort into learning the proper Commands to use a Lifeless, not to mention learning to maintain the thing.”

“We don’t need her.”

“Yes,” Denth said. “Yes we~\textit{do.}~Princess, you’ve brought a lot of biases into this city. It’s not my place to tell you what to do with them. I’m just your employee. But I will tell you that you don’t know half the things you think you do.”

“It’s not about what I ‘think I know,’ Denth,” Vivenna said. “It’s what I~\textit{believe.}~A person’s body shouldn’t be abused by making it come back to life and serve you.”

“Why not?” he asked. “Your own theology says a soul leaves when the body dies. The corpse is just recycled dirt. Why not use it?”

“It’s wrong,” Vivenna said.

“The family of the corpse was well paid for the body.”

“Doesn’t matter,” Vivenna said.

Denth leaned forward. “Well, fine then. But if you order Jewels away, you order us all away. I’ll give your money back, then we’ll go hire you another team of bodyguards. You can use them instead.”

“I thought you were my employee,” Vivenna snapped.

“I am,” Denth said. “But I can quit whenever I want.”

She sat quietly, stomach unsettled.

“Your father was willing to use means that he didn’t agree with,” Denth said. “Judge him if you must, but tell me this. If using a Lifeless could save your kingdom, who are you to ignore the opportunity?”

“Why do you care?” Vivenna asked.

“I just don’t like leaving things unfinished.”

Vivenna glanced away.

“Look at it this way, Princess,” he said. “You can work with us—which will give you chances to explain your views, maybe change our minds on things like Lifeless and BioChroma. Or you can send us away. But if you reject us because of our sins, aren’t you being ostentatious? Don’t the Five Visions say something about that?”

Vivenna frowned.~\textit{How does he know so much about Austrism?}~“I’ll think about it,” she said. “Why did Jewels bring all those swords?”

“We’ll need weapons,” Denth said. “You know, has to do with that violence thing we mentioned earlier.”

“You don’t have any already?”

Denth shrugged. “Tonk usually has a cudgel or knife on him, but a full sword draws attention in T’Telir. It’s best not to stand out, sometimes. Your people have some interesting wisdom in that area.”

“But now~.~.~.”

“Now we don’t really have a choice,” he said. “If we keep moving forward with Lemex’s plans, things are going to get dangerous.” He eyed her. “Which reminds me. I have something else for you to think about.”

“What?”

“Those Breaths you hold,” Denth said. “They’re a tool. Just like the Lifeless. Now, I know you don’t agree with how they were obtained. But the fact is, you have them. If a dozen slaves die to forge a sword, does it do any good to melt down the sword and refuse to use it? Or is it better to use that sword and try to stop the men who did such evil in the first place?”

“What are you saying?” Vivenna said, feeling that she probably already knew.

“You should learn to use the Breaths,” Denth said. “Tonks and I could sure use an Awakener backing us up.”

Vivenna closed her eyes. Did he have to hit her with that now, right after twisting around her concerns about the Lifeless? She had expected to find uncertainties and obstacles in T’Telir. She just hadn’t expected so many difficult decisions. And she hadn’t expected them to endanger her soul.

“I’m not going to become an Awakener, Denth,” Vivenna said quietly. “I might turn a blind eye toward that Lifeless, for now. But I will~\textit{not}~Awaken. I expect to take these Breaths to my death so that nobody else can benefit from harvesting them. No matter what you say, if you buy that sword forged by overworked slaves, then you’ll just encourage the evil merchants.”

Denth fell silent. Then he nodded, standing. “You’re the boss, and it’s your kingdom. If we fail, the only thing~\textit{I}~lose is an employer.”

“Denth,” Jewels said, approaching. She barely gave Vivenna a glance. “I don’t like this. I don’t like the fact that~\textit{he}~got here first. He has Breath—reports say he looked to have reached at least the Fourth Heightening. Maybe the Fifth. I’ll bet he got it from that rebel, Vahr.”

“How do you even know it’s him?” Denth asked.

Jewels snorted. “Word’s all over. People being found slaughtered in alleyways, the wounds corrupt and black. Sightings of a new, powerful Awakener roaming the city carrying a black-handled sword in a silver sheath. It’s Tax, all right. Goes by a different name now.”

Denth nodded. “Vasher. He’s used it for a while. It’s a joke on his part.”

Vivenna frowned.~\textit{Black-handled sword. Silver sheath. The man at the arena?}~“Who are we talking about?”

Jewels shot her an annoyed look, but Denth just shrugged. “Old~.~.~. friend of ours.”

“He’s bad trouble,” Tonk Fah said, walking up. “Tax tends to leave a lot of bodies in his wake. Has strange motivations—doesn’t think like other people.”

“He’s interested in the war for some reason, Denth,” Jewels said.

“Let him be,” Denth snapped. “That will just bring him across my path all the sooner.” He turned away, waving a hand indifferently. Vivenna watched him go, noting the frustration in his step, the curtness of his motions.

“What is wrong with him?” she asked Tonk Fah.

“Tax—or, I guess, Vasher—” Tonk Fah said. “He killed a good friend of ours over in Yarn Dred a couple months back. Denth used to have four people in this team.”

“It shouldn’t have happened,” Jewels said. “Arsteel was a brilliant duelist—almost as good as Denth. Vasher’s never been able to beat either of them.”

“He used that~.~.~. sword of his,” Tonk Fah grumbled.

“There was no blackness around the wound,” Jewels said.

“Then he cut the blackness out,” Tonk Fah snapped, watching Denth belt a sword to his waist. “There’s no way Vasher beat Arsteel in a fair duel.~\textit{No}~way.”

“This Vasher,” Vivenna found herself saying. “I saw him.”

Jewels and Tonk Fah turned sharply.

“He was at the court yesterday,” Vivenna said. “Tall man, carrying a sword when nobody else did. It had a black hilt and a silver sheath. He looked ragged. Hair unkempt, beard scraggly, clothing ripped in places. Only a rope for a belt. He was watching me from behind. He looked~.~.~. dangerous.”

Tonk Fah cursed quietly.

“That’s him,” Jewels said. “Denth!”

“What?” Denth asked.

Jewels gestured at Vivenna. “He’s a step ahead of us. Been tailing your princess here. She saw him watching her at the court.”

“Colors!” Denth swore, snapping a dueling blade into the sheath at his waist. “Colors, Colors,~\textit{Colors}!”

“What?” Vivenna asked, paling. “Maybe it was just a coincidence. He could have just come to watch the court.”

Denth shook his head. “There~\textit{are}~no coincidences where that man is concerned, Princess. If he was watching you, then you can bet on the Colors that he knows exactly who you are and where you came from.” He met her eyes. “And he’s probably planning to kill you.”

Vivenna fell silent.

Tonk Fah laid a hand on her shoulder. “Ah, don’t worry, Vivenna. He wants to kill~\textit{us}~too. At least you’re in good company.”

