% \section{Chapter Twenty-Three}
\chapter{}

Lightsong found Blushweaver in the grassy portion of the courtyard behind her palace. She was enjoying the art of one of the city’s master gardeners.

Lightsong strolled through the grass, his entourage hovering around him, holding up a large parasol to shield him from the sun, and generally seeing that he was suitably pampered. He passed hundreds of planters, pots, and vases filled with various kinds of growing things, all arranged into elaborate formal patterns and rows.

Temporary flower beds. The gods were too godly to leave the court and visit the city gardens, so the gardens had to be brought to them. Such an enormous undertaking required dozens of workers and carts full of plants. Nothing was too good for the gods.

Except, of course, freedom.

Blushweaver stood admiring one of the patterns of vases. She noticed Lightsong as he approached, his moving BioChroma successively making the flowers shine more vibrantly in the afternoon sunlight. She was wearing a surprisingly modest dress. It had no sleeves and appeared to be made entirely of a single wrapping of green silk, but it covered up the essential bits and then some.

“Lightsong, dear,” she said, smiling. “Visiting a lady in her home? How charmingly forward. Well, enough of this small talk. Let us retire to the bedroom.”

He smiled, holding up a sheet of paper as he approached her.

She paused, then accepted it. The front was covered with colored dots—the artisans’ script. “What is this?” she asked.

“I figured I knew how our conversation would begin,” he said. “And so I saved us the trouble of having to go through it. I had it written out beforehand.”

Blushweaver raised an eyebrow, then read. “~‘To start, Blushweaver says something that is mildly suggestive.’~” She glanced at him. “Mildly? I invited you to the bedroom. I’d call that blatant.”

“I underestimated you,” Lightsong said. “Please continue.”

“~‘Then Lightsong says something to deflect her,’~” Blushweaver read. “~‘It is so incredibly charming and clever that she is left stunned by his brilliance and cannot speak for several minutes~.~.~.’ Oh, honestly, Lightsong. Do I have to read this?”

“It’s a masterpiece,” he said. “Best work I’ve ever done. Please, the next part is important.”

She sighed. “~‘Blushweaver says something about politics which is dreadfully boring but she offsets it by wiggling her chest. After that, Lightsong apologizes for being so distant lately. He explains that he had some things to work out.’~” She paused, eyeing him. “Does this mean that you’re finally ready to be part of my plans?”

He nodded. To the side, a group of gardeners removed the flowers. They returned in waves, building a pattern of small blossoming trees in large pots around Blushweaver and Lightsong, a living kaleidoscope with the two Returned gods at its center.

“I don’t think that the queen is involved in a plot to take the throne,” Lightsong said. “Although I’ve spoken with her only briefly, I am convinced.”

“Then why agree to join with me?”

He stood quietly for a moment, enjoying the blossoms. “Because,” he said. “I intend to see that you don’t crush her. Or the rest of us.”

“My dear Lightsong,” Blushweaver said, pursing bright red lips. “I assure you that I’m harmless.”

He raised an eyebrow. “I doubt that.”

“Now, now,” she said, “you should never point out a lady’s departure from strict truth. Anyway, I’m glad you came. We have work to do.”

“Work?” he said. “That sounds like~.~.~. work.”

“Of course, dear,” she said, walking away. Gardeners immediately ran forward, pulling aside the small trees to clear a path for them. The master gardener himself stood by directing the evolving composition like the conductor of a botanical orchestra.

Lightsong hurried and caught up. “Work,” he said. “Do you know what my philosophy on that word is?”

“I have somehow gotten the subtle impression that you do not approve of it,” Blushweaver said.

“Oh, I wouldn’t say that. Work, my dear Blushweaver, is like fertilizer.”

“It smells?”

He smiled. “No, I was thinking that work is like fertilizer in that I’m glad it exists; I just don’t ever want to get stuck in it.”

“That’s unfortunate,” Blushweaver said. “Because you just agreed to do so.”

He sighed. “I thought I smelled something.”

“Don’t be tedious,” she said, smiling to some workers as they lined her path with vases of flowers. “This is going to be fun.” She turned back to him, eyes twinkling. “Mercystar got attacked last night.”

\orn

“Oh, my dear Blushweaver. It was positively~\textit{tragic}.”

Lightsong raised an eyebrow. Mercystar was a gorgeously voluptuous woman who offered a striking contrast with Blushweaver. Both were, of course, perfect examples of feminine beauty. Blushweaver was simply the slim—yet busty—type while Mercystar was the curvaceous—yet busty—type. Mercystar lounged back on a plush couch, being fanned with large palm leaves by several of her serving men.

She didn’t have Blushweaver’s subtle sense of style. There was a skill to choosing bright clothing that didn’t edge into garishness. Lightsong himself didn’t have it—but he had servants who did. Mercystar, apparently, didn’t even know such a skill existed.

\textit{Though admittedly,}~he thought,~\textit{orange and gold aren’t exactly the easiest colors to wear with dignity.}

“Mercystar, dear,” Blushweaver said warmly. One of the servants provided a cushioned stool, sliding it beneath Blushweaver just as she sat at Mercystar’s elbow. “I can understand how you must feel.”

“Can you?” Mercystar asked. “Can you possibly? This is terrible. Some~.~.~. some\textit{miscreant}~snuck into my palace, accosting my servants! The very home of a goddess! Who would do such a thing?”

“Indeed, he must have been deranged,” Blushweaver said soothingly. Lightsong stood beside her, smiling sympathetically, hands clasped behind his back. A cool afternoon breeze blew across the courtyard and through the pavilion. Some of Blushweaver’s gardeners had brought over flowers and trees, surrounding the pavilion’s canopy, filling the air with their mingled perfumes.

“I can’t understand it,” Mercystar said. “The guards at the gates are supposed to prevent these kinds of things! Why do we have walls if people can just walk in and violate our homes? I just don’t feel safe anymore.”

“I’m certain the guards will be more diligent in the future,” Blushweaver said.

Lightsong frowned, glancing toward Mercystar’s palace, where servants buzzed about like bees around a disturbed hive. “What was the intruder after, do you suppose?” he said, almost to himself. “Works of art, perhaps? Surely there are merchants who would be much easier to rob.”

“We may not know what they want,” Blushweaver said smoothly, “but we at least know\textit{something}~about them.”

“We do?” Mercystar said, perking up.

“Yes, dear,” Blushweaver said. “Only someone with no respect for tradition, propriety, or religion would dare trespass in the home of a god. Someone base. Disrespectful. Unbelieving~.~.~.”

“An Idrian?” Mercystar asked.

“Did you ever wonder, dear,” Blushweaver said, “why they sent their~\textit{youngest}~daughter to the God King instead of their eldest?”

Mercystar frowned. “They did?”

“Yes, dear,” Blushweaver said.

“That is rather suspicious, now, isn’t it?”

“Something is going on in the Court of Gods, Mercystar,” Blushweaver said, leaning over. “These could be dangerous times for the Crown.”

“Blushweaver,” Lightsong said. “A word, if you please?”

She eyed him in annoyance. He met her gaze steadily, which eventually caused her to sigh. She patted Mercystar’s hand and then retreated from the pavilion with Lightsong, their servants and priests trailing behind.

“What are you doing?” Lightsong said as soon as they were out of Mercystar’s hearing.

“Recruiting,” Blushweaver said, a glint in her eye. “We’re going to need her Lifeless Commands.”

“I’m still not myself persuaded that we will need them,” Lightsong said. “War may not be necessary.”

“As I said,” Blushweaver replied, “we need to be careful. I’m just making preparations.”

“All right,” he said. There was a wisdom to that. “But we don’t know that it was an Idrian who broke into Mercystar’s palace. Why are you implying that it was?”

“And you think it’s just coincidence? Someone sneaks into one of our palaces~\textit{now,}~with the war approaching?”

“Coincidence.”

“And the intruder just~\textit{happened}~to pick one of the four Returned who hold Lifeless access Commands? If I were going to go to war with Hallandren, the first thing I’d do would be try to search out those commands. Maybe see if they were written down anywhere, or perhaps try to kill the gods who held them.”

Lightsong glanced back at the palace. Blushweaver’s arguments held some merit, but they weren’t enough. He had an odd impulse to look into this more deeply. However, that sounded like work. He really couldn’t afford to make an exception to his usual habits, particularly without a lot of complaining first. It set a poor pre cedent. So he just nodded his head, and Blushweaver led them back to the pavilion.

“Dear,” Blushweaver said, quickly sitting back beside Mercystar and looking a little bit more anxious. She leaned in. “We’ve talked it over and decided to trust you.”

Mercystar sat up. “Trust me? With what?”

“Knowledge,” Blushweaver whispered. “There are those of us who fear that the Idrians aren’t content with their mountains and are determined to control the lowlands as well.”

“But we’ll be joined by blood,” Mercystar said. “There will be a Hallandren God King with royal blood on our throne.”

“Oh?” Blushweaver said. “And could that not also be interpreted as an~\textit{Idrian}~king with Hallandren blood on the throne?”

Mercystar wavered. Then, oddly, she glanced at Lightsong. “Do you believe this?”

Why did people look toward him? He did everything to discourage such behavior, but they still tended to act like he was some kind of moral authority. “I think that some~.~.~. preparation would be wise,” he said. “Though, of course, the same can be said for dinner.”

Blushweaver gave him an annoyed look, though by the time she looked back at Mercystar, she had her consoling face on again. “We understand that you’ve had a difficult day,” she said. “But please, consider our offer. We would like you to join with us in our precautions.”

“What kind of precautions are you talking about?” Mercystar asked.

“Simple ones,” Blushweaver said quickly. “Thinking, talking, planning. Eventually, if we think we have enough evidence, we will bring what we know to the God King.”

This seemed to ease Mercystar’s mind. She nodded. “Yes, I can see. Preparation. It~\textit{would}be wise.”

“Rest now, dear,” Blushweaver said, rising and leading Lightsong away from the pavilion. They walked leisurely across the perfect lawn back toward Blushweaver’s own palace. He felt a reluctance to go, however. Something about the meeting bothered him.

“She’s a dear,” Blushweaver said, smiling.

“You just say that because she’s so easy to manipulate.”

“Of course,” Blushweaver said. “I positively~\textit{love}~people who do as they should. ‘Should’ being defined as whatever I think is best.”

“At least you’re open about it,” Lightsong said.

“To you, my dear, I’m as easy to read as a book.”

He snorted. “Maybe one that hasn’t been translated to Hallandren yet.”

“You just say that because you’ve never~\textit{really}~tried reading me,” she said, smiling at him. “Though, I must say that there is one thing about dear Mercystar that positively annoys me.”

“And that is?”

“Her armies,” Blushweaver said, folding her arms. “Why did~\textit{she,}~goddess of kindness, get command of ten thousand Lifeless? It’s obviously a dire error in judgment. Particularly since I don’t have command of~\textit{any}~troops.”

“Blushweaver,” he said with amusement, “you’re the goddess of honesty, communication, and interpersonal relationships. Why in the world would you be given stewardship of armies?”

“There are many interpersonal relationships related to armies,” she said. “After all, what do you call one man hitting another with a sword? That’s interpersonal.”

“Quite so,” Lightsong said, glancing back at Mercystar’s pavilion.

“Now,” Blushweaver said, “I should think that you’d appreciate my arguments, since relationships are, in fact, war. As is clear in~\textit{our}~relationship, dear Lightsong. We~.~.~.” She trailed off, then poked him in the shoulder. “Lightsong? Pay attention to me!”

“Yes?”

She folded her arms petulantly. “I must say, your banter has been decidedly off today. I may just have to find someone else to play with.”

“Hum, yes,” he said, studying Mercystar’s palace. “Tragic. Now, the break-in at Mercystar’s. It was just one person?”

“Supposedly,” Blushweaver said. “It’s not important.”

“Was anyone injured?”

“A couple of servants,” Blushweaver said with a wave of the hand. “One was found dead, I believe. You should be paying attention to~\textit{me,}~not that—”

Lightsong froze. “Someone was~\textit{killed}?”

She shrugged. “So they say.”

He turned around. “I’m going to go back and talk to her some more.”

“Fine,” Blushweaver snapped. “But you’ll do it without me. I have gardens to enjoy.”

“All right,” Lightsong said, already turning away. “I’ll talk to you later.”

Blushweaver let out a huff of indignation, her hands on her hips, watching him go. Lightsong ignored her irritation, however, more focused on~.~.~.

What? So some servants had been hurt. It wasn’t his place to be involved in criminal disturbances. And yet, he walked straight to Mercystar’s pavilion again, his servants and priests trailing behind, as ever.

She was still reclining on her couch. “Lightsong?” she asked with a frown.

“I returned because I just heard that one of your servants was killed in the attack.”

“Ah, yes,” she said. “The poor man. What a terrible occurrence. I’m sure he’s found his blessings in heaven.”

“Funny, how they’re always in the last place you consider looking,” Lightsong said. “Tell me, how did the murder happen?”

“It’s very odd, actually,” she said. “The two guards at the door were knocked unconscious. The intruder was discovered by four of my servants who were walking through the ser vice hallway. He fought them, knocked out one, killed another, and two escaped.”

“How was the man killed?”

Mercystar sighed. “I really don’t know,” she said with a wave of the hand. “My priests can tell you. I fear I was too traumatized to take in the details.”

“It would be all right if I talked to them?”

“If you must,” Mercystar said. “Have I mentioned exactly how thoroughly out of sorts I am? One would think that you’d prefer to stay and comfort me.”

“My dear Mercystar,” he said. “If you know anything of me, then you will realize that leaving you alone is by far the best comfort I can offer.”

She frowned, looking up.

“It was a joke, my dear,” he said. “I am, unfortunately, quite bad at them. Scoot, you coming?”

Llarimar, who stood—as always—with the rest of the priests, looked toward him. “Your Grace?”

“No need to upset the others any further,” Lightsong said. “I think that you and I alone will be sufficient for this exercise.”

“As you command, Your Grace,” Llarimar said. Once again, Lightsong’s servants found themselves separated from their god. They clustered uncertainly on the grass—like a group of children abandoned by their parents.

“What is this about, Your Grace?” Llarimar asked quietly as they walked up to the palace.

“I honestly have no idea,” Lightsong said. “I just feel that there’s something odd going on here. The break-in. The death of that man. Something is wrong.”

Llarimar looked at him, a strange expression on his face.

“What?” Lightsong asked.

“It is nothing, Your Grace,” Llarimar finally said. “This is just a very uncharacteristic of you.”

“I know,” Lightsong said, feeling confident about the decision nonetheless. “I honestly can’t say what prompted it. Curiosity, I guess.”

“Curiosity that outweighs your desire to avoid doing~.~.~. well, anything at all?”

Lightsong shrugged. He felt energized as he walked into the palace. His normal lethargy retreated, and instead he felt excitement. It was almost familiar. He found a group of priests chatting inside the servants’ corridor. Lightsong walked right up to them, and they turned to regard him with shock.

“Ah, good,” Lightsong said. “I assume you can tell me more of this break-in?”

“Your Grace,” one said as all three bowed their heads. “I assure you, we have everything under control. There is no danger to you or your people.”

“Yes, yes,” Lightsong said, looking over the corridor. “Is this where the man was killed, then?”

They glanced at one another. “Over there,” one of them said reluctantly, pointing to a turn in the hallway.

“Wonderful. Accompany me, if you please.” Lightsong walked up to the indicated section. A group of workers were removing the boards from the floor, probably to be replaced. Bloodstained wood, no matter how well cleaned, would not do for a goddess’s home.

“Hum,” Lightsong said. “Looks messy. How did it happen?”

“We aren’t sure, Your Grace,” said one of the priests. “The intruder knocked the men at the doorway unconscious, but did not otherwise harm them.”

“Yes, Mercystar mentioned that,” Lightsong said. “But then he fought with four of the servants?”

“Well, ‘fought’ isn’t quite the right word,” the priest said, sighing. Though Lightsong wasn’t their god, he was~\textit{a}~god. They were bound by oath to answer his questions.

“He immobilized one of them with an Awakened rope,” the priest continued. “Then, while one remained behind to delay the intruder, the other two ran for aid. The intruder quickly knocked the remaining man unconscious. At that time, the one who had been tied up was still alive.” The priest glanced at his colleagues. “When help finally came—delayed by a Lifeless animal that was causing confusion—they found the second man still unconscious. The first, still tied up, was dead. Stabbed through the heart with a dueling blade.”

Lightsong nodded, kneeling beside the broken boards. The servants who had been working there bowed their heads and retreated. He wasn’t certain what he expected to find. The floor had been scrubbed clean, then torn apart. However, there was a strange patch a short distance away. He walked over and knelt, inspecting it more closely.~\textit{Completely devoid of color,}~he thought. He looked up, focusing on the priests. “An Awakener, you say?”

“Undoubtedly, Your Grace.”

He looked back down at the grey patch.~\textit{There’s no chance an Idrian did this,}~he realized.\textit{Not if he used Awakening.}~“What was this Lifeless creature you mentioned?”

“A Lifeless squirrel, Your Grace,” one of the men said. “The intruder used it as a diversion.”

“Well made?” he asked.

They nodded. “Using modern Command words, if its actions were any judge,” one said. “It even had ichor-alcohol instead of blood. Took us the better part of the night to catch the thing!”

“I see,” Lightsong said, standing. “But the intruder escaped?”

“Yes, Your Grace,” one of them said.

“What do you suppose he was after?”

The priests wavered. “We don’t know for sure, Your Grace,” one of them said. “We scared him away before he could reach his goal—one of our men saw him fleeing back out the way he had come. Perhaps the resistance was too much for him.”

“We think that he may have been a common burglar, Your Grace,” one said. “Here to sneak into the gallery and steal the art.”

“Sounds likely enough to me,” Lightsong said, standing. “Good work with this, and all that.” He turned, walking back down the hallway toward the entrance. He felt strangely surreal.

The priests were lying to him.

He didn’t know how he could tell. Yet he did—he knew it deep inside, with some instincts he hadn’t realized he possessed. Instead of disturbing him, for some reason the lies excited him.

“Your Grace,” Llarimar said, hurrying up. “Did you find what you wanted?”

“That was no Idrian who broke in,” Lightsong said quietly as they walked into the sunlight.

Llarimar raised an eyebrow. “There have been cases of Idrians coming to Hallandren and buying themselves Breath, Your Grace.”

“And have you ever heard of one using a Lifeless?”

Llarimar fell quiet. “No, Your Grace,” he finally admitted.

“Idrians hate Lifeless. Consider them abominations, or some such nonsense. Either way, it wouldn’t make sense for an Idrian to try and get in like that. What would be the point? Assassinating a single one of the Returned? He or she would only be replaced, and the protocols in place would be certain that even the Lifeless armies weren’t without someone to direct them for long. The possibility for retaliation would far outweigh the benefit.”

“So you believe that it was a thief?”

“Of course not,” Lightsong said. “A ‘common burglar’ with enough money or Breath that he can~\textit{waste}~a Lifeless, just for a diversion? Whoever broke in, he was already rich. Besides, why sneak through the servants’ hallway? There are no valuables there. The~\textit{interior}~of the palace holds far more wealth.”

Llarimar fell quiet again. He looked over at Lightsong, the same curious expression as before on his face. “That’s some very solid reasoning, Your Grace.”

“I know,” Lightsong said. “I feel positively unlike myself. Perhaps I need to go get drunk.”

“You can’t get drunk.”

“Ah, but I certainly enjoy trying.”

They walked back toward his palace, picking up his servants on the way. Llarimar seemed unsettled. Lightsong, however, simply felt excited.~\textit{Murder in the Court of Gods,}~he thought.\textit{True, it was only a servant—but I’m supposed to be a god for all people, not just important ones. I wonder how long it’s been since someone was killed in the court? Hasn’t happened in my lifetime, certainly.}

Mercystar’s priests were hiding something. Why had the intruder released a diversion—particularly such an expensive one—if he were simply going to run away? The servants of the Returned were not formidable soldiers or warriors. So why had he given up so easily?

All good questions. Good questions that he, of all people, shouldn’t have bothered to wonder about. And yet, he did.

All the way back to the palace, through a nice meal, and even into the night.

