% \section{Chapter Forty-Two}
\chapter{}

“Her Grace is not interested in seeing you,” the priestess said, maintaining a reverent posture.

“Well I’m not interested in her uninterest,” Lightsong said. “Perhaps you should ask her again, just to be sure.”

The priestess bowed her head. “My pardons, Your Grace, but I have already asked fourteen times. Goddess Allmother is growing impatient with your requests, and she instructed me not to respond to them anymore.”

“Did she give the same command to the other priestesses?”

The priestess paused. “Well, no, Your Grace.”

“Wonderful,” Lightsong said. “Send for one of them. Then send~\textit{her}~to ask Allmother if she will see me.” The priestess sighed audibly; Lightsong considered that something of a victory. Allmother’s priests were among the most pious—and most humble—in the court. If he could annoy them, he could annoy anyone. He waited, hands on hips, as the priestess went to do his bidding. Allmother could give them orders and commands, but she couldn’t tell them to completely ignore Lightsong. After all, he was a god too. As long as he asked them to do something other than what Allmother had explicitly forbidden, they had to obey.

Even if it annoyed their goddess. “I’m developing a new skill,” Lightsong said. “Irritation by proxy!”

Llarimar sighed. “What about your speech to Goddess Blushweaver a few days ago, Your Grace? It seemed to imply that you were~\textit{not}~going to annoy people as much.”

“I said nothing of the sort,” Lightsong said. “I simply said that I was coming to recognize within myself a little more of the person I used to be. That doesn’t mean I’m going to discard all the progress I’ve made over the last few years.”

“Your sense of self-awareness is remarkable, Your Grace.”

“I know! Now, hush. The priestess is coming back.”

Indeed, the woman approached and bowed before Lightsong on the grass. “My apologies, Your Grace. Our goddess, however, has now requested that~\textit{no}~priestess be allowed to ask her if you can come in to see her.”

“Did she tell them that they couldn’t ask if she would come out here?”

“Yes, Your Grace,” the priestess said. “And every other phrasing that would imply asking her to come within Your Grace’s proximity, or communicate with him by letter, or relay messages from him in any form.”

“Hum,” he said, tapping his chin. “She’s getting better. Well, I guess there’s nothing to be done.”

The priestess relaxed visibly.

“Scoot, set up my pavilion here in front of her palace,” Lightsong said. “I’m going to be sleeping here tonight.”

The priestess looked up.

“You’re going to do~\textit{what}?” Llarimar asked.

Lightsong shrugged. “I’m not moving until I meet with her. That means staying until she acknowledges me. It’s been over a week! If she wants to be stubborn, then I’ll prove that I can be~\textit{equally}~stubborn.” He eyed the priestess. “I’m quite practiced at it, you know. Comes from being an insufferable buffoon, and all. I don’t suppose she forbade you from allowing squirrels into the building?”

“Squirrels, Your Grace?” the woman asked.

“Excellent,” Lightsong said, sitting down as his servants erected the pavilion. He pulled the Lifeless squirrel from its box and held it forward.

“Almond grass,” he said quietly, giving the new Command he’d had his people imprint on the Lifeless. Then he spoke louder, so that the priestess could hear. “Go into the building, search out the Returned who lives in it, and run around in circles squeaking as loudly as you can. Don’t let anyone catch you. Oh, and destroy as much furniture as you can.” Then, more quietly, he repeated, “Almond grass.”

The squirrel immediately jumped off his hand and shot toward the palace. The priestess twisted her head to follow it, horrified. The squirrel began to screech with a sound that seemed amazingly un-squirrel-like. It disappeared into the building, slipping between the legs of a startled guard.

“What a delightful afternoon it’s becoming,” Lightsong said, reaching for a handful of grapes as the priestess rushed after the squirrel.

“It won’t be able to follow all of those orders, Your Grace,” Llarimar said. “It has the mind of a squirrel, despite the power that Breath gives it to obey Commands.”

Lightsong shrugged. “We shall see.”

He began to hear shouts of annoyance from inside the palace. He smiled.

It took longer than he had expected. Allmother was stubborn, as proved by Blushweaver’s complete inability to manipulate her. As he sat—idly listening to a group of musicians—a priestess occasionally checked on him. Several hours passed. He didn’t eat or drink very much so he didn’t need to visit the privy.

He ordered his musicians to play louder. He had picked a group with a lot of percussion.

Finally, a frazzled-looking priestess came out of the palace. “Her Grace will see you,” the woman said, bowing before Lightsong.

“Hum?” Lightsong said. “Oh, that. Do I have to go now? Can’t I finish listening to this song?”

The priestess glanced up. “I—”

“Oh, very well then,” Lightsong said, rising.

\orn

Allmother was still in her audience chamber. Lightsong hesitated in the doorway—which, like those in every palace, was designed at the godly scale. He frowned to himself.

People still waited in a line and Allmother sat on a throne at the front of the room. She was stocky for a goddess, and he had always considered her white hair and wrinkled face an oddity within the pantheon. In bodily age, she was the oldest of the gods.

It had been a while since he’d come to visit her. In fact~.~.~.~\textit{The last time I was here was the night before Calmseer gave up her Breath,}~he realized.~\textit{That evening, years ago, when we shared what would be her last meal.}

He’d never come back. What would have been the point? They’d only gotten together in the first place because of Calmseer. On most of those occasions, Allmother had been quite vocal about what she thought of Lightsong. At least she was honest.

That was more than he could say for himself.

She didn’t acknowledge him as he entered. She continued to sit, a little stooped over, listening to the man presenting his petition. He was middle-aged and stood awkwardly, leaning on a walking staff.

“. . . my children are starving now,” he said. “I cannot afford the food. I figured if my leg worked, I could go back to the docks.” He looked down.

“Your faith is commendable,” Allmother said. “Tell me, how did you lose the use of your leg?”

“A fishing accident, Your Grace,” the man said. “I came down from the highlands a few years back, when early frosts took my crops. I took a job on one of the stormrunners—the ships who go out during the spring tempests, catching fish when others remain in the harbor. The accident crushed a barrel against me leg. Nobody will take me on to work the boats, not with a lame leg.”

Allmother nodded.

“I wouldn’t have come to you,” he said. “But with my wife sick and my daughter crying with such hunger~.~.~.”

Allmother reached a hand out, laying it on the man’s shoulder. “I understand your difficulties, but your problems are not as severe as you may think. Go and speak with my high priest. I have a man on the docks who owes me allegiance. You have two good hands; you will be put to work sewing nets.”

The man looked up, hope glimmering in his eyes.

“We will send you back with enough food to care for your family until you learn your new trade,” Allmother said. “Go with my blessing.”

The man rose, then fell back to his knees and began to cry. “Thank you,” he whispered. “Thank you.”

Priests walked forward and led the man away. The room fell still, and Allmother looked over, meeting Lightsong’s eyes. She nodded to the side, where a priest stepped up, holding a small bundle of fur tied tightly with ropes.

“That is yours, I am told?” Allmother asked.

“Ah, yes,” Lightsong said, flushing slightly. “Terribly sorry. It kind of got away from me.”

“With an accidental Command to find me?” Allmother asked. “Then run around in circles screaming?”

“That actually worked?” Lightsong said. “Interesting. My high priest didn’t think the squirrel’s brain would be capable of following such complicated Commands.”

Allmother regarded him with a stern look.

“Oh,” Lightsong said. “I mean, ‘Whoops. It completely misunderstood me. Stupid squirrel.’ My deepest apologies, honored sister.”

Allmother sighed, then waved toward a doorway on the side of the room. Lightsong walked that way and she followed, a few servants trailing. Allmother moved with the stiffness of age.~\textit{Is it me, or does she look older than she did before?}~That was, of course, impossible. Returned did not age. At least, not the ones who had reached maturity.

Once they were out of earshot and view of the petitioners, Allmother grabbed his arm. “What in the name of the Colors do you think you are doing?” she snapped.

Lightsong turned, raising an eyebrow. “Well, you wouldn’t see me, and—”

“Do you intend to destroy what little authority we have left, you idiot?” Allmother asked. “Already, people in the city are saying that the Returned are growing weak, that the best of us died years ago.”

“Maybe they’re right.”

Allmother scowled. “If too many of them believe that, then we lose our access to Breaths. Have you considered that? Have you considered what your lack of decorum, your flippancy, could cost all of us?”

“Is that the reason for the show then?” he asked, glancing back through the doorway.

“Once, the Returned didn’t just listen to petitions and say yes or no,” Allmother said. “They would take the time to hear each person who came to them, then seek to help them as best they could.”

“Seems like an awful lot of trouble.”

“We’re their~\textit{gods.}~Should a bit of trouble deter us?” She eyed him. “Oh, of course. We wouldn’t want to let something as simple as the pains of our people interfere with our leisure time. Why am I even talking to you?” She turned to leave the room.

“I came to give you my Lifeless Commands,” Lightsong said.

Allmother froze.

“Blushweaver has control of two sets of the Commands,” Lightsong said, “which gives her control of half of our armies. That worries me. I mean, I trust her as much as I trust any other Returned. But if war does come, then she’ll quickly become the second-most-powerful person in the kingdom. Only the God King would have more authority.”

Allmother regarded him with an unreadable expression.

“I figure that the best way to counter her is to have someone else who has two sets of Commands,” Lightsong said. “Perhaps it will give her pause. Keep her from doing anything rash.”

There was silence in the room.

“Calmseer trusted you,” Allmother finally said.

“Her one flaw, I must profess,” Lightsong said. “Even goddesses have them, or so it seems. I’ve found it gentlemanly to never point out such things.”

“She was the best of us,” Allmother said, glancing out in the direction of her supplicants. “She would meet with people all day. They loved her.”

“Bottom line blue,” Lightsong said. “That’s my core security phrase. Please, take it. I’ll tell Blushweaver that you bullied me into giving it to you. She’ll be angry at me, of course, but it won’t be the first time.”

“No,” Allmother finally said. “No, I’m not letting you out of this so easily, Lightsong.”

“What?” he asked, startled.

“Can’t you feel it?” she asked. “Something is happening in the city. This mess with the Idrians and their slums, the increasingly fierce arguments among our priests.” She shook her head. “I’m not letting you wiggle out of your part. You were chosen for that place of yours. You’re a god, like the rest of us, even if you do your best to pretend otherwise.”

“You already have my Command, Allmother,” he said with a shrug, walking toward a doorway to leave. “Do what you will with it.”

“Verdant bells,” Allmother said. “That’s mine.”

Lightsong froze in midstep.

“Now two of us know both of them,” Allmother said. “If what you said earlier was true, then it’s better that our Commands be distributed.”

He spun. “You were just calling me a fool! Now you entrust me with command of your soldiers? I must ask, Allmother, and please think me not rude. But what in the name of the~\textit{Colors}~is wrong with you?”

“I dreamed that you would come,” she said, meeting his gaze. “I saw it in the pictures a week ago. All week, I’ve seen patterns of circles in the paintings, all red and gold. Your colors.”

“Coincidence,” he said.

She snorted quietly. “Someday, you’ll have to get over your foolish selfishness, Lightsong. This isn’t just about us. I’ve decided to start doing a better job of things. Perhaps you should take a look at who you are and what you are doing.”

“Ah, my dear Allmother,” Lightsong said. “You see, the problem in that challenge is the presumption that I haven’t~\textit{tried}~to be something other than what I am. Every time I do, disaster is the result.”

“Well, you now have my Commands. For better, or for worse.” The aged goddess turned away, walking back toward her room of supplicants. “I, for one, am curious to see how you handle them.”

