% \section{Chapter Forty-One}
\chapter{}

Vivenna presented her coin.

“One bit?” Cads asked. “That’s all? One~\textit{single}~bit?” He was among the dirtiest men she’d met, even in the streets. He liked fancy clothing, though. It was his style—worn and dirty clothing in the latest designs. He seemed to think it was funny. A mockery of the highborn.

He turned her coin over in his grime-covered fingers. “One bit,” he repeated.

“Please,” Vivenna whispered. They stood at the mouth of an alley at the back of two restaurants. Just inside the alley, she could see urchins rooting in the garbage. Fresh garbage from~\textit{two}~restaurants. She salivated.

“I find it hard to believe, lady girly,” he said, “that~\textit{this}~is all you made today.”

“Please, Cads,” she said again. “You know~.~.~. you know I don’t beg well.” It was starting to rain. Again.

“You should do better,” he said. “Even the children can bring me at least two.”

Behind him, the fortunates who had pleased him continued to feast. It smelled so good. Or maybe that was the restaurants.

“I haven’t eaten in days,” she whispered, blinking away the rain.

“Then do better tomorrow,” he said, shooing her away.

“My coin—”

Cads immediately waved for his toughs as she reached toward him. Vivenna shied away reflexively, stumbling.

“Two tomorrow,” Cads said, walking into his alleyway. “I have to pay the restaurant owners, you know. Can’t let you eat for free.”

Vivenna stood, staring at him. Not because she thought she could get him to change his mind. But because she just had trouble making her mind understand. It was her last chance for food this day. One bit wouldn’t buy anything more than a mouthful elsewhere, but here—last time—it had allowed her to eat until she was full.

That had been a week ago. How long had she been on the streets now? She didn’t know. She turned, dully, and pulled her shawl tight. It was dusk. She should go beg some more.

She couldn’t. Not after losing that bit. She felt shaken, as if her most valuable possession had been stolen.

No.~\textit{No.}~She still had that. She pulled the shawl close.

Why was it important? She had trouble remembering.

She shuffled back toward the Highlands. Her home. A part of her realized that she shouldn’t feel so distant from the person she had been. She was a princess, wasn’t she? But she felt so sick lately, sick enough that she didn’t even think she could feel the hunger anymore. It was all so wrong. So very, very wrong.

She entered the slums and crept along, careful to keep her head bowed, her back cowed, lest someone take offense at her. She hesitated as she walked, however, passing a street to her right. It was where the whores waited, protected from the drizzle by an awning.

Vivenna stared at them, standing in their revealing clothing. It was only two streets into the slum, a place that wasn’t too threatening for outsiders. Everyone knew not to rob a man on his way to visit the whores. The slumlords didn’t like it when their customers got scared away. Bad for business, as Denth might say.

Vivenna stood for a long moment. The whores looked fed. They weren’t dirty. Several of them laughed. She could join them. An urchin had spoken of it the other day, mentioned that she was still young. He’d wanted her to come to the slumlord with him, hoping to get some coin for recruiting a willing girl.

It was so tempting. Food. Warmth. A dry bed.

\textit{Blessed Austre,}~she thought, shaking herself.~\textit{What am I thinking? What is wrong with my mind?}~It was so hard to focus. As if she were in a trance all the time.

She forced herself to keep moving, stumbling away from the women. She wouldn’t do that. Not yet.

Not yet.

\textit{Oh, Lord of Colors,}~she thought with horror.~\textit{I need to get out of this city. Better for me to die, starving on the road back to Idris—better to get taken by Denth and tortured—than to end up in the brothel.}

However, much like the morality of stealing, the morality of using her body seemed much vaguer to her now, when her hunger was such a constant need. She made her way to her latest alleyway. She’d been kicked out of the others. But this one was good. It was secluded, yet often filled with younger urchins. Their company made her feel better, though she knew they searched her at night for coins.

\textit{I can’t believe how tired I am~.~.~.}~she thought, head spinning, putting her hand against the wall. She took a few deep breaths. The dizzy spells struck often these days.

She started forward again. The alleyway was empty, everyone else staying out in the evening to try for a few extra coins. She took the best of the spots—an earthen mound which had managed to grow a small tuft of grass. There weren’t even that many lumps in the dirt, though it would be wet with mud from the light rain. She didn’t care about that.

Shadows darkened the alleyway behind her.

Her reaction was immediate. She started to run. Living on the streets taught quick lessons. Weak as she was, in her panic she managed a burst of speed. Then another shadow stepped across the other end of the alley ahead of her. She froze, then turned to see a group of thugs moving up the alleyway behind her.

At their back was the man who had robbed her a few weeks ago, the one who had taken her dress. He looked chagrined. “Sorry, Princess,” he said. “Bounty just got too high. Took me blasted long enough to find you, though. You did a great job of hiding.”

Vivenna blinked. And then she simply let herself slide down to the ground.

\textit{I just can’t take any more,}~she thought, wrapping her arms around herself. She was exhausted. Mentally, emotionally, completely. In a way, she was glad it was over. She didn’t know what the men would do to her, but she did know it was over. Whomever they sold her to wouldn’t be careless enough to let her escape again.

The thugs clustered around her. She heard one mention taking her to Denth. Rough hands grabbed her arm, towing her to her feet. She followed with head bowed. They led her out onto the main street. It was growing dim, but no urchins or beggars made their way toward the alley.

\textit{I should have realized,}~she thought.~\textit{It was too deserted.}

Everything, finally, overwhelmed her. She couldn’t summon the energy to care about escaping, not again. A part of her, deep inside, realized that her tutors had been right. When you were weak and hungry, it was hard to summon the energy to care about anything, even escape.

She had trouble remembering her tutors now. She had trouble even remembering what it was like to not be hungry.

The thugs stopped walking. Vivenna looked up, blinking away her dizziness. There was something in the dark, wet street in front of them. A black sword. The weapon, silver sheath and all, had been rammed into the dirt.

The street grew still. One of the thugs stepped forward, pulling the sword from the ground. He undid the sheath clasp. Vivenna felt a sudden nausea, more of a memory than a real sensation. She stumbled back, horrified.

The other thugs, transfixed, gathered up around their friend. One of them reached for the hilt.

The man carrying the sword struck. He swung the weapon, sheath and all, into the face of his friend. A black smoke began to twist off the sword, rising from the tiny sliver of blade that was visible.

Men cried out, each one scrambling for the sword. The man holding it continued to swing, the weapon hitting with far more force and damage than it should have. Bones broke, blood began to run on the cobblestones. The man continued to attack, moving with terrible speed. Vivenna, still stumbling backward, could see his eyes.

They were terrified.

He killed his last friend—the one who had robbed her on that day that now seemed so long ago—by slamming the sheathed sword down against the man’s back. Bones cracked. By now, the clothing on the sword wielder’s arm had disintegrated, and a blackness—like vines growing on a wall—had twisted up around his shoulder. Black, pulsing veins that bulged out of the skin. The man screamed a piercing, desperate cry.

Then he twisted the sword around and rammed it, sheath and all, through his chest. It cut skin and flesh, though the sheath itself didn’t look sharpened. The man stumbled to his knees, then slumped backward, twitching, staring up into the air as the black veins on his arm began to evaporate. He died like that, kneeling, held upright by the sword that came out through his back, propping him up from behind.

Vivenna stood alone on a street littered with corpses. A figure descended from a rooftop, lowered by two twisting lengths of animated rope. He landed softly, ropes falling dead. He passed Vivenna, ignoring her, and grabbed the sword. He paused for a moment, then did up the clasp and pulled the weapon—sheath and all—free from the corpse.

The dead man finally fell to the ground.

Vivenna stared dully ahead. Then, numb, she sat down in the street. She didn’t even flinch as Vasher picked her up and slung her over his shoulder.

