% \section{Chapter Thirty-Three}
\chapter{}

Jewels worked quietly, ignoring Vivenna and pulling another stitch tight. Clod’s guts—intestines, stomach, and some other things Vivenna didn’t want to identify—lay on the floor beside him, carefully pulled out and arranged so that they could be repaired. Jewels was working on the intestines at the moment, sewing with a special thick thread and curved needle.

It was gruesome. And yet it didn’t really affect Vivenna, not after the shock she’d had earlier. They were in the safe house. Tonk Fah had gone to scout the regular house to see if Parlin was all right. Denth was downstairs, fetching something.

Vivenna sat on the floor. She’d changed to a long dress, purchased on the way—her skirt was filthy from its time in the mud—and she sat with legs pulled up against her chest. Jewels continued to ignore Vivenna, working atop a sheet on the floor. She was muttering to herself, still angry. “Stupid thing,” Jewels said under her breath. “Can’t believe we let you get hurt like this just to protect~\textit{her.}”

Hurt. Did that even mean anything to a creature like Clod? He was awake; she could see that his eyes were open. What was the point of sewing up his insides? Would they heal? He didn’t need to eat. Why bother with intestines? Vivenna shivered, looking away. She felt, in a way, as if her own insides had been ripped out. Exposed. For the world to see.

Vivenna closed her eyes. Hours later, and she was~\textit{still}~shaking from the terror of huddling in that alleyway, thinking that she’d be dead in a moment. What had she learned about herself when finally threatened? Modesty had meant nothing—she’d pulled off her skirt rather than let it trip her again. Her hair had meant nothing; she’d ignored it as soon as the danger arrived. Her religion, apparently, meant nothing. Not that she’d been able to use the Breath—she hadn’t even managed to commit blasphemy successfully.

“I’m half-tempted to just leave,” Jewels muttered. “You and I. Go away.”

Clod began to shuffle, and Vivenna opened her eyes to see him trying to stand up, even though his insides were hanging out.

Jewels swore. “Lie back down,” she hissed, barely audible. “Colorscursed thing. Howl of the sun. Go inactive. Howl of the sun.”

Vivenna watched as Clod lay down and then stopped moving.~\textit{They might obey commands,}~she thought.~\textit{But they aren’t very smart. It tried to walk out, obeying Jewels’s apparent Command to “go away.”}~And what was that nonsense Jewels had said about the sun? Was that one of the security phrases Denth had mentioned?

Vivenna heard footsteps on the stairs leading down to the cellar, and then the door opened and Denth appeared. He closed the door, then came over and handed Jewels something that looked like a large wineskin. The woman took it and immediately turned back to her work.

Denth walked over and sat down beside Vivenna.

“They say a man doesn’t know himself until he faces death for the first time,” he said in a conversational tone. “I don’t know about that. It seems to me that the person you are when you’re about to die isn’t as important as the person you are during the rest of your life. Why should a few moments matter more than an entire lifetime?”

Vivenna didn’t respond.

“Everyone gets scared, Princess. Even brave men sometimes run the first time they see battle. In armies, that’s why there’s so much training. The ones who hold aren’t the courageous ones, they’re the well-trained ones. We have instincts like any other animal. They take over sometimes. That’s all right.”

Vivenna continued to watch as Jewels carefully placed the intestines back into Clod’s belly. She took out a small package and removed something that looked like a strip of meat.

“You did well, actually,” Denth said. “Kept your wits about you. Didn’t freeze. Found the quickest way out. I’ve protected some people who will just stand there and die unless you shake them and force them to run.”

“I want you to teach me Awakening,” Vivenna whispered.

He started, glancing at her. “Do you~.~.~. want to think about that a bit first?”

“I have,” she whispered, arms around knees, chin resting against them. “I thought I was stronger than I am. I thought I’d rather die than use it. That was a lie. In that moment, I would have done~\textit{anything}~to survive.”

Denth smiled. “You’d make a good mercenary.”

“It’s wrong,” she said, still staring forward. “But I can’t claim to be pure anymore. I might as well understand what I have. Use it. If that damns me, then so be it. At least it will have helped me survive long enough to destroy the Hallandren.”

Denth raised an eyebrow. “You want to~\textit{destroy}~them now, eh? No more simple sabotage and undermining?”

She shook her head. “I want this kingdom overthrown,” she whispered. “Just like the slumlords said. It can corrupt those poor people. It can corrupt even me. I hate it.”

“I—”

“No, Denth,” Vivenna said. Her hair bled to a deep red, and for once she didn’t care. “I\textit{really}~hate it. I’ve always hated this people. They took my childhood. I had to prepare. Become their queen. Get ready to marry their God King. Everyone said he was unholy and a heretic. Yet\textit{I}~was supposed to have sex with him!

“I hate this entire city, with its colors and its gods! I hate the fact that it stole away my life, then demanded that I leave behind all that I love! I hate the busy streets, the placating gardens, the commerce, and the suffocating weather.

“I hate their arrogance most of all. Thinking they could push my father around, force him into that treaty twenty years ago. They’ve controlled my life. Dominated it.~\textit{Ruined}~it. And now they have my sister.”

She drew in a deep breath through gritted teeth.

“You’ll have your vengeance, Princess,” Denth whispered.

She looked at him. “I want them to hurt, Denth. The attack today wasn’t about subduing a rebellious element. The Hallandren sent those soldiers in to kill. Kill the poor that~\textit{they}~created. We’re going to stop them from doing things like that. I don’t care what it takes. I’m tired of being pretty and nice and ignoring ostentation. I want to~\textit{do}~something.”

Denth nodded slowly. “All right. We’ll change course, start making our attacks a little more painful.”

“Good,” she said. She squeezed her eyes shut, feeling frustrated, wishing that she was strong enough to keep all of these emotions away. But she wasn’t. She’d kept them in too long. That was the problem.

“This was never about your sister, was it?” Denth asked. “Coming here?”

She shook her head, eyes still shut.

“Why, then?”

“I had trained all of my life,” she whispered. “I was the one who would sacrifice herself. When Siri left in my place, I became nothing. I had to come and get it back.”

“But you just said that you’ve always hated Hallandren,” he said, sounding confused.

“I have. And I do. That’s why I had to come.”

He was silent for a few moments. “Too complicated for a mercenary, I guess.”

She opened her eyes. She wasn’t sure if she understood, either. She’d always kept a firm grip on her hatred, only letting it manifest in disdain for Hallandren and its ways. She confronted the hatred now. Acknowledged it. Somehow, Hallandren could be loathsome yet enticing at the same time. It was as if~.~.~. she knew that until she came and saw the place for herself, she wouldn’t have a real focus—a real understanding, a real image—of what it was that had destroyed her life.

Now she understood. If her Breaths would help, then she would use them. Just like Lemex. Just like those slumlords. She wasn’t above that. She never had been.

She doubted Denth would understand. Instead, Vivenna nodded toward Jewels. “What is she doing?”

Denth turned. “Attaching a new muscle,” he said. “One of the ones in his side got cut, sheared right through. Muscles won’t work right if you just sew them together. She has to replace the whole thing.”

“With screws?”

Denth nodded. “Right into the bone. It works all right. Not perfectly, but all right. No wound can ever be~\textit{perfectly}~fixed on a Lifeless, though he will heal some. You just sew them up and pump them full of fresh ichor-alcohol. If you fix them enough times, the body will stop working right and you’ll have to spend another Breath to keep them going. By then, it’s usually just best to buy another body.”

Saved by a monster. Perhaps that was what made her so determined to use her Breath. She should be dead, but Clod had saved her. A Lifeless. She owed her life to something that should not exist. Even worse, if she looked deep within herself, she found herself feeling a traitorous pity for the thing. Even an affection. Considering that, she figured that she was already damned to the point where using her Breaths wouldn’t matter.

“He fought well,” she whispered. “Better than the Lifeless that the city guard was using.”

Denth glanced at Clod. “They’re not all equal. Most Lifeless, they’re just made out of whatever body happens to be around. If you pay good money, you can get one who was very skillful in life.”

She felt a chill, remembering then that moment of humanity she’d seen on Clod’s face as he defended her. If an undead monstrosity could be a hero, then a pious princess could blaspheme. Or was she still just trying to justify her actions?

“Skill,” she whispered. “They keep it?”

Denth nodded. “Some semblance of it, at least. Considering what we paid for this guy, he must have been quite the soldier. And that’s why it’s worth the money, time, and trouble to repair him, rather than buy a new Lifeless.”

\textit{They treat him just like a thing,}~Vivenna thought. Just as she should. And yet, more and more, she thought of Clod as a “he.” He had saved her life. Not Denth, not Tonk Fah. Clod. It seemed to her that they should show more respect for him.

Jewels finished with the muscles, then sewed the skin closed with a thick string.

“Though he’ll kind of heal,” Denth said, “it’s best to use something strong in the repair, so the wound doesn’t rip apart again.”

Vivenna nodded. “And the~.~.~. juice.”

“Ichor-alcohol,” Denth said. “Discovered by the Five Scholars. Wonderful stuff. Keeps a Lifeless going really well.”

“That’s what let the Manywar occur?” she whispered. “Getting the mixture right?”

“That’s part of it. That and the discovery—again by one of the Five Scholars, I forget which one—of some new Commands. If you really want to be an Awakener, Princess, that’s what you have to learn. The Commands.”

She nodded. “Teach me.”

To the side Jewels got out a small pump and attached a small hose to a little valve at the base of Clod’s neck. She began to pump the ichor-alcohol, moving the pump very slowly, probably in order to keep from bursting the blood vessels.

“Well,” Denth said, “there are a~\textit{lot}~of Commands. If you want to bring a rope to life—like that one you tried to use back in the alleyway—a good Command is ‘hold things.’ Speak it with a clear voice, willing your Breath to act. If you do it right, the rope will grab whatever is closest. ‘Protect me’ is another good one, though it can be interpreted in fairly strange ways if you don’t imagine exactly what you want.”

“Imagine?” Vivenna asked.

He nodded. “You have to form the Command in your head, not just speak it. The Breath you give up, it’s part of your life. Your soul, you Idrians would say. When you Awaken something, it becomes part of you. If you’re good—and practiced—the things you Awaken will do what you expect of them. They’re part of you. They understand, just like your hands understand what you want them to do.”

“I’ll start practicing, then,” she said.

He nodded. “You should pick it up fairly quickly. You’re a clever woman, and you have a lot of Breaths.”

“That makes a difference?”

He nodded, looking somewhat distant. As if distracted by his own thoughts. “The more Breaths you hold when you start, the easier it is for you to learn how to Awaken. It’s like~.~.~. I don’t know, the Breath is more part of you. Or you’re more part of it.”

She sat back, contemplating that. “Thank you,” she finally said.

“What? For explaining Awakening? Half the children on the streets could have told you that much.”

“No,” she said. “Though I appreciate the instruction, the thanks is for other things. For not condemning me as a hypocrite. For being willing to change plans and take risks. For protecting me today.”

“Last I checked, those were all the things a good employee should do. At least if that employee is a mercenary.”

She shook her head. “It’s more than that. You’re a good man, Denth.”

He met her eyes, and she could see something in them. An emotion she couldn’t describe. Again, she thought of the mask he wore—the persona of the laughing, joking mercenary. That man seemed just a front, when she looked into those eyes, and saw so much more.

“A good man,” he said, turning away. “Sometimes, I wish that were still true, Princess. I haven’t been a good man for some years now.”

She opened her mouth to reply, but something made her hesitate. Outside, a shadow passed the window. Tonk Fah entered a few moments later. Denth stood up without glancing at her. “Well?” he asked Tonk Fah.

“Looks safe,” Tonk Fah said, eyeing Clod. “How’s the stiff?”

“Just finished,” Jewels said. She leaned down, saying something very soft to the Lifeless. Clod started moving again, sitting up, looking about. Vivenna waited as his eyes passed over her, but there didn’t seem to be recognition in them. He wore the same dull expression.

\textit{Of course,}~Vivenna thought, standing.~\textit{He’s Lifeless, after all.}~Jewels had said something to make him start working again. It was probably the same thing Jewels had used to make him stop moving in the first place. That odd phrase~.~.~.

Howl of the sun. Vivenna filed it away, then followed as they left the building.

\orn

A short time later, they were home. Parlin rushed out, expressing his fears for their safety. He went to Jewels first, though she brushed him off. As Vivenna entered the building, he moved up to her. “Vivenna? What happened?”

She just shook her head.

“There was fighting,” he said, following her up the stairs. “I heard about it.”

“There was an attack on the camp we visited,” Vivenna said wearily, reaching the top of the stairs. “A squad of Lifeless. They started killing people.”

“Lord of Colors!” Parlin said. “Is Jewels all right?”

Vivenna flushed, turning on the landing, looking down the stairs toward him. “Why do you ask about~\textit{her}~?”

Parlin shrugged. “I think she’s nice.”

“Should you be saying things like that?” Vivenna asked, noticing halfheartedly that her hair was turning red again. “Aren’t you engaged to~\textit{me}?”

He frowned. “You were engaged to the God King, Vivenna.”

“But you know what our fathers wanted,” she said, hands on hips.

“I did,” Parlin said. “But, well, when we left Idris, I figured we were both going to get disinherited. There’s really no reason to keep up the charade.”

\textit{Charade?}

“I mean, let’s be honest, Vivenna,” he said, smiling. “You really haven’t ever been that nice to me. I know you think I’m stupid; I guess you’re probably right. But if you really cared, I figured that you wouldn’t make me~\textit{feel}~stupid, too. Jewels grumbles at me, but she laughs at my jokes sometimes. You’ve never done that.”

“But~.~.~.” Vivenna said, finding herself at a slight loss for words. “But why did you follow me down to Hallandren?”

He blinked. “Well, for Siri, of course. Isn’t that why we came? To rescue her?” He smiled fondly, then shrugged. “Good night, Vivenna.” He trailed down the steps, calling to Jewels to see if she was hurt.

Vivenna watched him go.

\textit{He’s twice the person I am,}~she thought with shame, turning toward her room.~\textit{But I’m just finding it hard to care anymore.}~Everything had been taken from her. Why not Parlin, too? Her hatred for Hallandren grew a little more firm as she stepped into her room.

\textit{I just need to sleep,}~she thought.~\textit{Maybe after that, I can figure out just what in the name of the Colors I’m doing in this city.}

One thing remained firm. She was going to learn how to Awaken. The Vivenna from before—the one who had a right to stand tall and denounce Breath as unholy—no longer had a place in T’Telir. The real Vivenna hadn’t come to Hallandren to save her sister. She’d come because she couldn’t stand being unimportant.

She’d learn. That was her punishment.

Inside her room, she pushed the door closed, locking the bolt. Then she walked over to pull the drapes closed.

A figure stood on her balcony, resting easily against the railing. He wore several days’ worth of stubble on his face and his dark clothing was worn, almost tattered. He carried a deep black sword.

Vivenna jumped, eyes wide.

“You,” he said in an angry voice, “are causing a lot of trouble.”

She opened her mouth to scream, but the drapes snapped forward, muffling her neck and mouth. They squeezed tightly, choking her. They wrapped around her entire body, pinning her arms to her sides.

\textit{No!}~she thought.~\textit{I survive the attack and the Lifeless, and then fall in my own room?}

She struggled, hoping someone would hear her thrashing and come for her. But nobody did. At least, not before she fell unconscious.

