% \section{Chapter Seventeen}
\chapter{}

Vivenna walked back toward Lemex’s house, dissecting the argument she’d heard at the Court of Gods. Her tutors had instructed her that discussions in the Court Assembly didn’t always lead to action; just because they talked of war didn’t mean it would happen.

This discussion, however, seemed to mean more. It was too passionate, with too many voices for one side. It indicated that her father was right, and that war was inevitable.

She walked with her head down on a nearly deserted street. She was beginning to learn that she could avoid the roiling masses by walking through more residential sections of the city. It appeared that people in T’Telir liked to be where everybody else was.

The street was in a wealthy neighborhood and had a slate stone sidewalk running along the side of it. It made for pleasant walking. Parlin walked beside her, occasionally pausing to study ferns or palm trees. The Hallandren liked plants; most of the homes were shaded by trees, vines, and exotic blooming shrubs. In Idris, each of the large homes along the street would have been considered a mansion, but here they were only of average size—probably the homes of merchants.

\textit{I need to stay focused,}~she thought.~\textit{Is Hallandren going to attack soon? Or is this just a prelude to something still months, perhaps years, away?}

Real action wouldn’t occur until the gods voted, and Vivenna wasn’t sure what it would take to get them to that point. She shook her head. Only one day in T’Telir, and already she knew that her training and tutorials hadn’t prepared her half as well as she’d assumed.

She felt as if she knew nothing. And that left her feeling very lost. She was not the confident, competent woman she’d assumed herself to be. The frightening truth was, should she have been sent to become the God King’s bride, she would have been nearly as in effec tive and confused as poor Siri undoubtedly was.

They turned a corner, Vivenna trusting in Parlin’s amazing sense of direction to get them back to Lemex’s house, and they passed under the gaze of one of the silent D’Denir statues. The proud warrior stood with sword raised above his stone head, his armor—carved into the statue—augmented by a red scarf tied and flapping around his neck. He looked dramatic, as if he were going gloriously to war. It wasn’t long before they approached the steps to Lemex’s house. Vivenna froze, however, when she saw that the door was hanging from one hinge. The lower part was cracked, as if it had been kicked very hard.

Parlin pulled up beside her, then hissed, holding up a hand for her to be silent. His hand went to the long hunting knife at his belt and he glanced around. Vivenna stepped back, nerves itching to flee. And yet, where would she go? The mercenaries were her only connection in the city. Denth and Tonk Fah could have handled an attack, right?

Someone approached from the other side of the door. Her BioChromatic senses warned her of the proximity. She laid a hand on Parlin’s arm, preparing to bolt.

Denth pushed the broken door open, sticking his head out. “Oh,” he said. “It’s you.”

“What happened?” she asked. “Were you attacked?”

Denth glanced at the door and chuckled to himself. “Nah,” he said, pushing the door open and waving her in. Through the broken door she could see that furniture had been ripped apart, there were holes in the walls, and pictures were slashed and broken. Denth wandered back inside, kicking aside some stuffing from a cushion, making his way toward the stairs. Several of the steps had been broken.

He glanced back, noting her confusion. “Well, we~\textit{did}~say we were going to search the house, Princess. Figured we might as well do a good job of it.”

\orn

Vivenna sat down very carefully, half-expecting the chair to collapse beneath her. Tonk Fah and Denth had been~\textit{very}~thorough in their search—they had broken every bit of wood in the house, it seemed, including chair legs. Fortunately, her current chair had been propped up reasonably well, and it held her weight.

The desk in front of her—Lemex’s desk—was splintered. The drawers had been removed, and a false back had been revealed, the compartment emptied. A group of papers and several bags sat on the desktop.

“That’s everything,” Denth said, leaning against the room’s doorframe. Tonk Fah lounged on a broken couch, its stuffing sticking out awkwardly.

“Did you have to break so much?” Vivenna asked.

“Had to be certain,” Denth said, shrugging. “You’d be surprised where people hide things.”

“Inside the front door?” Vivenna asked flatly.

“Would~\textit{you}~have thought to look there?”

“Of course not.”

“Sounds like a pretty good hiding place to me, then. We knocked, and thought we found a hollow space. Just turned out to be a section of different wood, but it was important to check.”

“People get really clever when it comes to hiding important stuff,” Tonk Fah said with a yawn.

“You know the thing I hate most about being a mercenary?” Denth asked, holding up a hand.

Vivenna raised an eyebrow.

“Splinters,” he said, wiggling several red fingers.

“No hazard pay for those,” Tonk Fah added.

“Oh, now you’re just being silly,” Vivenna said, sorting through the items on the table. One of the bags clinked suggestively. Vivenna undid the drawstring and pulled open the top.

Gold glistened inside. A lot of it.

“Little over five thousand marks in there,” Denth said lazily. “Lemex had it stashed all over the house. Found one bar of it in the leg of your chair.”

“Got easier when we discovered the paper he’d used to remind himself of where he hid it all,” Tonk Fah noted.

“\textit{Five thousand marks?}” Vivenna said, feeling her hair lighten slightly in shock.

“Seems like old Lemex was storing up quite the little nest egg,” Denth said, chuckling. “That, mixed with the amount of Breath he held~.~.~. he must have extorted even more from Idris than I assumed.”

Vivenna stared at the bag. Then, she looked up at Denth. “You~.~.~. gave it to me,” she said. “You could have taken it and spent it!”

“Actually, we did,” Denth said. “Took about ten bits for lunch. Should be here any minute.”

Vivenna met his eyes.

“Now there’s what I’m talking about, eh, Tonks?” Denth said, glancing down at the larger man. “If I’d been, say, a butler, would she be looking at me like that? Just because I didn’t take the money and run? Why does everyone expect a mercenary to rob them?”

Tonk Fah grunted, stretching again.

“Look through those papers, Princess,” Denth said, kicking Tonk Fah’s couch, then nodding toward the door. “We’ll wait for you downstairs.”

Vivenna watched them retreat, Tonk Fah grumbling as he had to rise, bits of stuffing sticking to the back of his clothing. They thumped their way down the stairs, and soon she heard dishes rattling. They’d likely sent one of the street boys—who passed periodically yelling that they would bring food from a local restaurant—for the meal.

Vivenna didn’t move. She was increasingly uncertain of her purpose in the city. Yet she still had Denth and Tonk Fah, and—surprisingly—she was finding herself growing attached to them. How many soldiers in her father’s army—good men, all of them—would have been able to resist running off with five thousand marks? There was more to these mercenaries than they let on.

She turned her attention to the books, letters, and papers on the desk.

\orn

Several hours later, Vivenna still sat alone, a solitary candle burning and dripping wax onto the splintered desk corner. She had long since stopped reading. A plate of food sat uneaten by the door, brought by Parlin some time before.

Letters lay spread out on the desk before her. It had taken time to put them in order. Most were penned in her father’s familiar hand. Not the hand of her father’s scribe. Her father’s~\textit{own}hand. That had been her first clue. He only wrote his most personal, or most secret, communications on his own.

Vivenna kept her hair under control. She deliberately breathed in and out. She didn’t look out the darkened window at the lights of a city that should have been asleep. She simply sat.

Numb.

The final letter—the last before Lemex’s death—sat on top of the pile. It was only a few weeks old.

\textit{My friend,}~her father’s script read.

\textit{Our conversations have worried me more than I care to admit. I have spoken with Yarda at length. We can see no solution.}

\textit{War is coming. We all know that now. The continued—and increasingly vigorous—arguments in the Court of Gods show a disturbing trend. The money we sent to buy you enough Breath to attend those meetings is some of the best I have ever spent.}

\textit{All signs point to the inevitability of Hallandren Lifeless marching to our mountains. Therefore, I give you leave to do as we have discussed. Any disruptions you can cause in the city—any delays you can earn us—will be extremely valuable. The additional funds you requested should have arrived by now.}

\textit{My friend, I must admit a weakness in myself. I will never be able to send Vivenna to be a hostage in that dragon’s nest of a city. To send her would be to kill her, and I cannot do that. Even though I know it would be best for Idris if I did.}

\textit{I’m not yet sure what I will do. I will not send her, for I love her too much. However, breaking the treaty would bring the Hallandren wrath against my people even more quickly. I fear I may have to make a very difficult decision in the days to come.}

\textit{But that is the essence of a king’s duty.}

\textit{Until we correspond again,}

\textit{Dedelin, your liege and your friend.}

Vivenna looked away from the letter. The room was too perfectly silent. She wanted to scream at the letter and her father, who was now so far away. And yet, she could not. She had been trained for better. Tantrums were useless displays of arrogance.

Don’t draw attention to yourself. Don’t set yourself above others. He who makes himself high will be cast down low. But what of the man who murders one of his daughters to save the other? What of the man who claims—to your face—that the switch was for other reasons? That it was for the good of Idris? That it wasn’t about favoritism at all?

What of the king who betrayed the highest tenets of his religion by purchasing Breath for one of his spies?

Vivenna blinked at a tear in her eye, then gritted her teeth, angry at herself and the world. Her father was supposed to be a good man. The perfect king. Wise and knowing, always sure of himself and always right.

The man she saw in these letters was far more human. Why should she be so shocked to learn that?

\textit{It doesn’t matter,}~she told herself.~\textit{None of that matters.}~Factions in the Hallandren government were rallying the nation for war. Reading her father’s candid words, she finally believed him completely. Hallandren troops would likely march on her homeland before the year was out. And then, the Hallandren—so colorful yet so deceptive—would hold Siri hostage and threaten to kill her unless Dedelin surrendered.

Her father would not give up his kingdom. Siri would be executed.

\textit{And}~that~\textit{is what I’m here to stop,}~Vivenna thought. Her hands grew tighter, gripping the edges of the desktop, jaw set. She brushed away the traitorous tear. She had been trained to be strong even when surrounded by an unfamiliar city and its people. She had work to do.

She rose, leaving the letters on the table with the bag of coins and Lemex’s journal. She made her way down the stairs, avoiding the broken steps, to where the mercenaries were teaching Parlin how to play a game with wooden cards. The three men looked up as Vivenna approached. She settled herself carefully on the floor, sitting with her legs beneath her in an unassuming posture.

She met their eyes as she spoke. “I know where some of Lemex’s money came from,” she said. “Idris and Hallandren will soon go to war. Because of this threat, my father gave much greater resources to Lemex than I’d realized. He sent enough money for Lemex to buy fifty Breaths, allowing him to enter the court and report on its proceedings. Obviously, my father didn’t know that Lemex already~\textit{had}~a sizable amount of Breath.”

The three men were silent. Tonk Fah shot a glance at Denth, who sat back, resting against an overturned, broken chair.

“I believe that Lemex was still loyal to Idris,” she said. “His personal writings make that relatively clear. He was not a traitor; he was simply greedy. He wanted as much Breath as possible because he had heard that it extended a person’s life. Lemex and my father had planned to hinder the war preparations from inside Hallandren. Lemex promised he would find a way to sabotage the Lifeless armies, damage the city’s supplies, and generally undermine their ability to wage war. For him to accomplish this, my father sent him a large sum of money.”

“About five thousand marks’ worth?” Denth asked, rubbing his chin.

“Less than that,” Vivenna said. “But a large chunk nonetheless. I believe that you are right about Lemex, Denth—he has been stealing from the Crown for some time.”

She fell silent. Parlin looked confused. That wasn’t uncommon. The mercenaries, however, didn’t look surprised.

“I don’t know if Lemex intended to do as my father asked,” Vivenna said, keeping her voice even. “The way he hid the money, some of the things he wrote~.~.~. well, maybe he was finally planning to turn traitor and run. We can’t know what he would eventually have decided. We do, however, have a vague list of things he planned to accomplish. Those plans were convincing enough to persuade my father, and the urgency of his letters has convinced me. We are going to continue Lemex’s work and undermine Hallandren’s ability to wage war.”

The room fell silent. “And~.~.~. your sister?” Parlin finally asked.

“We will get her out,” Vivenna said firmly. “Her rescue and safety is our first priority.”

“That is all easier discussed than accomplished, Princess,” Denth said.

“I know.”

The mercenaries shared a look. “Well,” Denth finally said, standing up. “Better get back to work, then.” He nodded at Tonk Fah, who sighed and grumbled, standing.

“Wait,” Vivenna said, frowning. “What?”

“I figured once you saw those papers that you’d want to continue,” Denth said, stretching. “Now that I’ve seen what he was up to, I can piece together why he had us do some of the things we were involved in. One of those was to contact and support some rebellious factions here in the city, including one that was stamped out just a few weeks back. Cult of disaffection centered on a guy named Vahr.”

“Always wondered why Lemex gave him support,” Tonk Fah said.

“That faction’s dead,” Denth said, “along with Vahr himself. But a lot of his followers are still around. Waiting for trouble to come their way. We can contact them. There are a few other leads I think we can look into, things Lemex didn’t explain completely, but which I might be able to figure out.”

“And~.~.~. you can handle something like this?” Vivenna asked. “You just said it wouldn’t be easy.”

Denth shrugged. “Won’t be. But if you haven’t realized it yet, this kind of thing is why Lemex hired us. A team of three high-priced, specialist mercenaries isn’t exactly the type of thing you keep around to serve your tea.”

“Unless you want the tea rammed up someplace uncomfortable,” Tonk Fah noted.

\textit{Three mercenaries?}~Vivenna thought.~\textit{That’s right. There’s another one. A woman.}“Where’s the other member of your team?”

“Jewels?” Denth asked. “You’ll meet her soon enough.”

“Unfortunately,” Tonk Fah said under his breath.

Denth elbowed his friend. “For now, let us go back out and see how things stand on our projects. Gather what you want from this house. We’ll move out tomorrow.”

“Move out?” Vivenna said.

“Unless you want to sleep on a mattress Tonk Fah ripped into five pieces,” Denth noted. “He has a thing about mattresses.”

“And chairs,” Tonk Fah said cheerfully, “and tables, and doors, and walls, actually. Oh, and people.”

“Either way, Princess,” Denth said, “this building was well known to people who worked with Lemex. As you’ve discovered, he wasn’t exactly the most honest fellow around. I doubt you want the baggage that comes with being associated with him.”

“Best to move to another house,” Tonk Fah agreed.

“We’ll try not to break up the next one quite so badly,” Denth said.

“No promises though,” Tonk Fah said with a wink.

And then the two left.

