\section{Chapter Ten}

Vivenna’s hair instantly bleached to a stark white.~\textit{Think!}~she told herself.~\textit{You’ve been trained in politics! You studied hostage negotiation. But~.~.~. what do you do when you}~are\textit{the hostage?}~Suddenly, the two men burst out laughing. The larger man thumped the table several times with his hand, causing his bird to squawk. “Sorry, Princess,” Denth—the thinner man—said, shaking his head. “Just a bit of mercenary humor.”

“We kill sometimes, but we don’t murder,” Tonk Fah said. “That’s assassin work.”

“Assassins,” Denth said, holding up a finger. “Now,~\textit{they}~get respect. Why do you suppose that is? They’re really just mercenaries with fancier names.” Vivenna blinked, struggling to get control of her nerves. “You’re not here to kill me,” she said, voice stiff. “So you’re just going to kidnap me?”

“Gods, no,” Denth said. “Bad business, that. How do you make money at it? Every time you kidnap someone worth the ransom, you upset people a whole lot more powerful than you are.”

“Don’t make important people angry,” Tonk Fah said, yawning. “Unless you’re getting paid by people who are even~\textit{more}~powerful.”

Denth nodded. “And that isn’t even considering the feeding and care of captives, the exchanging of ransom notes, and the arranging of drop-offs. It’s a headache, I tell you. Terrible way to make money.”

The table fell silent. Vivenna placed her hands flat on its top to keep them from quivering.\textit{They know who I am,}~she thought, forcing herself to think logically.~\textit{Either they recognize me, or~.~.~.}

“You work for Lemex,” she said.

Denth smiled widely. “See, Tonk? He said she was a clever one.”

“Guess that’s why she’s a princess and we’re just mercenaries,” Tonk Fah said.

Vivenna frowned.~\textit{Are they mocking me or not?}~“Where is Lemex? Why didn’t he come himself?”

Denth smiled again, nodding toward the restaurant owner as the man brought a large pot of steaming stew to the table. It smelled of hot spices, and had what appeared to be crab claws floating in it. The owner dropped a group of wooden spoons to the table, then retreated.

Denth and Tonk Fah didn’t wait for permission to eat her meal. “Your friend,” Denth said, grabbing a spoon, “Lemex—our employer—isn’t doing so well.”

“Fevers,” Tonk Fah said between slurps.

“He requested that we bring you to him,” Denth said. He handed her a folded piece of paper with one hand, while cracking a claw between three fingers of the other. Vivenna cringed as he slurped the contents out.

\textit{Princess,}~the paper read.~\textit{Please trust these men. Denth has served me well for some mea sure now, and he is loyal—if any mercenary can be called loyal. He and his men have been paid, and I am confident he will stay true to us for the duration of his contract. I offer proof of authenticity by virtue of this password: bluemask.}

The writing was in Lemex’s hand. More than that, he had given the proper password. Not “bluemask”—that was misdirection. The true password was using the word “measure” instead of time. She glanced at Denth, who slurped out the insides of another claw.

“Ah, now,” he said, tossing aside the shell. “This is the tricky part; she has to make a decision. Are we telling her the truth, or are we fooling her? Have we fabricated that letter? Or maybe we took the old spy captive and tortured him, forcing him to write the words.”

“We could bring you his fingers as proof of our good faith,” Tonk Fah said. “Would that help?

Vivenna raised an eyebrow. “Mercenary humor?”

“Such that it is,” Denth said with a sigh. “We’re not generally a clever lot. Otherwise, we’d probably have selected a profession without such a high mortality rate.”

“Like your profession, Princess,” Tonks said. “Good lifespans, usually. I’ve often wondered if I should apprentice myself to one.”

Vivenna frowned as the two men chuckled.~\textit{Lemex wouldn’t have broken under torture,}she thought.~\textit{He’s too well trained. Even if he had broken, he wouldn’t have included both the real password and the false one.}

“Let’s go,” she said, standing.

“Wait,” Tonk Fah said, spoon to lips, “we’re skipping the rest of our meal?”

Vivenna eyed the red-colored soup and its bobbing crustacean limbs. “Definitely.”

\bigskip \hrule \bigskip

Lemex coughed quietly. His aged face was streaked with sweat, his skin clammy and pale, and he occasionally gave a whispered mumble of delirious ramblings.

Vivenna sat on a stool beside his bed, hands in her lap. The two mercenaries waited with Parlin at the back of the room. The only other person present was a solemn nurse—the same woman who had informed Vivenna in a quiet voice that nothing more could be done.

Lemex was dying. It was unlikely that he would last the day.

This was the first Vivenna had seen Lemex’s face, though she’d often corresponded with him. The face looked~.~.~. wrong. She knew that Lemex was growing old; that made him a better spy, for few looked for spies among the elderly. Yet he wasn’t supposed to be this frail stick of a person, shaking and coughing. He was supposed to be a spry, quick-tongued old gentleman. That was what she had imagined.

She felt like she was losing one of her dearest friends, though she had never really known him. With him went her refuge in Hallandren, her secret advantage. He was the one she had supposed would make this insane plan of hers work. The skilled, crafty mentor she had counted on having at her side.

He coughed again. The nurse glanced at Vivenna. “He goes in and out of lucidity, my lady. Just this morning, he spoke of you, but now he’s getting worse and worse.~.~.~.”

“Thank you,” Vivenna said quietly. “You are excused.”

The woman bowed and left.

\textit{Now it is time to be a princess,}~Vivenna thought, rising and leaning over Lemex’s bed.

“Lemex,” she said. “I need you to pass on your knowledge. How do I contact your spy networks? Where are the other Idrian agents in the city? What are the passcodes that will get them to listen to me?”

He coughed, staring unseeingly, whispering something. She leaned closer.

“. . . never say it,” he said. “You can torture me all that you want. I won’t give in.”

Vivenna sat back. By design, the Idrian spy network in Hallandren was loosely orga nized. Her father knew all of their agents, but Vivenna had only ever communicated with Lemex, the leader and coordinator of the network. She gritted her teeth, leaning forward again. She felt like a grave robber as she shook Lemex’s head slightly.

“Lemex, look at me. I’m not here to torture you. I’m the princess. You received a letter from me earlier. Now I’ve come to you.”

“Can’t fool me,” the old man whispered. “Your torture is nothing. I won’t give it up. Not to you.”

Vivenna sighed, looking away.

Suddenly, Lemex shuddered, and a wave of color washed across the bed, over Vivenna, and pulsed along the floor before fading. Despite herself, Vivenna stepped back in shock.

Another pulse came. It wasn’t color itself. It was a wave of~\textit{enhanced}~color—a ripple that made the hues in the room stand out more as it passed. The floor, the sheets, her own dress—it all flared to vibrant vividness for a second, then faded back to the original hues.

“What in Austre’s name was~\textit{that}?” Vivenna asked.

“BioChromatic Breath, Princess,” Denth said as he stood, leaning against the doorframe. “Old Lemex has a lot of it. Couple hundred Breaths, I’d guess.”

“That’s impossible,” Vivenna said. “He’s Idrian. He’d never accept Breath.”

Denth shot a look at Tonk Fah, who was scratching his parrot’s neck. The bulky soldier just shrugged.

Another wave of color came from Lemex.

“He’s dying, Princess,” Denth said. “His Breath is going irregular.”

Vivenna glared at Denth. “He doesn’t have—”

Something grabbed her arm. She jumped, looking down at Lemex, who had managed to reach up and take hold of her. He was focused on her face. “Princess Vivenna,” he said, eyes showing some lucidity at least.

“Lemex,” she said. “Your contacts. You have to give them to me!”

“I’ve done something bad, Princess.”

She froze.

“Breath, Princess,” he said. “I inherited it from my predecessor, and I’ve bought more. A lot more~.~.~.”

\textit{God of Colors~.~.~.}~Vivenna thought with a sick feeling in her stomach.

“I know it was wrong,” Lemex whispered. “But~.~.~. I felt so powerful. I could make the very dust of the earth obey my command. It was for the good of Idris! Men with Breath are respected here in Hallandren. I could get into parties where I normally would have been excluded. I could go to the Court of Gods when I wished and hear the Court Assembly. The Breath extended my life, made me spry despite my age. I~.~.~.”

He blinked, eyes unfocusing.

“Oh, Austre,” he whispered. “I’ve damned myself. I’ve gained notoriety through abusing the souls of others. And now I’m dying.”

“Lemex!” Vivenna said. “Don’t think about that now. Names! I need names and passcodes. Don’t leave me alone!”

“Damned,” he whispered. “Someone take it. Please take it away from me!”

Vivenna tried to pull back, but he still held on to her arm. She shuddered, thinking about the Breath he held.

“You know, Princess,” Denth said from behind. “Nobody really tells mercenaries anything. It’s an unfortunate—but very realistic—drawback of our profession. Never trusted. Never looked to for advice.”

She glanced back at him. He leaned against the door, Tonk Fah a short distance away. Parlin stood there as well, holding that ridiculous green hat in his fingers.

“Now, if someone~\textit{were}~to ask my opinion,” Denth continued, “I’d point out how much those Breaths are worth. Sell them, and you’d have enough money to buy your~\textit{own}~spy network—or pretty much anything else you wanted.”

Vivenna looked back at the dying man. He was mumbling to himself.

“If he dies,” Denth said, “that Breath dies with him. All of it.”

“A shame,” Tonk Fah said.

Vivenna paled. “I will not traffic in the souls of men! I don’t care how much they’re worth.”

“Suit yourself,” Denth said. “Hope nobody suffers when your mission fails, though.”

\textit{Siri~.~.~.}

“No,” Vivenna said, partially to herself. “I couldn’t take them.” It was true. Even the thought of letting someone else’s Breath mingle with her own—the idea of drawing another person’s soul into her own body—made her sick.

Vivenna turned back to the dying spy. His BioChroma was burning brightly now, and his sheets practically glowed. It was better to let that Breath die with him.

Yet without Lemex, she would have no help in the city, no one to guide her and provide refuge for her. She’d barely brought along enough money to cover lodging and meals, let alone bribes or supplies. She told herself that taking the Breath would be like using goods one had found in a bandit’s cavern. Did you throw it away just because it had originally been acquired through crime? Her training and lessons whispered that she needed resources badly, and that the damage had already been done.~.~.~.

\textit{No!}~she thought again.~\textit{It just isn’t right! I can’t hold it. I couldn’t.}

Of course, perhaps it would be wise to let someone~\textit{else}~hold the Breaths for a time. Then she could think about what to do with them at her leisure. Maybe~.~.~. maybe even find the people they had been taken from and give them back. She turned back, glancing at Denth and Tonk Fah.

“Don’t look at me like that, Princess,” Denth said, chuckling. “I see the glint in your eyes. I’m not going to keep that Breath for you. Having that much BioChroma makes a man far too important.”

Tonk Fah nodded. “It’d be like hiking about the city with a bag of gold on your back.”

“I like my Breath the way it is,” Denth said. “I only need one, and it’s functioning just fine. Keeps me alive, doesn’t draw attention to me, and sits there waiting to be sold if I need it.”

Vivenna glanced at Parlin. But~.~.~. no, she couldn’t force the Breath on him. She turned back to Denth. “What kind of things does your agreement with Lemex provide for?”

Denth glanced at Tonk Fah, then glanced back at her. The look in his eyes was enough. He was paid to obey. He’d take the Breath if she commanded it.

“Come here,” she said, nodding to a stool beside her.

Denth approached reluctantly. “You know, Princess,” he said, sitting. “If you give me that Breath, then I could just run off with it. I’d be a wealthy man. You wouldn’t want to put that kind of temptation into the hands of an unscrupulous mercenary, now, would you?”

She hesitated.

\textit{If he runs off with it, then what do I lose?}~That would solve a lot of problems for her. “Take it,” she ordered.

He shook his head. “That’s not the way it works. Our friend there has to give it to me.”

She looked at the old man. “I~.~.~.” She began to command Lemex to do just that, but she had second thoughts. Austre wouldn’t want her to take the Breath, no matter what the circumstances—a man who took Breath from others was worse than a slaver.

“No,” she said. “No, I’ve changed my mind. We won’t take the Breath.”

At that moment, Lemex stopped his mumbling. He looked up, meeting Vivenna’s eyes.

His hand was still on her arm.

“My life to yours,” he said in an eerily clear voice, his grip tight on her arm as she jumped back. “\textit{My Breath become yours!}”

A vibrant cloud of shifting, iridescent air burst from his mouth, puffing toward her. Vivenna closed her mouth, eyes wide, hair white. She ripped her arm free from Lemex’s grip, even as his face grew dull, his eyes losing their luster, the colors around him fading.

The Breath shot toward her. Her closed mouth had no effect; the Breath struck, hitting her like a physical force, washing across her body. She gasped, falling to her knees, body quivering with a perverse pleasure. She could suddenly~\textit{feel}~the other people in the room. She could sense them watching her. And—as if a light had been lit—everything around her became more vibrant, more real, and more alive.

She gasped, shaking in awe. She vaguely heard Parlin rushing to her side, speaking her name. But, oddly, the only thing she could think of was the melodic quality of his voice. She could pick out each tone in every word he spoke. She knew them instinctively.

\textit{Austre, God of Colors!}~she thought, steadying herself with one hand against the wooden floor as the shakes subsided.~\textit{What have I done?}

