% \section{Chapter Forty-Four}
\chapter{}

Siri watched Susebron with affection as he ate a third dessert. Their night’s meal lay spread out on the table and floor, some dishes completely devoured, others barely tasted. That first night when Susebron had ordered a meal had started a tradition. Now they ordered food every night—though only after Siri did her act for the listening priests. Susebron claimed to find it very amusing, though she noticed the curiosity in his eyes as he watched her.

Susebron had proven to have quite a sweet tooth now that disapproving priests and their sense of etiquette were absent. “You should probably watch out,” she noted as he finished another pastry. “If you eat too many of those, you will get fat.”

He reached for his writing board.~\textit{No I won’t.}

“Yes you will,” she said, smiling. “That’s the way it works.”

\textit{Not for gods,}~he wrote.~\textit{My mother explained it. Some men become more bulky if they exercise a lot and become fat if they eat a lot. That doesn’t happen to Returned. We always look the same.}

Siri couldn’t offer argument. What did she know of Returned?

\textit{Is food in Idris like this?}~Susebron wrote.

Siri smiled. He was always so curious about her homeland. She could sense a longing in him, the wish to be free of his palace and see the outside. And yet, he didn’t want to be disobedient, even when the rules were harsh.

“I really need to work on corrupting you some more,” she noted.

He paused.~\textit{What does that have to do with food?}

“Nothing,” she said. “But it’s true nonetheless. You’re far too good a person, Susebron.”

\textit{Sarcasm?}~he wrote.~\textit{I certainly hope that it is.}

“Only half,” she said, lying down on her stomach and watching him across their impromptu picnic setting.

\textit{Half-sarcasm?}~he wrote.~\textit{Is this something new?}

“No,” she said, sighing. “There is truth sometimes even in sarcasm. I don’t~\textit{really}~want to corrupt you, but I do think that you’re just too perfectly obedient. You need to be a little more reckless. Impulsive and inde pendent.”

\textit{It’s hard to be impulsive when you are locked in a palace surrounded by hundreds of servants,}~he wrote.

“Good point.”

\textit{However, I have been thinking about the things you’ve said. Please don’t be mad at me.}

Siri perked up, noting the embarrassment in his expression. “All right. What did you do?”

\textit{I talked to my priests,}~he said.~\textit{With the artisans’ script.}

Siri felt a moment of panic. “You told them about us?”

\textit{No, no,}~he wrote quickly.~\textit{I did tell them I was worried about having a child. I asked why my father died right after he had a child.}

Siri frowned. Part of her wished that he’d let her handle such negotiations. However, she said nothing. She didn’t want to keep him pinned down as his priests did. It was his life that was being threatened—he deserved the chance to work on the problem too.

“Good,” she said.

\textit{You’re not mad?}

She shrugged. “I was just encouraging you to be more impulsive! I can’t complain now. What did they say?”

He erased, then continued.~\textit{They told me not to worry. They said everything would be all right. So I asked them again, and again they gave me a vague answer.}

Siri nodded slowly.

\textit{It hurts me to write this, but I’m beginning to think that you are right. I’ve noticed that my guards and Awakeners are staying particularly close lately. We even skipped going to the Court Assembly yesterday.}

“That’s a bad sign,” she agreed. “I haven’t had much luck finding out what is going to happen. I’ve ordered in three other storytellers but none of them had any better information than what Hoid gave me.”

\textit{You still think it’s about the Breath I hold?}

She nodded. “Remember what I said about my conversation with Treledees? He talked about that Breath of yours with reverence. To him, it’s something to be passed from generation to generation, like a family tapestry.”

\textit{In one of the children’s stories in my book,}~he wrote,~\textit{there is a magic sword. A young boy is given it by his grandfather, and it turns out the sword was an heirloom—the symbol of kingship in the land.}

“What are you saying?” she asked.

\textit{Perhaps the entire monarchy of Hallandren is nothing more than a way to guard the Breath. The only way to safely pass Breath between individuals and generations is to use people as hosts. So they created a dynasty of God Kings who could hold the treasure and pass it from father to son.}

Siri nodded slowly. “That would mean that the God King is more of a vessel than I am. A sheath for a magic weapon.”

\textit{Exactly,}~Susebron wrote, hand moving quickly.~\textit{They had to make my family kings because of how much Breath was in that treasure. And they had to give it to a Returned—otherwise their king and their gods might have competed for power.}

“Perhaps. It seems awfully convenient that the God King always bears a stillborn son who becomes Returned~.~.~.”

She trailed off. Susebron saw it too.

\textit{Unless the next God King isn’t really the son of the current one,}~he wrote, hand shaking slightly.

“Austre!” Siri said. “God of Colors! That’s it. Somewhere in the kingdom, a baby died and Returned. That’s why it’s so urgent that I get pregnant! They already have the next God King, now they just need to keep up the farce. They marry me to you, hope for a child as quickly as possible, then switch the baby for the Returned one.”

\textit{Then they kill me and somehow take my Breaths away,}~he wrote.~\textit{And give it to this child, who can become the next God King.}

“Wait. Do infants even Return?” she asked.

\textit{Yes,}~he wrote.

“But, how does an~\textit{infant}~Return in a way that is heroic, or virtuous, or anything like that?”

Susebron hesitated, and she could tell he didn’t have an answer for her. Infant Returned. Among her own people, they didn’t believe that a person was chosen to Return because of some virtue they exemplified. That was a Hallandren belief. To her, it seemed a hole in their theology, but she didn’t want to challenge Susebron on it further. He already worried about how she didn’t believe in his divinity.

Siri sat back. “That doesn’t really matter. The real question is more important. If the God Kings are just vessels to hold Breath, then why bother changing them? Why not just leave one man holding the Breath?”

\textit{I don’t know,}~Susebron wrote.~\textit{It doesn’t seem to make sense, does it? Maybe they are worried about keeping a single God King captive that long. Children are easier to control, perhaps?}

“If that’s the case, they would want to change~\textit{more}~often,” Siri said. “Some of those God Kings lasted centuries. Of course, it could just have to do with how rebellious they think their king is.”

\textit{I do everything I’m supposed to! You just complained that I am too obedient.}

“Compared to me, you are,” she said. “Maybe from their viewpoint, you’re a wild man. After all, you did hide that book your mother gave you, and then you learned to write. Perhaps they know you well enough to realize that you weren’t going to stay docile. So now that they have an opportunity to replace you, they’re intending to take it.”

\textit{Maybe,}~he wrote.

Siri thought through their conclusions again. Looked at critically, she could see that they were just speculations. Yet everyone said that the other Returned couldn’t have children, and so why would the God King be different? That might just be a means of obfuscating the fact that they were bringing in a new person to be God King when they found one.

That still didn’t answer the most important question. What were they going to do to Susebron to get his Breaths away from him?

Susebron leaned back, staring up at the dark ceiling. Siri watched him, noting the look of sadness in his eyes. “What?” she asked.

He just shook his head.

“Please? What is it?”

He sat for a moment, then looked down, writing.~\textit{If what you say is true, then the woman who raised me was not my mother. I would have been born to someone random out in the countryside. The priests would have taken me once I Returned, then raised me in the palace as the “son” of the God King they’d just killed.}

Seeing him in pain made her insides twist. She moved around the blanket, sitting beside him, putting her arms around him and resting her head on his arm.

\textit{She’s the only person to have shown me real kindness in my life,}~he wrote.~\textit{The priests, they revere me and care for me—or, at least, I assumed that they did. However, they never really loved me. Only my mother did that. And now I’m not sure I even know who she is.}

“If she raised you, she’s your mother,” Siri said. “It doesn’t matter who gave birth to you.”

He didn’t respond to that.

“Maybe she was your real mother,” Siri said. “If they were going to bring you to the palace in secret, they might as well bring your mother too. Who better to care for you?”

He nodded, then scribbled on the board with one hand—the other was around Siri’s waist.~\textit{Perhaps you are right. Though it now seems suspicious to me that she would die as she did. She was one of the few who could have told me the truth.}

This seemed to make him even more sad, and Siri pulled him closer, laying her head on his chest.

\textit{Please,}~he wrote.~\textit{Tell me of your family.}

“My father was often frustrated with me,” Siri said. “But he did love me.~\textit{Does}~love me. He just wanted me to do what they thought was right. And~.~.~. well, the more time I spend in Hallandren, the more I wish I had listened to him, at least a little bit.

“Ridger is my older brother. I was always getting him into trouble. He was the heir, and I had him~\textit{thoroughly}~corrupted, at least until he got old enough to appreciate his duties. He’s a little like you. Very kindhearted, always trying to do what is right. He didn’t eat as many sweets, though.”

Susebron smiled faintly, squeezing her shoulder.

“Between us is Fafen, but I didn’t really know her that well. She joined a monastery when I was still quite young—and I was glad. It’s seen as a duty in Idris to provide at least one child for the monasteries. They’re the ones who grow the food for the needy and take care of things that need to be done around the city. Pruning, washing, painting. Anything to be of ser vice.”

He reached over.~\textit{A little like a king,}~he wrote.~\textit{Living a life to serve others.}

“Sure,” Siri said. “Only they don’t get locked up and they can stop doing it, if they want. Either way, I’m glad it was Fafen and not me. I would have gone~\textit{crazy}~living as a monk. They have to be pious all the time, and are supposed to be the least ostentatious in the city.”

\textit{Not a good match for your hair,}~he wrote.

“Definitely,” she said.

\textit{Though,}~he wrote, frowning slightly.~\textit{It’s stopped changing colors so often lately.}

“I’ve had to learn to control it better,” Siri said with a grimace. “People can read me too easily by it. Here.” She changed it from black to yellow, and he smiled, running his fingers through its lengthy locks.

“After Fafen and Ridger,” Siri said, “there’s just the eldest, Vivenna. She’s the one you were supposed to marry. She spent her entire life preparing to move to Hallandren.”

\textit{She must hate me,}~Susebron wrote.~\textit{Growing up knowing she would have to leave her family and live with a man she didn’t know.}

“Nonsense,” Siri said. “Vivenna looked forward to it. I don’t think she~\textit{can}~feel hatred. She was always just calm and careful and perfect.”

Susebron frowned.

“I sound bitter, don’t I?” Siri said, sighing. “I don’t mean to. I really do love Vivenna. She was always there, watching out for me. But it seemed to me that she made too many efforts to cover up for me. My big sister, pulling me out of trouble, scolding me calmly, then seeing that I wasn’t punished as much as I should have been.” She hesitated. “They’re all probably at home right now, worried sick about me.”

\textit{You sound like you’re worried about them,}~he wrote.

“I am,” she said. “I’ve been listening to the priests argue in the court. It doesn’t sound good, Seb. There are a lot of Idrians in the city and they’re being very reckless. The city guard was forced to send troops into one of the slums a few weeks back. That isn’t helping reduce tensions between our countries.”

Susebron didn’t write a response, but instead wrapped his arm around her again, pulling her close. It felt good to be held against him. Very good.

After a few minutes, he pulled his arm away and wrote again, awkwardly erasing first.~\textit{I was wrong, you know.}

“About what?”

\textit{About one of the things I said earlier. I wrote that my mother was the only person to ever show me love and kindness. That’s not true. There’s been another.}

He stopped writing and looked at her. Then he glanced at the board again.~\textit{You didn’t have to show me kindness,}~he wrote.~\textit{You could have hated me for taking you from your family and your homeland. Instead, you taught me to read, befriended me. Loved me.}

He stared at her. She stared at him. Then, hesitant, he leaned down and kissed her.

\textit{Oh, dear~.~.~.}~Siri thought, a dozen objections popping into her head. She found it difficult to move, to resist, or to do anything.

Anything other than kiss him back.

She felt hot. She knew that they needed to stop, lest the priesthood get exactly what they were waiting for. She~\textit{understood}~all of these things. Yet those objections began to seem less and less rational as she kissed him, as her breathing grew more hurried.

He paused, obviously uncertain what to do next. Siri looked up at him, breathing heavily, then pulled him down to kiss him again, feeling her hair bleed to a deep, passionate red.

At that point, she stopped caring about anything else. Susebron didn’t know what to do. But she did.~\textit{I really am too hasty,}~she thought as she pulled off her shift.~\textit{I need to get better at controlling my impulses.}

\textit{Some other time.}

