% \section{Chapter Four}
\chapter{}

Siri’s carriage rolled to a stop outside of T’Telir, capital of Hallandren. She stared out the window and realized something very, very intimidating: Her people had~\textit{no}~idea what it meant to be ostentatious. Flowers weren’t ostentatious. Ten soldiers protecting a carriage was not ostentatious. Throwing a tantrum in public wasn’t ostentatious.

The field of forty thousand soldiers, dressed in brilliant blue and gold, standing in perfect rows, spears raised high with blue tassels flapping in the wind~.~.~.~\textit{that}~was ostentatious. The twin line of cavalrymen atop enormous, thick-hoofed horses, both men and beasts draped with golden cloth that shimmered in the sun.~\textit{That}~was ostentatious. The massive city, so large it made her mind numb to consider it, domes and spires and painted walls all competing to draw her attention.~\textit{That}~was ostentatious.

She’d thought that she was prepared. The carriage had passed through cities as they’d made their way to T’Telir. She’d seen the painted houses, the bright colors and patterns. She’d stayed at inns with plush beds. She’d eaten foods mixed with spices that made her sneeze.

She hadn’t been prepared for her reception at T’Telir. Not at all.

\textit{Blessed Lord of Colors~.~.~.}~she thought.

Her soldiers pulled in tight around the carriage, as if wishing they could climb inside and hide from the overwhelming sight. T’Telir was built up against the shore of the Bright Sea, a large but landlocked body of water. She could see it in the distance, reflecting the sunlight, strikingly true to its name.

A figure in blue and silver rode up to her carriage. His deep robes weren’t simple, like those the monks wore back in Idris. These had massive, peaked shoulders that almost made the costume look like armor. He wore a matching headdress. That, combined with the brilliant colors and complex layers of the robes, made Siri’s hair pale to an intimidated white.

The figure bowed. “Lady Sisirinah Royal,” the man said in a deep voice, “I am Treledees, high priest of His Immortal Majesty, Susebron the Grand, Returned God and King of Hallandren. You will accept this token honor guard to guide you to the Court of Gods.”

\textit{Token?}~Siri thought.

The priest didn’t wait for a response; he just turned his horse and started back down the highway toward the city. Her carriage rolled after him, her soldiers marching uncomfortably around the vehicle. The jungle gave way to sporadic bunches of palm trees, and Siri was surprised to see how much sand was mixed with the soil. Her view of the landscape soon grew obstructed by the vast field of soldiers who stood at attention on either side of the road.

“Austre, God of Colors!” one of Siri’s guards whispered. “They’re Lifeless!”

Siri’s hair—which had begun to drift to auburn—snapped back to fearful white. He was right. Under their colorful uniforms, the Hallandren troops were a dull grey. Their eyes, their skin, even their hair: all had been drained completely of color, leaving behind a monochrome.

\textit{Those can’t be Lifeless!}~she thought.~\textit{They look like men!}

She’d imagined Lifeless as skeletal creatures, the flesh rotting and falling from the bones. They were, after all, men who had died, then been brought back to life as mindless soldiers. But these that she passed looked so human. There was nothing to distinguish them save for their lack of color and the stiff expressions on their faces. That, and the fact that they stood unnaturally motionless. No shuffling, no breathing, no quivers of muscle or limb. Even their eyes were still. They seemed like statues, particularly considering their grey skin.

\textit{And~.~.~. I’m going to marry one of these things?}~Siri thought. But no, Returned were different from Lifeless, and both were different from Drabs, which were people who had lost their Breath. She could vaguely remember a time when someone back in her village had Returned. It had been nearly ten years back, and her father hadn’t let her visit the man. She did recall that he’d been able to speak and interact with his family, even if he hadn’t been able to remember them.

He’d died again a week later.

Eventually, her carriage passed through the ranks of Lifeless. The city walls were next; they were im mense and daunting, yet they almost looked more artistic than functional. The wall’s top was curved in massive half-circles, like rolling hills, and the rim was plated with a golden metal. The gates themselves were in the form of two twisting, lithe sea creatures who curved up in a massive archway. Siri passed through them, and the guard of Hallandren cavalrymen—who appeared to be living men—accompanied her.

She had always thought of Hallandren as a place of death. Her impressions were based on stories told by passing ramblemen or by old women at the winter hearth. They spoke of city walls built from skulls, then painted with sloppy, ugly streaks of color. She’d imagined the buildings inside splattered with different clashing hues. Obscene.

She’d been wrong. True, there~\textit{was}~an arrogance to T’Telir. Each new wonder seemed as if it wanted to grab her attention and shake her about by her eyes. People lined the street—more people than Siri had seen in her entire life—crowding together to watch her carriage. If there were poor among them, Siri couldn’t tell, for they all wore brightly colored clothing. Some did have more exaggerated outfits—probably merchants, since Hallandren was said to have no nobility beyond its gods—but even the simplest of clothing had a cheerful brightness to it.

Many of the painted buildings did clash, but none of it was sloppy. There was a sense of craftsmanship and art to everything from the storefronts, to the people, to the statues of mighty soldiers that frequently stood on corners. It was terribly overwhelming. Garish. A vibrant, enthusiastic garishness. Siri found herself smiling—her hair turning a tentative blond—though she felt a headache coming on.

\textit{Maybe~.~.~. maybe this is why Father sent me,}~Siri thought.~\textit{Training or no training, Vivenna would never have fit in here. But I’ve always been far too interested in color.}

Her father was a good king with good instincts. What if—after twenty years of raising and training Vivenna—he had come to the conclusion that she wasn’t the right one to help Idris? Was that why, for the first time in their lives, Father had chosen Siri over Vivenna?

\textit{But, if that’s true, what am I supposed to do?}~She knew that her people feared Hallandren would invade Idris, but she couldn’t see her father sending one of his daughters if he believed war was close. Perhaps he hoped that she’d be able to help ease the tensions between the kingdoms?

That possibility only added to her anxiety. Duty was something unfamiliar to her, and not a little unsettling. Her father trusted her with the very fate and lives of their people. She couldn’t run, escape, or hide.

Particularly from her own wedding.

As her hair twinged white with fear at what was coming, she diverted her attention to the city again. It wasn’t hard to let it take her attention. It was enormous, sprawling like a tired beast curled around and over hills. As the carriage climbed the southern section of town, she could see—through gaps in the buildings—that the Bright Sea broke into a bay before the city. T’Telir curved around the bay, running right up to the water, forming a crescent shape. The city wall, then, only had to run in a half-circle, abutting the sea, keeping the city boxed in.

It didn’t seem cramped. There was a lot of open space in the city—malls and gardens, large swaths of unused land. Palms lined many of the streets and other foliage was common. Plus, with the cool breeze coming over the sea, the air was a lot more temperate than she had expected. The road led up to a seaside overlook within the city, a small plateau that had an excellent view. Except the entire plateau was surrounded by a large, obstructive wall. Siri watched with growing apprehension as the gates to this smaller city-within-a-city opened up to let the carriage, soldiers, and priests enter.

The common people stayed outside.

There was another wall inside, a barrier to keep anyone from seeing in through the gate. The procession turned left and rounded the blinding wall, entering the Hallandren Court of Gods: an enclosed, lawn-covered courtyard. Several dozen enormous mansions dominated the enclosure, each one painted a distinct color. At the far end of the court was a massive black structure, much taller than the other buildings.

The walled courtyard was quiet and still. Siri could see figures sitting on balconies, watching her carriage roll across the grass. In front of each of the palaces, a crew of men and women knelt prostrate on the grass. The color of their clothing matched that of their building, but Siri spared little time to study them. Instead, she nervously peered at the large, black structure. It was pyramidal, formed of giant steplike blocks.

\textit{Black,}~she thought.~\textit{In a city of color.}~Her hair paled even further. She suddenly wished she were more devout. She doubted Austre was all that pleased with her outbursts, and most days she even had trouble naming the Five Visions. But he’d watch over her for the sake of her people, wouldn’t he?

The procession pulled to a stop at the base of the enormous triangular building. Siri looked up through the carriage window at the shelves and knobs at the summit, which made the architecture seem top-heavy. She felt as if the dark blocks would come tumbling down in an avalanche to bury her. The priest rode his horse back up to Siri’s window. The cavalrymen waited quietly, the shuffling of their beasts the only sound in the massive, open courtyard.

“We have arrived, Vessel,” the man said. “As soon as we enter the building, you will be prepared and taken to your husband.”

“Husband?” Siri asked uncomfortably. “Won’t there be a wedding ceremony?”

The priest smirked. “The God King does not need ceremonial justification. You became his wife the moment he desired it.”

Siri shivered. “I was just hoping that maybe I could see him, before, you know~.~.~.”

The priest shot her a harsh look. “The God King does not perform for your whims, woman. You are blessed above all others, for you will be allowed to touch him—if only at~\textit{his}~discretion. Do not pretend that you are anything other than you are. You have come because he desires it, and you will obey. Otherwise, you will be put aside and another will be chosen in your place—which, I think, might bode unfavorably for your rebel friends in the highlands.”

The priest turned his horse, then clopped his way toward a large stone ramp, leading up to the building. The carriage lurched into motion, and Siri was drawn toward her fate.

