\section{Chapter Thirty-Four}

Lightsong watched the young queen dart away from his pavilion and felt an odd sense of guilt.~\textit{How very uncharacteristic of me,}~he thought, taking a sip of wine. After the grapes, it tasted a little sour.

Maybe the sourness was from something else. He’d spoken to Siri about the God King’s death in his usual flippant way. In his opinion, it was usually best for people to hear the truth bluntly—and, if possible, amusingly.

He hadn’t expected such a reaction from the queen. What was the God King to her? She’d been sent to be his bride, probably against her will. Yet she seemed to take the prospect of his death with grief. He eyed her appraisingly as she fled.

Such a small, young thing she was, all dressed up in gold and blue.~\textit{Young?}~he thought.~\textit{Yet she’s been alive longer than I have.}

He retained some things from his former life—such as his perception of his own age. He didn’t feel like he was five. He felt far older. That age should have taught him to hold his tongue when speaking of making widows out of young women. Could the girl actually have feelings for the God King?

She’d been in the city for only a couple of months, and he knew—through rumors—what her life must be like. Forced to perform her duty as a wife for a man to whom she could not speak and whom she could not know. A man who represented all the things that her culture taught were profane. The only thing Lightsong could suppose, then, was that she was worried about what might happen to her if her husband killed himself. A legitimate worry. The queen would lose most of her stature if she lost her husband.

Lightsong nodded to himself, turning to look down at the arguing priests. They were done with sewage and guard patrols and had moved on to other topics. “We~\textit{must}~prepare ourselves for war,” one of them was saying. “Recent events make it clear that we cannot coexist with the Idrians with any assurance of peace or security. This conflict will come, whether we wish it or not.”

Lightsong sat listening, tapping one finger against the arm rest of his chair.

\textit{For five years, I’ve been irrelevant,}~he thought.~\textit{I didn’t have a vote on any of the important court councils, I simply held the codes to a division of the Lifeless. I’ve crafted a divine reputation of being useless.}

The tone below was even more hostile than it had been during previous meetings. That wasn’t what worried him. The problem was the priest spearheading the movement for war. Nanrovah, high priest of Stillmark the Noble. Normally, Lightsong wouldn’t have bothered paying attention. Yet Nanrovah had always been the most outspoken~\textit{against}~war.

What had made him change his mind?

It wasn’t long before Blushweaver made her way to his box. By the time she arrived, Lightsong’s taste for the wine had returned, and he was sipping thoughtfully. The voices against war from below were soft and infrequent.

Blushweaver sat beside him, a rustle of cloth and a waft of perfume. Lightsong didn’t look toward her.

“How did you get to Nanrovah?” he finally asked.

“I didn’t,” Blushweaver said. “I don’t know why he changed his mind. I wish he hadn’t done it so quickly—it seems suspicious and makes people think I manipulated him. Either way, I’ll take the support.”

“You wish for war so much?”

“I wish for our people to be aware of the threat,” Blushweaver said. “You think I~\textit{want}~this to happen? You think I want to send our people to die and to kill?”

Lightsong looked at her, judging her sincerity. She had such beautiful eyes. One rarely noticed that, considering how she proffered the rest of her assets so blatantly. “No,” he said. “I don’t think you want a war.”

She nodded sharply. Her dress was sleek and trim this day, as always, but it was particularly revealing up top, where her breasts were pressed up and forward, demanding attention. Lightsong looked away.

“You’re boring today,” Blushweaver said.

“I’m distracted.”

“We should be happy,” Blushweaver said. “The priests have almost all come around. Soon there will be a call for attack made to the main assembly of gods.”

Lightsong nodded. The main assembly of gods was called to deliberate only in the most important of situations. In that case, they all had a vote. If the vote was for war, the gods with Lifeless Commands—gods like Lightsong—would be called upon to administrate and lead the battle.

“You’ve changed the Commands on Hopefinder’s ten thousand?” Lightsong asked.

She nodded. “They’re mine now, as are Mercystar’s.”

\textit{Colors,}~he thought.~\textit{Between the two of us, we now control three-quarters of the kingdom’s armies.}

\textit{What in the name of the Iridescent Tones am I getting myself into?}

Blushweaver settled back in her chair, eyeing the smaller one that Siri had vacated. “I am annoyed, however, at Allmother.”

“Because she’s prettier than you, or because she’s smarter?”

Blushweaver didn’t dignify that with a verbal response; she just shot him a look of annoyance.

“Just trying to act less boring, my dear,” he said.

“Allmother controls the last group of Lifeless,” Blushweaver said.

“An odd choice, don’t you think?” Lightsong said. “I mean,~\textit{I}~am a logical choice—assuming you don’t know me, of course—since I’m supposedly bold. Hopefinder represents justice, a nice mix with soldiers. Even Mercystar, who represents benevolence, makes a kind of sense for one who controls soldiers. But Allmother? Goddess of matrons and families? Giving her ten thousand Lifeless is enough to make even me consider my drunk-monkey theory.”

“The one who chooses names and titles of the Returned?”

“Exactly,” Lightsong said. “I’ve actually considered expanding the theory. I am now proposing to believe that God—or the universe, or time, or whatever you think controls all of this—is~\textit{all}~really just a drunk monkey.”

She leaned over, squeezing her arms together, seriously threatening to pop her bosom out the front of her dress. “And, you think~\textit{my}~title was chosen by happenstance? Goddess of honesty and interpersonal relations. Seems to fit, wouldn’t you say?”

He hesitated. Then he smiled. “My dear, did you just try to prove the existence of God with your cleavage?”

She smiled. “You’d be surprised what a good wriggle of the chest can accomplish.”

“Hum. I’d never considered the theological power of your breasts, my dear. If there were a Church devoted to them, perhaps you’d make a theist out of me after all. Regardless, are you going to tell me what specifically Allmother did to annoy you?”

“She won’t give me her Lifeless Commands.”

“Not surprising,” Lightsong said. “\textit{I}~hardly trust you, and I’m your friend.”

“We need those security phrases, Lightsong.”

“Why?” he asked. “We’ve got three of the four—we dominate the armies already.”

“We can’t afford infighting or divisiveness,” Blushweaver said. “If her ten were to turn against our thirty, we’d win, but we’d be left badly weakened.”

He frowned. “Surely she wouldn’t do that.”

“Surely we’d rather be certain.”

Lightsong sighed. “Very well, then. I’ll talk to her.”

“That might not be a good idea.”

He raised an eyebrow.

“She doesn’t like you very much.”

“Yes, I know,” he said. “She has remarkably good taste. Unlike some other people I know.”

She glared at him. “Do I need to wriggle my breasts at you again?”

“No, please. I don’t know if I’d be able to stand the theological debate that would follow.”

“All right, then,” she said, sitting back, looking down at the priests who were still arguing.

\textit{They sure are taking a long time on this one,}~he thought. He glanced toward the other side, where Siri had paused to look out over the arena, her arms resting on the stonework; it was too high for her to do so comfortably.

\textit{Perhaps it wasn’t thinking of her husband’s death that bothered her,}~he thought.\textit{Maybe it was because the discussion turned to war.}

A war her people couldn’t win. That was another good reason why the conflict was becoming inevitable. As Hoid had implied, when one side had an unbeatable advantage, war was the result. Hallandren had been building its Lifeless armies for centuries, and the size was becoming daunting. Hallandren had less and less to lose from an attack. He should have realized that earlier, rather than assuming this would all blow over once the new queen arrived.

Blushweaver huffed beside him, and he noticed that~\textit{she}~had noticed his study of Siri. She was watching the queen with obvious dislike.

Lightsong immediately changed the topic. “Do you know anything about a tunnel complex beneath the Court of Gods?”

Blushweaver turned back toward him, shrugging. “Sure. Some of the palaces have tunnels beneath them, places for storage and the like.”

“Have you ever been down in any of them?”

“Please. Why would I go crawling about in storage tunnels? I only know about them because of my high priestess. When she joined my ser vice, she asked me if I wanted mine connected to the main complex of tunnels. I said I didn’t.”

“Because you didn’t want others to have access to your palace?”

“No,” she said, turning back to watching the priests below. “Because I didn’t want to put up with the racket of all that digging. Can I have some more wine, please?”

\bigskip \hrule \bigskip

Siri watched the proceedings for quite a long time. She felt a little like Lightsong said he did. Because she didn’t have a say about what the court did, it was frustrating to pay attention. Yet she wanted to know. The arguments of the priests were, in a way, her only connection to the outside world.

She was not encouraged by what she heard. As the time passed, the sun falling close to the horizon and servants lighting massive torches along the walkway, Siri found herself feeling more and more daunted. Her husband was probably either going to be killed or persuaded to kill himself in the upcoming year. Her homeland, in turn, was about to be invaded by the very kingdom her husband ruled—yet he could do nothing to stop it because he had no way to communicate.

Then there was the guilt she felt for actually~\textit{enjoying}~all the challenges and problems. Back home, she’d had to be contrary and disobedient to find any kind of excitement. Here she only had to stand and watch, and things would begin to topple against each other and cause a clatter. There was far~\textit{too}~much clatter at present, but that didn’t stop her from thrilling at her part in it.

\textit{Silly fool,}~she told herself.~\textit{Everything you love is in danger and you’re thinking about how exciting it is?}

She needed to find a way to help Susebron. In doing so, perhaps she could bring him out from beneath the oppressive control of the priests. Then he might be able to do something to help her homeland. As she followed that line of thought, she almost missed a comment from below. It was spoken by one of the priests most strongly in favor of attacking.

“Have you not heard of the Idrian agent who has been causing havoc in the city?” the priest asked. “The Idrians are preparing for the war!~\textit{They}~know that a conflict is inevitable and so they’ve begun to work against us!”

Siri perked up.~\textit{Idrian agents in the city?}

“Bah,” said another of the priests. “The ‘infiltrator’ you speak of is said to be a princess of the royal family. That’s obviously a story for the common people. Why would a princess come in secret to T’Telir? These stories are ridiculous and unfounded.”

Siri grimaced. That, at least, was obviously true. Her sisters were not the types to come and work as “Idrian agents.” She smiled, imagining her soft-spoken monk of a sister—or even Vivenna in her prim outfits and stony attitude—coming to T’Telir in secret. Part of her had a little trouble believing that Vivenna had really been intended to become Susebron’s bride. Starchy Vivenna? Having to deal with the exotic court and the wild costumes?

Vivenna’s stoic coldness would never have coaxed Susebron out of his imperial mask. Vivenna’s obvious disapproval would have alienated her from gods like Lightsong. Vivenna would have hated wearing the beautiful dresses and would never have appreciated the colors and variety in the city. Siri might not have been ideal for the position, but she was slowly coming to realize that Vivenna hadn’t been a good choice either.

A group of people was approaching along the walkway. Siri remained where she was; she was too distracted by her thoughts to pay much attention.

“Are they talking about a relative of yours?” a voice asked.

Siri started, spinning. Behind her stood a dark-haired goddess wearing a lavish—and revealing—gown of green and silver. Like most of the gods, she stood a good head taller than a mortal person, and she looked down at Siri with a raised eyebrow.

“Your~.~.~. Grace?” Siri responded, confused.

“They’re discussing the famous hidden princess,” the goddess said with a wave of her hand. “She’d be a relative of yours, if she really does have the Royal Locks.”

Siri glanced back at the priests. “They must be mistaken. I’m the only princess here.”

“The stories of her are quite pervasive.”

Siri fell silent.

“My Lightsong has taken a liking to you, Princess,” the goddess said, folding her arms.

“He has been very kind to me,” Siri said carefully, trying to present the right image—that of the person she was, only less threatening. A little more confused. “Might I ask which goddess you are, Your Grace?”

“I am Blushweaver,” the goddess said.

“I am pleased to meet you.”

“No you aren’t,” Blushweaver said. She leaned in, eyes narrowing. “I don’t like what you’re doing here.”

“Excuse me?”

Blushweaver raised a finger. “He’s a better man than any of us,~\textit{Princess.}~Don’t you go spoiling him and pulling him into your schemes.”

“I don’t know what you mean.”

“You don’t fool me with your false na{\"i}vet{\'e},” Blushweaver said. “Lightsong is a good person—one of the last ones we have left in this court. If you taint him, I will destroy you. Do you understand?”

Siri nodded dumbly; then Blushweaver turned and moved away, muttering, “Find someone else’s bed to climb into, you little slut.”

Siri watched her go, shocked. When she finally regained her composure, she blushed furiously, then fled.

\bigskip \hrule \bigskip

By the time she got back to the palace, Siri was quite ready for her bath. She entered the bathing chamber, letting her serving women undress her. They retreated with the clothing, then exited to prepare the evening’s gown. That left Siri in the hands of a group of lesser attendants, the ones whose job it was to follow her into the massive tub and scrub her clean.

Siri relaxed and leaned back, sighing as the women went to work. Another group—standing fully clothed in the deep water—pulled her hair straight and then cut most of it free, something she’d ordered them to do every night.

For a few moments, Siri floated and let herself forget the threats to her people and her husband. She even let herself forget Blushweaver and her snappish misunderstanding. She just enjoyed the heat and the scents of the perfumed water.

“You wanted to speak with me, My Queen?” a voice asked.

Siri started, splashing as she dunked her body beneath the water. “Bluefingers,” she snapped. “I thought we’d cleared this up on the first day!”

He stood at he rim of the tub, fingers blue, typically anxious as he began to pace. “Oh, please,” he said. “I have daughters twice your age. You sent word that you wanted to talk to me. Well, this is where I will talk. Away from random ears.”

He nodded to several of the serving girls, and they began to splash just a bit more, speaking quietly, creating a low noise. Siri flushed, her short hair a deep red—though a few cut-off strands that floated in the water remained blond.

“Haven’t you gotten over your shyness yet?” Bluefingers asked. “You’ve been in Hallandren for months.”

Siri eyed him, but didn’t relax her concealing posture, even if she did let the serving women continue to work on her hair and scrub her back. “Won’t it seem suspicious to have the serving women making so much noise?” she asked.

Bluefingers waved a hand. “They’re already considered second-class servants by most in the palace.” She understood what he meant. These women, as opposed to her regular servants, wore brown. They were from Pahn Kahl.

“You sent me a message earlier,” Bluefingers said. “What did you mean by claiming to have information relating to my plans?”

Siri bit her lip, sorting through the dozens of ideas she had considered, discarding them all. What did she know? How could she make Bluefingers willing to trade?

\textit{He gave me clues,}~she thought.~\textit{He tried to scare me into not sleeping with the king. But he had no reason to help me. He barely knew me. He must have other motives for not wanting an heir to be born.}

“What happens when a new God King takes the throne?” she asked carefully.

He eyed her. “So you’ve figured that out, then?”

\textit{Figured out what?}~“Of course I have,” she said out loud.

He wrung his hands nervously. “Of course, of course. Then you can see why I’m so nervous? We worked hard to get me where I am. It isn’t easy for a Pahn Kahl man to rise high in the theocracy of Hallandren. Once I got into place, I worked so hard to provide work for my people. The serving girls who wash you, they have far better lives than the Pahn Kahl who work the dye fields. That will all be lost. We don’t believe in their gods. Why would we be treated as well as people of their own faith?”

“I still don’t see why it has to happen,” Siri said carefully.

He waved a nervous hand. “Of course it doesn’t~\textit{have}~to, but tradition is tradition. The Hallandren are very lax in every area but religion. When a new God King is chosen, his servants are replaced. They won’t kill us to send us into the afterlife along with our lord—that horrid custom hasn’t been in effect since the days before the Manywar—but we~\textit{will}~be dismissed. A new God King represents a fresh start.”

He stopped pacing, looking at her. She was still naked in the water, awkwardly covering herself as best she could. “But,” he said, “I guess my job security is the lesser of our problems.”

Siri snorted. “Don’t tell me you’re worried about~\textit{my}~safety above your own place in the palace.”

“Of course not,” he said, kneeling down beside the tub, speaking quietly. “But the God King’s life~.~.~. well, that worries me.”

“So,” Siri said, “I haven’t been able to decide yet. Do the God Kings give up their lives willingly once they have an heir, or are they coerced into it?”

“I’m not sure,” Bluefingers admitted. “There are stories, spoken of by my people regarding the last God King’s death. They say that the plague he cured—well, he wasn’t even in the city when the ‘curing’ happened. My suspicion is that they somehow coerced him to give up his Breaths to his son and that killed him.”

\textit{He doesn’t know,}~Siri thought.~\textit{He doesn’t realize that Susebron is a mute.}~“How closely have you served the God King?”

He shrugged. “As close as any servant considered unholy. I’m not allowed to touch him or speak to him. But, Princess, I’ve~\textit{served}~him all my life. He’s not my god, but he’s something better. I think these priests look upon their gods as placeholders. It doesn’t really matter to them who is holding the station. Me, I’ve served His Majesty for my entire life. I was hired by the palace as a lad and I remember Susebron’s childhood. I cleaned his quarters. He’s not my god, but he~\textit{is}~my liege. And now these priests are planning to kill him.”

He turned back to his pacing, wringing his hands. “But there’s nothing to be done.”

“Yes, there is,” she said.

He waved a hand. “I gave you a warning and you ignored it. I know that you’ve been performing your duties as a wife. Perhaps we could find some way of making certain that no pregnancy of yours comes to term.”

Siri flushed. “I would never do such a thing! Austre forbids it.”

“Even to save the life of the God King? But~.~.~. of course. What is he to you? Your captor and imprisoner. Yes. Perhaps my warnings were useless.”

“I~\textit{do}~care, Bluefingers,” she said. “And I think we can stop this before it gets to the point of worrying about an heir. I’ve been talking to the God King.”

Bluefingers froze, looking directly at her. “What?”

“I’ve been talking to him,” Siri admitted. “He’s not as heartless as you might think. I don’t think this has to end with him dying or your people losing their places in the palace.”

Bluefingers studied her, staring at her to the point that she flushed again, ducking further down into the water.

“I see that you’ve found yourself a position of power,” he noted.

\textit{Or, at least, one that looks powerful,}~she thought ruefully. “If things turn out as I want them to, I’ll make certain your people are cared for.”

“And my side of the bargain?” he asked.

“If things don’t turn out as I want them to,” she said, taking a deep breath, heart fluttering, “I want you to get Susebron and me out of the palace.”

Silence.

“Deal,” he said. “But let us make certain it does not come to that. Is the God King aware of the danger from his own priests?”

“He is,” Siri lied. “In fact, he knew about it before I did. He’s the one who told me I needed to contact you.”

“He did?” Bluefingers asked, frowning slightly.

“Yes,” Siri said. “I will be in touch on how to make this turn out well for all of us. And, until then, I would appreciate it if you’d let me get back to my bath.”

Bluefingers nodded slowly, then retreated from the bathing chamber. Siri, however, found it hard to still her nerves. She wasn’t certain if she’d handled the exchange well or not. She seemed to have gained something. Now she just had to figure out how to use it.

