\section{Chapter Twenty}

For the first time in her several weeks at the palace, Siri stood before the God King’s door and felt neither worried nor tired.

Bluefingers, oddly, wasn’t scribbling on his pad. He watched her silently, expression unreadable.

Siri almost smiled to herself. Gone were the days when she’d had to lie on the floor, awkwardly trying to kneel while her back complained. Gone were the days when she had to fall asleep on the marble, her discarded dress her only comfort. Ever since she’d grown daring enough to climb into the bed the previous week, she’d slept well each night, comfortable and warm. And not once had she been touched by the God King.

It was a nice arrangement. The priests—apparently satisfied that she was doing her wifely duty—left her alone. She didn’t have to be naked in front of anyone, and she was beginning to learn the social dynamic of the palace. She’d even gone to a few more sessions of the Court Assembly, though she hadn’t mingled with the Returned.

“Vessel,” Bluefingers said quietly.

She turned toward him, raising an eyebrow.

He shuffled uncomfortably. “You~.~.~. have found a way to make the king respond to your advances, then?”

“That got out, did it?” she asked, looking back at the door. Inside, her smile deepened.

“Indeed it did, Vessel,” Bluefingers said, tapping his ledger from beneath. “Only those in the palace know about any of this, of course.”

\textit{Good,}~Siri thought. She glanced to the side.

Bluefingers did not look pleased.

“What?” she asked. “I’m out of danger. The priests can stop worrying about an heir.”~\textit{For a few months, at least. They’ll get suspicious eventually.}

“Vessel,” Bluefingers said with a harsh whisper. “Doing your duty as the Vessel~\textit{was}~the danger!”

She frowned, looking at Bluefingers as the little scribe tapped his board. “Oh gods, oh gods, oh gods~.~.~.” he whispered to himself.

“What?” she asked.

“I shouldn’t say.”

“Then what is the point of bringing it up in the first place! Honestly, Bluefingers, you’re getting frustrating. Leave me too confused, and I might just start asking questions—”

“No!” Bluefingers said sharply, then immediately glanced behind him, cringing slightly. “Vessel, you must not speak to others of my fears. They’re silly, really, nothing to bother anyone else with. Just~.~.~.”

“What?” she asked.

“You~\textit{must}~not bear him a child,” Bluefingers said. “That is the danger, both to yourself and to the God King himself. This all~.~.~. everything here in the palace~.~.~. it is not what it appears to be.”

“That’s what everyone says,” she snapped. “If it’s not what it seems, then tell me what it~\textit{is.}”

“There is no need,” Bluefingers said. “And I will not speak of this again. After tonight, you will conduct yourself to the bedchamber—you obviously have the pattern down well enough. Just wait a hundred heartbeats or so after the women let you out of the dressing room.”

“You have to tell me something!” Siri said.

“Vessel,” Bluefingers said, leaning in. “I advise you to please keep your voice down. You don’t know how many factions shift and move inside the palace. I am a member of many of them, and a stray word on your part could~.~.~. no,~\textit{would}~.~.~. mean my death. Do you understand that?~\textit{Can}~you understand that?”

She hesitated.

“I should~\textit{not}~be putting my life in danger because of you,” he said. “But there are things about this arrangement with which I do not agree. And so, I give my warning. Avoid giving the God King a child. If you want to know more than that, read your histories. Honestly, I would think that you’d have come to all this a little more prepared.”

And with that, the little man left.

Siri shook her head, then sighed and pushed open the door and entered the God King’s chamber. She closed the door, then eyed the God King—who watched her, as always—and pulled off her dress, leaving her shift on. She went to the bed and sat down, waiting a few minutes before climbing up on her knees to do her bouncing, moaning act. She varied it sometimes, doing several different rhythms, getting creative.

Once she was done, she snuggled down in the blankets and lay back in the pillows to think.\textit{Could Bluefingers have been any more obscure?}~she thought with frustration. What little Siri knew of political intrigue told her that people preferred to be subtle—obscure, even—to protect themselves from implication.

\textit{Read your histories.~.~.~.}

It seemed an odd suggestion. If the secrets were that visible, then why would they be dangerous?

Still, as she thought, she did find herself feeling grateful for Bluefingers. She couldn’t really blame him for his hesitation. He’d probably already endangered himself far more than he should have. Without him, she wouldn’t have known she was in danger.

In a way, he was the only friend she had in the city—a person like herself, a person drawn in from another country. A country that was overshadowed by beautiful, bold Hallandren. A man who~.~.~.

Her thoughts trailed off; she felt something odd. She opened her eyes.

Someone loomed over her in the darkness.

Despite herself, Siri screamed in surprise. The God King jumped back, stumbling. Heart thumping, Siri shuffled backward on the bed, pulling the covers up over her chest—though, of course, he had seen her unclothed so often that it was a ridiculous gesture.

The God King stood in his dark black clothing, looking uncertain in the hearth’s wavering light. She’d never asked her servants why he wore black. One would think that he would prefer white, which he could affect so dramatically with his BioChroma.

For a few moments, Siri sat with the blankets clutched before her, then forced herself to relax.~\textit{Stop being so silly,}~she told herself.~\textit{He’s never so much as threatened you.}

“It’s all right,” she said softly. “You just startled me.”

He glanced at her. And—with a jolt of surprise—she realized this was the first time she’d addressed him since her outburst the previous week. Now that he stood, she could see even better how~.~.~. heroic he looked. Tall, broad-shouldered, like a statue. Human, but of more dramatic proportions. Carefully, showing more uncertainty than she’d ever expected from a man who had the title of God King, he moved back to the bed. He sat down on its edge.

Then he reached to his shirt, pulling it up.

\textit{Oh, Austre,}~she thought with sudden shock.~\textit{Oh, God, Lord of Colors! This is it! He’s finally coming for me!}

She couldn’t fight off the trembles. She’d convinced herself that she was safe, comfortable. She shouldn’t have to go through this. Not again!

\textit{I can’t do it! I can’t! I—}

The God King pulled something out from underneath his shirt, then let the garment drape back down. Siri sat, breath coming in gasps, slowly realizing that he was making no further moves toward her. She calmed herself, forcing the color back into her hair. The God King laid the object on the bed, and the firelight revealed it to be~.~.~. a book. Siri immediately thought of the histories Bluefingers had mentioned, but she quickly discarded the idea. This book, from the title on the spine, was a book of stories for children.

The God King let his fingers rest on it, then he delicately opened to the first page. The white parchment bent in the force of his BioChroma, shooting out prismatic colors. This didn’t distort the text, and Siri carefully inched forward, looking at the words.

She looked up at the God King. His face seemed less stiff than usual. He nodded down at the page, then pointed at the first word.

“You want me to read this?” Siri asked in a low whisper, mindful of the priests who might be listening.

The God King nodded.

“It says ‘Stories for Children,’~” Siri said, confused.

He turned the book around, looking at it himself. He rubbed his chin in thought.

\textit{What’s going on?}~she thought. It didn’t seem like he was going to bed her. Did he, instead, expect her to read a story to him? She couldn’t imagine him asking for something that childish. She looked up at him again. He turned the book around, pointing at the first word. He nodded toward it.

“Stories?” Siri asked.

He pointed at the word. She looked closely, trying to discern some hidden meaning or mysterious text. She sighed, looking up at him. “Why don’t you just tell me?”

He paused, cocking his head. Then he opened his mouth. By the waning light of the hearth’s fire, Siri saw something shocking.

The God King of Hallandren had no tongue.

There was a scar. She could just barely see it if she squinted closely. Something had happened to him, some terrible accident had ripped it free. Or~.~.~. had it been taken purposefully? Why would anyone remove the tongue of the king himself?

The answer came to her almost immediately.

\textit{BioChromatic Breath,}~she realized, thinking back to a half-remembered lesson from her childhood.~\textit{To Awaken objects, a person must give a Command. Words spoken in a crisp, clear voice. No slurring or mumbling allowed, or the Breath will not function.}

The God King looked away, suddenly, seeming ashamed. He picked up the book, holding it to his chest, and moved to stand.

“No, please,” Siri said, edging forward. She reached her hand forward and touched his arm.

The God King froze. She immediately pulled her hand back. “I didn’t mean to look so disgusted,” Siri said in her whispered voice. “That wasn’t because of~.~.~. your mouth. It was because I was realizing why it must have been done to you.”

The God King studied her, then slowly seated himself again. He held himself back far enough that they were not touching, and she did not reach for him again. However, he did carefully—almost reverently—put his book back down on the bed. He opened to the first page again, then looked at her, his eyes pleading.

“You can’t read, can you?” Siri asked.

He shook his head.

“That’s the secret,” she whispered. “The thing that scares Bluefingers so much. You’re not king, you’re a puppet! A~\textit{figurehead.}~You’re paraded around by your priests, given a BioChromatic aura so strong that it makes people fall to their knees in wonder. Yet they took your tongue so that you couldn’t ever use it, and they never taught you to read, lest you learn too much or manage to communicate with others.”

He sat and looked away.

“All so that they could control you.”~\textit{No wonder Bluefingers is so scared. If they would do that to their own god~.~.~. then the rest of us are nothing to them.}

It made sense, now, why they had been so adamant about her not talking to—or even kissing—the king. It made sense why they would dislike her so much. They were worried about someone spending time alone with the God King. Someone who might discover the truth.

“I’m sorry,” she whispered.

He shook his head, then met her eyes. There was a strength in them she wouldn’t have expected of a man who had been sheltered and isolated as he must have been. Finally, he looked down, pointing back at the words on the page. The first word. The first letter, actually.

“That is the letter ‘shash,’~” Siri said, smiling. “I can teach you them all, if you wish.”

The priests were right to be worried.

