% \section{Chapter Fifty-One}
\chapter{}

\textit{I’m glad you came back for me,}~Nightblood said.~\textit{It was very lonely in that closet.}

Vasher didn’t reply as he walked across the top of the wall surrounding the Court of Gods. It was late, dark, and quiet, though a few of the palaces still shone with light. One of those belonged to Lightsong the Bold.

\textit{I don’t like the darkness,}~Nightblood said.

“You mean darkness like now?” Vasher asked.

\textit{No. In the closet.}

“You can’t even see.”

\textit{A person knows when they’re in darkness,}~Nightblood said.~\textit{Even when they can’t see.}

Vasher didn’t know how to respond to that. He paused atop the wall, overlooking Lightsong’s palace. Red and gold. Bold colors indeed.

\textit{You shouldn’t ignore me,}~Nightblood said.~\textit{I don’t like it.}

Vasher knelt down, studying the palace. He’d never met the one called Lightsong, but he had heard rumors. The most scurrilous of the gods, the most condescending and mocking. And this was the person who held the fate of two kingdoms in his hands.

There was an easy way to influence that fate.

\textit{We’re going to kill him, aren’t we?}~Nightblood said, eagerness sharp in his voice.

Vasher just stared at the palace.

\textit{We should kill him,}~Nightblood continued.~\textit{Come on. We should do it. We}~really~\textit{should do it.}

“Why do you care?” Vasher whispered. “You don’t know him.”

\textit{He’s evil,}~Nightblood said.

Vasher snorted. “You don’t even know what that is.”

For once, Nightblood was silent.

That was the great crux of the problem, the issue that had dominated most of Vasher’s life. A thousand Breaths. That was what it took to Awaken an object of steel and give it sentience. Even Shashara hadn’t fully understood the process, though she had first devised it.

It took a person who had reached the Ninth Heightening to Awaken stone or steel. Even then, this process shouldn’t have worked. It should have created an Awakened object with no more of a mind than the tassels on his cloak.

Nightblood should not be alive. And yet he was. Shashara had always been the most talented of them, far more capable than Vasher himself, who had used tricks—like encasing bones in steel or stone—to make his creations. Shashara had been spurred on by the knowledge that she’d been shown up by Yesteel and the development of ichor-alcohol. She had studied, experimented, practiced. And she’d done it. She’d learned to forge the Breath of a thousand people into a piece of steel, Awaken it to sentience, and give it a Command. That single Command took on im mense power, providing a foundation for the personality of the object Awakened.

With Nightblood, she and Vasher had spent much time in thought, then finally chosen a simple, yet elegant, Command. “Destroy evil.” It had seemed like such a perfect, logical choice. There was only one problem, something neither of them had foreseen.

How was an object of steel—an object that was so removed from life that it would find the experience of living strange and alien—supposed to understand what “evil” was?

\textit{I’m figuring it out,}~Nightblood said.~\textit{I’ve had a lot of practice.}

The sword wasn’t really to blame. It was a terrible, destructive thing—but it had been created to destroy. It still didn’t understand life or what that life meant. It only knew its Command, and it tried so very hard to fulfill it.

\textit{That man down there,}~Nightblood said.~\textit{The god in the palace. He holds the power to start this war. You don’t want this war to start. That’s why he’s evil.}

“Why does that make him evil?”

\textit{Because he will do what you don’t want him to.}

“We don’t know that for certain,” Vasher said. “Plus, who is to say that my judgment is best?”

\textit{It is,}~Nightblood said.~\textit{Let’s go. Let’s kill him. You told me war is bad. He will start a war. He’s evil. Let’s kill him. Let’s kill him.}

The sword was getting excited; Vasher could feel it—feel the danger in its blade, the twisted power of Breaths that had been pulled from living hosts and shoved into something unnatural. He could picture them breathing out, black and corrupted, twisting in the wind. Drawing him toward Lightsong. Pushing him to kill.

“No,” Vasher said.

Nightblood sighed.~\textit{You locked me in a closet,}~he reminded.~\textit{You should apologize.}

“I’m not going to apologize by killing someone.”

\textit{Just throw me in there,}~Nightblood said.~\textit{If he’s evil, he’ll kill himself.}

This gave Vasher pause.~\textit{Colors,}~he thought. The sword seemed to be getting more subtle each year, though Vasher knew he was just imagining things, projecting. Awakened objects didn’t change or grow, they simply were what they were.

It was still a good idea.

“Maybe later,” Vasher said, turning away from the building.

\textit{You are afraid,}~Nightblood said.

“You don’t know what fear is,” Vasher replied.

\textit{I do. You don’t like killing Returned. You’re afraid of them.}

The sword was wrong, of course. But, on the outside, Vasher supposed that his hesitation did look like fear. It had been a long time since he’d dealt with the Returned. Too many memories. Too much pain.

He made his way to the God King’s palace. The structure was old, far older than the palaces that surrounded it. Once, this place had been a seaside outpost, overlooking the bay. No city. No colors. Just the stark, black tower. It amused Vasher that it had become the home of the God King of the Iridescent Tones.

Vasher slid Nightblood into a strap on his back, then jumped from the wall toward the palace. Awakened tassels around his legs gave him extra strength, letting him leap some twenty feet. He slammed against the side of the building, smooth onyx blocks rubbing his skin. He twitched his fingers, and the tassels on his sleeves grabbed on to the ledge above him, holding him tight.

He Breathed. The belt at his waist—touching his skin, as always—Awakened. Color drained from the kerchief tied to his leg beneath his trousers.

“Climb things, then grab things, then pull me up,” he Commanded. Three Commands in one Awakening, a difficult task for some. For him, however, it had become as simple as blinking.

The belt untied itself, revealing it to be far longer than it looked when wrapped around him. The twenty-five feet of rope snaked up the side of the building, curling inside of a window. Seconds later, the rope hauled Vasher up and into the air. Awakened objects could, if created well, have much more strength than regular muscles. He’d once seen a small group of ropes not much thicker than his own lift and toss boulders at an enemy fortification.

He released his tassel grips, then pulled Nightblood free as the rope deposited him inside the building. He knelt silently, eyes searching the darkness. The room was unoccupied. Carefully, he drew back his Breath, then wrapped the rope around his arm and held it in a loose coil. He stalked forward.

\textit{Who are we going to kill?}~Nightblood asked.

\textit{It’s not always about killing,}~Vasher said.

\textit{Vivenna. Is she in here?}

The sword was trying to interpret his thoughts again. It had trouble with things that weren’t fully formed in Vasher’s head. Most thoughts passed through a man’s mind were fleeting and momentary. Flashes of image, sound, or scent. Connections made, then lost, then recovered again. That sort of thing was difficult for Nightblood to interpret.

Vivenna. The source of a lot of his troubles. His work in the city had been easier when he’d been able to assume that she was working willingly with Denth. Then, at least, he’d been able to blame her.

\textit{Where is she? Is she here? She doesn’t like me, but I like her.}

Vasher hesitated in the dark hallway.~\textit{You do?}

\textit{Yes. She’s nice. And she’s pretty.}

Nice and pretty—words that Nightblood didn’t really understand. He had simply learned when to use them. Still, the sword did have opinions, and it rarely lied. It must like Vivenna, even if it couldn’t explain why.

\textit{She reminds me of a Returned,}~the sword said.

\textit{Ah,}~Vasher thought.~\textit{Of course. That makes sense.}~He moved on.

\textit{What?}~Nightblood said.

\textit{She’s descended from one,}~he thought.~\textit{You can tell by the hair. There’s a bit of Returned in her.}

Nightblood didn’t respond to that, but Vasher could feel it thinking.

He paused at an intersection. He was pretty sure he knew where the God King’s chambers would be. However, a lot of the interior seemed different now. The fortress had been stark, built with odd twists and turns to confuse an invading foe. Those remained—all the stonework was the same—but the open dining halls or garrison rooms had been split into many, smaller rooms, colorfully decorated in the mode of the Hallandren upper class.

Where would the God King’s wife be? If she was pregnant, she’d be under the care of servants. One of the larger complex of chambers, he assumed, on a higher level. He made his way to a stairwell. Fortunately, it seemed late enough that there were very few people awake.

\textit{The sister,}~Nightblood said.~\textit{That’s who you’re after. You’re rescuing Vivenna’s sister!}

Vasher nodded quietly in the darkness, feeling his way up the stairs, counting on his BioChroma to let him know if he approached anyone. Though most of his Breath was stored in his clothing, he had just enough to awaken the rope and to keep him aware.

\textit{You like Vivenna too!}~Nightblood said.

\textit{Nonsense,}~Vasher thought.

\textit{Then why?}

\textit{Her sister,}~he thought.~\textit{She’s a key to all of this, somehow. I realized it today. As soon as the queen arrived, the real move to start the war surged.}

Nightblood fell silent. That kind of logical leap was a bit too complex for it.~\textit{I see,}~he said, though Vasher smiled at the confusion he sensed in the voice.

\textit{At the very least,}~Vasher thought,~\textit{she’s a very handy hostage for the Hallandren. The God King’s priests—or whoever’s behind this—can threaten the girl’s life, should the war go poorly for them. She makes an excellent tool.}

\textit{One you intend to remove,}~Nightblood said.

Vasher nodded, reaching the top of the stairwell and slinking through one of the corridors. He walked until he sensed someone nearby—a maid servant approaching.

Vasher Awakened his rope, stood in the shadows of an alcove, and waited. As she passed, the rope shot from the shadows, wrapped around her waist, and yanked her into the darkness. Vasher had one of his tassel hands wrapped around her mouth before she could scream.

She squirmed, but the rope tied her tightly. He felt a little stab of guilt as he loomed over her, her terrified eyes tearing up. He reached for Nightblood and pulled the sword slightly out of its sheath. The girl immediately looked sick. A good sign.

“I need to know where the queen is,” Vasher said, forcing Nightblood up so that his hilt touched her cheek. “You’re going to tell me.”

He held her like that for a time, watching her squirm, feeling unhappy with himself. Finally, he relaxed the tassels, keeping the sword against her cheek. She began to vomit, and he turned her to the side.

“Tell me,” he whispered.

“Southern corner,” the girl whispered, trembling, spittle on her cheek. “This floor.”

Vasher nodded, then tied her up with the rope, gagged her, and took his Breath back. He pushed Nightblood back into the sheath and then rushed down the hallway.

\textit{You won’t kill a god who plans to march his armies to war?}~Nightblood asked.~\textit{But you’ll nearly choke a young woman to death?}

It was a complicated statement for the sword. However, it lacked the accusation that a human would have put into the words. To Nightblood it really was just a question.

\textit{I don’t understand my morality either,}~Vasher thought.~\textit{I’d suggest you avoid confusing yourself.}

He found the place easily. It was guarded by a large group of brutish men who seemed rather out of place in the fine palace hallways.

Vasher paused.~\textit{Something strange is going on here.}

\textit{What do you mean?}~Nightblood asked.

He hadn’t meant to address the sword, but that was the trouble with an object that could read minds. Any thoughts Vasher formed in his head, Nightblood thought were directed at it. After all, in the sword’s opinion,~\textit{everything}~really should have been directed toward it.

Guards at the door. Soldiers, not servants. So they had already taken her captive. Was she really even pregnant? Were the priests just securing their power?

That many men would be impossible to kill without making noise. The best he could hope for was to take them fast. Maybe they were far enough from anyone else that a brief fight wouldn’t be heard.

He sat for a few minutes, jaw clenched. Then, finally, he stepped closer and tossed Nightblood in amongst the men. He’d let them fight each other and then be ready to deal with any who weren’t taken into the sword’s influence.

Nightblood clanged to the stones. All of the men’s eyes turned toward it. And, at that moment, something grabbed Vasher by the shoulder and yanked him backward.

He cursed, spinning, throwing his hands up to wrestle with whatever had him. An Awakened rope. Men started to fight behind him. Vasher grunted, pulling out the knife in his boot, then slicing the Awakened rope. Someone tackled him as he got free, and he was thrown back against the wall.

He grabbed his attacker by the face with one of his arm tassels, then twisted the man back and threw him into the wall. Another figured charged him from behind, but Vasher’s Awakened cloak caught that one, tripping him.

“Grab things other than me,” Vasher said quickly, snatching the cloak of one of the fallen men and Awakening it. That cloak whipped about, taking down another man, whom Vasher then killed with a swipe of his dagger. He kicked another man, throwing him backward, opening a pathway.

Vasher lunged, making for Nightblood, but three more figures burst out the rooms around him, cutting him off. They were the same kind of brutish men that were now fighting over the sword. Men were all around. Dozens of them. Vasher kicked out, breaking a leg, but one man pulled Vasher’s cloak off with a lucky twist. Others piled on top of him. And then, another Awakened rope snapped out, tying his legs together.

Vasher reached for his vest. “Your Breath to—” he began, trying to draw in some Breath to use for an attack, but three men grabbed his hand and pulled it away. Within seconds, he was wrapped up in the Awakened rope. His cloak still fought against three men who were struggling to cut it up, but Vasher himself was pinned.

Someone emerged from the room to his left.

“Denth,” Vasher spat, struggling.

“My good friend,” Denth said, nodding for one of his lackeys—the one known as Tonk Fah—to move down the hallway toward the queen’s room. Denth knelt beside Vasher. “Very good to see you.”

Vasher spat again.

“Still as eloquent as ever, I see,” Denth said with a sigh. “You know the best thing about you, Vasher? You’re solid. Predictable. I guess I am too, in a way. Hard to live as long as we have without falling into patterns, eh?”

Vasher didn’t reply, though he did try to yell as some men gagged him. He noticed with satisfaction that he’d taken down a good dozen opponents before they’d managed to stop him.

Denth eyed the fallen soldiers. “Mercenaries,” he said. “No risk is too great, assuming the pay is right.” He said it with a twinkle in his eye. Then he leaned down, his joviality gone as he met Vasher’s eyes. “And you were always to be~\textit{my}~payment, Vasher. I owe you. For Shashara, even still. We’ve been waiting, hidden in the palace here for a good two weeks, knowing that eventually the good Princess Vivenna would send you to save her sister.”

Tonk Fah returned with a bundle held in a blanket. Nightblood.

Denth eyed it. “Throw that out somewhere far away,” he said, grimacing.

“I don’t know, Denth,” Tonk Fah said. “I kind of think we should keep it. It could be very useful.~.~.~.” The beginnings of the lust began to show in his eyes, the desire to draw Nightblood, to use the sword. To destroy evil. Or, really, just to destroy.

Denth stood and snatched the bundle away. Then he smacked Tonk Fah on the back of the head.

“Ow!” Tonk Fah said.

Denth rolled his eyes. “Stop whining; I just saved your life. Go check on the queen and then clean up that mess. I’ll take care of the sword myself.”

“You always get so nasty when Vasher’s around,” Tonk Fah grumbled, waddling away. Denth wrapped up Nightblood securely; Vasher watched, hoping to see the lust appear in Denth’s eyes. Unfortunately, Denth was far too strong-willed to be taken by the sword. He had nearly as much history with it as Vasher did.

“Take away all his Awakened clothing,” Denth said to his men, walking away. “Then hang him up in that room over there. He and I are going to have a long talk about what he did to my sister.”

