% \section{Chapter Fifty-Four}
\chapter{}

What’s the word on the street, Tuft?” Vivenna asked, sidling up to a beggar.

He snorted, holding out his cup to those few who passed in the early light. Tuft was always one of the first to arrive in the mornings. “Why do I care?” he said.

“Come on,” Vivenna said. “You kicked me out of this spot on three different occasions. I figure you owe me something.”

“I don’t owe nobody nothing,” he said, squinting at the passers by with his one eye. The other eye was simply an empty hole. He didn’t wear a patch. “Particularly don’t owe you nothing,” he said. “You were a plant all the time. Not a real beggar.”

“I~.~.~.” Vivenna paused. “I wasn’t a plant, Tuft. I just thought I should know what it was like.”

“Huh?”

“Living among you,” she said. “I figured your life couldn’t be easy. But I couldn’t know—not really~\textit{know}—until I tried it for myself. So I came to the streets. Determined to live here for a time.”

“Foolish thing to do.”

“No,” she said. “The fools are those who pass, without even thinking about what it must be like to live like you. Maybe if they knew, they’d give you something.” She reached into her pocket, pulling out one of the bright handkerchiefs. She placed one in the cup. “I don’t have any coins, but I know you can sell that.”

He grunted, eyeing it. “What do you mean by word on the street?”

“Disturbances,” Vivenna said. “Ones that are out of the ordinary. Perhaps involving Awakeners.”

“Go to the Third Dock slums,” Tuft said. “Look around the buildings near the wharf. Maybe you’ll find what you’re looking for there.”

\orn

Light peeked through the window.

\textit{Morning already?}~Vasher thought, head down, still hanging by his wrists.

He knew what to expect from torture. He was not new to it. He knew how to scream, how to give the torturer what he wanted. He knew how to not expend his strength in resisting too much.

He also knew that none of that was likely to do any good. How would he be after a week of torture? Blood dripped down his chest, staining his undershorts. A dozen small pains nagged at his skin, cuts that had been drenched in lemon juice.

Denth stood with his back facing Vasher, bloodied knives on the ground around him.

Vasher looked up, forcing a smile. “Not as much fun as you thought it would be, is it, Denth?”

Denth didn’t turn.

\textit{There’s still a good man in there,}~Vasher thought.~\textit{Even after all these years.}

\textit{He’s just been beaten down. Bloodied. Cut up worse than I have been.}

“Torturing me won’t bring her back,” Vasher said.

Denth turned, eyes dark. “No. It won’t.” He picked up another knife.

\orn

The priests pushed Siri through the passageways of the palace. They occasionally passed corpses in the dark black hallways, and she could still hear fighting in places.

\textit{What is going on?}~Someone was attacking the palace. But who? For a moment, she hoped it was her people—her father’s soldiers, coming to save her. She discarded that immediately. The men opposing the priests were using Lifeless soldiers; that ruled out Idris.

It was someone else. A third force. And they wanted to free her from the grip of the priests. Hopefully, her calls for help would not go unheeded. Treledees and his men led her quickly through the palace, passing through the colorful inner rooms in their rush to get to wherever they were going.

The white cuffs of Siri’s dress suddenly began to bend with color. She looked up with hope as they entered a last room. The God King stood inside the room, surrounded by a group of priests and soldiers.

“Susebron!” she said, straining against her captives.

He took a step toward her, but a guard held his arm, pulling him back.~\textit{They’re touching him,}~Siri thought.~\textit{All semblance of respect is gone. No need to pretend now.}

The God King looked down at his arm, frowning. He tried to tug it free, but another soldier stepped up to help hold him. Susebron glanced at this man, then at Siri, confused.

“I don’t understand either,” she said.

Treledees entered the room. “Bless the Colors,” he said. “You’ve arrived. Quickly, we must go. This place is not safe.”

“Treledees,” Siri said, turning to glare at him. “What is going on?”

He ignored her.

“I am your~\textit{queen,}” Siri said. “You will answer my question!”

He actually stopped, surprising her. He turned with an annoyed look. “A group of Lifeless has attacked the palace, Vessel. They are trying to get to the God King.”

“I figured out that much, priest,” Siri snapped. “Who are they?”

“We don’t know,” Treledees said, turning from her. As he did, a distant scream came from outside the room. It was followed by the sound of fighting.

Treledees glanced toward the sounds. “We have to move,” he said to one of the other priests. There were, perhaps, a dozen of them in the room, as well as a half-dozen soldiers. “The palace has too many doorways and passages. It would be too easy to surround us.”

“The back exit?” the other priest said.

“If we can get to it,” Treledees responded. “Where is that squadron of reinforcements I demanded?”

“They’re not coming, Your Grace,” a new voice said. Siri turned to see Bluefingers, looking haggard, enter through the far door with a couple of wounded soldiers. “The enemy has taken the east wing and is pushing this way.”

Treledees cursed.

“We have to get His Majesty to safety!” Bluefingers said.

“I’m well aware of that,” Treledees snapped.

“If the east wing has fallen,” the other priest said, “we won’t be able to get out that way.”

Siri watched, helpless, trying to get Bluefingers’s attention. He met her eyes, then nodded covertly, smiling. “Your Grace,” Bluefingers said. “We can escape through the tunnels.”

The sounds of fighting were growing closer. It seemed to Siri that their room was virtually surrounded by combat.

“Perhaps,” Treledees said as one of his priests rushed to the door to peek out. The soldiers who had come with Bluefingers were resting by the wall, bleeding. One of them seemed to have stopped breathing.

“We should go,” Bluefingers said urgently.

Treledees was quiet. Then he walked over to one of the fallen soldiers and picked up the man’s sword. “Very well,” he said. “Gendren, take half of the soldiers and go with Bluefingers. Take His Majesty to safety.” He looked at Bluefingers. “Seek the docks, if you can.”

“Yes, Your Grace,” Bluefingers said, looking relieved. The priests released the God King, and he rushed to Siri, taking her in his arms. She held him, tense, trying to sort through her emotions.

Bluefingers. Going with him made sense—the look in his eyes indicated that he had a plan to save her and the God King, get them away from the priests. And yet~.~.~. something felt wrong to her.

One of the priests gathered three of the soldiers and then moved to the far side of the room, peeking out. They waved to Siri and the God King. The other priests joined Treledees, taking weapons from the dead guards, their expressions grim.

Bluefingers pulled on Siri’s arm. “Come, my queen,” he whispered. “I made you a promise before. Let’s get you out of this mess.”

“What about the priests?” she asked.

Treledees glanced at her. “Foolish girl. Go! The attackers are moving in this direction. We will let them see us, then we will lead them in another direction. They will assume we know where the God King is.” The priests with him did not look hopeful. If—when—they were caught, they would be slaughtered.

“Come on!” Bluefingers hissed.

Susebron looked at her, frightened. She slowly let Bluefingers tug her and the God King to the side, to where the solitary priest and three soldiers had been joined by a group of servants in brown. Something whispered in her mind. Something~.~.~. Lightsong had told her.

\textit{Don’t make too many waves until you’re ready to strike,}~he had said.~\textit{Sudden and surprising, that’s how you want to do things. You don’t want to appear nonthreatening—people are always suspicious of the innocent. The trick is to appear average.}

\textit{Average.}

It was good advice. Advice that, likely, others knew. And understood. She glanced at Bluefingers, walking beside her, urging her forward. Nervous, as always.

\textit{The fighting,}~she thought.~\textit{Several groups have been contending back and forth, seizing control of my room. One force belongs to the priests. The second force—the one with the Lifeless—belongs to someone else. This mysterious third party.}

Someone in T’Telir had been pushing the kingdom toward war. But who would have anything at all to gain from such a disaster? Hallandren, which would expend huge resources to quell rebels, fighting a battle that they would win—but likely at great cost? It didn’t make sense.

Who would gain the most if Hallandren and Idris went to war?

“Wait!” Siri said, stopping. Things were suddenly falling into place.

“Vessel?” Bluefingers asked. Susebron laid a hand on her shoulder, looking at her with confusion.~\textit{Why would the priests sacrifice themselves if they were planning to kill Susebron? Why would they simply let us go, allow us to flee, if the God King’s safety were not their prime concern?}

She looked into Bluefingers’s eyes, and saw him grow more nervous. His face paled, and she knew. “How does it feel, Bluefingers?” she asked. “You’re from Pahn Kahl, yet everyone always just assumes that your people are Hallandren. The Pahn Kahl people were here first, in this land, but it was taken from you. Now you’re just another province, part of the kingdom of your conquerors.

“You want to be free, but your people have no military of their own. And so here you are. Unable to fight. Unable to free yourselves. Considered second-class. And yet, if your oppressors were to get into a war, it might give you an opening. A chance to break away~.~.~.”

He met her eyes, then took off in a dash, fleeing from the room.

“What in the name of the colors?” Treledees said.

Siri ignored him, looking up into the God King’s face. “You were right all along,” she said. “We~\textit{should}~have trusted your priests.”

“Vessel?” Treledees said, stalking over.

“We can’t go that way,” Siri said. “Bluefingers was leading us into a trap.”

The high priest opened his mouth to respond, but she met his eyes sternly and turned her hair the deep red of anger. Bluefingers had betrayed her. The~\textit{one}~person she’d thought she could trust to help them.

“We go for the front gates, then,” Treledees said, looking over their motley collection of priests and wounded soldiers. “And try to fight our way out.”

\orn

It was easy for Vivenna to find the location the beggar had mentioned. The building—a slum tenement—was surrounded by gawkers, despite the morning hour. People whispered, talking about spirits and death and ghosts from the sea. Vivenna stopped at the perimeter, trying to see what had drawn their attention.

The docks were to her left, the sea brine pungent. The dock slums, where many of the dockhands lived and drank, were a small section of buildings clustered between warehouses and shipyards. Why would Vasher have come here? He had been planning to visit the Court of Gods. From what she could gather, there had been a murder in the building where the crowd had formed. People whispered of ghosts and of Kalad’s Phantoms, but Vivenna simply shook her head. This wasn’t what she was looking for. She’d have to—

\textit{Vivenna?}~The voice was faint, but she could just barely make it out. And recognize it.

“Nightblood?” she whispered.

\textit{Vivenna. Come get me.}

She shivered. She wanted to turn and run—even thinking about the sword was nauseating. Yet Vasher had taken Nightblood with him. She was in the right place after all.

The gawkers spoke of a murder. Was Vasher the person who had been killed?

Suddenly concerned, she shoved her way through the crowd, ignoring yells that she should stay back. She climbed up the stairs, passing door after door. In her haste, she almost missed the one with black smoke creeping out under it.

She froze. Then, taking a deep breath, she pushed the door open and stepped inside.

The room was poorly kept, the floor littered with trash, the furniture rickety and worn. Four dead bodies lay on the floor. Nightblood was stuck in the chest of the fourth, an old man with a leathery face who lay on his side, dead eyes wide.

\textit{Vivenna!}~Nightblood said happily.~\textit{You found me. I’m so excited. I tried to get them to take me to the Court of Gods, but it didn’t turn out well. He did draw me a little bit. That’s good, right?}

She fell to her knees, feeling sick.

\textit{Vivenna?}~Nightblood asked.~\textit{I did well, right? VaraTreledees threw me into the ocean, but I got back out. I’m quite satisfied. You should tell me that I did well.}

She didn’t respond.

\textit{Oh,}~Nightblood said.~\textit{And Vasher is hurt, I think. We should go find him.}

She looked up. “Where?” she asked, uncertain if the sword would even be able to hear her.

\textit{The God King’s palace,}~Nightblood said.~\textit{He went to get your sister out. I think he likes you, even though he says he doesn’t. He says you’re annoying.}

Vivenna blinked. “Siri? You went after Siri?”

\textit{Yes, but VaraTreledees stopped us.}

“Who is that?” She asked, frowning.

\textit{You call him Denth. He’s Shashara’s brother. I wonder if she’s here too. I’m not sure why he threw me in the water. I thought he liked me.}

“Vasher~.~.~.” she said, climbing back to her feet, feeling woozy from the sword’s influence. Vasher had been taken by Denth. She shivered, remembering the anger in Denth’s voice when he’d spoken of Vasher. She gritted her teeth and grabbed a dirty blanket off the crude bed and wrapped it around Nightblood so that she wouldn’t have to touch him.

\textit{Ah,}~Nightblood said.~\textit{You don’t really need to do that. I had the old man clean me off after he got me out of the water.}

She ignored the sword, managing to lift the bundle with only slight nausea. Then she left, heading for the Court of Gods.

\orn

Lightsong sat, staring at the stones in front of him. A trickle of Blushweaver’s blood was making its way down a crack in the rock.

“Your Grace?” Llarimar asked quietly. He stood up against the bars between their cages.

Lightsong didn’t respond.

“Your Grace, I’m sorry. I shouldn’t have yelled at you.”

“What good is godhood?” Lightsong whispered.

Silence. Lanterns flickered on either side of the small chamber. Nobody had cleaned up Blushweaver’s body, though they had left a couple of priests and Lifeless behind to watch Lightsong. They still needed him, should it turn out that he’d lied about the Command phrases.

He hadn’t.

“What?” Llarimar finally asked.

“What good is it?” Lightsong said. “We aren’t gods. Gods don’t die like that. A little cut. Not even as wide as my palm.”

“I’m sorry,” Llarimar said. “She was a good woman, even among gods.”

“She wasn’t a god,” Lightsong said. “None of us are. Those dreams are lies, if they led me to this. I’ve always known the truth, but nobody pays attention to what I say. Shouldn’t they listen to the one they worship? Particularly if he’s telling you~\textit{not}~to worship him?”

“I~.~.~.” Llarimar seemed at a loss for words.

“They should have seen,” Lightsong hissed. “They should have seen the truth about me! An idiot. Not a god, but a scribe. A silly little scribe who was allowed to play god for a few years! A coward.”

“You’re no coward,” Llarimar said.

“I couldn’t save her,” Lightsong said. “I couldn’t do anything. I just sat there and screamed. Maybe if I’d been more brave, I’d have joined with her and taken control of the armies. But I hesitated. And now she’s dead.”

Silence.

“You were a scribe,” Llarimar said quietly to the damp air. “And you were one of the best men I’d ever known. You were my brother.”

Lightsong looked up.

Llarimar stared out through the bars, staring at one of the flickering lanterns hanging from the stark stone wall. “I was a priest, even then. I worked in the palace of Kindwinds the Honest. I saw how he lied to play political games. The longer I stayed in that palace, the more my faith waned.”

He fell silent for a moment, then he looked up. “And then you died. Died rescuing my daughter. That’s the girl you see in your visions, Lightsong. The description is perfect. She was your favorite niece. Still would be, I assume. If you hadn’t~.~.~.” He shook his head. “When we found you dead, I lost hope. I was going to resign my position. I knelt above your body, weeping. And then, the Colors started to glow. You lifted your head, body changing, getting larger, muscles growing stronger.

“I knew it at that moment. I knew that if a man like~\textit{you}~were chosen to Return—a man who had died to save another—then the Iridescent Tones were real. The visions were real. And the gods were real. You gave me back my faith, Stennimar.”

He met Lightsong’s eyes. “You~\textit{are}~a god. To me, at least. It doesn’t matter how easily you can be killed, how much Breath you have, or how you look. It has to do with who you are and what you mean.”

