\chapter{}

Siri sat, stunned, in a rattling carriage, her homeland growing more and more distant with each bump and shake.

Two days had passed, and she still didn’t understand. This was supposed to be Vivenna’s task. Everybody understood that. Idris had thrown a celebration on the day of Vivenna’s birth. The king had started her classes from the day she could walk, training her in the ways of court life and politics. Fafen, the second daughter, had also taken the lessons in case Vivenna died before the day of the wedding. But not Siri. She’d been redundant. Unimportant.

No more.

She glanced out the window. Her father had sent the kingdom’s nicest carriage—along with an honor guard of twenty soldiers—to bear her southward. That, combined with a steward and several serving boys, made for a procession as grand as Siri had ever seen. It bordered on ostentation, which might have thrilled her, had it not been bearing her away from Idris.

\textit{This isn’t the way it’s supposed to be,}~she thought.~\textit{This isn’t the way}~any~\textit{of it is supposed to happen!}

And yet it had.

Nothing made sense. The carriage bumped, but she just sat, numb.~\textit{At the very least,}~she thought,~\textit{they could have let me ride horse back, rather than forcing me to sit in this carriage.}~But that, unfortunately, wouldn’t have been an appropriate way to enter Hallandren.

Hallandren.

She felt her hair bleach white with fear. She was being sent to~\textit{Hallandren,}~a kingdom her people cursed with every second breath. She wouldn’t see her father again for a long while, if ever. She wouldn’t speak with Vivenna, or listen to the tutors, or be chided by Mab, or ride the royal horses, or go looking for flowers in the wilderness, or work in the kitchens. She’d~.~.~.

Marry the God King. The terror of Hallandren, the monster that had never drawn a living breath. In Hallandren, his power was absolute. He could order an execution on a whim.

\textit{I’ll be safe, though, won’t I?}~she thought.~\textit{I’ll be his wife. Wife. I’m getting married. Oh Austre, God of Colors~.~.~.}~she thought, feeling sick. She curled up with her legs against her chest—her hair growing so white that it seemed to shine—and lay down on the seat of the carriage, not sure if the shaking she felt was her own trembling or the carriage continuing its inexorable path southward.

\orn

“I think that you should reconsider your decision, Father,” Vivenna said calmly, sitting decorously—as she’d been trained—with hands in her lap.

“I’ve considered and reconsidered, Vivenna,” King Dedelin said, waving his hand. “My mind is made up.”

“Siri is not suited to this task.”

“She’ll do fine,” her father said, looking through some papers on his desk. “All she really needs to do is have a baby. I’m certain she’s ‘suited’ to that task.”

\textit{What then of my training?}~Vivenna thought.~\textit{Twenty-two years of preparation? What was that, if the only point in being sent was to provide a convenient womb?}

She kept her hair black, her voice solemn, her face calm. “Siri must be distraught,” she said. “I don’t think she’s emotionally capable of dealing with this.”

Her father looked up, his hair fading a bit red—the black bleeding away like paint running off a canvas. It showed his annoyance.

\textit{He’s more upset by her departure than he’s willing to admit.}

“This is for the best for our people, Vivenna,” he said, working—with obvious effort—to turn his hair black again. “If war comes, Idris will need you here.”

“If war comes, what of Siri?”

Her father fell silent. “Perhaps it won’t come,” he finally said.

\textit{Austre~.~.~.}~Vivenna thought with shock.~\textit{He doesn’t believe that. He thinks he’s sent her to her death.}

“I know what you are thinking,” her father said, drawing her attention back to his eyes. So solemn. “How could I choose one over the other? How could I send Siri to die and leave you here to live? I didn’t do it based on personal preference, no matter what people may think. I did what will be best for Idris when this war comes.”

\textit{When}~this war comes. Vivenna looked up, meeting his eyes. “I was going to stop the war, Father. I was to be the God King’s bride! I was going to speak with him, persuade him. I’ve been trained with the political knowledge, the understanding of customs, the—”

“Stop the war?” her father asked, cutting in. Only then did Vivenna realize how brash she must have sounded. She looked away.

“Vivenna, child,” her father said. “There is no stopping this war. Only the promise of a daughter of the royal line kept them away this long, and sending Siri may buy us time. And~.~.~. perhaps I’ve sent her to safety, even when war flares. Perhaps they will value her bloodline to the point that they leave her alive—a backup should the heir she bears pass away.” He grew distant. “Yes,” he continued, “perhaps it is not Siri we should be fearing for, but~.~.~.”

\textit{But ourselves,}~Vivenna finished in her mind. She was not privy to all of her father’s war planning, but she knew enough. War would not favor Idris. In a conflict with Hallandren, there was little chance they would win. It would be devastating for their people and their way of life.

“Father, I—”

“Please, Vivenna,” he said quietly. “I cannot speak of this further. Go now. We will converse later.”

Later. After Siri had traveled even farther away, after it would be much more difficult to bring her back. Yet Vivenna rose. She was obedient; it was the way she had been trained. That was one of the things that had always separated her from her sister.

She left her father’s study, closing the door behind her, then walked through the wooden palace hallways, pretending that she didn’t see the stares or hear the whispers. She made her way to her room—which was small and unadorned—and sat down on her bed, hands in her lap.

She didn’t agree at all with her father’s assessment. She~\textit{could}~have done something. She was to have been the God King’s bride. That would have given her influence in the court. Everyone knew that the God King himself was distant when it came to the politics of his nation, but surely his wife could have played a role in defending the interests of her people.

And her father had thrown that away?

\textit{He really must believe that there is nothing that can be done to stop the invasion.}~That turned sending Siri into simply another political maneuver to buy time. Just as Idris had been doing for decades. Either way, if the sacrifice of a royal daughter to the Hallandren was that important, then it still should have been Vivenna’s place to go. It had always been~\textit{her}~duty to prepare for marriage to the God King. Not Siri’s, not Fafen’s. Vivenna’s.

In being saved, she didn’t feel grateful. Nor did she feel that she would better serve Idris by staying in Bevalis. If her father died, Yarda would be far better suited to rule during wartime than Vivenna. Besides, Ridger—Vivenna’s younger brother—had been groomed as heir for years.

She had been preserved for no reason. It seemed a punishment, in some ways. She’d listened, prepared, learned, and practiced. Everyone said that she was perfect. Why, then, wasn’t she good enough to serve as intended?

She had no good answer for herself. She could only sit and fret, hands in her lap, and face the awful truth. Her purpose in life had been stolen and given to another. She was redundant now. Useless.

Unimportant.

\orn

“What was he~\textit{thinking}!” Siri snapped, hanging half out the window of her carriage as it bounced along the earthen road. A young soldier marched beside the vehicle, looking uncomfortable in the afternoon light.

“I mean really,” Siri said. “Sending~\textit{me}~to marry the Hallandren king. That’s silly, isn’t it? Surely you’ve heard about the kinds of things I do. Wandering off when nobody’s looking. Ignoring my lessons. I throw angry fits, for Color’s sake!!”

The guard glanced at her out of the corner of his eye, but otherwise gave no reaction. Siri didn’t really care. She wasn’t yelling at him so much as just~\textit{yelling.}~She hung precariously from the window, feeling the wind play with her hair—long, red, straight—and stoking her anger. Fury kept her from weeping.

The green spring hills of the Idris highlands had slowly faded away as the days had passed. In fact, they were probably in Hallandren already—the border between the two kingdoms was vague, which wasn’t surprising, considering that they’d been one nation up until the Manywar.

She eyed the poor guard—whose only way of dealing with a raving princess was ignoring her. Then she finally slumped back into the carriage. She shouldn’t have treated him so, but, well, she’d just been sold off like some hunk of mutton—doomed by a document that had been written years before she’d even been born. If anyone had a right to a tantrum, it was Siri.

\textit{Maybe that’s the reason for all of this,}~she thought, crossing her arms on the windowsill.\textit{Maybe Father was tired of my tantrums, and just wanted to get rid of me.}

That seemed a little far-fetched. There were easier ways to deal with Siri—ways that didn’t include sending her to represent Idris in a foreign court. Why, then? Did he really think she’d do a good job? That gave her pause. Then she considered how ridiculous it was. Her father wouldn’t have assumed that she’d do a better job than Vivenna. Nobody did~\textit{anything}~better than Vivenna.

Siri sighed, feeling her hair turn a pensive brown. At least the landscape was interesting, and in order to keep herself from feeling any more frustrated, she let it distract her for the moment. Hallandren was in the lowlands, a place of tropical forests and strange, colorful animals. Siri had heard the descriptions from ramblemen, and even confirmed their accounts in the occasional book she’d been forced to read. She’d thought she knew what to expect. Yet as the hills gave way to deep grasslands and then the trees finally began to crowd the road, Siri began to realize that there was something no tome or tale could adequately describe.

Colors.

In the highlands, flower patches were rare and unconnected, as if they understood how poorly they fit with Idrian philosophy. Here, they appeared to be everywhere. Tiny flowers grew in great blanketing swaths on the ground. Large, drooping pink blossoms hung from trees, like bundles of grapes, flowers growing practically on top of one another in a large cluster. Even the weeds had flowers. Siri would have picked some of them, if not for the way that the soldiers regarded them with hostility.

\textit{If I feel this anxious,}~she realized,~\textit{those guards must feel more so.}~She wasn’t the only one who had been sent away from family and friends. When would these men be allowed to return? Suddenly, she felt even more guilty for subjecting the young soldier to her outburst.

\textit{I’ll send them back when I arrive,}~she thought. Then she immediately felt her hair grow white. Sending the men back would leave her alone in a city filled with Lifeless, Awakeners, and pagans.

Yet what good would twenty soldiers do her? Better that someone, at least, be allowed to return home.

\orn

“One would think that you would be happy,” Fafen said. “After all, you no longer have to marry a tyrant.”

Vivenna plopped a bruise-colored berry into her basket, then moved on to a different bush. Fafen worked on one nearby. She wore the white robes of a monk, her hair completely shorn. Fafen was the middle sister in almost every way—midway between Siri and Vivenna in height, less proper than Vivenna, yet hardly as careless as Siri. Fafen was a bit curvier than either of them, which had caught the eyes of several young men in the village. However, the fact that they would have to become monks themselves if they wanted to marry her kept them in check. If Fafen noticed how popular she was, she’d never shown it. She’d made the decision to become a monk before her tenth birthday, and her father had wholeheartedly approved. Every noble or rich family was traditionally obligated to provide one person to the monasteries. It was against the Five Visions to be selfish, even with one’s own blood.

The two sisters gathered berries that Fafen would later distribute to those in need. The monk’s fingers were dyed slightly purple by the work. Vivenna wore gloves. That much color on her hands would be unseemly.

“Yes,” Fafen said, “I do think you’re taking this all wrong. Why, you act as if you~\textit{want}~to go down and be married to that Lifeless monster.”

“He’s not Lifeless,” Vivenna said. “Susebron is Returned, and there is a large difference.”

“Yes, but he’s a false god. Besides, everyone knows what a terrible creature he is.”

“But it was my~\textit{place}~to go and marry him. That is who I am, Fafen. Without it, I am nothing.”

“Nonsense,” Fafen said. “You’ll inherit now, instead of Ridger.”

\textit{Thereby unsettling the order of things even further,}~Vivenna thought.~\textit{What right do I have to take his place from him?}

She allowed this aspect of the conversation to lapse, however. She’d been arguing the point for several minutes now, and it wouldn’t be proper to continue. Proper. Rarely before had Vivenna felt so frustrated at having to be proper. Her emotions were growing rather~.~.~. inconvenient.

“What of Siri?” she found herself saying. “You’re happy that this happened to her?”

Fafen looked up, then frowned a little to herself. She had a tendency to avoid thinking things through unless she was confronted with them directly. Vivenna felt a little ashamed for making such a blunt comment, but with Fafen, there often wasn’t any other way.

“You do have a point,” Fafen said. “I don’t see why~\textit{anyone}~had to be sent.”

“The treaty,” Vivenna said. “It protects our people.”

“Austre protects our people,” Fafen said, moving on to another bush.

\textit{Will he protect Siri?}~Vivenna thought. Poor, innocent, capricious Siri. She’d never learned to control herself; she’d be eaten alive in the Hallandren Court of Gods. Siri wouldn’t understand the politics, the backstabbing, the false faces and lies. She would also be forced to bear the next God King of Hallandren. Performing that duty was not something Vivenna had looked forward to. It would have been a sacrifice, yet it would have been~\textit{her}~sacrifice, given willingly for the safety of her people.

Such thoughts continued to pester Vivenna as she and Fafen finished with the berry picking, then moved down the hillside back toward the village. Fafen, like all monks, dedicated all of her work to the good of the people. She watched flocks, harvested food, and cleaned houses for those who could not do it themselves.

Without a duty of her own, Vivenna had little purpose. And yet, as she considered it, there\textit{was}~someone who still needed her. Someone who had left a week before, teary-eyed and frightened, looking to her big sister with desperation.

Vivenna wasn’t needed in Idris, whatever her father said. She was useless here. But she~\textit{did}know the people, cultures, and society of Hallandren. And—as she followed Fafen onto the village road—an idea began to form in Vivenna’s head.

One that was not, by any stretch of the imagination, proper.

