\chapter{Rights Explanation}

I am releasing~\textit{Warbreaker}~under a Creative Commons Attribution-Noncommercial-No Derivative Works 3.0 United States License. For an official explanation of this, visit the \href{https://creativecommons.org/licenses/by-nc-nd/3.0/us/}{Creative Commons website}.

In a more specific explanation, this means that:

\begin{enumerate}
    \item You are free to share this book with anyone you like, provided you don’t change the document at all or profit from the distribution.

    \item You may print off copies of the book for personal use, but—again—may not profit from doing so.

    \item You may not change the text of the work in any way, or imply that you wrote the book, or anything of that nature.

    \item There is a no derivative works clause on this, since I don’t want people adding chapters to the end or altering the work. However, I provide an exemption for fan art, provided you do not attach it to the document and clearly explain that the art is not mine or related officially to the project.

    \item I also provide an exemption for fanfics, provided that—again—you do not attach them to this work or imply they are my work. In addition, by writing a fanfic that uses these characters, this magic, or that is related to this work in any way, you waive all rights to that work. (In other words, you can’t write a~\textit{Warbreaker}~fanfic, then sue me for compensation if I happen to write something similar in a sequel. I’m not going to steal your ideas, but I’ve got to write something like this just in case. It’s every author’s nightmare to get sued for writing in their own worlds, and is one of the reasons so many of them are so afraid of fanfiction.)

    \item The above also holds for any feedback or suggestions you give me regarding this work on my forums. By offering feedback, you waive all rights to those suggestions and waive all rights to compensation for your help. I love to get feedback, and it’s one of the reasons why I decided to post these chapters online as I wrote them. However, don’t sue me if I actually decide to take some of your suggestions!

\end{enumerate}

\hfill Brandon Sanderson June 2009

